### 2024-08-14 index.qmd
docs(quarto): add basic/empty quarto site

---
authors:
  - name: Amy Heather
    url: https://github.com/amyheather
    orcid: 0000-0002-6596-3479
    affiliation: University of Exeter
---

Summary of the six computational reproducibility assessments conducted as part of STARS Work Package 1. These assessed six discrete-event simulation papers with models in Python and R.

### 2024-08-14 index.qmd
chore(quarto): minor python to ensure site working
docs(quarto): reworked into a book with empty pages to complete

@@
 ---
+title: Overview
 authors:
@@
 
-Summary of the six computational reproducibility assessments conducted as part of STARS Work Package 1. These assessed six discrete-event simulation papers with models in Python and R.
+TODO: Overview page

### 2024-08-14 pages/paper_evaluation.qmd
docs(quarto): reworked into a book with empty pages to complete

---
title: "Evaluation of the article"
---

TODO: Add evaluation of article against STRESS-DES and against the guidelines derived from ISPOR-SDM. Include record of timings to complete this part of the evaluation for each.

### 2024-08-14 pages/protocol.qmd
docs(quarto): reworked into a book with empty pages to complete

---
title: "Protocol"
---

TODO: This page summarises the method from the protocol.

### 2024-08-14 pages/reflections.qmd
docs(quarto): reworked into a book with empty pages to complete

---
title: "Reflections from reproductions"
---

TODO: Table with reflections from each study

### 2024-08-14 pages/repo_evaluation.qmd
docs(quarto): reworked into a book with empty pages to complete

---
title: "Evaluation of the repository"
---

TODO: Add table with results from evaluation of repository against STARS framework and against journal badges. Include record of timings to complete this part of the evaluation for each.

### 2024-08-14 pages/reproduction.qmd
docs(quarto): reworked into a book with empty pages to complete

---
title: "Reproduction"
---

TODO: Describe reproduction tasks, success, and timings.

* Information about each study and what was trying to reproduce
* Description of success for each
* Combined figure with time to reproduce each item in scope

### 2024-08-14 pages/reproduction.qmd
feat(reproduction): completed the reproduction page

@@
 title: "Reproduction"
+echo: False
+bibliography: ../references.bib
 ---
 
-TODO: Describe reproduction tasks, success, and timings.
+## Studies
 
-* Information about each study and what was trying to reproduce
-* Description of success for each
-* Combined figure with time to reproduce each item in scope
+<!-- TODO: Modify descriptions so each contains consistent information about each study - e.g.
+making sure each includes a mention of what was used to make model (e.g.
+R simmer, base R, python simpy) -->
+
+**Shoaib and Ramamohan 2022:** This is a discrete-event simulation modelling primary health centres (PHCs) in India.
+There are four patient types: outpatients, inpatients, childbirth cases and antenatal care patients.
+Four model configurations are developed based on observed PHC practices or government-mandated operational guidelines.
+The paper explores different operational patterns for scenarios where very high utilisation was observed, to explore what might help reduce utilisation of these resources.
+
+**Huang et al.
+2019:** This is a discrete-event simulation model of an endovascular clot retrieval (ECR) service.
+ECR is a treatment for acute ischaemic stroke.
+The model includes the stroke pathway, as well as three other pathways that share resources with the stroke pathway: an elective non-stroke interventional neuroradiology pathway, an emergency interventional radiology pathway, and an elective interventional radiology pathway.
+The model is created using R Simmer.
+The paper explores waiting times and resource utilisation - particularly focussing on the biplane angiographic suite (angioINR).
+A few scenarios are tried to help examine why the wait times are so high for the angioINR.
+
+**Lim et al.
+2020:** This is a discrete-event simulation modelling the transmission of COVID-19 in laboratory.
+It examines the proportion of staff infected in scenarios varying the: number of shifts per day; number of staff per shift; overall staff pool; shift patterns; secondary attack rate of the virus; introduction of protective measures (social distancing and personal protective equipment).
+The model is created using Python.
+
+**Kim et al.
+2021:** This study adapts a previously developed discrete-event simulation model for abdominal aortic aneurysm (AAA) screening of men in England.
+It aims to explore different approaches to resuming screening and surgical repair for AAA, as these survives were paused or substantially reduced during COVID-19 due to concerns about virus transmission.
+
+**Anagnostou et al.
+2022:** This paper includes two models - we have focussed just on the dynamiC Hospital wARd Management (CHARM) model.
+CHARM is a discrete-event simulation modelling intensive care units (ICU) in the COVID-19 pandemic (as well as subsequent stays in a recovery bed).
+It includes three types of admission to the ICU (emergency, elective or COVID-19).
+COVID-19 patients are kept seperate, and if they run out of capacity due to a surge in COVID-19 admissions, additional capacity can be pooled from the elective and emergency capacity.
+
+**Johnson et al. 2021:** TBC <!-- TODO: Add Johnson -->
+
+## Scope
+
+| Study | Scope | Success | Time |
+| --- | --- | --- | --- |
+| Shoaib and Ramamohan 2022 | 17 items:<br>• 1 table<br>• 9 figures<br>• 7 in-text results | 16 out of 17 (94%) | 28h 14m |
+| Huang et al. 2019 | 8 items:<br>• 5 figures<br>• 3 in-text results | 3 out of 8 (37.5%) | 24h 10m |
+| Lim et al. 2020 | 9 items:<br>• 5 tables<br>• 4 figures | 9 out of 9 (100%) | 12h 27m |
+| Kim et al. 2021 | 10 items:<br>• 3 tables<br>• 6 figures<br>• 1 in-text result | 10 out of 10 (100%) | 13h 59m |
+| Anagnostou et al. 2022 | 1 item:<br>• 1 figure | 1 out of 1 (100%) | 2h 10m |
+| Johnson et al. 2021 | 5 items:<br>• 1 table<br>• 4 figures | TBC | TBC |
+
+## Time to completion
+
+<!-- TODO: Add Johnson et al. 2021 once conducted reproduction -->
+
+```{python}
+# Import required libraries and functions
+import matplotlib.pyplot as plt
+import matplotlib.ticker as mtick
+import numpy as np
+import pandas as pd
+from plotly import graph_objects as go
+from time_to_complete import process_times, success_static, success_interactive
+
+# Create a dataframe of times from each of the reproductions
+
+# Shoaib and Ramamohan 2022 (16/17)
+time_sho = [
+    [856, 'Table 6'],
+    [971, 'Figure 2A'],
+    [889, 'Figure 2B'],
+    [910, 'Figure 2C'],
+    [981, 'Figure 2D'],
+    [1002, 'Figure 3A'],
+    [1008, 'Figure 3B'],
+    [1009, 'Figure 3C'],
+    [1012, 'Figure 3D'],
+    [1165, 'Figure 4'],
+    [1196, 'In-text result 1'],
+    [1274, 'In-text result 2'],
+    [1383, 'In-text result 3'],
+    [1396, 'In-text result 4'],
+    [1557, 'In-text result 5'],
+    [1490, 'In-text result 6'],
+    [1694, 'In-text result 7']]
+df_sho = process_times(time_sho, adjust='In-text result 7')
+
+# Huang et al. 2019 (3/8)
+time_hua = [
+    [516, 'In-text result 1'],
+    [1193, 'In-text result 2'],
+    [1450, 'Figure 2'], # Finished work, not completed, adjust to set to NaN
+    [np.nan, 'Figure 3'],
+    [np.nan, 'Figure 4'],
+    [1228, 'Figure 5'],
+    [np.nan, 'Supplementary figure'],
+    [np.nan, 'In-text result 3']]
+df_hua = process_times(time_hua, adjust='Figure 2')
+
+# Lim et al. 2020 (9/9)
+time_lim = [
+    [607, 'Figure 2'],
+    [647, 'Figure 3'],
+    [655, 'Figure 4'],
+    [747, 'Figure 5'],
+    [486, 'Supplemental table 2'],
+    [513, 'Supplemental table 3'],
+    [513, 'Supplemental table 4'],
+    [714, 'Supplemental table 5'],
+    [690, 'Supplemental table 6']]
+df_lim = process_times(time_lim)
+
+# Kim et al. 2021 (10/10)
+time_kim = [
+    [445, 'Figure 1'],
+    [511, 'Table 2'],
+    [581, 'Figure 2'],
+    [619, 'Figure 3'],
+    [774, 'In-text result 1'],
+    [672, 'Figure 4'],
+    [785, 'Figure 5'],
+    [793, 'Table 3'],
+    [875, 'Supplementary figure 3'],
+    [839, 'Supplementary table 2']]
+df_kim = process_times(time_kim)
+
+# Anagnostou et al. 2022 (1/1)
+time_ana = [
+    [130, 'Figure 3']]
+df_ana = process_times(time_ana)
+
+# Johnson et al. 2021
+# TODO: Add times once completed reproduction
+
+# Create list with the dataframes, labels and colours, to use for each plot
+to_plot = [
+    (df_sho, 'Shoaib and<br>Ramamohan<br>2022', '#ee6677'),
+    (df_hua, 'Huang et<br>al. 2019', '#228833'),
+    (df_lim, 'Lim et<br>al. 2020', '#4477aa'),
+    (df_kim, 'Kim et<br>al. 2021', '#ccbb44'),
+    (df_ana, 'Anagnostou<br>et al. 2022', '#66ccee')
+    # 'Johnson et al. 2021', '#aa3377')
+]
+```
+
+Non-interactive figure:
+
+```{python}
+# Create figure object
+fig, ax = plt.subplots()
+
+# Loop through and add lines for each reproduction
+for x in to_plot:
+    success_static(x[0], ax, x[1], x[2])
+
+# Amend appearance
+plt.xlim(0, 30)
+plt.ylim(0, 100)
+plt.xlabel('Time elapsed (hours)')
+plt.ylabel('Percentage of items reproduced')
+ax.yaxis.set_major_formatter(mtick.PercentFormatter())
+ax.legend(loc='center left', bbox_to_anchor=(1, 0.5))
+
+# Show figure
+plt.show()
+```
+
+Interactive figure:
+
+```{python}
+# Create figure object
+fig = go.Figure()
+
+# Loop through and add lines for each reproduction
+for x in to_plot:
+    success_interactive(x[0], fig, x[1], x[2])
+
+# Amend appearance
+fig.update_layout(
+    xaxis=dict(
+        title='Time elapsed (hours)',
+        range=[0, 30]
+    ),
+    yaxis=dict(
+        title='Percentage of items reproduced',
+        range=[0, 100],
+        ticksuffix='%'
+    ),
+    showlegend=True)
+
+# Show plot, hiding toolbar and not allowing zoom
+fig.layout.xaxis.fixedrange = True
+fig.layout.yaxis.fixedrange = True
+fig.show(config={'displayModeBar': False})
+```

### 2024-08-14 pages/time_to_complete.py

@@ -1,0 +1,131 @@
+import numpy as np
+import pandas as pd
+from plotly import graph_objects as go
+
+
+def process_times(time_list, adjust=False):
+    '''
+    Process the times to completion
+
+    Parameters:
+    -----------
+    time_list : list of lists
+        List of 2-item lists where first element is time-to-completion in
+        minutes and second element is name of the item
+    adjust : string
+        Name of item to reset to np.nan (used when want line to extend to when
+        stopped reproduction, without it marking it as another item complete).
+        Default is False (which means nothing is adjusted).
+
+    Returns:
+    --------
+    plt_times: dataframe
+        Processed dataframe of times, ready for plotting
+    '''
+    # Create times dataframe...
+
+    # Convert to dataframe
+    times = pd.DataFrame(time_list, columns=['time', 'item'])
+
+    # Sort the DataFrame by 'time' to correctly plot the ECDF
+    times_clean = times.sort_values(by='time').reset_index(drop=True)
+
+    # Compute the ECDF values
+    times_clean['ecdf'] = np.arange(
+        1, len(times_clean) + 1) / len(times_clean) * 100
+
+    # Amend item to set as np.nan (so time extends to that point)
+    if adjust is not False:
+        times_clean.loc[times_clean['item'] == adjust, 'ecdf'] = np.nan
+
+    # Insert the starting point (0, 0) in the ECDF
+    times_clean.loc[-1] = [0, 'Start', 0]
+    times_clean.index = times_clean.index + 1
+    times_clean = times_clean.sort_index()
+
+    # Convert time to hours
+    times_clean['hours'] = times_clean['time']/60
+
+    # Add points for the 90 degree turns in the line...
+
+    # Adjust index so it goes 0 2 4 6...
+    times_original = times_clean.copy()
+    times_original.index = times_clean.index*2
+
+    times_extra = times_clean.copy()
+
+    # Get result from row 1 to final, and add another row with np.nan
+    next_result = times_clean['time'][1:].reset_index(drop=True)
+    next_result[len(next_result)] = np.nan
+    # Replace time with those values (i.e. the value from the row below)
+    times_extra['time'] = next_result
+    times_extra['item'] = np.nan
+    # Then adjust index so it goes 1 3 5 7...
+    times_extra.index = (times_extra.index*2)+1
+
+    # Combine (so have alternating rows from each due to odd and even indexes)
[…]

### 2024-08-14 index.qmd
feat(overview): completed the overview page

@@
 authors:
-  - name: Amy Heather
+  - name: Ms Amy Heather
     url: https://github.com/amyheather
     orcid: 0000-0002-6596-3479
-    affiliation: University of Exeter
+    affiliation: Peninsula Collaboration for Health Operational Research and Data Science (PenCHORD), University of Exeter Medical School
+  - name: Associate Professor Tom Monks
+    url: https://github.com/TomMonks
+    orcid: 0000-0003-2631-4481
+    affiliation: Peninsula Collaboration for Health Operational Research and Data Science (PenCHORD), University of Exeter Medical School
+  - name: Dr Alison Harper
+    url: https://github.com/AliHarp
+    orcid: 0000-0001-5274-5037
+    affiliation: Centre for Simulation, Analytics and Modelling (CSAM), University of Exeter Business School
 ---
 
-TODO: Overview page
+## Overview {.unnumbered}
+
+This book describes the findings from work package 1 of the project **STARS: Sharing Tools and Artefacts for Reproducible Simulations in healthcare**.
+
+Use the sidebar to navigate through:
+
+* **Introduction** - background on the STARS project, pilot work, and the aim of work package 1
+* **Methods** - summarises the methods which are described in detail in our protocol
+* **Results** - describes the results of the reproductions and evaluations, and reflections from the process
+* **Discussion** - considers and applies findings \
+
+## Funding {.unnumbered}
+
+This work is supported by the Medical Research Council [grant number [MR/Z503915/1](https://gtr.ukri.org/projects?ref=MR%2FZ503915%2F1)].
+
+## License {.unnumbered}
+
+This book is licensed under a [Creative Commons Attribution 4.0 International (CC BY 4.0)](https://github.com/pythonhealthdatascience/stars_wp1_summary/blob/1a7e932013abd8e4810764b8925e98e9a6473844/LICENSE) license.
+
+[![License: CC BY 4.0](https://licensebuttons.net/l/by/4.0/80x15.png)](https://creativecommons.org/licenses/by/4.0/)
+[![License: CC BY 4.0](https://img.shields.io/badge/License-CC_BY_4.0-lightgrey.svg)](https://creativecommons.org/licenses/by/4.0/)

### 2024-08-14 pages/protocol.qmd
docs(quarto): minor amendment to title and a little content for the protocol page

@@
 
-TODO: This page summarises the method from the protocol.
+<!-- TODO: Write out a summary here -->
+
+The protocol for this work is summarised in the diagram below and archived on Zenodo:
+
+> Heather, A., Monks, T., Harper, A., Mustafee, N., & Mayne, A.
+(2024).
+Protocol for assessing the computational reproducibility of discrete-event simulation models on STARS.
+Zenodo.
+<https://doi.org/10.5281/zenodo.12179846>.
+
+![Workflow for STARS work package 1](../images/stars_wp1_workflow.png)

### 2024-08-14 pages/background.qmd
docs(quarto): add empty page for background

---
title: "STARS"
---

TODO: Add background about STARS, pilot work, and aim of WP1

### 2024-08-15 pages/functions.py
feat(functions): rename to functions.py and add eval_chart()

@@ -1,6 +1,7 @@
 import numpy as np
 import pandas as pd
 from plotly import graph_objects as go
+import plotly.express as px
 
 
 def process_times(time_list, adjust=False):
@@ -129,3 +130,68 @@ def success_static(times_df, ax, label, colour):
     '''
     ax.plot(times_df['hours'], times_df['ecdf'], marker='.', markevery=2,
             label=label.replace('<br>', '\n'), color=colour)
+
+
+def eval_chart(df):
+    '''
+    Create a stacked bar chart presenting the results from evaluation for
+    each study.
+
+    Parameters:
+    -----------
+    df : dataframe
+        Wide dataframe where columns are result of evaluation, and rows
+        are the study
+    '''
+    eval = (df
+            .melt(ignore_index=False)
+            .reset_index()
+            .rename(columns={'index': 'guideline',
+                             'variable': 'result',
+                             'value': 'count'}))
+
+    # Add percentages
+    eval['total'] = eval['count'].groupby(eval['guideline']).transform('sum')
+    eval['percent'] = eval['count'] / eval['total']
+    eval['percentage'] = round(eval['percent']*100, 1).astype(str) + '%'
+
+    # Create stacked bar visualisation
+    fig = px.bar(
+        eval,
+        x='percent',
+        y='guideline',
+        color='result',
+        color_discrete_map={'fully': '#06a94d',
+                            'partially': '#ffd68c',
+                            'not': '#ff9999',
+                            'na': '#d1dcea'},
+        orientation='h',
+        hover_data={
+            'count': True,
+            'percent': False,
+            'percentage': True,
+            'guideline': False,
+            'result': False})
+
+    # Amend x axis label and ticks
+    fig.update_layout(xaxis=dict(
+        range=[0, 1],
+        tickmode='array',
+        tickvals=[0, 0.2, 0.4, 0.6, 0.8, 1],
+        ticktext=['0%', '20%', '40%', '60%', '80%', '100%'],
+        title=''))
+
+    # Amend y axis label and order, and add space between ticks and plot
+    fig.update_layout(yaxis=dict(
+        autorange='reversed',
+        title=''))
+    fig.update_yaxes(ticksuffix='  ')
+
+    # Relabel legend
+    fig.update_layout(legend_title_text='Result')
+    newnames = {'fully': 'Fully met', 'partially': 'Partially met',
+                'not': 'Not met', 'na': 'Not applicable'}
[…]

### 2024-08-15 pages/reproduction.qmd
docs(reproduction): import from functions and add citations

@@
 
-**Shoaib and Ramamohan 2022:** This is a discrete-event simulation modelling primary health centres (PHCs) in India.
+**@shoaib_simulation_2021:** This is a discrete-event simulation modelling primary health centres (PHCs) in India.
 There are four patient types: outpatients, inpatients, childbirth cases and antenatal care patients.
@@
 The paper explores different operational patterns for scenarios where very high utilisation was observed, to explore what might help reduce utilisation of these resources.
+*(Article published as @shoaib_simulation_2022, but we used the green open access pre-print)*
 
-**Huang et al.
-2019:** This is a discrete-event simulation model of an endovascular clot retrieval (ECR) service.
+**@huang_optimizing_2019:** This is a discrete-event simulation model of an endovascular clot retrieval (ECR) service.
 ECR is a treatment for acute ischaemic stroke.
@@
 
-**Lim et al.
-2020:** This is a discrete-event simulation modelling the transmission of COVID-19 in laboratory.
+**@lim_staff_2020:** This is a discrete-event simulation modelling the transmission of COVID-19 in laboratory.
 It examines the proportion of staff infected in scenarios varying the: number of shifts per day; number of staff per shift; overall staff pool; shift patterns; secondary attack rate of the virus; introduction of protective measures (social distancing and personal protective equipment).
@@
 
-**Kim et al.
-2021:** This study adapts a previously developed discrete-event simulation model for abdominal aortic aneurysm (AAA) screening of men in England.
+**@kim_modelling_2021:** This study adapts a previously developed discrete-event simulation model for abdominal aortic aneurysm (AAA) screening of men in England.
 It aims to explore different approaches to resuming screening and surgical repair for AAA, as these survives were paused or substantially reduced during COVID-19 due to concerns about virus transmission.
 
-**Anagnostou et al.
-2022:** This paper includes two models - we have focussed just on the dynamiC Hospital wARd Management (CHARM) model.
+**@anagnostou_facs-charm_2022:** This paper includes two models - we have focussed just on the dynamiC Hospital wARd Management (CHARM) model.
 CHARM is a discrete-event simulation modelling intensive care units (ICU) in the COVID-19 pandemic (as well as subsequent stays in a recovery bed).
@@
 
-**Johnson et al. 2021:** TBC <!-- TODO: Add Johnson -->
+**@johnson_cost_2021:** TBC <!-- TODO: Add Johnson -->
 
@@
 from plotly import graph_objects as go
-from time_to_complete import process_times, success_static, success_interactive
+from functions import process_times, success_static, success_interactive
 
@@
 ```
+
+## References

### 2024-08-15 pages/paper_evaluation.qmd
feat(evaluation): completed evaluation of the article page

@@
 title: "Evaluation of the article"
+echo: False
+format:
+    html:
+        page-layout: full
+bibliography: ../references.bib
 ---
 
-TODO: Add evaluation of article against STRESS-DES and against the guidelines derived from ISPOR-SDM. Include record of timings to complete this part of the evaluation for each.
+This page shares the results from the evaluation of the journal articles against criteria from two discrete-event simulation study reporting guidelines:
+
+* @monks_strengthening_2019 - STRESS-DES: Strengthening The Reporting of Empirical Simulation Studies (Discrete-Event Simulation) (Version 1.0).
+* @zhang_reporting_2020 - The generic reporting checklist for healthcare-related discrete event simulation studies derived from the the International Society for Pharmacoeconomics and Outcomes Research Society for Medical Decision Making (ISPOR-SDM) Modeling Good Research Practices Task Force reports.
+
+## Summary
+
+<!-- TODO: Add Johnson et al. 2021 and Kim et al. 2021 -->
+
+**STRESS-DES:**
+
+```{python}
+import pandas as pd
+from functions import eval_chart
+
+# Create dataframe of results
+col = ['fully', 'partially', 'not', 'na']
+stress_dict = {
+  'Shoaib and<br>Ramamohan 2021': [17, 6, 1, 0],
+  'Huang et al. 2019': [14, 6, 3, 1],
+  'Lim et al. 2020': [16, 2, 3, 3],
+  'Kim et al. 2021': [0, 0, 0, 1],
+  'Anagnostou et al. 2022': [14, 2, 5, 3],
+  'Johnson et al. 2021': [0, 0, 0, 1]
+}
+stress_wide = pd.DataFrame(stress_dict, index=col).T
+
+eval_chart(stress_wide)
+```
+
+**DES checklist derived from ISPOR-SDM:**
+
+```{python}
+# Create dataframe of results
+col = ['fully', 'partially', 'not', 'na']
+ispor_dict = {
+  'Shoaib and<br>Ramamohan 2021': [11, 2, 2, 3],
+  'Huang et al. 2019': [7, 2, 7, 2],
+  'Lim et al. 2020': [12, 0, 4, 2],
+  'Kim et al. 2021': [0, 0, 0, 1],
+  'Anagnostou et al. 2022': [8, 3, 4, 3],
+  'Johnson et al. 2021': [0, 0, 0, 1]
+}
+ispor_wide = pd.DataFrame(ispor_dict, index=col).T
+
+eval_chart(ispor_wide)
+```
+
+## STRESS-DES
+
+<!-- Using HTML so can set target="_blank" which opens link in new tab -->
+
+Key:
+
+* **S:** @shoaib_simulation_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-shoaib-2022/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>
+* **H:** @huang_optimizing_2019  - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-huang-2019/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>
+* **L:** @lim_staff_2020 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-lim-2020/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>
+* **K:** @kim_modelling_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-kim-2021/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>
+* **A:** @anagnostou_facs-charm_2022 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-anagnostou-2022/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>
+* **J:** @johnson_cost_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-johnson-2021/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>
+
+<!-- TODO: Add Johnson et al. 2021, and update after discussion of Kim et al. 2021 -->
+
+| Item | S | H | L | K | A | J |
+| - | - | - | - | - | - | - | - |
+| **Objectives** | 
+| **1.1 Purpose of the model**<br>Explain the background and objectives for the model | ✅ | ✅ | ✅ | ✅ | ✅ |
+| **1.2 Model outputs**<br>Define all quantitative performance measures that are reported, using equations where necessary.
+Specify how and when they are calculated during the model run along with how any measures of error such as confidence intervals are calculated.
+| 🟡 | ✅ | ✅ | ✅ | ✅ |
+| **1.3 Experimentation aims**<br>If the model has been used for experimentation, state the objectives that it was used to investigate.<br>(A) Scenario based analysis – Provide a name and description for each scenario, providing a rationale for the choice of scenarios and ensure that item 2.3 (below) is completed.<br>(B) Design of experiments – Provide details of the overall design of the experiments with reference to performance measures and their parameters (provide further details in data below).<br>(C) Simulation Optimisation – (if appropriate) Provide full details of what is to be optimised, the parameters that were included and the algorithm(s) that was be used.
+Where possible provide a citation of the algorithm(s).
+| ✅ | ✅ | ✅ | ✅ | N/A |
+| **Logic** |
+| **2.1 Base model overview diagram**<br>Describe the base model using appropriate diagrams and description.
+This could include one or more process flow, activity cycle or equivalent diagrams sufficient to describe the model to readers.
+Avoid complicated diagrams in the main text.
+The goal is to describe the breadth and depth of the model with respect to the system being studied.
+| ✅ | ✅ | ✅ | tbc | ✅ |
+| **2.2 Base model logic**<br>Give details of the base model logic. Give additional model logic details sufficient to communicate to the reader how the model works. | ✅ | ✅ | ✅ | tbc | ✅ |
+| **2.3 Scenario logic**<br>Give details of the logical difference between the base case model and scenarios (if any).
+This could be incorporated as text or where differences are substantial could be incorporated in the same manner as 2.2.
+| ✅ | ✅ | ✅ | ✅ | N/A |
+| **2.4 Algorithms**<br>Provide further detail on any algorithms in the model that (for example) mimic complex or manual processes in the real world (i.e.
+scheduling of arrivals/ appointments/ operations/ maintenance, operation of a conveyor system, machine breakdowns, etc.).
+Sufficient detail should be included (or referred to in other published work) for the algorithms to be reproducible.
+Pseudo-code may be used to describe an algorithm.
+| ✅ | 🟡 | ✅ | tbc | ✅ |
+| **2.5.1 Components - entities**<br>Give details of all entities within the simulation including a description of their role in the model and a description of all their attributes.
+| ✅ | ✅ | ✅ | ✅ | ✅ |
+| **2.5.2 Components - activities**<br>Describe the activities that entities engage in within the model. Provide details of entity routing into and out of the activity. | ✅ | ✅ | ✅ | tbc | ✅ |
+| **2.5.3 Components - resources**<br>List all the resources included within the model and which activities make use of them. | ✅ | ✅ | N/A | tbc | ✅ |
+| **2.5.4 Components - queues**<br>Give details of the assumed queuing discipline used in the model (e.g.
+First in First Out, Last in First Out, prioritisation, etc.).
+Where one or more queues have a different discipline from the rest, provide a list of queues, indicating the queuing discipline used for each.
+If reneging, balking or jockeying occur, etc., provide details of the rules.
+Detail any delays or capacity constraints on the queues.
+| ✅ | ✅ | N/A | tbc | ✅ |
+| **2.5.5 Components - entry/exit points**<br>Give details of the model boundaries i.e.
+all arrival and exit points of entities.
+Detail the arrival mechanism (e.g.
+‘thinning’ to mimic a non-homogenous Poisson process or balking) | ✅ | ✅ | ✅ | ✅ | ✅ |
+| **Data** |
+| **3.1 Data sources**<br>List and detail all data sources.
+Sources may include:<br>• Interviews with stakeholders,<br>• Samples of routinely collected data,<br>• Prospectively collected samples for the purpose of the simulation study,<br>• Public domain data published in either academic or organisational literature.
+Provide, where possible, the link and DOI to the data or reference to published literature.<br>All data source descriptions should include details of the sample size, sample date ranges and use within the study.
+| ✅ | ✅ | ✅ | ✅ | ✅ |
+| **3.2 Pre-processing**<br>Provide details of any data manipulation that has taken place before its use in the simulation, e.g.
+interpolation to account for missing data or the removal of outliers.
+| ✅ | N/A | N/A | ✅ | N/A |
+| **3.3 Input parameters**<br>List all input variables in the model.
+Provide a description of their use and include parameter values.
+For stochastic inputs provide details of any continuous, discrete or empirical distributions used along with all associated parameters.
+Give details of all time dependent parameters and correlation.<br>Clearly state:<br>• Base case data<br>• Data use in experimentation, where different from the base case.<br>• Where optimisation or design of experiments has been used, state the range of values that parameters can take.<br>• Where theoretical distributions are used, state how these were selected and prioritised above other candidate distributions.
+| 🟡 | 🟡 | ✅ | 🟡 | ✅ |
+| **3.4 Assumptions**<br>Where data or knowledge of the real system is unavailable what assumptions are included in the model?
+This might include parameter values, distributions or routing logic within the model.
+| ✅ | ❌ | ✅ | ✅ | ❌ |
+| **Experimentation** |
+| **4.1 Initialisation**<br>Report if the system modelled is terminating or non-terminating.
+State if a warm-up period has been used, its length and the analysis method used to select it.
+For terminating systems state the stopping condition.<br>State what if any initial model conditions have been included, e.g., pre-loaded queues and activities.
+Report whether initialisation of these variables is deterministic or stochastic.
+| 🟡 | ❌ | ❌ | tbc | ❌ |
+| **4.2 Run length**<br>Detail the run length of the simulation model and time units. | ✅ | ✅ | ✅ | ✅ | 🟡 |
+| **4.3 Estimation approach**<br>State the method used to account for the stochasticity: For example, two common methods are multiple replications or batch means.
+Where multiple replications have been used, state the number of replications and for batch means, indicate the batch length and whether the batch means procedure is standard, spaced or overlapping.
+For both procedures provide a justification for the methods used and the number of replications/size of batches.
+| 🟡 | 🟡 | ✅ | ✅ | ✅ |
+| **Implementation** |
+| **5.1 Software or programming language**<br>State the operating system and version and build number.<br>State the name, version and build number of commercial or open source DES software that the model is implemented in.<br>State the name and version of general-purpose programming languages used (e.g.
+Python 3.5).<br>Where frameworks and libraries have been used provide all details including version numbers.
+| 🟡 | 🟡 | 🟡 | 🟡 | 🟡 |
+| **5.2 Random sampling**<br>State the algorithm used to generate random samples in the software/programming language used e.g.
+Mersenne Twister.<br>If common random numbers are used, state how seeds (or random number streams) are distributed among sampling processes.
+| ❌ | 🟡 | ❌ | ❌ | ❌ |
+| **5.3 Model execution**<br>State the event processing mechanism used e.g.
+three phase, event, activity, process interaction.<br>*Note that in some commercial software the event processing mechanism may not be published.
+In these cases authors should adhere to item 5.1 software recommendations.*<br>State all priority rules included if entities/activities compete for resources.<br>If the model is parallel, distributed and/or use grid or cloud computing, etc., state and preferably reference the technology used.
+For parallel and distributed simulations the time management algorithms used.
+If the HLA is used then state the version of the standard, which run-time infrastructure (and version), and any supporting documents (FOMs, etc.) | 🟡 |❌ | ❌ | tbc | ❌ |
+| **5.4 System specification**<br>State the model run time and specification of hardware used.
+This is particularly important for large scale models that require substantial computing power.
+For parallel, distributed and/or use grid or cloud computing, etc.
+state the details of all systems used in the implementation (processors, network, etc.) | ✅ | ❌ | 🟡 | tbc | ❌ |
+| **Code access** |
+| **6.1 Computer model sharing statement**<br>Describe how someone could obtain the model described in the paper, the simulation software and any other associated software (or hardware) needed to reproduce the results.
+Provide, where possible, the link and DOIs to these.
+| ✅ | ✅ | ✅ | ✅ | ✅ |
+: {tbl-colwidths="[70, 5, 5, 5, 5, 5, 5]"}
+
+## DES checklist derived from ISPOR-SDM
+
+Key:
+
+* **S:** @shoaib_simulation_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-shoaib-2022/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>
+* **H:** @huang_optimizing_2019  - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-huang-2019/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>
+* **L:** @lim_staff_2020 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-lim-2020/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>
+* **K:** @kim_modelling_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-kim-2021/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>
+* **A:** @anagnostou_facs-charm_2022 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-anagnostou-2022/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>
+* **J:** @johnson_cost_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-johnson-2021/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>
+
+<!-- TODO: Add Johnson and amend Kim after discussion if required -->
+
+| Item | S | H | L | K | A | J |
+| - | - | - | - | - | - | - | - |
+| **Model conceptualisation** |
+| **1 Is the focused health-related decision problem clarified?**<br>...the decision problem under investigation was defined.
+DES studies included different types of decision problems, eg, those listed in previously developed taxonomies.
+| ✅ | ✅ | ✅ | ✅ | ✅ |
+| **2 Is the modeled healthcare setting/health condition clarified?**<br>...the physical context/scope (eg, a certain healthcare unit or a broader system) or disease spectrum simulated was described.
+| ✅ | ✅ | ✅ | ✅ | ✅ |
+| **3 Is the model structure described?**<br>...the model’s conceptual structure was described in the form of either graphical or text presentation. | ✅ | ✅ | ✅ | tbc | ✅ |
+| **4 Is the time horizon given?**<br>...the time period covered by the simulation was reported. | ✅ | ✅ | ✅ | ✅ | ✅ | ❌ |
+| **5 Are all simulated strategies/scenarios specified?**<br>...the comparators under test were described in terms of their components, corresponding variations, etc | ✅ | ✅ | ✅ | ✅ | ✅ | N/A |
+| **6 Is the target population described?**<br>...the entities simulated and their main attributes were characterized. | ✅ | ❌ | ✅ | ✅ | 🟡 |
+| **Paramaterisation and uncertainty assessment** |
+| **7 Are data sources informing parameter estimations provided?**<br>...the sources of all data used to inform model inputs were reported. | ✅ | ✅ | ✅ | ✅ | ✅ |
+| **8 Are the parameters used to populate model frameworks specified?**<br>...all relevant parameters fed into model frameworks were disclosed. | 🟡 | 🟡 | ✅ | ✅ | ✅ |
+| **9 Are model uncertainties discussed?**<br>...the uncertainty surrounding parameter estimations and adopted statistical methods (eg, 95% confidence intervals or possibility distributions) were reported.
+| 🟡 | ❌ | ❌ | ❌ | ✅ |
+| **10 Are sensitivity analyses performed and reported?**<br>...the robustness of model outputs to input uncertainties was examined, for example via deterministic (based on parameters’ plausible ranges) or probabilistic (based on a priori-defined probability distributions) sensitivity analyses, or both.
+| ✅ | ❌ | ✅ | ❌ | N/A |
+| **Validation** |
+| **11 Is face validity evaluated and reported?**<br>...it was reported that the model was subjected to the examination on how well model designs correspond to the reality and intuitions.
+It was assumed that this type of validation should be conducted by external evaluators with no stake in the study.
+| ❌ | ❌ | ❌ | ❌ | ❌ |
+| **12 Is cross validation performed and reported**<br>...comparison across similar modeling studies which deal with the same decision problem was undertaken. | N/A | ❌ | ❌ | ✅ | ❌ |
+| **13 Is external validation performed and reported?**<br>...the modeler(s) examined how well the model’s results match the empirical data of an actual event modeled. | N/A | N/A | N/A | ✅ | ❌ |
+| **14 Is predictive validation performed or attempted?**<br> ...the modeler(s) examined the consistency of a model’s predictions of a future event and the actual outcomes in the future.
+If this was not undertaken, it was assessed whether the reasons were discussed.
+| N/A | N/A | N/A | N/A | N/A |
+| **Generalisability and stakeholder involvement** |
+| **15 Is the model generalizability issue discussed?**<br>...the modeler(s) discussed the potential of the resulting model for being applicable to other settings/populations (single/multiple application).
+| ✅ | ✅ | ✅ | ❌ | 🟡 |
+| **16 Are decision makers or other stakeholders involved in modeling?**<br>...the modeler(s) reported in which part throughout the modeling process decision makers and other stakeholders (eg, subject experts) were engaged.
+| ❌ | ❌ | ❌ | ❌ | ✅ |
+| **17 Is the source of funding stated?**<br>...the sponsorship of the study was indicated. | ✅ | ❌ | ✅ | ✅ | ✅ |
+| **18 Are model limitations discussed?**<br>...limitations of the assessed model, especially limitations of interest to decision makers, were discussed. | ✅ | 🟡 | ✅ | ✅ | 🟡 |
+: {tbl-colwidths="[70, 5, 5, 5, 5, 5, 5]"}
+
+## Timings
+
+<!-- TODO: Add timings for each from evaluation for reporting
+Also issue may be that I can't necessarily disaggregate into reporting and code times-->
+
+## References

### 2024-08-15 pages/reproduction.qmd
docs(reproduction): add links to reproductions

@@
 The paper explores different operational patterns for scenarios where very high utilisation was observed, to explore what might help reduce utilisation of these resources.
-*(Article published as @shoaib_simulation_2022, but we used the green open access pre-print)*
+*(Article published as @shoaib_simulation_2022, but we used the green open access pre-print).* <a href="https://pythonhealthdatascience.github.io/stars-reproduce-shoaib-2022/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>
 
@@
 A few scenarios are tried to help examine why the wait times are so high for the angioINR.
+<a href="https://pythonhealthdatascience.github.io/stars-reproduce-huang-2019/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>
 
@@
 The model is created using Python.
+<a href="https://pythonhealthdatascience.github.io/stars-reproduce-lim-2020/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>
 
@@
 It aims to explore different approaches to resuming screening and surgical repair for AAA, as these survives were paused or substantially reduced during COVID-19 due to concerns about virus transmission.
+<a href="https://pythonhealthdatascience.github.io/stars-reproduce-kim-2021/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>
 
@@
 COVID-19 patients are kept seperate, and if they run out of capacity due to a surge in COVID-19 admissions, additional capacity can be pooled from the elective and emergency capacity.
+<a href="https://pythonhealthdatascience.github.io/stars-reproduce-anagnostou-2022/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>
 

### 2024-08-15 pages/repo_evaluation.qmd
feat(evaluation): completed repository evaluation page

@@
 title: "Evaluation of the repository"
+echo: False
+bibliography: ../references.bib
 ---
 
-TODO: Add table with results from evaluation of repository against STARS framework and against journal badges. Include record of timings to complete this part of the evaluation for each.
+The code and related research artefacts in the original code repositories were evaluated against:
+
+* The criteria of badges related to reproducibility from various organisations and journals.
+* Recommendations from the STARS framework for the sharing of code and associated materials from discrete-event simulation models (@monks_towards_2024).
+
+Between each journal badge, there was often alot of overlap in criteria.
+Hence, a list of unique criteria was produced.
+The repositories are evaluated against this criteria, and then depending on which criteria they met, against the badges themselves.
+
+*Caveat: Please note that these criteria are based on available information about each badge online, and that we have likely differences in our procedure (e.g.
+allowed troubleshooting for execution and reproduction, not under tight time pressure to complete).
+Moreover, we focus only on reproduction of the discrete-event simulation, and not on other aspects of the article.
+We cannot guarantee that the badges below would have been awarded in practice by these journals.*
+
+## Summary
+
+**Unique badge criteria:**
+
+```{python}
+import pandas as pd
+from functions import eval_chart
+
+# Create dataframe of results
+col = ['fully', 'partially', 'not', 'na']
+criteria_dict = {
+  'Shoaib and<br>Ramamohan 2021': [3, 0, 9, 0],
+  'Huang et al. 2019': [3, 0, 9, 0],
+  'Lim et al. 2020': [3, 0, 9, 0],
+  'Kim et al. 2021': [0, 0, 0, 1],
+  'Anagnostou et al. 2022': [10, 0, 2, 0],
+  'Johnson et al. 2021': [0, 0, 0, 1]
+}
+criteria_wide = pd.DataFrame(criteria_dict, index=col).T
+
+eval_chart(criteria_wide)
+```
+
+**Badges:**
+
+```{python}
+# Create dataframe of results
+col = ['fully', 'partially', 'not', 'na']
+badge_dict = {
+  'Shoaib and<br>Ramamohan 2021': [3, 0, 9, 0],
+  'Huang et al. 2019': [0, 0, 12, 0],
+  'Lim et al. 2020': [3, 0, 9, 0],
+  'Kim et al. 2021': [0, 0, 0, 1],
+  'Anagnostou et al. 2022': [5, 0, 7, 0],
+  'Johnson et al. 2021': [0, 0, 0, 1]
+}
+badge_wide = pd.DataFrame(badge_dict, index=col).T
+
+eval_chart(badge_wide)
+```
+
+**Essential components of STARS framework:**
+
+```{python}
+# Create dataframe of results
+col = ['fully', 'partially', 'not', 'na']
+essential_dict = {
+  'Shoaib and<br>Ramamohan 2021': [2, 0, 6, 0],
+  'Huang et al. 2019': [2, 0, 6, 0],
+  'Lim et al. 2020': [2, 0, 6, 0],
+  'Kim et al. 2021': [0, 0, 0, 1],
+  'Anagnostou et al. 2022': [7, 0, 1, 0],
+  'Johnson et al. 2021': [0, 0, 0, 1]
+}
+essential_wide = pd.DataFrame(essential_dict, index=col).T
+
+eval_chart(essential_wide)
+```
+
+**Optional components of STARS framework:**
+
+```{python}
+# Create dataframe of results
+optional_dict = {
+  'Shoaib and<br>Ramamohan 2021': [0, 0, 5, 0],
+  'Huang et al. 2019': [2, 0, 3, 0],
+  'Lim et al. 2020': [0, 0, 5, 0],
+  'Kim et al. 2021': [0, 0, 0, 1],
+  'Anagnostou et al. 2022': [1, 1, 3, 0],
+  'Johnson et al. 2021': [0, 0, 0, 1]
+}
+optional_wide = pd.DataFrame(optional_dict, index=col).T
+
+eval_chart(optional_wide)
+```
+
+## Journal badges
+
+Key:
+
+* **S:** @shoaib_simulation_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-shoaib-2022/evaluation/badges.html" target="_blank">link to evaluation</a>
+* **H:** @huang_optimizing_2019  - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-huang-2019/evaluation/badges.html" target="_blank">link to evaluation</a>
+* **L:** @lim_staff_2020 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-lim-2020/evaluation/badges.html" target="_blank">link to evaluation</a>
+* **K:** @kim_modelling_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-kim-2021/evaluation/badges.html" target="_blank">link to evaluation</a>
+* **A:** @anagnostou_facs-charm_2022 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-anagnostou-2022/evaluation/badges.html" target="_blank">link to evaluation</a>
+* **J:** @johnson_cost_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-johnson-2021/evaluation/badges.html" target="_blank">link to evaluation</a>
+
+<!-- TODO: Add Johnson et al. 2021 -->
+
+**Unique criteria:**
+
+| Item | S | H | L | K | A | J |
+| - | - | - | - | - | - | - | - |
+| **Criteria related to how artefacts are shared** |
+| Stored in a permanent archive that is publicly and openly accessible | ❌ | ❌ | ❌ | ❌ | ✅ |
+| Has a persistent identifier | ❌ | ❌ | ❌ | ❌ | ✅ |
+| Includes an open license | ❌ | ✅ | ❌ | ✅ | ✅ |
+| **Criteria related to what artefacts are shared** |
+| Artefacts are relevant to and contribute to the article’s results | ✅ | ✅ | ✅ | ✅ | ✅ |
+| Complete set of materials shared (as would be needed to fully reproduce article) | ❌ | ❌ | ❌ | ❌ | ❌ |
+| **Criteria related to the structure and documentation of the artefacts** |
+| Artefacts are well structured/organised (e.g. to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community) | ❌ | ❌ | ❌ | ✅ | ✅ |
+| Artefacts are sufficiently documented (i.e. to understand how it works, to enable it to be run, including package versions) | ❌ | ❌ | ❌ | ❌ | ✅ |
+| Artefacts are carefully documented (more than sufficient - i.e. to the extent that reuse and repurposing is facilitated - e.g. changing parameters, reusing for own purpose) | ❌ | ❌ | ❌ | ❌ | ✅ |
+| Artefacts are clearly documented and accompanied by a README file with step-by-step instructions on how to reproduce results in the manuscript | ❌ | ❌ | ❌ | ❌ | ✅ |
+| **Criteria related to running and reproducing results** |
+| Scripts can be successfully executed | ✅ | ✅ | ✅ | ✅ | ✅ |
+| Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ |
+| Reproduced within approximately one hour (excluding compute time) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
+: {tbl-colwidths="[70, 5, 5, 5, 5, 5, 5]"}
+
+\
+
+**Badges:**
+
+The badges are grouped into three categories:
+
+* "Open objects" badges: These badges relate to research artefacts being made openly available.
+* "Object review" badges: These badges relate to the research artefacts being reviewed against criteria of the badge issuer.
+* "Reproduced" badges: These badges relate to an independent party regenerating the reuslts of the article using the author objects.
+
+<!-- TODO: Add Johnson et al. 2021 -->
+
+| Item | S | H | L | K | A | J |
+| - | - | - | - | - | - | - | - |
+| **“Open objects” badges** |
+| **NISO "Open Research Objects (ORO)"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier<br>• Includes an open license | ❌ | ❌ | ❌ | ❌ | ✅ |
+| **NISO "Open Research Objects - All (ORO-A)"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier<br>• Includes an open license<br>• Complete set of materials shared (as would be needed to fully reproduce article) | ❌ | ❌ | ❌ | ❌ | ❌ |
+| **ACM "Artifacts Available"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier | ❌ | ❌ | ❌ | ❌ | ✅ |
+| **COS "Open Code"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier<br>• Includes an open license<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Artefacts are sufficiently documented (i.e.
+to understand how it works, to enable it to be run, including package versions) | ❌ | ❌ | ❌ | ❌ | ❌ |
+| **IEEE "Code Available"**<br>• Complete set of materials shared (as would be needed to fully reproduce article) | ❌ | ❌ | ❌ | ❌ | ❌ |
+| **"Object review" badges** |
+| **ACM "Artifacts Evaluated - Functional"**<br>• Artefacts are sufficiently documented (i.e.
+to understand how it works, to enable it to be run, including package versions)<br>• Artefacts are relevant to and contribute to the article’s results<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Scripts can be successfully executed | ❌ | ❌ | ❌ | ❌ | ❌ |
+| **ACM "Artifacts Evaluated - Reusable"**<br>• Artefacts are sufficiently documented (i.e.
+to understand how it works, to enable it to be run, including package versions)<br>• Artefacts are carefully documented (more than sufficient - i.e.
+to the extent that reuse and repurposing is facilitated - e.g.
+changing parameters, reusing for own purpose)<br>• Artefacts are relevant to and contribute to the article's results<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Scripts can be successfully executed<br>• Artefacts are well structured/organised (e.g.
+to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community) | ❌ | ❌ | ❌ | ❌ | ❌ |
+| **IEEE "Code Reviewed"**<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Scripts can be successfully executed | ❌ | ❌ | ❌ | ❌ | ❌ |
+| **"Reproduced" badges** |
+| **NISO "Results Reproduced (ROR-R)"**<br>• Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ |
+| **ACM "Results Reproduced"**<br>• Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ |
+| **IEEE "Code Reproducible"**<br>• Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ |
+| **Psychological Science "Computational Reproducibility"**<br>• Independent party regenerated results using the authors research artefacts<br>• Reproduced within approximately one hour (excluding compute time)<br>• Artefacts are well structured/organised (e.g.
+to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community)<br>• Artefacts are clearly documented and accompanied by a README file with step-by-step instructions on how to reproduce results in the manuscript | ❌ | ❌ | ❌ | ❌ | ❌ |
+: {tbl-colwidths="[70, 5, 5, 5, 5, 5, 5]"}
+
+## STARS framework
+
+Key:
+
+* **S:** @shoaib_simulation_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-shoaib-2022/evaluation/artefacts.html" target="_blank">link to evaluation</a>
+* **H:** @huang_optimizing_2019  - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-huang-2019/evaluation/artefacts.html" target="_blank">link to evaluation</a>
+* **L:** @lim_staff_2020 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-lim-2020/evaluation/artefacts.html" target="_blank">link to evaluation</a>
+* **K:** @kim_modelling_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-kim-2021/evaluation/artefacts.html" target="_blank">link to evaluation</a>
+* **A:** @anagnostou_facs-charm_2022 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-anagnostou-2022/evaluation/artefacts.html" target="_blank">link to evaluation</a>
+* **J:** @johnson_cost_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-johnson-2021/evaluation/artefacts.html" target="_blank">link to evaluation</a>
+
+<!-- TODO: Add Johnson et al. 2021 -->
+
+| Item | S | H | L | K | A | J |
+| - | - | - | - | - | - | - | - |
+| **Essential components** |
+| **Open license**<br>Free and open-source software (FOSS) license (e.g. MIT, GNU Public License (GPL)) | ❌ | ✅ | ❌ | ✅ | ✅ |
+| **Dependency management**<br>Specify software libraries, version numbers and sources (e.g. dependency management tools like virtualenv, conda, poetry) | ❌ | ❌ | ❌ | 🟡 | ✅ |
+| **FOSS model**<br>Coded in FOSS language (e.g. R, Julia, Python) | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ |
+| **Minimum documentation**<br>Minimal instructions (e.g.
+in README) that overview (a) what model does, (b) how to install and run model to obtain results, and (c) how to vary parameters to run new experiments | ❌ | ❌ | ❌ | ✅ | ✅ |
+| **ORCID**<br>ORCID for each study author | ❌ | ❌ | ❌ | ❌ | ❌ |
+| **Citation information**<br>Instructions on how to cite the research artefact (e.g. CITATION.cff file) | ❌ | ❌ | ❌ | ❌ | ✅ |
+| **Remote code repository**<br>Code available in a remote code repository (e.g. GitHub, GitLab, BitBucket) | ✅ | ❌ | ✅ | ✅ | ✅ |
+| **Open science archive**<br>Code stored in an open science archive with FORCE11 compliant citation and guaranteed persistance of digital artefacts (e.g.
+Figshare, Zenodo, the Open Science Framework (OSF), and the Computational Modeling in the Social and Ecological Sciences Network (CoMSES Net)) | ❌ | ❌ | ❌ | ❌ | ✅ |
+| **Optional components** |
+| **Enhanced documentation**<br>Open and high quality documentation on how the model is implemented and works  (e.g.
+via notebooks and markdown files, brought together using software like Quarto and Jupyter Book).
+Suggested content includes:<br>• Plain english summary of project and model<br>• Clarifying license<br>• Citation instructions<br>• Contribution instructions<br>• Model installation instructions<br>• Structured code walk through of model<br>• Documentation of modelling cycle using TRACE<br>• Annotated simulation reporting guidelines<br>• Clear description of model validation including its intended purpose | ❌ | ❌ | ❌ | ❌ | ❌ |
+| **Documentation hosting**<br>Host documentation (e.g. with GitHub pages, GitLab pages, BitBucket Cloud, Quarto Pub) | ❌ | ❌ | ❌ | ❌ | ❌ |
+| **Online coding environment**<br>Provide an online environment where users can run and change code (e.g. BinderHub, Google Colaboratory, Deepnote) | ❌ | ❌ | ❌ | ❌ | ❌ |
+| **Model interface**<br>Provide web application interface to the model so it is accessible to less technical simulation users | ❌ | ✅ | ❌ | ❌ | ✅ |
+| **Web app hosting**<br>Host web app online (e.g. Streamlit Community Cloud, ShinyApps hosting) | ❌ | ✅ | ❌ | ❌ | 🟡 |
+: {tbl-colwidths="[70, 5, 5, 5, 5, 5, 5]"}
+
+## Timings
+
+<!-- TODO: Add timings for each from evaluation for reporting
+Also issue may be that I can't necessarily disaggregate into reporting and code times-->
+
+## Badge sources
+
+**National Information Standards Organisation (NISO)** (@niso_reproducibility_badging_and_definitions_working_group_reproducibility_2021)
+
+* "Open Research Objects (ORO)"
+* "Open Research Objects - All (ORO-A)"
+* "Results Reproduced (ROR-R)"
+
+**Association for Computing Machinery (ACM)** (@association_for_computing_machinery_acm_artifact_2020)
+
+* "Artifacts Available"
+* "Artifacts Evaluated - Functional"
+* "Artifacts Evaluated - Resuable"
+* "Results Reproduced"
+
+**Center for Open Science (COS)** (@blohowiak_badges_2023)
+
+* "Open Code"
+
+**Institute of Electrical and Electronics Engineers (IEEE)** (@institute_of_electrical_and_electronics_engineers_ieee_about_nodate)
+
+* "Code Available"
+* "Code Reviewed"
+* "Code Reproducible"
+
+**Psychological Science** (@hardwicke_transparency_2023 and @association_for_psychological_science_aps_psychological_2023)
+
+* "Computational Reproducibility"
+
+## References

### 2024-08-15 pages/paper_evaluation.qmd
feat(evaluation): add timings

@@
 
-<!-- TODO: Add timings for each from evaluation for reporting
-Also issue may be that I can't necessarily disaggregate into reporting and code times-->
+<!-- Add johnson and kim -->
+
+* @shoaib_simulation_2021 - 1h 56m
+* @huang_optimizing_2019 - 1h 28m
+* @lim_staff_2020 - 1h 12m
+* @kim_modelling_2021
+* @anagnostou_facs-charm_2022 - 53m
+* @johnson_cost_2021
 

### 2024-08-15 pages/repo_evaluation.qmd
feat(evaluation): add timings

@@
 
-<!-- TODO: Add timings for each from evaluation for reporting
-Also issue may be that I can't necessarily disaggregate into reporting and code times-->
+<!-- Add johnson and kim -->
+
+* @shoaib_simulation_2021 - 30m
+* @huang_optimizing_2019 - 17m
+* @lim_staff_2020 - 18m
+* @kim_modelling_2021
+* @anagnostou_facs-charm_2022 - 19m
+* @johnson_cost_2021
 

### 2024-08-15 pages/functions.py
feat(functions): add calculate time functions

@@ -1,3 +1,4 @@
+from datetime import datetime
 import numpy as np
 import pandas as pd
 from plotly import graph_objects as go
@@ -195,3 +196,62 @@ def eval_chart(df):
 
     # Show without toolbar
     fig.show(config={'displayModeBar': False})
+
+
+def min_hour(time):
+    '''
+    Creates a string with time in minutes, or hours and minutes
+
+    Parameters:
+    -----------
+    time: int
+        Time in minutes
+
+    Returns:
+    --------
+    string : str
+        String stating the time in minutes, or hours and minutes
+    '''
+    return f'{int(time)}m, or {int(time)//60}h {int(time)%60}m'
+
+
+def calculate_times(used_to_date, times, limit=True):
+    '''
+    Calculates the time used today, total time used, and time remaining.
+
+    Parameters:
+    -----------
+    used_to_date : int
+        Total time used prior to that day in minutes
+    times : list
+        List of tuples with 24h times
+        Example: [('11.01', '12.13'), ('14.45', '14.59')]
+    limit : boolean
+        Whether there is a 40h time limit (and hence, whether to return
+        proportion of time used, and time remaining)
+    '''
+    FMT = '%H.%M'
+    total_min = 0
+    for t in times:
+        # Convert to datetime object
+        h0 = datetime.strptime(t[0], FMT)
+        h1 = datetime.strptime(t[1], FMT)
+        # Find difference in minutes and add to total
+        total_min += (h1 - h0).total_seconds() / 60
+
+    # Time in hours and minutes
+    print(f'Time spent today: {min_hour(total_min)}')
+
+    # Total time used
+    total_used = total_min + used_to_date
+    print(f'Total used to date: {min_hour(total_used)}')
+
+    if limit:
+        # Find time remaining
+        max = 40*60
+        remain_min = max - total_used
+        print(f'Time remaining: {min_hour(remain_min)}')
+
+        # Find proportion out of 40 hours
+        prop = round((total_min+used_to_date)/max*100, 1)
+        print(f'Used {prop}% of 40 hours max')

### 2024-08-15 pages/reflections.qmd
feat(reflections): started on reflections, with 2 alternative versions for layout

@@
 title: "Reflections from reproductions"
+bibliography: ../references.bib
 ---
 
-TODO: Table with reflections from each study
+The table below outlines the factors that helped facilitate reproductions, or that would have been helpful (i.e. their absence was a barrier to the reproduction).
+
+To present this concisely, each facilitator identified has been listed in a table, and I have evaluated for each study whether this was fully met (✅), partially met (🟡), not met (❌) or not applicable (N/A).
+
+# Version 1
+
+## Environment
+
+::: {.callout-note appearance="minimal" collapse=true}
+
+## List required packages
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ |
+
+@shoaib_simulation_2021: Became a time-consuming issue as it took a while to identify a dependency that was needed for the code to work (`greenlet`), and a while longer to realise I had installed another package when the package I needed was in base (`statistics`).
+
+:::
+
+::: {.callout-note appearance="minimal" collapse=true}
+
+## Provide versions
+
+| S | H | L | K | A | J |
+| :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ |
+
+* In one study (@shoaib_simulation_2021) I had to backdate the package versions as the didn't work with the latest
+* @huang_optimizing_2019 -
+* @lim_staff_2020 -
+* @kim_modelling_2021 -
+* @anagnostou_facs-charm_2022 -
+* @johnson_cost_2021
+
+:::
+
+## Running model programmatically
+
+::: {.callout-note appearance="minimal" collapse=true}
+
+## A
+
+:::
+
+# Version 2
+
+Key:
+
+* **S:** @shoaib_simulation_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-shoaib-2022/evaluation/reflections.html" target="_blank">link to reflections</a>
+* **H:** @huang_optimizing_2019  - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-huang-2019/evaluation/reflections.html" target="_blank">link to reflections</a>
+* **L:** @lim_staff_2020 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-lim-2020/evaluation/reflections.html" target="_blank">link to reflections</a>
+* **K:** @kim_modelling_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-kim-2021/evaluation/reflections.html" target="_blank">link to reflections</a>
+* **A:** @anagnostou_facs-charm_2022 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-anagnostou-2022/evaluation/reflections.html" target="_blank">link to reflections</a>
+* **J:** @johnson_cost_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-johnson-2021/evaluation/reflections.html" target="_blank">link to reflections</a>
+
+| Facilitator | S | H | L | K | A | J |
+| - | - | - | - | - | - | - |
+| **Environment** |
+| List required packages | ❌ |
+| Provide versions | ❌ |
+| **Running model programmatically** |
+| |
+| **Run time** |
+| |
+| **Parameters, scenarios and outputs** |
+| All the required outputs are calculated | ❌ |
+| **Output format** |
+| Saves output to a file | ✅ |
+| Easy to figure out how to use output table/s to create tables/figures | ❌ |
+| **Seeds** |
+| |
+| **Code to produce article results** |
+| Provide code to process results into tables | ❌ |
+| Provide code to process results into figures | ❌ |
+| Provide code to calculate results mentioned in the text (but no in tables/figures) | ❌ |
+: {tbl-colwidths="[70, 5, 5, 5, 5, 5, 5]"}
+
+\
+
+## Extra notes
+
+**Environment: List required packages**
+
+@shoaib_simulation_2021: Became a time-consuming issue as it took a while to identify a dependency that was needed for the code to work (greenlet), and a while longer to realise I had installed another package when the package I needed was in base (statistics)
+
+**Environment: Versions**
+
+* In one study (@shoaib_simulation_2021) I had to backdate the package versions as the didn't work with the latest
+* @huang_optimizing_2019 -
+* @lim_staff_2020 -
+* @kim_modelling_2021 -
+* @anagnostou_facs-charm_2022 -
+* @johnson_cost_2021
+
+**Output format: Easy to figure out how to use output table/s to create tables/figures**
+
+* For @shoaib_simulation_2021, there were two alternative results spreadsheets with some duplicate metrics but sometimes differing results between them, which made it a bit confusing to work out what to use
+
+## References

### 2024-08-15 pages/reflections.qmd
feat(reflections): completed for shoaib

--- 2024-08-14 pages/reflections.qmd
@@
 title: "Reflections from reproductions"
+bibliography: ../references.bib
 ---
 
-TODO: Table with reflections from each study
+This page describes the facilitators for each reproduction (and, conversely, the barriers to the reproduction, in their absence).
+With each section, I have created a table which evaluates whether the facilitators were fully met (✅), partially met (🟡), not met (❌) or not applicable (N/A) for each study.
+
+Links to each study:
+
+* @shoaib_simulation_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-shoaib-2022/evaluation/reflections.html" target="_blank">link to reflections</a>
+* @huang_optimizing_2019  - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-huang-2019/evaluation/reflections.html" target="_blank">link to reflections</a>
+* @lim_staff_2020 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-lim-2020/evaluation/reflections.html" target="_blank">link to reflections</a>
+* @kim_modelling_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-kim-2021/evaluation/reflections.html" target="_blank">link to reflections</a>
+* @anagnostou_facs-charm_2022 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-anagnostou-2022/evaluation/reflections.html" target="_blank">link to reflections</a>
+* @johnson_cost_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-johnson-2021/evaluation/reflections.html" target="_blank">link to reflections</a>
+
+## Environment
+
+::: {.callout-note icon=false collapse=true}
+
+## List required packages
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ |
+
+@shoaib_simulation_2021: Became a time-consuming issue as it took a while to identify a dependency that was needed for the code to work (`greenlet`), and a while longer to realise I had installed another package when the package I needed was in base (`statistics`).
+
+:::
+
+::: {.callout-note icon=false collapse=true}
+
+## Provide versions
+
+| S | H | L | K | A | J |
+| :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ |
+
+In @shoaib_simulation_2021 I had to backdate the package versions as the didn't work with the latest.
+
+<!-- TODO: Note whether it not it worked with latest versions/versions used, if the versions needed weren't provided.
+Explain the backdating v.s.
+not backdating stuff with R (but that might fall under providing the environment itself?) -->
+
+:::
+
+## Structure of code and scripts
+
+::: {.callout-warning icon=false collapse=true}
+
+## Model is designed to be run programmatically
+
+| S | H | L | K | A | J |
+| :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ |
+
+@shoaib_simulation_2021: Model was designed so that you directly change parameters in the script itself.
+This meant you couldn't run multiple versions of the model using the same script.
+It also meant hidden errors were more likely (e.g.
+if miss changing a parameter somewhere, or input the wrong parameters and don’t realise).
+
+:::
+
+::: {.callout-warning icon=false collapse=true}
+
+## Don't hard code parameters that you will want to change for scenario analyses
+
+| S | H | L | K | A | J |
+| :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ |
+
+@shoaib_simulation_2021: Parameters were often hard-coded, and so it took time to spot where these were and correctly adjust them to be modifiable inputs.
+
+:::
+
+::: {.callout-warning icon=false collapse=true}
+
+## Avoid large amounts of code duplication
+
+| S | H | L | K | A | J |
+| :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ |
+
+@shoaib_simulation_2021: The model often contained very similar code before or after warm-up.
+This has the potential to introduce mistakes - with a suspected (although unconfirmed) mistake being that the lower boundary for the doctor consultation times in configuration 1 differed before and after warm-up.
+
+:::
+
+## Run time
+
+::: {.callout-important icon=false collapse=true}
+
+## Quicker models are easier to work with
+
+I have not evaluated like as a criteria, as a long run time is not inherently a bad thing.
+However, I definitely found that the run time of models had a big impact on how easy it was to reproduce results as longer run times meant it was tricky (or even impossible) to run in the first place, or tricky to re-run.
+
+The studies where I made adjustments were:
+
+* @shoaib_simulation_2021: Add parallel processing and ran fewer replications
+
+:::
+
+## Parameters, scenarios and outputs
+
+::: {.callout-tip icon=false collapse=true}
+
+## Provide code for all scenarios
+
+| S | H | L | K | A | J |
+| :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ |
+
+@shoaib_simulation_2021: There were several instances where it took quite a while to understand how and where to modify the code in order to run scenarios (e.g.
+no arrivals, transferring admin work, reducing doctor intervention in deliveries).
+
+:::
+
+::: {.callout-tip icon=false collapse=true}
+
+## All the required outputs are calculated
+
+| S | H | L | K | A | J |
+| :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ |
+
+@shoaib_simulation_2021: Had to add some outputs and calculations (e.g. proportion of childbirth cases referred, standard deviation)
+
+:::
+
+::: {.callout-tip icon=false collapse=true}
+
+## If not provided in the script, then clearly present all parameters in the paper
+
+| S | H | L | K | A | J |
+| :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ |
+
+@shoaib_simulation_2021: Although there was a scenario table, this did not include all the parameters I would need to change.
+It was more challenging to identify parameters that were only described in the body of the article.
+There were also some discrepancies in parameters between the main text of the article, and the tables and figures.
+Some scenarios were quite ambiguous/unclear from their description in the text, and I initially misunderstood the required parameters for the scenarios.
+
+:::
+
+::: {.callout-tip icon=false collapse=true}
+
+## Provide all the required parameters
+
+| S | H | L | K | A | J |
+| :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ |
+
+@shoaib_simulation_2021: Some parameters that could not be calculated were not provided - ie. what consultation boundaries to use when mean length of doctor consultation was 2.5 minutes
+
+:::
+
+::: {.callout-tip icon=false collapse=true}
+
+## If will need to process parameters, provide required calculations
+
+| S | H | L | K | A | J |
+| :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ |
+
+@shoaib_simulation_2021: It was unclear how to estimate inter-arrival time
+
+:::
+
+## Output format
+
+::: {.callout-caution icon=false collapse=true}
+
+## Saves output to a file
+
+| S | H | L | K | A | J |
+| :-: | :-: | :-: | :-: | :-: | :-: |
+| ✅ |
+
+:::
+
+::: {.callout-caution icon=false collapse=true}
+
+## Easy to figure out how to use output table/s to create tables/figures
+
+| S | H | L | K | A | J |
+| :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ |
+
+For @shoaib_simulation_2021, there were two alternative results spreadsheets with some duplicate metrics but sometimes differing results between them, which made it a bit confusing to work out what to use.
+
+:::
+
+## Seeds
+
+::: {.callout-note icon=false collapse=true}
+
+## Use seeds to control stochasticity
+
+| S | H | L | K | A | J |
+| :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ |
+
+@shoaib_simulation_2021: The lack of seeds wasn't actually a barrier to the reproduction though due to the replication number.
+I later add seeds so my results could be reproduced, and found that the ease of setting seeds with salabim was a greater facilitator to the work.
+I only had to change one or two lines of code to then get consistent results between runs (unlike other simulation software like SimPy where you have to consider the use of seeds by different sampling functions).
+Moreover, by default, salabim would have set a seed (although overridden by original authors to enable them to run replications).
+
+:::
+
+## Code to produce article results
+
+::: {.callout-warning icon=false collapse=true}
+
+## Provide code to process results into tables
+
+| S | H | L | K | A | J |
+| :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ |
+
+:::
+
+::: {.callout-warning icon=false collapse=true}
+
+## Provide code to process results into figures
+
+| S | H | L | K | A | J |
+| :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ |
+
+:::
+
+::: {.callout-warning icon=false collapse=true}
+
+## Provide code to calculate results mentioned in the text (but no in tables/figures)
+
+| S | H | L | K | A | J |
+| :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ |
+
+:::
+
+## Other
+
+Include tick marks/grid lines on figures, so it is easier to read across and judge whether a result is above or below a certain Y value.
+
+## References

### 2024-08-15 pages/reflections.qmd
feat(reflections): add reflections from Huang 2019 and Lim 2020

@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ |
+| ❌ | ❌ | ✅ |
 
@@
 
-| S | H | L | K | A | J |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ |
+| ❌ | ❌ | 🟡 |
 
@@
 
-<!-- TODO: Note whether it not it worked with latest versions/versions used, if the versions needed weren't provided.
-Explain the backdating v.s.
-not backdating stuff with R (but that might fall under providing the environment itself?) -->
+@huang_optimizing_2019 was an R model.
+As no versions were provided, I initially tried to create an environment with R and package versions that were prior to the article publication date.
+However, I had great difficulties implementing this with R, and never managed to successfully do this.
+This was related to:
+
+* The difficulty of switching between R versions
+* Problems in finding available/a source for specific package versions for specific versions or R
+
+@lim_staff_2020: Provides major Python version, but chose minor and package versions based on article publication date.
 
@@
 
+## Model is provided in a "runnable" format
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: |
+| ✅ | ❌ |
+
+@huang_optimizing_2019: The code provided was to run the model as part of a web application, but the paper was not focused on this application, but instead on specific model scenarios, so I had to extract the model code and transform it into a format that was "runnable" as an R script/notebook.
+
+:::
+
+::: {.callout-warning icon=false collapse=true}
+
 ## Model is designed to be run programmatically
 
-| S | H | L | K | A | J |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ |
+| ❌ | ✅ | 🟡 |
 
@@
 if miss changing a parameter somewhere, or input the wrong parameters and don’t realise).
+
+@huang_optimizing_2019: Model was set up as a function, with many of the required parameters already set as inputs to that function.
+
+@lim_staff_2020: Structure of provided code (model largely in functions) made it easier when making changes to run it programmatically.
+However, it wasn't all in functions, and the model itself was designed to run a single scenario, so I did need to change to a function that can call to easily vary parameters and run scenarios programmatically.
+<!-- TODO: Consider whether I have evaluated this correctly -->
 
@@
 
-| S | H | L | K | A | J |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ |
+| ❌ | ❌ | ❌ |
 
 @shoaib_simulation_2021: Parameters were often hard-coded, and so it took time to spot where these were and correctly adjust them to be modifiable inputs.
+
+<!-- TODO: Double-check this is marked correctly for Huang... I think it is, as some were not hard coded but some were... potentialy could say partially... -->
+
+@lim_staff_2020: Several parameters were hard coded
 
@@
 
-| S | H | L | K | A | J |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
 | :-: | :-: | :-: | :-: | :-: | :-: |
@@
 
-## Run time
+::: {.callout-warning icon=false collapse=true}
+
+## Include sufficient comments in the code
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: |
+| <!--TODO--> | ❌ | ✅ |
+
+@huang_optimizing_2019: Would have benefitted from more comments, as it took some time to decipher and ensure I have correctly understood code as it uses lots of abbreviations.
+
+@lim_staff_2020: Lots of comments in the code (including doc-string-style comments at the start of functions) that aided understanding of how it worked.
+
+:::
+
+## Run time and memory usage
 
@@
 * @shoaib_simulation_2021: Add parallel processing and ran fewer replications
+* <!-- TODO: Check run time of Huang -->
+* @lim_staff_2020: Add parallel processing
+
+:::
+
+::: {.callout-important icon=false collapse=true}
+
+## For slow models, it's very important to state the expected run time
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: |
+| <!----> | <!----> | ❌ |
+
+For long models with no statement, it can take a while to realise that it's not an error in the code or anything, but actually just a long run time!
+And hard to know how long to expect, and whether it is without the capacities of your machine and so on.
+
+:::
+
+::: {.callout-important icon=false collapse=true}
+
+## For computationally expensive models, state memory usage, and potentially include alternatives for running it on machines without the capacity for it
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: |
+| <!----> | <!----> | <!----> |
 
@@
 
-| S | H | L | K | A | J |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ |
+| ❌ | ❌ | ❌ |
 
@@
 no arrivals, transferring admin work, reducing doctor intervention in deliveries).
+
+@huang_optimizing_2019: Set up a notebook to programmatically run the model scenarios.
+It took alot of work to modify and write code that could run the scenarios, and I often made mistakes in my interpretation for the implementation of scenarios, which could be avoided if code for those scenarios was provided.
+
+@lim_staff_2020: Several parameters or scenarios were not incorporated in the code, and had to be added (e.g.
+with conditional logic to skip or change code run, removing hard-coding, adding parameters to existing).
 
@@
 
-## All the required outputs are calculated
+## All the required outputs are calculated/provided
 
-| S | H | L | K | A | J |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ |
+| ❌ | <!--TODO--> | ❌ |
 
 @shoaib_simulation_2021: Had to add some outputs and calculations (e.g. proportion of childbirth cases referred, standard deviation)
+
+@lim_staff_2020: The model script provided was only set up to provide results from days 7, 14 and 21. The figures require daily results, so I needed to modify the code to output that.
 
@@
 
-## If not provided in the script, then clearly present all parameters in the paper
+## Include correct parameters in the script (even if just for one scenario)
 
-| S | H | L | K | A | J |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ |
+| <!--TODO--> | ❌ |
+
+@huang_optimizing_2019: The baseline model in the script did not match the baseline model in the paper, so had to modify parameters.
+
+:::
+
+::: {.callout-tip icon=false collapse=true}
+
+## Provide all the required parameters
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ❌ | ❌ |
+
+@shoaib_simulation_2021: Some parameters that could not be calculated were not provided - ie. what consultation boundaries to use when mean length of doctor consultation was 2.5 minutes
+
+@huang_optimizing_2019: In this case, patient arrivals and resource numbers were listed in the paper, and there were several discprepancies between this and the provided code.
+However, for many of the model parameters like length of appointment, these were not mentioned in the paper, and so it was not possible to confirm whether or not those were correct.
+
+@lim_staff_2020: For Figure 5, had to guess the value for `staff_per_shift`.
+
+:::
+
+::: {.callout-tip icon=false collapse=true}
+
+## If not provided in the script, then *clearly* present all parameters in the paper
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | | ✅ |
 
@@
 
-## Provide all the required parameters
-
-| S | H | L | K | A | J |
-| :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ |
-
-@shoaib_simulation_2021: Some parameters that could not be calculated were not provided - ie. what consultation boundaries to use when mean length of doctor consultation was 2.5 minutes
-
-:::
-
-::: {.callout-tip icon=false collapse=true}
-
 ## If will need to process parameters, provide required calculations
 
-| S | H | L | K | A | J |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ |
+| ❌ | ✅ |
 
 @shoaib_simulation_2021: It was unclear how to estimate inter-arrival time
+
+@huang_optimizing_2019: The calculations for inter-arrival times were provided in the code, and the inputs to the code were the number of arrivals, as reported in the paper, and so making it easy to compare those parameters and check if numbers were correct or not.
 
@@
 
-| S | H | L | K | A | J |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ✅ |
+| ✅ | <!----> | ❌ |
 
@@
 
-## Easy to figure out how to use output table/s to create tables/figures
+## Understandable output tables
 
-| S | H | L | K | A | J |
+E.g. Easy to figure out how to use output table/s to create tables/figures.
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
 | :-: | :-: | :-: | :-: | :-: | :-: |
@@
 Moreover, by default, salabim would have set a seed (although overridden by original authors to enable them to run replications).
+
+@huang_optimizing_2019: It would have been beneficial to include seeds, as there was a fair amount of variability, so with seeds I could then I could be sure that my results do not differ from the original simply due to randomness.
+
+@lim_staff_2020: The results obtained looked very similar to the original article, with minimal differences that I felt to be within the expected variation from the model stochasticity.
+However, if seeds had been present, we would have been able to say with certainty.
+I did not feel I needed to add seeds during the reproduction to get the same results.
 
@@
 
-| S | H | L | K | A | J |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ |
+| ❌ | N/A | <!--TODO--> |
+
+<!--TODO: Lim 2020... I think from memory that this output tables  similar to the paper, but I then changed them as that format was difficult to compare/work with -->
 
@@
 
-| S | H | L | K | A | J |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ |
+| ❌ | ❌ | ❌ |
+
+@huang_optimizing_2019: Had to write code from scratch.
+For one of the figures, it would have been handy if informed that plot was produced by a simmer function (as didn’t initially realise this).
+It also took a bit of time for me to work out how to transform the figure axes as this was not mentioned in the paper (and no code was provided for these).
+It was also unclear and a bit tricky to work out how to standardise the density in the figures (since it is only described in the text and no formula/calculations are provided there or in the code).
+<!-- TODO: Consider whether this should be split into another box (i.e.
+about providing the processing?) -->
 
@@
 
-## Provide code to calculate results mentioned in the text (but no in tables/figures)
+## Provide code to calculate in-text results
 
-| S | H | L | K | A | J |
+By "in-text results", I am referred to results that are mentioned in the text but not included in/cannot be deduced from any of the tables or figures.
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ |
+| ❌ | ❌ | N/A |
 
@@
 
+For @lim_staff_2020, the simplicity of the model structure and code, and simplicity and similarity between figures, really helped to facilitate the reproduction.
+
+<!-- TODO: Check if any of these should be above.
+e.g.
+might want to put simplicity in a same way as i put run time - as simplicity is not inherently required (its about focus of project partly) BUT it is really handy (and it is always a good principle to hold) -->
+
 ## References

### 2024-08-15 pages/reflections.qmd
feat(reflections): add reflections from Kim et al. 2021

@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ✅ |
+| ❌ | ❌ | ✅ | ✅ |
 
 @shoaib_simulation_2021: Became a time-consuming issue as it took a while to identify a dependency that was needed for the code to work (`greenlet`), and a while longer to realise I had installed another package when the package I needed was in base (`statistics`).
+
+@kim_modelling_2021: Provides commands to install packages required at the start of scripts, which I could then easily base renv on automatically (as it detects them).
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | 🟡 |
+| ❌ | ❌ | 🟡 | 🟡 |
 
@@
 @lim_staff_2020: Provides major Python version, but chose minor and package versions based on article publication date.
+
+@kim_modelling_2021: States version of R but not package.
+Due to prior issues with backdating R, used latest versions.
+There were no issues using the latest versions of R and packages, but if there had been, it would be important to know what versions had previously been used and worked.
 
@@
 * @lim_staff_2020: Add parallel processing
+* @kim_modelling_2021: Reduced number of people in simulation, and switched from serial to the provided parallel option.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| <!----> | <!----> | ❌ |
+| <!----> | <!----> | ❌ | ❌ | N/A |
 
@@
 And hard to know how long to expect, and whether it is without the capacities of your machine and so on.
+
+@anagnostou_facs-charm_2022: Very quick! Seconds!
 
@@
 | <!----> | <!----> | <!----> |
+
+<!--TODO: Figure where to put this...
+Kim et al.
+2021: reproduction facilitated by provision of option to run model with parallel processing.
+However, would've been beneficial to provide suggestions for how to run model quicker on lower spec machine (e.g.
+lowering number of people) -->
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | <!--TODO--> | ❌ |
+| ❌ | <!--TODO--> | ❌ | ❌ |
 
@@
 @lim_staff_2020: The model script provided was only set up to provide results from days 7, 14 and 21. The figures require daily results, so I needed to modify the code to output that.
+
+@kim_modelling_2021: Had to write code to find aorta sizes of people with AAA-related deaths.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ✅ |
+| ❌ | ✅ | <!--TODO--> |
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ✅ | <!----> | ❌ |
+| ✅ | <!--TODO--> | ❌ |
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ |
+| ❌ | ❌ | ❌ | ✅ |
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | N/A | <!--TODO--> |
+| ❌ | N/A | <!--TODO--> | ❌ |
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ |
+| ❌ | ❌ | ❌ | ❌ |
 
@@
 For @lim_staff_2020, the simplicity of the model structure and code, and simplicity and similarity between figures, really helped to facilitate the reproduction.
+For @kim_modelling_2021, reproduction was facilitated by having relatively simple and repetitive plots which were easy to understand and create.
+
+Fix errors in script.
+For @kim_modelling_2021, an error appears to have been introduced with the aoorta diameter thresholds by switching between nested and unnested lists, which I’m anticipating was unresolved due to the long run times of the model meaning they weren’t all run in sequence at the end.
 

### 2024-08-15 pages/reflections.qmd
feat(reflections): add reflections from anagnostou 2022

@@
 With each section, I have created a table which evaluates whether the facilitators were fully met (✅), partially met (🟡), not met (❌) or not applicable (N/A) for each study.
+
+<!--TODO: Add Johnson et al. 2021 reflections once have finished reproduction -->
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ✅ | ✅ |
+| ❌ | ❌ | ✅ | ✅ | ✅ |
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | 🟡 | 🟡 |
+| ❌ | ❌ | 🟡 | 🟡 | ✅ |
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ✅ | ❌ |
+| ✅ | ❌ | <!--TODO--> | <!--TODO--> | ✅ |
 
@@
 * @kim_modelling_2021: Reduced number of people in simulation, and switched from serial to the provided parallel option.
+* @anagnostou_facs-charm_2022: Model was super quick which made it really easy to run and re-run each time
+
+For @kim_modelling_2021, an error appears to have been introduced with the aoorta diameter thresholds by switching between nested and unnested lists, which I’m anticipating was unresolved due to the long run times of the model meaning they weren’t all run in sequence at the end.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| <!----> | <!----> | <!----> |
+| <!----> | <!----> | <!----> | <!--TODO--> | N/A |
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ |
+| ❌ | ❌ | ❌ | <!--TODO--> | N/A |
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | <!--TODO--> | ❌ | ❌ |
+| ❌ | <!--TODO--> | ❌ | ❌ | ✅ |
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| <!--TODO--> | ❌ |
+| <!--TODO--> | ❌ | <!--TODO--> | <!--TODO--> | ✅ |
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ |
+| ❌ | ❌ | ❌ | <!--TODO--> | ✅ |
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | | ✅ |
+| ❌ | <!--TODO--> | ✅ | <!--TODO--> | N/A |
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ✅ | <!--TODO--> |
+| ❌ | ✅ | <!--TODO--> | <!--TODO--> | N/A |
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ✅ | <!--TODO--> | ❌ |
+| ✅ | <!--TODO--> | ❌ | <!--TODO--> | ✅ |
+
+@anagnostou_facs-charm_2022: Outputs to `OUT_STATS.csv`.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ |
+| ❌ | <!--TODO--> | <!--TODO--> | <!--TODO--> | ✅ |
 
 For @shoaib_simulation_2021, there were two alternative results spreadsheets with some duplicate metrics but sometimes differing results between them, which made it a bit confusing to work out what to use.
+
+@anagnostou_facs-charm_2022: The layout of the results spreadsheet was simple, understandable and easy to read, making it easy to adapt into figures.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | ✅ |
+| ❌ | ❌ | ❌ | ✅ | ✅ |
 
@@
 I did not feel I needed to add seeds during the reproduction to get the same results.
+
+@anagnostou_facs-charm_2022: The authors included a random seed so the results I got were identical to the original (so no need for any subjectivity in deciding whether its similar enough, as I could perfectly reproduce).
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | ❌ |
+| ❌ | ❌ | ❌ | ❌ | ❌ |
 
@@
 
+## Documentation
+
+::: {.callout-warning icon=false collapse=true}
+
+## Include instructions on how to run the model/script
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: |
+| <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | ✅ |
+
+@anagnostou_facs-charm_2022: Clear README with instructions on how to run the model was really helpful.
+
+:::
+
 ## Other
@@
 For @kim_modelling_2021, reproduction was facilitated by having relatively simple and repetitive plots which were easy to understand and create.
+For @anagnostou_facs-charm_2022, the figures were simple (just means and CI which are already calculated).
 
@@
 For @kim_modelling_2021, an error appears to have been introduced with the aoorta diameter thresholds by switching between nested and unnested lists, which I’m anticipating was unresolved due to the long run times of the model meaning they weren’t all run in sequence at the end.
+<!--TODO: Have put in run time, or does it need seperate place -->
+
+@anagnostou_facs-charm_2022: Although not needed for the reproduction itself, when I tried to amend the name and location of the csv file output the model for use in tests, this was very tricky to do as it was hard coded into the scripts and I found difficult to amend due to how the model is run and set up.
+<!-- TODO: Fall under hard coding?
+Or output file flexibility?
+-->
+
+@anagnostou_facs-charm_2022: Included data dictionary for input parameters. Although I didn’t need this, this would have been great if I needed to change the input parameters at all.
 

### 2024-08-19 pages/reflections.qmd
docs(refections): further completed the reflection sections for each paper

@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ✅ | ✅ | ✅ |
+| ❌ | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> |
 
-@shoaib_simulation_2021: Became a time-consuming issue as it took a while to identify a dependency that was needed for the code to work (`greenlet`), and a while longer to realise I had installed another package when the package I needed was in base (`statistics`).
+@shoaib_simulation_2021: Not met.
+This became a time-consuming issue as it took a while to identify a dependency that was needed for the code to work (`greenlet`) (based on reading the documentation for `salabim`), and a while longer to realise I had installed another package when the package I needed was in base (`statistics`).
 
-@kim_modelling_2021: Provides commands to install packages required at the start of scripts, which I could then easily base renv on automatically (as it detects them).
+@huang_optimizing_2019: Not met. However, this was fairly easily resolved based on imports to `.R` script, and then on extra imports suggested by RStudio when I tried and failed to run the script.
+
+@lim_staff_2020: Partially met. The only packages needed (`numpy` and `pandas`) are mentioned in the paper (although only listed as imports in the script).
+
+@kim_modelling_2021: Fully met. Provides commands to install packages required at the start of scripts, which I could then easily base renv on automatically (as it detects them).
+
+@anagnostou_facs-charm_2022: Fully met. Provides `requirements.txt`
+
+@johnson_cost_2021: <!--TODO-->
+
+**Reflections:**
+
+* The `import` statements can be sufficient in indicating all the packages required but this is not always the case if there are "hidden"/unmentioned dependencies that don't get imported
+* There are various options for listing the packages (e.g. comprehensive import statements, installation lines in the script, environment files).
+* This was a common issue.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | 🟡 | 🟡 | ✅ |
+| ❌ | ❌ | 🟡 | 🟡 | 🟡 | <!--TODO--> |
 
-In @shoaib_simulation_2021 I had to backdate the package versions as the didn't work with the latest.
+@shoaib_simulation_2021: Not met. I had to backdate the package versions as the model didn't work with the latest.
 
-@huang_optimizing_2019 was an R model.
-As no versions were provided, I initially tried to create an environment with R and package versions that were prior to the article publication date.
+@huang_optimizing_2019: Not met.
+I initially tried to create an environment with R and package versions that were prior to the article publication date.
 However, I had great difficulties implementing this with R, and never managed to successfully do this.
@@
 
-@lim_staff_2020: Provides major Python version, but chose minor and package versions based on article publication date.
+@lim_staff_2020: Partially met. Provides major Python version, but chose minor and the package versions based on article publication date.
 
-@kim_modelling_2021: States version of R but not package.
+@kim_modelling_2021: Partially met.
+States version of R but not package.
 Due to prior issues with backdating R, used latest versions.
 There were no issues using the latest versions of R and packages, but if there had been, it would be important to know what versions had previously been used and worked.
+
+@anagnostou_facs-charm_2022: Partially met (depending on how strict you are being).
+The Python version was stated in the paper, and the simpy version was stated in the complementary app repository (although neither were mentioned in the model repository itself).
+
+@johnson_cost_2021: <!--TODO-->
+
+**Reflections:**
+
+* Models will sometimes work with the latest versions of packages, but likewise, you will sometimes need to backdate as it no longer works with the latest
+* For Python, it was very easy to "backdate" the python and package versions. However, I found this very difficult to in R, and ended up always using the latest versions.
+* Versions are sometimes provided elsewhere (e.g. in paper, in other repositories), but would be handy to be in model repository itself
+* This was a very common issue.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ✅ | ❌ | <!--TODO--> | <!--TODO--> | ✅ |
+| ✅ | ❌ | ✅ | ✅ | ✅ | <!--TODO--> |
 
-@huang_optimizing_2019: The code provided was to run the model as part of a web application, but the paper was not focused on this application, but instead on specific model scenarios, so I had to extract the model code and transform it into a format that was "runnable" as an R script/notebook.
+@shoaib_simulation_2021: Fully met. Provided as a single `.py` file which ran model with function `main()`.
+
+@huang_optimizing_2019: Not met.
+The model code was provided within the code for a web application, but the paper was not focused on this application, and instead on specific model scenarios.
+I had to extract the model code and transform it into a format that was "runnable" as an R script/notebook.
+
+@lim_staff_2020: Fully met. Provided as a single `.py` file which ran the model with a for loop.
+
+@kim_modelling_2021: Fully met. Has seperate `.R` scripts for each scenario which ran the model by calling functions from elsewhere in repository.
+
+@anagnostou_facs-charm_2022: Fully met. Can run model from command line.
+
+@johnson_cost_2021: <!--TODO-->
+
+**Reflections:**
+
+* If you are presenting the results of a model, then provide the code for that model in a "runnable" format.
+* This was an uncommon issue.
 
@@
 
+In other words, there is some provision for re-running the model with different parameters without changing the code for the model itself.
+
 | @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ✅ | 🟡 |
+| ❌ | ✅ | ✅ | ✅ | ✅ | <!--TODO--> |
 
-@shoaib_simulation_2021: Model was designed so that you directly change parameters in the script itself.
+@shoaib_simulation_2021: Not met.
+The model is set up as classes and run using a function.
+However, it is not designed to allow any variation in inputs.
+Everything uses default inputs, and it designed in such a way that - if you wish to vary model parameters - you need to directly change these in the script itself.
 This meant you couldn't run multiple versions of the model using the same script.
@@
 
-@huang_optimizing_2019: Model was set up as a function, with many of the required parameters already set as inputs to that function.
+@huang_optimizing_2019: Fully met. Model was set up as a function, with many of the required parameters already set as "changeable" inputs to that function.
 
-@lim_staff_2020: Structure of provided code (model largely in functions) made it easier when making changes to run it programmatically.
-However, it wasn't all in functions, and the model itself was designed to run a single scenario, so I did need to change to a function that can call to easily vary parameters and run scenarios programmatically.
-<!-- TODO: Consider whether I have evaluated this correctly -->
+@lim_staff_2020: Fully met.
+The model is created from a series of functions and run with a for loop that iterates through different parameters.
+As such, the model is able to be run programmatically (within that for loop, which varied e.g.
+staff per shift and so on and re-ran the model).
+
+@kim_modelling_2021: Fully met. Each scenario is an R script which states different parameters and then calls functions to run model.
+
+@anagnostou_facs-charm_2022: Fully met. Change inputs in input `.csv` files.
+
+@johnson_cost_2021: <!--TODO-->
+
+**Reflections:**
+
+* Design model so that you can re-run it with different parameters without needing to make changes to the model code itself.
+    * This allows you to run multiple versions of the model with the same script.
+    * It also reduces the likelihood of missing errors (e.g. if miss changing an input parameter somewhere, or input the wrong parameters and don't realise).
+* This was an uncommon issue.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ |
+| ❌ | 🟡 | ❌ | ✅ | N/A | <!--TODO--> |
 
-@shoaib_simulation_2021: Parameters were often hard-coded, and so it took time to spot where these were and correctly adjust them to be modifiable inputs.
+@shoaib_simulation_2021: Not met.
+Although some parameters sat "outside" of the model within the `main()` function (and hence were more "changeable", even if not "changeable" inputs to that function, but changed directly in script).
+However, many of the other parameters were hard-coded within the model itself.
+It took time to spot where these were and correctly adjust them to be modifiable inputs.
 
-<!-- TODO: Double-check this is marked correctly for Huang... I think it is, as some were not hard coded but some were... potentialy could say partially... -->
+@huang_optimizing_2019: Partially met.
+Pretty much all of the parameters that we wanted to change were not hard coded and were instead inputs to the model function `simulate_nav()`.
+However, I did need to add an `exclusive_use` scenario which conditionally changed `ir_resources`, but that is the only exception.
+I also add `ed_triage` as a changeable input but didn't end up needing that to reproduce any results (was just part of troubleshooting).
+I also
 
-@lim_staff_2020: Several parameters were hard coded
+@lim_staff_2020: Not met. Some parameters were not hard coded within the model, but lots of them were not.
+
+@kim_modelling_2021: Fully met. All model parameters could be varied from "outside" the model code itself, as they were provided as changeable inputs to the model.
+
+@anagnostou_facs-charm_2022: N/A as no scenarios.
+
+@johnson_cost_2021: <!--TODO-->
+
+**Reflections:**
+
+* It can be quite difficult to change parameters that are hard coded into the model. Ideally, all the parameters that a user might want to change should be easily changeable and not hard coded.
+* This is a somewhat common issue.
+* There is overlap between this and whether the code for scenarios is provided (as typically, the code for scenario is conditionally changing parameter values, although this can be facilitated by not hard coding the parameters, so you call need to change the values from "outside" the model code, rather than making changes to the model functions themselves).
+Hence, have included as two seperate reflections.
 

### 2024-08-19 pages/reflections.qmd
docs(reflections): completed some more reflections sections for each of the papers

@@
 
-## Model is designed to be run programmatically
-
-In other words, there is some provision for re-running the model with different parameters without changing the code for the model itself.
+## Model is designed to be run programmatically (i.e. can run model with different parameters without needing to change the model code)
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ |
+| ❌ | ✅ | ✅ | ❌ | ✅ | <!--TODO--> |
 
-@shoaib_simulation_2021: The model often contained very similar code before or after warm-up.
+@shoaib_simulation_2021: Not met.
+The model often contained very similar blocks of code before or after warm-up.
 This has the potential to introduce mistakes - with a suspected (although unconfirmed) mistake being that the lower boundary for the doctor consultation times in configuration 1 differed before and after warm-up.
+
+@huang_optimizing_2019: Fully met.
+
+@lim_staff_2020: Fully met.
+
+@kim_modelling_2021: Not met.
+There was alot of duplication when running each scenario (e.g.
+repeated calls to `Eventsandcosts`, and repeatedly defining the same parameters).
+This meant, if changing a parameter that you want to be consistent between all the scripts (e.g.
+number of persons), you had to change each of the scripts one by one.
+
+@johnson_cost_2021: Fully met.
+
+@johnson_cost_2021: <!--TODO-->
+
+**Reflections:** Large amounts of code duplication are non-ideal as they can:
+
+* Make code less readable
+* Make it trickier to change universal parameters
+* Increase the likelihood of introducing mistakes
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| <!--TODO--> | ❌ | ✅ |
+| ❌ | ❌ | ✅ | 🟡 | 🟡 | <!--TODO--> |
 
-@huang_optimizing_2019: Would have benefitted from more comments, as it took some time to decipher and ensure I have correctly understood code as it uses lots of abbreviations.
+@shoaib_simulation_2021 and @huang_optimizing_2019: Not met.
+Would have benefitted from more comments, as it took some time to ensure I have correctly understood code, particularly if they used lots of abbreviations.
 
-@lim_staff_2020: Lots of comments in the code (including doc-string-style comments at the start of functions) that aided understanding of how it worked.
+@lim_staff_2020: Fully met. There were lots of comments in the code (including doc-string-style comments at the start of functions) that aided understanding of how it worked.
+
+@kim_modelling_2021: Partially met.
+Didn't have any particular issues in working out the code.
+There are sufficient comments in the scenario scripts and at the start of the model scripts, although within the model scripts, there were sometimes quite dense sections of code that would likely benefit from some additional comments.
+
+@anagnostou_facs-charm_2022: Partially met.
+Didn't have to delve into the code much, so can't speak from experience as to whether the comments were sufficient.
+From looking through the model code, several scripts have lots of comments and docstrings for each function, but some do not.
+
+@johnson_cost_2021: <!--TODO-->
+
+**Reflections:**
+
+* With increasing code complexity, the inclusion of sufficient comments becomes increasingly important, as it can otherwise be quite time consuming to figure out how to fix and change sections of code
+* Define abbreviations used within the code
+* Good to have consistent comments and docstrings throughout (i.e. on all scripts, on not just some of them)
 
@@
 * @shoaib_simulation_2021: Add parallel processing and ran fewer replications
-* <!-- TODO: Check run time of Huang -->
+* @huang_optimizing_2019: No changes made.
 * @lim_staff_2020: Add parallel processing
@@
 * @anagnostou_facs-charm_2022: Model was super quick which made it really easy to run and re-run each time
+* @johnson_cost_2021: <!--TODO-->
 
 For @kim_modelling_2021, an error appears to have been introduced with the aoorta diameter thresholds by switching between nested and unnested lists, which I’m anticipating was unresolved due to the long run times of the model meaning they weren’t all run in sequence at the end.
+
+**Reflections:**
+
+* Reduce model run time if possible as it makes it easier to work with, and facilitates doing full re-runs of all scenarios (which can be important with code changes, etc).
+* Common issue (to varying degrees - i.e. taking 20 minutes, up to taking several hours).
 
@@
 
-## For slow models, it's very important to state the expected run time
+## For slow models, state the expected run time
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| <!----> | <!----> | ❌ | ❌ | N/A |
+| 🟡 | ❌ | ❌ | ❌ | N/A | <!--TODO--> |
 
-For long models with no statement, it can take a while to realise that it's not an error in the code or anything, but actually just a long run time!
+@shoaib_simulation_2021: Partially met. Run time stated in paper but not repository.
+
+@huang_optimizing_2019: Not met.
+
+@lim_staff_2020: Not met.
+
+@kim_modelling_2021: Not met. A prior paper describing the model development mentions the run time, but not the current paper or repository.
+
+@anagnostou_facs-charm_2022: Not applicable.
+Very quick!
+Seconds!
+So not particularly relevant - although, you could argue, potentially still important if there were some error that made it look like the model were running continuously (e.g.
+stuck in a loop) - although this is relatively unlikely.
+
+@johnson_cost_2021: <!--TODO-->
+
+**Reflections:**
+
+* For long models with no statement, it can take a while to realise that it's not an error in the code or anything, but actually just a long run time!
 And hard to know how long to expect, and whether it is without the capacities of your machine and so on.
-
-@anagnostou_facs-charm_2022: Very quick! Seconds!
+* Common issue.
 
@@
 
-## For computationally expensive models, state memory usage, and potentially include alternatives for running it on machines without the capacity for it
+## For computationally expensive models, state memory usage and provide alternatives for lower spec machines
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| <!----> | <!----> | <!----> | <!--TODO--> | N/A |
+| N/A | N/A | N/A | ❌ | N/A | <!--TODO--> |
 
-<!--TODO: Figure where to put this...
-Kim et al.
-2021: reproduction facilitated by provision of option to run model with parallel processing.
-However, would've been beneficial to provide suggestions for how to run model quicker on lower spec machine (e.g.
-lowering number of people) -->
+@shoaib_simulation_2021, @huang_optimizing_2019, and @lim_staff_2020: Not applicable. Didn't find it to be too computationally expensive for my machine.
+
+@kim_modelling_2021: Not met.
+Unable to run on my machine (`serial` took too long to run (would have to leave laptop on for many many hours which isn't feasible), and `parallel` was too computationally expensive and crashed the machine (with the original number of people)).
+This is not mentioned in the repository or paper, but only referred to in a prior publication.
+Would've been handy if it included suggestions like reducing number of people and so on (which is what I had to do to feasibly run it).
+
+@anagnostou_facs-charm_2022: Not applicable. Runs in seconds.
+
+**Reflections:**
+
+* Some models are so computationally expensive that it may be simply impossible to run it a feasible length of time without a high powered machine.
+* If a model is computationally expensive, it would be good to provide suggested alternatives that allow it to be run on lower spec machines
+* Not a common problem - only relevant to computationally expensive models
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | <!--TODO--> | N/A |
+| ❌ | ❌ | ❌ | ❌ | N/A | <!--TODO--> |
 
-@shoaib_simulation_2021: There were several instances where it took quite a while to understand how and where to modify the code in order to run scenarios (e.g.
+@shoaib_simulation_2021: Not met.
+There were several instances where it took quite a while to understand how and where to modify the code in order to run scenarios (e.g.
 no arrivals, transferring admin work, reducing doctor intervention in deliveries).
 
-@huang_optimizing_2019: Set up a notebook to programmatically run the model scenarios.
+@huang_optimizing_2019: Not met.
+Set up a notebook to programmatically run the model scenarios.
 It took alot of work to modify and write code that could run the scenarios, and I often made mistakes in my interpretation for the implementation of scenarios, which could be avoided if code for those scenarios was provided.
 
-@lim_staff_2020: Several parameters or scenarios were not incorporated in the code, and had to be added (e.g.
+@lim_staff_2020: Not met.
+Several parameters or scenarios were not incorporated in the code, and had to be added (e.g.
 with conditional logic to skip or change code run, removing hard-coding, adding parameters to existing).
+
+@kim_modelling_2021: Not met. Took alot of work to change model from for loop to function, to set all parameters as inputs (some were hard coded), and add conditional logic of scenarios when required.
+
+@anagnostou_facs-charm_2022: Not applicable. No scenarios.
+
+@johnson_cost_2021: <!--TODO-->
+
+**Reflections:**
+
+* Common issue
+* Time consuming and tricky to resolve
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | <!--TODO--> | ❌ | ❌ | ✅ |
+| ❌ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> |
 
-@shoaib_simulation_2021: Had to add some outputs and calculations (e.g. proportion of childbirth cases referred, standard deviation)
+@shoaib_simulation_2021: Not met. Had to add some outputs and calculations (e.g. proportion of childbirth cases referred, standard deviation)
 
-@lim_staff_2020: The model script provided was only set up to provide results from days 7, 14 and 21. The figures require daily results, so I needed to modify the code to output that.
+@huang_optimizing_2019: Not met.
+It has a complicated output (standardised density of patient in queue) that I was never certain on whether I correctly calculated.
+Although it outputs the columns required to calculate it, due its complexity, I feel this was not met, as it feels like a whole new output in its own right (and not just something simple like a mean).
 
-@kim_modelling_2021: Had to write code to find aorta sizes of people with AAA-related deaths.
+@lim_staff_2020: Not met. The model script provided was only set up to provide results from days 7, 14 and 21. The figures require daily results, so I needed to modify the code to output that.
+
+@kim_modelling_2021: Not met. Had to write code to find aorta sizes of people with AAA-related deaths.
+
+@anagnostou_facs-charm_2022: Fully met. Although worth noting this only had one scenario/version of model and one output to reproduce.
+
+@johnson_cost_2021: <!--TODO-->
+
+**Reflections:**
+
+* Calculate and provide all the outputs required
+* Appreicate this can be a bit "ambiguous" (e.g.
+if its just plotting a mean or simple calculation, then didn't consider that here) (however, combined with other criteria, we do want them to provide code to calculate outputs, so we would want them to provide that anyway)
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| <!--TODO--> | ❌ | <!--TODO--> | <!--TODO--> | ✅ |
+| 🟡 | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> |
 
-@huang_optimizing_2019: The baseline model in the script did not match the baseline model in the paper, so had to modify parameters.
+@shoaib_simulation_2021: Partially met. Script is set with parameters for base configuration 1, with the exception of number of replications.
+
+@huang_optimizing_2019: Not met. The baseline model in the script did not match the baseline model (or any scenario) in the paper, so had to modify parameters.
+
+@lim_staff_2020: Partially met.
+The included parameters were corrected, but the baseline scenario included varying staff strength to 2, and the provided code only varied 4 and 6.
+I had to add some code that enabled it to run with staff strength 2 (as there were an error that occured if you tried to set that).
+
+@kim_modelling_2021: Fully met.
+
+@anagnostou_facs-charm_2022: Fully met.
+
+@johnson_cost_2021: <!--TODO-->
+
+**Reflections:**
+
+* At least provide a script that can run the baseline model as in the paper (even if not providing the scenarios)
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | <!--TODO--> | ✅ |
+| ❌ | ❌ | ❌ | ✅ | ✅ | <!--TODO--> |
 
@@
 @lim_staff_2020: For Figure 5, had to guess the value for `staff_per_shift`.
+
+@kim_modelling_2021: Fully met.
+
+@anagnostou_facs-charm_2022: Fully met.
+
+@johnson_cost_2021: <!--TODO-->
+
+**Reflections:**
+
+* Provide all required parameters
 

### 2024-08-19 pages/reflections.qmd
docs(reflections): finished page (exc. johnson which not done yet)

@@
 * Reduce model run time if possible as it makes it easier to work with, and facilitates doing full re-runs of all scenarios (which can be important with code changes, etc).
+    * Relatedly, it is good practice to re-run all scripts before finishing up, as then you can spot any errors like the one mentioned for @kim_modelling_2021
 * Common issue (to varying degrees - i.e. taking 20 minutes, up to taking several hours).
@@
 * At least provide a script that can run the baseline model as in the paper (even if not providing the scenarios)
+* This can introduce difficulties - when some parameters are wrong, you rely on the paper to check which parameters are correct or not, but if the paper doesn't mention every single parameter (which is reasonably likely, as this includes those not varied by scenarios), then you aren't able to be sure that the model you are running is correct.
 
@@
 
-@huang_optimizing_2019: In this case, patient arrivals and resource numbers were listed in the paper, and there were several discprepancies between this and the provided code.
+@huang_optimizing_2019: Not met.
+In this case, patient arrivals and resource numbers were listed in the paper, and there were several discprepancies between this and the provided code.
 However, for many of the model parameters like length of appointment, these were not mentioned in the paper, and so it was not possible to confirm whether or not those were correct.
+Hence, marked as not met, as the presence of discrepenancies for several other parameters puts these into doubt.
 
-@lim_staff_2020: For Figure 5, had to guess the value for `staff_per_shift`.
+@lim_staff_2020: Not met. For Figure 5, had to guess the value for `staff_per_shift`.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | <!--TODO--> | ✅ | <!--TODO--> | N/A |
+| ❌ | ❌ | 🟡 | N/A | N/A | <!--TODO--> |
 
-@shoaib_simulation_2021: Although there was a scenario table, this did not include all the parameters I would need to change.
+@shoaib_simulation_2021: Not met.
+Although there was a scenario table, this did not include all the parameters I would need to change.
 It was more challenging to identify parameters that were only described in the body of the article.
@@
 Some scenarios were quite ambiguous/unclear from their description in the text, and I initially misunderstood the required parameters for the scenarios.
+
+@huang_optimizing_2019: Not met. As described above, paper didn't adequately describe all parameters.
+
+@lim_staff_2020: Partially met. Nearly all parameters are in the paper table, and others are described in the article. However, didn't provide information for the `staff_per_shift` for Figure 5.
+
+@kim_modelling_2021 and @anagnostou_facs-charm_2022: Not applicable. All provided.
+
+@johnson_cost_2021: <!--TODO-->
+
+**Reflections:**
+
+* Provide parameters in a table (including for each scenario), as it can be difficult/ambiguous to interpret them from the text, and hard to spot them too.
+* Be sure to mention every parameter that gets changed (e.g. for @lim_staff_2020, as there wasn't a default `staff_per_shift` across all scenarios, but not stated for the scenario, had to guess it).
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ✅ | <!--TODO--> | <!--TODO--> | N/A |
+| ❌ | ✅ | N/A | N/A | N/A | <!--TODO--> |
 
-@shoaib_simulation_2021: It was unclear how to estimate inter-arrival time
+@shoaib_simulation_2021: Not met. It was unclear how to estimate inter-arrival time.
 
-@huang_optimizing_2019: The calculations for inter-arrival times were provided in the code, and the inputs to the code were the number of arrivals, as reported in the paper, and so making it easy to compare those parameters and check if numbers were correct or not.
+@huang_optimizing_2019: Fully met.
+The calculations for inter-arrival times were provided in the code, and the inputs to the code were the number of arrivals, as reported in the paper, and so making it easy to compare those parameters and check if numbers were correct or not.
+
+@lim_staff_2020: Not applicable. The parameter not provided is not one that you would calculate.
+
+@kim_modelling_2021 and @anagnostou_facs-charm_2022: Not applicable. All provided.
+
+@johnson_cost_2021: <!--TODO-->
+
+**Reflections:**
+
+* If you are going to be mentioning the "pre-processed" values at all, then its important to include the calculation (ideally in the code, as that is the clearest demonstration of exactly what you did)
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ✅ | <!--TODO--> | ❌ | <!--TODO--> | ✅ |
+| ✅ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> |
+
+@shoaib_simulation_2021: Fully met. Outputs to `.xlsx` files
+
+@huang_optimizing_2019, @lim_staff_2020, and @kim_modelling_2021: Not met. Outputs to dataframe/s.
 
 @anagnostou_facs-charm_2022: Outputs to `OUT_STATS.csv`.
+Note: Although not needed for the reproduction itself, when I tried to amend the name and location of the csv file output the model for use in tests, this was very tricky to do as it was hard coded into the scripts and I found difficult to amend due to how the model is run and set up.
+
+@johnson_cost_2021: <!--TODO-->
+
+**Reflections:**
+
+* Common issue
+* Particularly important if model run time is even slightly long (even just minutes long, but even more so as becomes many minutes / hours), so don't always have to re-run it each time to get results
+* Set up this in such a way that it is easy to change the name and location of the output file.
 
@@
 
-E.g. Easy to figure out how to use output table/s to create tables/figures.
-
 | @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | <!--TODO--> | <!--TODO--> | <!--TODO--> | ✅ |
+| ❌ | ✅ | ✅ | ❌ | ✅ | <!--TODO--> |
 
-For @shoaib_simulation_2021, there were two alternative results spreadsheets with some duplicate metrics but sometimes differing results between them, which made it a bit confusing to work out what to use.
+@shoaib_simulation_2021: Not met.
+There were two alternative results spreadsheets with some duplicate metrics but sometimes differing results between them, which made it a bit confusing to work out what to use.
 
-@anagnostou_facs-charm_2022: The layout of the results spreadsheet was simple, understandable and easy to read, making it easy to adapt into figures.
+@huang_optimizing_2019, @lim_staff_2020, and @anagnostou_facs-charm_2022: Fully met. Didn't experience issues interpreting the contents of the output table/s.
+
+@kim_modelling_2021: Not met.
+It took me a little while to work out what surgery columns I needed, and to realise I needed to combine two of them.
+This required looking at what inputs genreated this, and referring to a input data dictionary.
+
+@johnson_cost_2021: <!--TODO-->
+
+**Reflections:**
+
+* Don't provide alternative results for the same metrics
+* Make it clear what each colum/category in the results table means, if it might not be immediately clear.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | ✅ | ✅ |
+| ❌ | ❌ | ❌ | ✅ | ✅ | <!--TODO--> |
 
-@shoaib_simulation_2021: The lack of seeds wasn't actually a barrier to the reproduction though due to the replication number.
+@shoaib_simulation_2021: Not met.
+The lack of seeds wasn't actually a barrier to the reproduction though due to the replication number.
 I later add seeds so my results could be reproduced, and found that the ease of setting seeds with salabim was a greater facilitator to the work.
@@
 
-@huang_optimizing_2019: It would have been beneficial to include seeds, as there was a fair amount of variability, so with seeds I could then I could be sure that my results do not differ from the original simply due to randomness.
+@huang_optimizing_2019: Not met.
+It would have been beneficial to include seeds, as there was a fair amount of variability, so with seeds I could then I could be sure that my results do not differ from the original simply due to randomness.
 
-@lim_staff_2020: The results obtained looked very similar to the original article, with minimal differences that I felt to be within the expected variation from the model stochasticity.
+@lim_staff_2020: Not met.
+The results obtained looked very similar to the original article, with minimal differences that I felt to be within the expected variation from the model stochasticity.
 However, if seeds had been present, we would have been able to say with certainty.
@@
 
-@anagnostou_facs-charm_2022: The authors included a random seed so the results I got were identical to the original (so no need for any subjectivity in deciding whether its similar enough, as I could perfectly reproduce).
+@kim_modelling_2021: Fully met. Included a seed, although I don't get identical results as I had to reduce number of people in simulation.
+
+@anagnostou_facs-charm_2022: Fully met.
+The authors included a random seed so the results I got were identical to the original (so no need for any subjectivity in deciding whether its similar enough, as I could perfectly reproduce).
+
+@johnson_cost_2021: <!--TODO-->
+
+**Reflections:**
+
+* Depending on your model and the outputs/type of output you are looking at, the lack of seeds can have varying impacts on the appearance of your results, and can make the subjective judgement of whether results are consistent harder (if discrepancies could be attributed to not having consistent seeds or not).
+* It can be really quite simple to include seeds.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | N/A | <!--TODO--> | ❌ |
+| ❌ | N/A | 🟡 | ❌ | N/A | <!--TODO--> |
 
 <!--TODO: Lim 2020... I think from memory that this output tables  similar to the paper, but I then changed them as that format was difficult to compare/work with -->
+
+@shoaib_simulation_2021: Not met.
+
+@huang_optimizing_2019: Not applicable. No tables in scope.
+
+@lim_staff_2020: Partially met.
+It outputs the results in a similar structure to the paper (like a section of a table).
+However, it doesn't have the full code to produce a table outright, for any of the tables, so additional processing still required.
+
+@kim_modelling_2021: Not met.
+Had to write code to generate tables, which included correctly implementing calculation of excess e.g.
+deaths, scaling to population size, and identify which columns provide the operation outcomes.
+
+@anagnostou_facs-charm_2022: Not applicable. No tables in scope.
+
+@johnson_cost_2021: <!--TODO-->
+
+**Reflections:**
+
+* It can take a bit of time to do this processing, so very handy for it to be provided.
+* Common issue.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | ❌ | ❌ |
+| ❌ | ❌ | ❌ | ❌ | ❌ | <!--TODO--> |
 
-@huang_optimizing_2019: Had to write code from scratch.
+@shoaib_simulation_2021: Not met.
+
+@huang_optimizing_2019: Not met.
+Had to write code from scratch.
 For one of the figures, it would have been handy if informed that plot was produced by a simmer function (as didn’t initially realise this).
@@
 about providing the processing?) -->
+
+@lim_staff_2020, @kim_modelling_2021 and @anagnostou_facs-charm_2022: Not met. However, the simplicity and repetition of the figures was handy.
+
+@johnson_cost_2021: <!--TODO-->
+
+**Reflections:**
+
+* It can take a bit of time to do this processing, particularly if the figure involves any transformations (and less so if the figure is simple), so very handy for it to be provided.
+* Common issue.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | N/A |
+| ❌ | ❌ | N/A | ❌ | N/A | <!--TODO--> |
+
+@shoaib_simulation_2021, @huang_optimizing_2019, @kim_modelling_2021: Not met.
+
+@lim_staff_2020, @anagnostou_facs-charm_2022: Not applicable (no in-text results).
+
+@johnson_cost_2021: <!--TODO-->
+
+**Reflections:**
+
+* Provide code to calculate in-text results
+* Common issue
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: |
-| <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | ✅ |
+| ❌ | ❌ | ❌ | 🟡 | ✅ | <!--TODO--> |
 
-@anagnostou_facs-charm_2022: Clear README with instructions on how to run the model was really helpful.
+@shoaib_simulation_2021: Not met. No instructions, although is just a single script that you run.
+
+@huang_optimizing_2019: Not met. Not provided in runnable form but, regardless, no instructions for running it as it is provided (as a web application - i.e. no info on how to get that running).
+
+@lim_staff_2020: Not met. No instructions, although is just a single script that you run.
+
+@kim_modelling_2021: Partially met. README tells you which folder has the scripts you need, although nothing further. Although all you need to do is run them.
+
+@anagnostou_facs-charm_2022: Fully met. Clear README with instructions on how to run the model was really helpful.
+
+**Reflections:**
+
+* Even if as simple as running a script, include instructions on how to do so
+* Common issue
 
@@
 
-For @lim_staff_2020, the simplicity of the model structure and code, and simplicity and similarity between figures, really helped to facilitate the reproduction.
-For @kim_modelling_2021, reproduction was facilitated by having relatively simple and repetitive plots which were easy to understand and create.
-For @anagnostou_facs-charm_2022, the figures were simple (just means and CI which are already calculated).
-
-Fix errors in script.
-For @kim_modelling_2021, an error appears to have been introduced with the aoorta diameter thresholds by switching between nested and unnested lists, which I’m anticipating was unresolved due to the long run times of the model meaning they weren’t all run in sequence at the end.
-<!--TODO: Have put in run time, or does it need seperate place -->
-
-@anagnostou_facs-charm_2022: Although not needed for the reproduction itself, when I tried to amend the name and location of the csv file output the model for use in tests, this was very tricky to do as it was hard coded into the scripts and I found difficult to amend due to how the model is run and set up.
-<!-- TODO: Fall under hard coding?
-Or output file flexibility?
--->
-
 @anagnostou_facs-charm_2022: Included data dictionary for input parameters. Although I didn’t need this, this would have been great if I needed to change the input parameters at all.
 
-<!-- TODO: Check if any of these should be above.
-e.g.
-might want to put simplicity in a same way as i put run time - as simplicity is not inherently required (its about focus of project partly) BUT it is really handy (and it is always a good principle to hold) -->
+**Reflections:**
+
+* Include grid lines
+* Include data dictionaries
 

### 2024-08-19 pages/framework.qmd
docs(framework): add framework page with notes on potential changes to stars framework based on reflections.qmd

---
title: "Modifying the framework"
bibliography: ../references.bib
---

## Contents of the framework

| Section from reflections | Consideration for framework |
| - | - |
| List required packages | The difference between listing all packages, and listing some that then have other dependencies. The various options there are for listing packages, and the downside of just assuming its obvious from imports. The options for guiding dependency management (e.g. providing scripts that download packages, and then environment management tools) |
| Provide version for Python/R and for packages | Important to do so for both (not just packages). Challenge of implementing in R. Ease of implementing in Python. Importance of listing in repository itself. Options for doing this in R and Python. Suggestions. Need to explore more with R. Is it a matter of providing renv but suggesting someone could try with latest versions in first instance? As not realistic to guarantee maintenance of research projects. But know at least when it worked - as being clear, it won't always, even in R |
| Model in a "runnable" format | This was an unusual case, but I think could merge more under the example of providing code that aligns with the paper, as in that case, it was the code for a web app when the paper wasn't about that |
| Model designed to run programmatically, and don't hard code parameters you want to change. | Consider whether framework will given guidance on model structure. If so, it should be suggesting that (A) parameters are seperate from model and (B) run scenarios by changing elsewhere (and not by directly modifying the model code). Why do this? Because its simpler to run multiple versions of model with same script, and reduces likelihood of missing errors of inputing wrong parameters |
| Avoid large amounts of code duplciation | This would also be a code structure thing (does it fit in framework?). Good to do in general - fairly standard coding practice. Here as it makes code more readable, makes it easier when want to change all scenarios, and reduces likelihood of introducing mistakes (which did see) |
| Sufficient comments in code | Likewise, code structure. Standard practice like docstrings (which only one or two had). The standard structures that are available for docstrings (e.g. roxygen in R). And then also just general comments in code itself. |
| Quicker models | Worth considering for framework, as this was practically one of the big things for me when it came to using the models. Think about the options that are available for reducing model run time. And from the start, principles of keeping it simple and small. Things to avoid that make it slow. Alternatives to those things. The value of a quicker model (e.g. in being able to make an app, to rerun it all easily and spot mistakes, to just be easier to work with). |
| State run time | Could include in minimum documentation |
| State memory usage and alterantives for lower spec machines | Could include in enhanced documentation? Or minimum? Need to consider that this can seem a daunting thing if not familiar and wouldn't know how to find this out or what this means |
| Provide code for all scenarios |
| Include correct parameters in script | Suggestion of default model parameters matching up to baseline in paper, and explaining that if not, issue becomes that its hard to check if model is all correct without code or paper listing every single parameter |
| Provide all required parameters |
| Clearly present parameters in paper | This would not be relevant for STARS framework, but could feed into STRESS-DES work? How it being in a table was so much easier than it being described in the text, and how it being comprehensive of all parameters that get varied (or clear if those are the only things changed from baseline, and so on) |
| Provide calculations | Again, might not quite fit into STARS? But if you are going to be mentioning the "pre-processed" values at all, then its important to include the calculation (ideally in the code, as that is the clearest demonstration of exactly what you did) |
| Saves output to a file | Code structure type thing. This was really handy, particularly for long run times. In doing this, set up in way that is easy to change name and location of output file, and not hard coded to one thing |
| Understandable output tables | Not sure where/if this might fit. But suggestion is to not provide alternative results for same metrics. And if a table or output might be unclear on what need or how to calculate, then providing some docs or something that supports |
| Using seeds | Explain how, how it can be quite simple, and what benefit of this is. Could be in enhanced |
| Provide code to produce (a) tables (b) figures (c) in-text results | Explaining why this is handy (being able to reproduce gives confidence model is running right and also important in science) (plus useful for self too if need to make changes in review process and so on). Noting importance of not forgetting about "in-text" results |
| Instructions on how to run model | Already in minimal documentation, but be aware, even as simple as "run this script and here is an example of how" is helpful |
| Grid lines | Minor, not sure if fits/to include |
| Data dictionaries | Minor and intersects with good commenting, might not be relevant for all, but also worth considering, if people are uploading data as part of model, what the principles and practices and recommendations are for shairng of data and linking to those (as this is likely part of those, along with other things). If there is overlap, make it clear the synergies (e.g. if talks about archiving data, how could do alongside code, and so on). |

## Presentation of the framework

**Checklist** table with categories, description and space to complete. But in multiple synced formats (perhaps auto conversion github action between them) - e.g. markdown, latex, docx

**Diagram**: Think about any ways could adapt this and if would benefit from that. E.g. gradual reveal with GIF. more icons. alt layout. etc.

**Website**: Could share like <https://joss.readthedocs.io/en/latest/paper.html> but would want to make sure we are adding sufficient detail on top of checklist.

### 2024-08-23 framework/stars_checklist.tex
docs(stars): example checklist document with conversions

\hypertarget{stars-framework-checklist}{%
\section{STARS Framework Checklist}\label{stars-framework-checklist}}

\hypertarget{essential-components}{%
\subsection{Essential components}\label{essential-components}}

\begin{longtable}[]{@{}ll@{}}
\toprule
\begin{minipage}[b]{0.47\columnwidth}\raggedright
Item\strut
\end{minipage} & \begin{minipage}[b]{0.47\columnwidth}\raggedright
Implementation\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.47\columnwidth}\raggedright
\textbf{Open license}\emph{Free and open-source software (FOSS) license
(e.g.~MIT, GNU Public License (GPL))}\strut
\end{minipage} & \begin{minipage}[t]{0.47\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.47\columnwidth}\raggedright
\textbf{Dependency management}\emph{Specify software libraries, version
numbers and sources (e.g.~dependency management tools like virtualenv,
conda, poetry)}\strut
\end{minipage} & \begin{minipage}[t]{0.47\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.47\columnwidth}\raggedright
\textbf{FOSS model}\emph{Coded in FOSS language (e.g.~R, Julia,
Python)}\strut
\end{minipage} & \begin{minipage}[t]{0.47\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.47\columnwidth}\raggedright
\textbf{Minimum documentation}\emph{Minimal instructions (e.g.~in
README) that overview (a) what model does, (b) how to install and run
model to obtain results, and (c) how to vary parameters to run new
experiments}\strut
\end{minipage} & \begin{minipage}[t]{0.47\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.47\columnwidth}\raggedright
\textbf{ORCID}\emph{ORCID for each study author}\strut
\end{minipage} & \begin{minipage}[t]{0.47\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.47\columnwidth}\raggedright
\textbf{Citation information}\emph{Instructions on how to cite the
research artefact (e.g.~CITATION.cff file)}\strut
\end{minipage} & \begin{minipage}[t]{0.47\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.47\columnwidth}\raggedright
\textbf{Remote code repository}\emph{Code available in a remote code
repository (e.g.~GitHub, GitLab, BitBucket)}\strut
\end{minipage} & \begin{minipage}[t]{0.47\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.47\columnwidth}\raggedright
\textbf{Open science archive}\emph{Code stored in an open science
archive with FORCE11 compliant citation and guaranteed persistance of
digital artefacts (e.g.~Figshare, Zenodo, the Open Science Framework
(OSF), and the Computational Modeling in the Social and Ecological
Sciences Network (CoMSES Net))}\strut
\end{minipage} & \begin{minipage}[t]{0.47\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{optional-components}{%
\subsection{Optional components}\label{optional-components}}

\begin{longtable}[]{@{}lll@{}}
\toprule
\begin{minipage}[b]{0.30\columnwidth}\raggedright
Item\strut
\end{minipage} & \begin{minipage}[b]{0.30\columnwidth}\raggedright
Description\strut
\end{minipage} & \begin{minipage}[b]{0.30\columnwidth}\raggedright
Implementation\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.30\columnwidth}\raggedright
Enhanced documentation\strut
\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
Open and high quality documentation on how the model is implemented and
works (e.g.~via notebooks and markdown files, brought together using
software like Quarto and Jupyter Book). Suggested content includes:•
Plain english summary of project and model• Clarifying license• Citation
instructions• Contribution instructions• Model installation
instructions• Structured code walk through of model• Documentation of
modelling cycle using TRACE• Annotated simulation reporting guidelines•
Clear description of model validation including its intended
purpose\strut
\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.30\columnwidth}\raggedright
Documentation hosting\strut
\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
Host documentation (e.g.~with GitHub pages, GitLab pages, BitBucket
Cloud, Quarto Pub)\strut
\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.30\columnwidth}\raggedright
Online coding environment\strut
\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
Provide an online environment where users can run and change code
(e.g.~BinderHub, Google Colaboratory, Deepnote)\strut
\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.30\columnwidth}\raggedright
Model interface\strut
\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
Provide web application interface to the model so it is accessible to
less technical simulation users\strut
\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.30\columnwidth}\raggedright
Web app hosting\strut
\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
Host web app online (e.g.~Streamlit Community Cloud, ShinyApps
hosting)\strut
\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

### 2024-09-03 framework/stars_checklist.tex
docs(framework): add a basic .md framework file with conversions to docx and tex

@@
-\hypertarget{stars-framework-checklist}{%
-\section{STARS Framework Checklist}\label{stars-framework-checklist}}
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[
+]{article}
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
+\usepackage{longtable,booktabs}
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
 
-\hypertarget{essential-components}{%
-\subsection{Essential components}\label{essential-components}}
+\author{}
+\date{}
+
+\begin{document}
+
+\section{STARS Framework}
+
+\subsection{Checklist}
 
@@
 \toprule
-\begin{minipage}[b]{0.47\columnwidth}\raggedright
-Item\strut
-\end{minipage} & \begin{minipage}[b]{0.47\columnwidth}\raggedright
-Implementation\strut
-\end{minipage}\tabularnewline
+Item & Implementation\tabularnewline
 \midrule
 \endhead
-\begin{minipage}[t]{0.47\columnwidth}\raggedright
-\textbf{Open license}\emph{Free and open-source software (FOSS) license
-(e.g.~MIT, GNU Public License (GPL))}\strut
-\end{minipage} & \begin{minipage}[t]{0.47\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.47\columnwidth}\raggedright
-\textbf{Dependency management}\emph{Specify software libraries, version
-numbers and sources (e.g.~dependency management tools like virtualenv,
-conda, poetry)}\strut
-\end{minipage} & \begin{minipage}[t]{0.47\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.47\columnwidth}\raggedright
-\textbf{FOSS model}\emph{Coded in FOSS language (e.g.~R, Julia,
-Python)}\strut
-\end{minipage} & \begin{minipage}[t]{0.47\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.47\columnwidth}\raggedright
-\textbf{Minimum documentation}\emph{Minimal instructions (e.g.~in
-README) that overview (a) what model does, (b) how to install and run
-model to obtain results, and (c) how to vary parameters to run new
-experiments}\strut
-\end{minipage} & \begin{minipage}[t]{0.47\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.47\columnwidth}\raggedright
-\textbf{ORCID}\emph{ORCID for each study author}\strut
-\end{minipage} & \begin{minipage}[t]{0.47\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.47\columnwidth}\raggedright
-\textbf{Citation information}\emph{Instructions on how to cite the
-research artefact (e.g.~CITATION.cff file)}\strut
-\end{minipage} & \begin{minipage}[t]{0.47\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.47\columnwidth}\raggedright
-\textbf{Remote code repository}\emph{Code available in a remote code
-repository (e.g.~GitHub, GitLab, BitBucket)}\strut
-\end{minipage} & \begin{minipage}[t]{0.47\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.47\columnwidth}\raggedright
-\textbf{Open science archive}\emph{Code stored in an open science
-archive with FORCE11 compliant citation and guaranteed persistance of
-digital artefacts (e.g.~Figshare, Zenodo, the Open Science Framework
-(OSF), and the Computational Modeling in the Social and Ecological
-Sciences Network (CoMSES Net))}\strut
-\end{minipage} & \begin{minipage}[t]{0.47\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
+\textbf{Essential components} &\tabularnewline
+Open license & \emph{Describe your implementation of this
+component}\tabularnewline
+Dependency management &\tabularnewline
+FOSS model &\tabularnewline
+Minimum documentation &\tabularnewline
+ORCID &\tabularnewline
+Citation information &\tabularnewline
+Remote code repository &\tabularnewline
+Open science archive &\tabularnewline
+\textbf{Optional components} &\tabularnewline
+Enhanced documentation &\tabularnewline
+Documentation hosting &\tabularnewline
+Online coding environment &\tabularnewline
+Model interface &\tabularnewline
+Web app hosting &\tabularnewline
 \bottomrule
@@
 
-\hypertarget{optional-components}{%
-\subsection{Optional components}\label{optional-components}}
+\subsection{Description}
 
-\begin{longtable}[]{@{}lll@{}}
-\toprule
-\begin{minipage}[b]{0.30\columnwidth}\raggedright
-Item\strut
-\end{minipage} & \begin{minipage}[b]{0.30\columnwidth}\raggedright
-Description\strut
-\end{minipage} & \begin{minipage}[b]{0.30\columnwidth}\raggedright
-Implementation\strut
-\end{minipage}\tabularnewline
-\midrule
-\endhead
-\begin{minipage}[t]{0.30\columnwidth}\raggedright
-Enhanced documentation\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
+\subsubsection{Essential components}
+
+\paragraph{Open license}
+
+Free and open-source software (FOSS) license (e.g. MIT, GNU Public
+License (GPL))
+
+\paragraph{Dependency management}
+
+Specify software libraries, version numbers and sources (e.g. dependency
+management tools like virtualenv, conda, poetry)
+
+\paragraph{FOSS model}
+
+Coded in FOSS language (e.g. R, Julia, Python)
+
+\paragraph{Minimum documentation}
+
+Minimal instructions (e.g. in README) that overview (a) what model does,
+(b) how to install and run model to obtain results, and (c) how to vary
+parameters to run new experiments
+
+\paragraph{ORCID}
+
+ORCID for each study author
+
+\paragraph{Citation information}
+
+Instructions on how to cite the research artefact (e.g. CITATION.cff
+file)
+
+\paragraph{Remote code repository}
+
+Code available in a remote code repository (e.g. GitHub, GitLab,
+BitBucket)
+
+\paragraph{Open science archive}
+
+Code stored in an open science archive with FORCE11 compliant citation
+and guaranteed persistance of digital artefacts (e.g. Figshare, Zenodo,
+the Open Science Framework (OSF), and the Computational Modeling in the
+Social and Ecological Sciences Network (CoMSES Net))
+
+\subsubsection{Optional components}
+
+\paragraph{Enhanced documentation}
+
 Open and high quality documentation on how the model is implemented and
-works (e.g.~via notebooks and markdown files, brought together using
-software like Quarto and Jupyter Book). Suggested content includes:•
-Plain english summary of project and model• Clarifying license• Citation
-instructions• Contribution instructions• Model installation
-instructions• Structured code walk through of model• Documentation of
-modelling cycle using TRACE• Annotated simulation reporting guidelines•
-Clear description of model validation including its intended
-purpose\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.30\columnwidth}\raggedright
-Documentation hosting\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
-Host documentation (e.g.~with GitHub pages, GitLab pages, BitBucket
-Cloud, Quarto Pub)\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.30\columnwidth}\raggedright
-Online coding environment\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
-Provide an online environment where users can run and change code
-(e.g.~BinderHub, Google Colaboratory, Deepnote)\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.30\columnwidth}\raggedright
-Model interface\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
+works (e.g. via notebooks and markdown files, brought together using
+software like Quarto and Jupyter Book). Suggested content includes:
+
+\begin{itemize}
+\tightlist
+\item
+  Plain english summary of project and model
+\item
+  Clarifying license
+\item
+  Citation instructions
+\item
+  Contribution instructions
+\item
+  Model installation instructions
+\item
+  Structured code walk through of model
+\item
+  Documentation of modelling cycle using TRACE
+\item
+  Annotated simulation reporting guidelines
+\item
+  Clear description of model validation including its intended purpose
+\end{itemize}
+
+\paragraph{Documentation hosting}
+
+Host documentation (e.g. with GitHub pages, GitLab pages, BitBucket
+Cloud, Quarto Pub)
+
+\paragraph{Online coding environment}
+
+Provide an online environment where users can run and change code (e.g.
+BinderHub, Google Colaboratory, Deepnote)
+
+\paragraph{Model interface}
+
 Provide web application interface to the model so it is accessible to
-less technical simulation users\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.30\columnwidth}\raggedright
-Web app hosting\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
-Host web app online (e.g.~Streamlit Community Cloud, ShinyApps
-hosting)\strut
-\end{minipage} & \begin{minipage}[t]{0.30\columnwidth}\raggedright
-\strut
-\end{minipage}\tabularnewline
-\bottomrule
-\end{longtable}
+less technical simulation users
+
+\paragraph{Web app hosting}
+
+Host web app online (e.g. Streamlit Community Cloud, ShinyApps hosting)
+
+\end{document}

### 2024-09-03 pages/reproduction.qmd
docs(reproduction): make study descriptions more consistent (e.g. mentioning model language and packages each time)

@@
 
-<!-- TODO: Modify descriptions so each contains consistent information about each study - e.g.
-making sure each includes a mention of what was used to make model (e.g.
-R simmer, base R, python simpy) -->
-
-**@shoaib_simulation_2021:** This is a discrete-event simulation modelling primary health centres (PHCs) in India.
-There are four patient types: outpatients, inpatients, childbirth cases and antenatal care patients.
+**@shoaib_simulation_2021:** Uses **python (salabim)** to model primary health centres (PHCs) in India.
+The model has four patient types: outpatients, inpatients, childbirth cases and antenatal care patients.
 Four model configurations are developed based on observed PHC practices or government-mandated operational guidelines.
 The paper explores different operational patterns for scenarios where very high utilisation was observed, to explore what might help reduce utilisation of these resources.
-*(Article published as @shoaib_simulation_2022, but we used the green open access pre-print).* <a href="https://pythonhealthdatascience.github.io/stars-reproduce-shoaib-2022/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>
+Note: The article was as @shoaib_simulation_2022, but we used the green open access pre-print @shoaib_simulation_2021.
+<a href="https://pythonhealthdatascience.github.io/stars-reproduce-shoaib-2022/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>
 
-**@huang_optimizing_2019:** This is a discrete-event simulation model of an endovascular clot retrieval (ECR) service.
+**@huang_optimizing_2019:** Uses **R (simmer)** to model an endovascular clot retrieval (ECR) service.
 ECR is a treatment for acute ischaemic stroke.
 The model includes the stroke pathway, as well as three other pathways that share resources with the stroke pathway: an elective non-stroke interventional neuroradiology pathway, an emergency interventional radiology pathway, and an elective interventional radiology pathway.
-The model is created using R Simmer.
 The paper explores waiting times and resource utilisation - particularly focussing on the biplane angiographic suite (angioINR).
@@
 
-**@lim_staff_2020:** This is a discrete-event simulation modelling the transmission of COVID-19 in laboratory.
+**@lim_staff_2020:** Uses **python (numpy and pandas)** to model the transmission of COVID-19 in a laboratory.
 It examines the proportion of staff infected in scenarios varying the: number of shifts per day; number of staff per shift; overall staff pool; shift patterns; secondary attack rate of the virus; introduction of protective measures (social distancing and personal protective equipment).
-The model is created using Python.
 <a href="https://pythonhealthdatascience.github.io/stars-reproduce-lim-2020/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>
 
-**@kim_modelling_2021:** This study adapts a previously developed discrete-event simulation model for abdominal aortic aneurysm (AAA) screening of men in England.
-It aims to explore different approaches to resuming screening and surgical repair for AAA, as these survives were paused or substantially reduced during COVID-19 due to concerns about virus transmission.
+**@kim_modelling_2021:** Adapts a previously developed **R (Rcpp, expm, msm, foreach, iterators, doParallel)** model for abdominal aortic aneurysm (AAA) screening of men in England.
+The model is adapted/used to explore different approaches to resuming screening and surgical repair for AAA, as these survives were paused or substantially reduced during COVID-19 due to concerns about virus transmission.
 <a href="https://pythonhealthdatascience.github.io/stars-reproduce-kim-2021/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>
@@
 **@anagnostou_facs-charm_2022:** This paper includes two models - we have focussed just on the dynamiC Hospital wARd Management (CHARM) model.
-CHARM is a discrete-event simulation modelling intensive care units (ICU) in the COVID-19 pandemic (as well as subsequent stays in a recovery bed).
+CHARM uses **Python (simpy)** to model intensive care units (ICU) in the COVID-19 pandemic (as well as subsequent stays in a recovery bed).
 It includes three types of admission to the ICU (emergency, elective or COVID-19).

### 2024-09-03 pages/background.qmd
docs(intro): add to introduction and methods a little
docs(background): wrote page (described pilot work and stars project)

@@
 ---
-title: "STARS"
+title: "Introduction"
+bibliography: ../references.bib
 ---
 
-TODO: Add background about STARS, pilot work, and aim of WP1
+This book describes work from **work package 1** of the project STARS: Sharing Tools and Artefacts for Reproducible Simulations in healthcare.
+
+![STARS: Sharing Tools and Artefacts for Reproducible Simulations in healthcare](../images/stars_banner.png)
+
+The project was funded for two years by the [Medical Research Council](https://gtr.ukri.org/projects?ref=MR%2FZ503915%2F1), from April 2024 to April 2026.
+Prior to this funding, some **pilot work** was carried out by Tom Monks, Alison Harper and Nav Mustafee.
+This included a review of code sharing practices and the development of the STARS framework.
+
+## Pilot work
+
+### Review of healthcare simulation sharing practices
+
+@monks_computer_2023 explored how discrete-event simulation (DES) models used in a health context (e.g.
+health services, health economics) were shared and whether this sharing adhered to best practice.
+The full study can be viewed at:
+
+> Monks, Thomas, and Alison Harper.
+2023.
+“Computer Model and Code Sharing Practices in Healthcare Discrete-Event Simulation: A Systematic Scoping Review.” Journal of Simulation 0 (0): 1–16.
+<https://doi.org/10.1080/17477778.2023.2260772>.
+
+In summary, they identified 564 papers describing a DES model from a health context published from 2019 to 2022.
+Of these, only **8.3% (47/564) had available model code** (either sharing the code themselves, or citing an openly available model).
+Looking by year, this rose from 4.0% for studies published in 2019, to 9.0% for 2022.
+
+Further findings:
+
+* More likely that code was shared if model was:
+    * Created using free and open source software (FOSS) (28.7%, 29/101)
+    * A COVID-19 model (24.6%, 17/69)
+* Of the papers that did share a model:
+    * Most were written in a programming language (66%, 31/47), the rest in a commercial off the shelf Visual Interactive Modelling (VIM) software
+    * These were evaluated in a best practice audit, with the results as follows: "In general, computer models and artefacts were published without a DOI (n = 7); rarely included ORCIDs for authors (n = 6); rarely included an open licence (n = 21); were mostly supported by a README file (n = 28); rarely included documentation detailing how to run the model (n = 15); provided no form of formal or informal dependency management (n = 21); did not include any evidence of model testing (n = 3); were almost all downloadable (n = 38); and rarely executable via a cloud-based platform (n = 10)." (@monks_computer_2023)
+* Few studies used a reporting guideline (12.8%, 72/564) - mostly using:
+    * One of the International Society for Pharmacoeconomics and Outcomes Research (ISPOR) publications (n=37), or
+    * The Strengthening the Reporting of Empirical Simulation Studies (STRESS) guidelines from @monks_strengthening_2019 (n=22)
+
+The review concludes that "there are many (simple) best practices the community can adopt, such as the use of trusted archives, and documentation, to improve its sharing". (@monks_computer_2023)
+
+### Pilot STARS framework
+
+@monks_towards_2024 introduces a pilot framework for sharing DES models called STARS: Sharing Tools and Artefacts for Reusable Simulations.
+Note that this "reusable" is changed into "reproducible" for the STARS project as we build on this work in the current project.
+
+The pilot STARS framework consists of essential components (minimum to make models "long-term, citable, functional, appropriately licenced") and optional components (enhance model "accessibility, understanding, and maintainability").
+(@monks_towards_2024)
+
+The essential components are:
+
+* Open license
+* Dependency management
+* FOSS model
+* Minimum documentation
+* Open Researcher and Contributor IDs (ORCID)
+* Citation information
+* Remote code repository
+* Open science archive
+
+The optional components are:
+
+* Enhanced documentation
+* Documentation hosting
+* Online coding environment
+* Model interface
+* Web app hosting
+
+This is summarised in the diagram below...
+
+![STARS framework overview](../images/stars_framework_overview.png){.lightbox}
+
+This was supported by example implementations in Python:
+
+* Example 1 - [stars-treat-sim](https://github.com/pythonhealthdatascience/stars-treat-sim)
+* Example 2 - [stars-streamlit-example](https://github.com/pythonhealthdatascience/stars-streamlit-example) and [stars-simpy-example-docs](https://github.com/pythonhealthdatascience/stars-simpy-example-docs) - with [web app](https://stars-simpy-example.streamlit.app/) and [hosted docs](https://pythonhealthdatascience.github.io/stars-simpy-example-docs)
+* Example 3 - [stars-ciw-example](https://github.com/pythonhealthdatascience/stars-ciw-example) - with [web app](https://pythonhealthdatascience.shinyapps.io/stars-ciw-examplar) and [hosted docs](https://pythonhealthdatascience.github.io/stars-ciw-example)
+
+## STARS project
+
+The MRC-funded STARS project builds on this pilot work. As stated in the funding application, the objective of this project is "to improve the quality and quantity of shared discrete-event
+simulation models, tools and other research artefacts:
+
+1. Identify barriers, and good practices for sharing simulation models;
+2. Develop a new framework for sharing computer models applicable the most common free and open-source languages;
+3. Test the framework in both retrospective and prospective case studies;
+4. Develop online interactive training materials;
+5. Transfer knowledge of our STARS framework to health data science researchers;
+6. Ensure sustainability of materials;
+7. Support our partner archival journals adopt open science principles and our findings;"
+
+This objectives will be achieved through four work packages:
+
+**Work package 1: Reproducibility of computational results**
+
+* Assess the computational reproducibility of six published DES models created in Python and R.
+* Evaluate the publication, code and associated artefacts against reporting guidelines, best practice for code sharing, and criteria from journal artefact badges.
+
+**Work package 2: R and Python framework for sharing DES models**
+
+* Improve the pilot framework (e.g. extend baesd on barriers and enablers to reproduction observed in work package 1, and making it relevant to R models)
+* Provide time-saving measures for researchers (e.g.
+automated support for STRESS, use of large language models (LLM) to support creating of summaries, automated testing of models, continuous integration tools)
+
+**Work package 3: Prospective and retrospective application of the framework**
+
+* Apply STARS framework within two case studies (one prospective and one retrospective)
+
+**Work package 4: Training**
+
+* Develop online interactive training materials to support researchers in using the STARS framework
+
+From this point onwards, this site/book summarises the findings from work package 1.
+
+## References

### 2024-09-03 pages/protocol.qmd
docs(intro): add to introduction and methods a little
docs(protocol): summarised protocol, described minor deviations, and sources of ambiguity in timings

--- 2024-08-14 pages/protocol.qmd
@@
 ---
-title: "Protocol"
+title: "Methods"
+bibliography: ../references.bib
 ---
 
-TODO: This page summarises the method from the protocol.
+For work package 1, the methods were described in our protocol, @heather_protocol_2024.
+
+> Heather, Amy, Thomas Monks, Alison Harper, Navonil Mustafee, and Andrew Mayne.
+2024.
+“Protocol for Assessing the Computational Reproducibility of Discrete-Event Simulation Models on STARS,” June.
+<https://zenodo.org/records/12179846>.
+
+These are summarised below, and deviations from the protocol are also described.
+
+## Protocol summary
+
+For this work, six published healthcare DES models were selected.
+These were models with publicly available code under an open license (either already available or add on request from the STARS team).
+For each model, the follow stages of work were conducted:
+
+**Stage 1: Reproduction** - assessing the computational reproducibility of each study
+
+* Informed authors about study and, if not available, asked if they would be happy to add an open license to their code
+* Set up repository for reproduction with the article and code
+* Read the article and defined the scope of the reproduction, archiving the scope (and repository) on Zenodo before proceeding
+* Looked over the model code, created a suitable environment with the software and packages required, and then ran the model.
+For each study, with any issues faced in running the model, troubleshooting was performed such as modifying or writing code.
+If troubleshooting was exhaused and there were still issues or discrepancies in the results, the original study authors were informed and provided the opportunity to advice on the reason for this (although with no pressure or requirement to do so)
+* For each item in the scope, a decision was made as to whether this had been successfully reproduced or not.
+This was a subjective decision which allowed some expected deviation due to model stochasticity (for example, lack of seed control).
+* This is timed (including time to produce each item in the scope), and limited to a maximum of 40 horus
+
+**Stage 2: Evaluation** - evaluating the publication, code and associated artefacts against sharing and reporting standards
+
+* The publication was evaluated against reporting guidelines for DES:
+    * @monks_strengthening_2019 - STRESS-DES: Strengthening The Reporting of Empirical Simulation Studies (Discrete-Event Simulation) (Version 1.0).
+    * @zhang_reporting_2020 - The generic reporting checklist for healthcare-related discrete event simulation studies derived from the the International Society for Pharmacoeconomics and Outcomes Research Society for Medical Decision Making (ISPOR-SDM) Modeling Good Research Practices Task Force reports.
+* The model code and associated artefacts (e.g. the GitHub repository shared by the authors) was evaluated against:
+    * The criteria of badges related to reproducibility from various organisations and journals - namely:
+        * National Information Standards Organisation (NISO)(@niso_reproducibility_badging_and_definitions_working_group_reproducibility_2021)
+        * Association for Computing Machinery (ACM) (@association_for_computing_machinery_acm_artifact_2020)
+        * Center for Open Science (COS) (@blohowiak_badges_2023)
+        * Institute of Electrical and Electronics Engineers (IEEE) (@institute_of_electrical_and_electronics_engineers_ieee_about_nodate)
+        * Psychological Science (@hardwicke_transparency_2023 and @association_for_psychological_science_aps_psychological_2023)
+    * Recommendations from the pilot STARS framework for the sharing of code and associated materials from discrete-event simulation models (@monks_towards_2024).
+* This is timed
+
+**Stage 3: Report and research compendium** - summary report and organised repository
+
+* Wrote a report summarising the computational reproducibility assessment and evaluation
+* Restructed the reposuitory into a "research compendium", which essentially consisted of organising the repository to ensure it is easy and clear for someone else to re-run. Steps included:
+    * Adding run times to the model notebooks
+    * Write a README for the reproduction folder
+    * Moving data, methods and outputs into seperate folders
+    * Creating tests which check if a user can get the same results from the model as we did during the reproduction
+    * A Dockerfile and Docker image published on the GitHub container registry
+* A second researcher from the STARS team then attempted to use the repository and confirm whether they were able to reproduce the results of the first researcher
+* Finally, the repository was archived on Zenodo, and the authors were informed.
+
+For each study, a quarto site was produced which shared the results from the reproduction and evaluation and the summary report.
+Throughout the work, a detailed logbook was kept to keep track of timings and to record work on each stage, such as detailing troubleshooting steps during the reproduction, or uncertainities discussed with another STARS team member during the evaluation.
+
+**Summary diagram**
+
+This process is captured in the diagram below:
+
+![Workflow for STARS work package 1](../images/stars_wp1_workflow.png){.lightbox}
+
+## Minor deviations from the protocol
+
+There were some minor deviations from the protocol, which are explained below...
+
+| Deviation | Description and reason for the change |
+| --- | --- |
+| Using the latest software packages | In the protocol, I had planned that - if no versions were provided  we select a version of the software and each package that is closest to but still prior to the date of the code archive or paper publication.
+I kept to this for the Python models (easily set using a conda/mamba environment).
+However, I had great difficulties attempting to do this in R, and could not successfully backdate both.
+As such, I used the latest versions of R and each package for those studies |
+| Using percentage difference in results to help decided reproduction success | This is not particularly deviation, as I did explore this, but I ultimately found it very unhelpful, as the percentage difference could be greatly impacted by scale (for example, 0.1 vs 0.2 would appear much greater than 3 vs 4, but the actual meaning of these differences might be similar (e.g.
+both might be considered a small difference) depending on the scale used and what is being compared - whilst in another context with a different scale, 0.1 vs 0.2 might actually reflect a huge difference!).
+|
+| Moving onto evaluation stage before receive author response regarding reproduction discrepancy | In the protocol, we required that authors are contacted if there are any remaining difficulties in running the code or items in the scope that were not reproduced.
+The authors were given a total of four weeks to respond if they chose to.
+We had implied that we must wait for this time to pass before continuing to the evaluation stage (since the three stages were presented as being completed one after another).
+The rationale for this was that the timings for the reproduction would be influenced by whether the evaluation had been completed or not, and vice versa.
+However, given the many possible influences on the timings, this was considered negligble.
+|
+| Organisation of the repository for the research compendium | In the protocol, we had planned that seperate folders were created for data, methods and outputs.
+This was generally followed but, if an alternative structure seemed more suitable (for example, if the original study already divided items well, but perhaps with different folder names or with multiple scripts folders or so on, we might have used that original structure, as it still served the purpose of being clear and easy to re-run, whilst reducing the number of differences compared with the original study).
+|
+
+## Timings
+
+As per the protocol, the reproduction and evaluation stages were timed.
+Although this was conducted carefully and thoroughly, it will not be perfect, and we recognise some of the potential sources of variation in timings between studies, such as:
+
+* Whether we consistently included amendments to the quarto site and repository and time spent on GitHub commits etc. within the timings for the reproduction.
+* For the first R study (@huang_optimizing_2019), I initially tried to create an environment with R and package versions prior to the article publication date, although had great difficulties with this and ended up using the latest versions.
+This contributed to the set-up time during this reproduction, but on later R models (@kim_modelling_2021 and @johnson_cost_2021), based on that experience, I did not attempt to backdate them when getting started.
+* Any estimated times (for example, if I were partway through working but someone in the office came to talk to me and I forgot to note the time of that, I might estimate if that were about five or ten minutes of conversation, and set the time accordingly).
+* Timings from consensus discussions regarding uncertainities in the evaluation or reproduction (as these might be longer if done in person rather than over email - or vice versa - and I sometimes spent longer on sorting/tidying these for some studies than others, which I would have included in the time)
+* Whether subjectively feel that need to add random seeds during reproduction stage, if results vary considerably between each run, and so a certain seed could get a much more similar result than another
+
+At an estimate, this uncertainty between study timings would lead me to conclude that the timings are approximately correct, give or take up to about four hours.
+However, this is just an estimate, and it is worth noting that @krafczyk_learning_2021, who also conducted computational reproducibility assessments in a different context, estimated that human error introduced a maximum of 8 hours ambiguity in the timings, due to the "non-precise nature of starting and stopping the watch consistently".
+
+## References

### 2024-09-03 pages/paper_evaluation.qmd
docs(evaluation): add key for symbols
fix(eval): correction to Anagnostou ISPOR 4 and 5

@@
 * **J:** @johnson_cost_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-johnson-2021/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>
+
+In this section and below, the criteria for each study are marked as either being fully met (✅), partially met (🟡), not met (❌) or not applicable (N/A).
 
@@
 | **3 Is the model structure described?**<br>...the model’s conceptual structure was described in the form of either graphical or text presentation. | ✅ | ✅ | ✅ | tbc | ✅ |
-| **4 Is the time horizon given?**<br>...the time period covered by the simulation was reported. | ✅ | ✅ | ✅ | ✅ | ✅ | ❌ |
-| **5 Are all simulated strategies/scenarios specified?**<br>...the comparators under test were described in terms of their components, corresponding variations, etc | ✅ | ✅ | ✅ | ✅ | ✅ | N/A |
+| **4 Is the time horizon given?**<br>...the time period covered by the simulation was reported. | ✅ | ✅ | ✅ | ✅ | ❌ |
+| **5 Are all simulated strategies/scenarios specified?**<br>...the comparators under test were described in terms of their components, corresponding variations, etc | ✅ | ✅ | ✅ | ✅ | N/A |
 | **6 Is the target population described?**<br>...the entities simulated and their main attributes were characterized. | ✅ | ❌ | ✅ | ✅ | 🟡 |

### 2024-09-03 pages/repo_evaluation.qmd
docs(evaluation): add key for symbols
fix(eval): correction to huang remote code repo

@@
 
+In this section and below, the criteria for each study are marked as either being fully met (✅), partially met (🟡), not met (❌) or not applicable (N/A).
+
 **Unique criteria:**
@@
 | **Citation information**<br>Instructions on how to cite the research artefact (e.g. CITATION.cff file) | ❌ | ❌ | ❌ | ❌ | ✅ |
-| **Remote code repository**<br>Code available in a remote code repository (e.g. GitHub, GitLab, BitBucket) | ✅ | ❌ | ✅ | ✅ | ✅ |
+| **Remote code repository**<br>Code available in a remote code repository (e.g. GitHub, GitLab, BitBucket) | ✅ | ✅ | ✅ | ✅ | ✅ |
 | **Open science archive**<br>Code stored in an open science archive with FORCE11 compliant citation and guaranteed persistance of digital artefacts (e.g.

### 2024-09-09 pages/paper_evaluation.qmd
feat(evaluation): add kim 2021

@@
 
-<!-- TODO: Add Johnson et al. 2021 and Kim et al. 2021 -->
+<!-- TODO: Add Johnson et al. 2021 -->
 
@@
   'Lim et al. 2020': [16, 2, 3, 3],
-  'Kim et al. 2021': [0, 0, 0, 1],
+  'Kim et al. 2021': [15, 5, 2, 2],
   'Anagnostou et al. 2022': [14, 2, 5, 3],
@@
   'Lim et al. 2020': [12, 0, 4, 2],
-  'Kim et al. 2021': [0, 0, 0, 1],
+  'Kim et al. 2021': [12, 0, 5, 1],
   'Anagnostou et al. 2022': [8, 3, 4, 3],
@@
 The goal is to describe the breadth and depth of the model with respect to the system being studied.
-| ✅ | ✅ | ✅ | tbc | ✅ |
-| **2.2 Base model logic**<br>Give details of the base model logic. Give additional model logic details sufficient to communicate to the reader how the model works. | ✅ | ✅ | ✅ | tbc | ✅ |
+| ✅ | ✅ | ✅ | ✅ | ✅ |
+| **2.2 Base model logic**<br>Give details of the base model logic. Give additional model logic details sufficient to communicate to the reader how the model works. | ✅ | ✅ | ✅ | ✅ | ✅ |
 | **2.3 Scenario logic**<br>Give details of the logical difference between the base case model and scenarios (if any).
@@
 Pseudo-code may be used to describe an algorithm.
-| ✅ | 🟡 | ✅ | tbc | ✅ |
+| ✅ | 🟡 | ✅ | 🟡 | ✅ |
 | **2.5.1 Components - entities**<br>Give details of all entities within the simulation including a description of their role in the model and a description of all their attributes.
 | ✅ | ✅ | ✅ | ✅ | ✅ |
-| **2.5.2 Components - activities**<br>Describe the activities that entities engage in within the model. Provide details of entity routing into and out of the activity. | ✅ | ✅ | ✅ | tbc | ✅ |
-| **2.5.3 Components - resources**<br>List all the resources included within the model and which activities make use of them. | ✅ | ✅ | N/A | tbc | ✅ |
+| **2.5.2 Components - activities**<br>Describe the activities that entities engage in within the model. Provide details of entity routing into and out of the activity. | ✅ | ✅ | ✅ | ✅ | ✅ |
+| **2.5.3 Components - resources**<br>List all the resources included within the model and which activities make use of them. | ✅ | ✅ | N/A | N/A | ✅ |
 | **2.5.4 Components - queues**<br>Give details of the assumed queuing discipline used in the model (e.g.
@@
 Detail any delays or capacity constraints on the queues.
-| ✅ | ✅ | N/A | tbc | ✅ |
+| ✅ | ✅ | N/A | N/A | ✅ |
 | **2.5.5 Components - entry/exit points**<br>Give details of the model boundaries i.e.
@@
 Report whether initialisation of these variables is deterministic or stochastic.
-| 🟡 | ❌ | ❌ | tbc | ❌ |
+| 🟡 | ❌ | ❌ | 🟡 | ❌ |
 | **4.2 Run length**<br>Detail the run length of the simulation model and time units. | ✅ | ✅ | ✅ | ✅ | 🟡 |
@@
 For parallel and distributed simulations the time management algorithms used.
-If the HLA is used then state the version of the standard, which run-time infrastructure (and version), and any supporting documents (FOMs, etc.) | 🟡 |❌ | ❌ | tbc | ❌ |
+If the HLA is used then state the version of the standard, which run-time infrastructure (and version), and any supporting documents (FOMs, etc.) | 🟡 |❌ | ❌ | ❌ | ❌ |
 | **5.4 System specification**<br>State the model run time and specification of hardware used.
@@
 For parallel, distributed and/or use grid or cloud computing, etc.
-state the details of all systems used in the implementation (processors, network, etc.) | ✅ | ❌ | 🟡 | tbc | ❌ |
+state the details of all systems used in the implementation (processors, network, etc.) | ✅ | ❌ | 🟡 | 🟡 | ❌ |
 | **Code access** |
@@
 
-<!-- TODO: Add Johnson and amend Kim after discussion if required -->
+<!-- TODO: Add Johnson -->
 
@@
 | ✅ | ✅ | ✅ | ✅ | ✅ |
-| **3 Is the model structure described?**<br>...the model’s conceptual structure was described in the form of either graphical or text presentation. | ✅ | ✅ | ✅ | tbc | ✅ |
+| **3 Is the model structure described?**<br>...the model’s conceptual structure was described in the form of either graphical or text presentation. | ✅ | ✅ | ✅ | ✅ | ✅ |
 | **4 Is the time horizon given?**<br>...the time period covered by the simulation was reported. | ✅ | ✅ | ✅ | ✅ | ❌ |
@@
 
-<!-- Add johnson and kim -->
+<!-- TODO: Add johnson -->
 
@@
 * @lim_staff_2020 - 1h 12m
-* @kim_modelling_2021
+* @kim_modelling_2021 - 2h 12m
 * @anagnostou_facs-charm_2022 - 53m

### 2024-09-09 pages/repo_evaluation.qmd
feat(evaluation): add kim 2021

@@
 
+<!-- TODO: Add Johnson et al. 2021 -->
+
 **Unique badge criteria:**
@@
   'Lim et al. 2020': [3, 0, 9, 0],
-  'Kim et al. 2021': [0, 0, 0, 1],
+  'Kim et al. 2021': [5, 0, 7, 0],
   'Anagnostou et al. 2022': [10, 0, 2, 0],
@@
   'Lim et al. 2020': [3, 0, 9, 0],
-  'Kim et al. 2021': [0, 0, 0, 1],
+  'Kim et al. 2021': [3, 0, 9, 0],
   'Anagnostou et al. 2022': [5, 0, 7, 0],
@@
   'Lim et al. 2020': [2, 0, 6, 0],
-  'Kim et al. 2021': [0, 0, 0, 1],
+  'Kim et al. 2021': [4, 1, 3, 0],
   'Anagnostou et al. 2022': [7, 0, 1, 0],
@@
   'Lim et al. 2020': [0, 0, 5, 0],
-  'Kim et al. 2021': [0, 0, 0, 1],
+  'Kim et al. 2021': [0, 0, 5, 0],
   'Anagnostou et al. 2022': [1, 1, 3, 0],
@@
 
-<!-- Add johnson and kim -->
+<!-- TODO: Add Johnson et al. 2021 -->
 
@@
 * @lim_staff_2020 - 18m
-* @kim_modelling_2021
+* @kim_modelling_2021 - 18m
 * @anagnostou_facs-charm_2022 - 19m

### 2024-09-09 index.qmd
docs(book): updates to index, framework and protocol pages

@@
 
-* **Introduction** - background on the STARS project, pilot work, and the aim of work package 1
+* **Introduction** - background on STARS, pilot work, and the aim of work package 1
 * **Methods** - summarises the methods which are described in detail in our protocol

### 2024-09-09 pages/framework.qmd
docs(book): updates to index, framework and protocol pages

@@
 ---
+
+<!--TODO: Consider implications of:
+* Reproduction
+* Evaluation of the repository
+* Evaluation of the article
+* Timings -->
 
@@
 **Website**: Could share like <https://joss.readthedocs.io/en/latest/paper.html> but would want to make sure we are adding sufficient detail on top of checklist.
+
+**Interactive web app**: Could make a web app that serves as a "form" for people to complete and then downloaded their completed framework like there is set up for the [PRISMA checklist](https://prisma.shinyapps.io/checklist/).
+
+## Reflections from the evaluations
+
+<!-- TODO: Restructure this into implications for framework, and implications for STRESS-DES-->
+
+**TBC - in progress below...**
+
+Although we can comment on how commonly or uncommonly something met a criteria, it is only a small sample (n=6), so when covered in the DES best practice audit, that might be more informative, as baesd on far more studies.
+
+From evaluation of repository:
+
+* Open license - available on about half, added on request for rest, a very important one as without it you technically cannot reuse someones code
+* Complete materials - rarely, so alot of time spent on writing code and figuring out how best to do that
+* Dependency management - rarely done, and although not an issue in simpler cases, a big impact in more complex
+* Model interface - provided for two although not helpful as (1) host no longer operating, and as not focus, didn't try to run locally, and (2) other app was viewable but didn't produce the figures and outcomes from paper (was more general, whilst paper delved into scenarios beyond app)
+
+From evaluation of paper:
+
+* It often took a long time (up to 2 hours).
+It would be valuable if the completed checklist were provided along with the paper, like how people often do with equator network reporting guidelines like PRISMA.
+Consider varying levels detail its possible to complete (yes/no, linking to sections, full detail).
+Linking to sections is minimum needed to be really useful.
+Yes/no doesn't impact time to find information really.
+* Input parameters - very handy, as if uncertain in code, use this to check or code
+* Some of my evaluations were more light handed (e.g. STRESS 1.2 and 1.3) whilst some were more nit-picky
+* Run length - important for knowing when its slow
+* Scenarios - important to be clear, felt provided in a table was the clearest
+
+Reflections on STRESS-DES from having worked on it:
+
+* 1.2 "how and when calculated" might feel like excess detail
+* 1.3A providing name for each scenario doesn't always seem necessary
+* 2.4 initially found confusing/irrelevant (e.g. "operation of conveyor")
+* 3.2 would be helpful to have more examples
+* 5.1 listing all packages and their versions is never particularly achievable or feasible.
+More feasible is specifying main package used for model (e.g.
+simmer, simpy, base R, numpy/pandas) and providing finer details in code (although it was helpful to have version of this package in the paper, when no versions were mentioned in the GitHub)
+* 5.2 Algorithm used is tricky/uncommon knowledge
+* 5.3 Event-processing machanism is tricky/uncommon knowledge
+* Too many different things in several (could benefit from being clearer, seperated, or into components like 2.5). This was the case for 1.3, 3.3, 4.1, 4.3, 5.1, 5.2, 5.3, 5.4
+
+Reflections from comparing what is in STRESS-DES v.s. ISPOR-derived:
+
+* Scenarios - ISPOR has a simpler description
+* Model uncertainities - nice that ISPOR requires this
+* ISPOR has lots of items that relate to validity and how "good" it is (9 to 18) - whilst STRESS doesn't touch on this

### 2024-09-09 pages/protocol.qmd
docs(book): updates to index, framework and protocol pages

@@
 |
-| Moving onto evaluation stage before receive author response regarding reproduction discrepancy | In the protocol, we required that authors are contacted if there are any remaining difficulties in running the code or items in the scope that were not reproduced.
+| Moving onto evaluation stage before receive author response regarding reproduction discrepancy or before getting consensus on reproduction | In the protocol, we required that authors are contacted if there are any remaining difficulties in running the code or items in the scope that were not reproduced.
 The authors were given a total of four weeks to respond if they chose to.
@@
 The rationale for this was that the timings for the reproduction would be influenced by whether the evaluation had been completed or not, and vice versa.
-However, given the many possible influences on the timings, this was considered negligble.
+However, given the many possible influences on the timings, this was considered negligble.<br><br>We also required consensus on whether items had been succesfully reproduced or not before moving on.
+In two cases, this was not done due to a two week period of annual leave where it wouldn't be possible to get a second opinion, and so I progressed with the evaluation and got consensus on reproductions afterwards.
 |

### 2024-09-10 pages/other_studies.qmd
docs(other studies): add some rough notes on comparison to other studies

---
title: "Comparison to other studies"
bibliography: ../references.bib
---

**In-progress**

TODO: Add page comparing our findings to other studies. This could include:

* Studies that have gone through this same process of finding barriers in reproductions
* Studies that recommend how to share code (although, it might be simpler to just start with that first bullet and then decide whether to do both)

*Do we also compare the evaluation results? Or do we just use that in context of barriers?* (e.g. @schwander_replication_2021 and @zhang_reporting_2020 for reporting... @laurinavichyute_share_2022 for code...)

*not sure if want to be comparing the actual proportions reproduced... or maybe do, but important to bare in mind what is being compared and what define as success... e.g. some include studies that haven't shared the code*

Starting points:

* @krafczyk_learning_2021 - results are recommendations based on experiences, which were:
    * can see completion in figure 1
    * being clear on links between article, code and data (e.g. which code uses which data, and which parts of code made each bit of article)
    * include scripts for each aspect of article, with it easy to locate the scripts needed, and the scripts including the parameters needed and clearly label
    * be clear about hardware needed, e.g. if large amount of computing resources would be required. at least report hardware used. ideally include "small test case that can be run by users with conventional hardware"
    * list software dependencies and versions
    * use seeds, and report seed you used
    * make all code and data available with an appropriate license
    * include master script that runs in computations in publication
    * use same terminology in code and article
    * use version control and specify the e.g. commit hash that identifies the version used
    * avoid hard coding parameters
    * design scripts in a way that allows people to easily change parameters and run again
    * avoid hard coding file paths
    * provide script that checks whether users results match original (within expected deviation)
    * if compare against competing methods, include info on how those were implemented and tested
    * use build system for C/C++ code
    * provide scripts to make the figures and tables
* @wood_push_2018
    * complete data: 27 comparable results, 5 minor differences, 0 major differences
    * incomplete data: 10 comparable, 4 minor differences, 1 major differences
    * main issue was the code and data not being shared
* @schwander_replication_2021
    * reproduction success for 3 out of 4 models
    * facilitators:
        * "Model structure and possible state transitions were presented in a state transition diagram"
        * "Overview of input parameters was provided in table format"
    * hurdles:
        * "PSAs were performed" (probablistic sensitivity analysis)
        * "Relevant PSA values for PSA result reproduction were provided (type of distribution and either mean and standard deviation or distribution parameters were provided)"
        * "Clinical event simulation results were provided (which are very helpful to guide potential assumptions to be made for rebuilding the model and which provide an additional means of testing the fit of the replication)"
        * "Relevant details on the underlying life tables were provided (including year of data)"
        * "Several self-created regression equations were introduced but without details on how to apply/solve the provided regressions correctly"
* @laurinavichyute_share_2022
* @konkol_computational_2019
* @hardwicke_analytic_2021

### 2024-09-10 pages/relationship_reproduction_evaluation.qmd
docs(relationship): add blank page to be completed with info on any relationship between reproduction and evaluation

---
title: "Relationship between reproduction and evaluation"
bibliography: ../references.bib
---

TODO: Add this page, to assess whether (and if so, how) there is a relationship between the evaluation (code and/or reporting) and how easy it was / able we were to reproduce

### 2024-09-27 pages/protocol.qmd
docs(protocol): add rationale for expanding from 6 to 8 studies

@@
 
+## Major deviations from the protocol
+
+There was one major deviation from the protocol...
+
+| Deviation | Description and reason for the change |
+| --- | --- |
+| Expanding from 6 to 8 studies | Whilst partway through the 6th study, we reflected on what we had found so far, and felt it would be beneficial to do a few more studies.
+The primary motivation for this was to try and include a selection of studies that reflect the range of studies in the literature.
+So far, we had a few studies where the model code/run times were very large or very small, and we felt it beneficial to try and include some more "medium-sized" studies, as these are more typical of the literature.
+We also thought it would be good to include an older study (for example, about 10 years ago, if we can find one), as all those included so far were within the last few years, but working with more outdated code will be/can be a problem people encounter.
+|
+
 ## Minor deviations from the protocol
@@
 |
+| Retrospective archiving | For Johnson et al.
+2021, I forgot to create a release to archive this repository after defining scope and before proceeding with reproduction.
+However, I was easily able to resolve this by setting the release to a prior commit, choosing the commit from that timepoint (between scope and reproduction), so it was as if it had been done at the time |
 

### 2024-10-11 pages/paper_evaluation.qmd
docs(evaluation): add spaces for hernandez and wood results

@@
 
+Consider: **What criteria are people struggling to meet from the guidelines?**
+
 ## Summary
 
-<!-- TODO: Add Johnson et al. 2021 -->
+<!-- TODO: Add Johnson et al. 2021, Hernandez et al. 2015 and Wood et al. 2021 -->
 
@@
   'Anagnostou et al. 2022': [14, 2, 5, 3],
-  'Johnson et al. 2021': [0, 0, 0, 1]
+  'Johnson et al. 2021': [0, 0, 0, 1],
+  'Hernandez et al. 2015': [18, 2, 3, 1],
+  'Wood et al. 2021': [0, 0, 0, 1]
 }
@@
   'Anagnostou et al. 2022': [8, 3, 4, 3],
-  'Johnson et al. 2021': [0, 0, 0, 1]
+  'Johnson et al. 2021': [0, 0, 0, 1],
+  'Hernandez et al. 2015': [10, 0, 8, 0],
+  'Wood et al. 2021': [0, 0, 0, 1]
 }
@@
 * **S:** @shoaib_simulation_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-shoaib-2022/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>
-* **H:** @huang_optimizing_2019  - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-huang-2019/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>
+* **Hu:** @huang_optimizing_2019  - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-huang-2019/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>
 * **L:** @lim_staff_2020 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-lim-2020/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>
@@
 * **J:** @johnson_cost_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-johnson-2021/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>
+* **He:** @hernandez_optimal_2015 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-hernandez-2015/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>
+* **W:** @wood_value_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-wood-2021/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>
 
@@
 
-<!-- TODO: Add Johnson et al. 2021, and update after discussion of Kim et al. 2021 -->
+<!-- TODO: Add Johnson et al. 2021, Hernandez et al. 2015 and Wood et al. 2021, and update after discussion of Kim et al. 2021 -->
 
-| Item | S | H | L | K | A | J |
-| - | - | - | - | - | - | - | - |
+| Item | S | Hu | L | K | A | J | He | W |
+| - | - | - | - | - | - | - | - | - | - |
 | **Objectives** | 
@@
 | ✅ | ✅ | ✅ | ✅ | ✅ |
-: {tbl-colwidths="[70, 5, 5, 5, 5, 5, 5]"}
+: {tbl-colwidths="[60, 5, 5, 5, 5, 5, 5, 5, 5]"}
 
@@
 * **S:** @shoaib_simulation_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-shoaib-2022/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>
-* **H:** @huang_optimizing_2019  - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-huang-2019/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>
+* **Hu:** @huang_optimizing_2019  - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-huang-2019/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>
 * **L:** @lim_staff_2020 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-lim-2020/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>
@@
 * **J:** @johnson_cost_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-johnson-2021/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>
+* **He:** @hernandez_optimal_2015 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-hernandez-2015/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>
+* **W:** @wood_value_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-wood-2021/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>
 
-<!-- TODO: Add Johnson -->
+<!-- TODO: Add Johnson et al. 2021, Hernandez et al. 2015 and Wood et al. 2021, and update after discussion of Kim et al. 2021 -->
 
-| Item | S | H | L | K | A | J |
-| - | - | - | - | - | - | - | - |
+| Item | S | Hu | L | K | A | J | He | W |
+| - | - | - | - | - | - | - | - | - | - |
 | **Model conceptualisation** |
@@
 | **18 Are model limitations discussed?**<br>...limitations of the assessed model, especially limitations of interest to decision makers, were discussed. | ✅ | 🟡 | ✅ | ✅ | 🟡 |
-: {tbl-colwidths="[70, 5, 5, 5, 5, 5, 5]"}
+: {tbl-colwidths="[60, 5, 5, 5, 5, 5, 5, 5, 5]"}
 
@@
 
-<!-- TODO: Add johnson -->
+<!-- TODO: Add johnson, hernandez, wood -->
 
@@
 * @johnson_cost_2021
+* @hernandez_optimal_2015
+* @wood_value_2021
 

### 2024-10-11 pages/reflections.qmd
docs(evaluation): add spaces for hernandez and wood results

@@
 
-<!--TODO: Add Johnson et al. 2021 reflections once have finished reproduction -->
+<!--TODO: Add Johnson et al. 2021, Hernandez et al. 2015 and Wood et al. 2021 reflections once have finished reproduction -->
 
@@
 * @johnson_cost_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-johnson-2021/evaluation/reflections.html" target="_blank">link to reflections</a>
+* @hernandez_optimal_2015 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-hernandez-2015/evaluation/reflections.html" target="_blank">link to reflections</a>
+* @wood_value_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-wood-2021/evaluation/reflections.html" target="_blank">link to reflections</a>
 
@@
 
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |
 
@@
 
-**Reflections:**
+@hernandez_optimal_2015: <!--TODO-->
+
+@wood_value_2021: <!--TODO-->
+
+**Reflections:** <!--TODO: Update reflections (since have added Johnson, Hernandez and Wood) -->
 
@@
 
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | 🟡 | 🟡 | 🟡 | <!--TODO--> |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ❌ | 🟡 | 🟡 | 🟡 | <!--TODO--> | <!--TODO--> | <!--TODO--> |
 
@@
 
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: |
-| ✅ | ❌ | ✅ | ✅ | ✅ | <!--TODO--> |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ✅ | ❌ | ✅ | ✅ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |
 
@@
 
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ✅ | ✅ | ✅ | ✅ | <!--TODO--> |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ✅ | ✅ | ✅ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |
 
@@
 
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | 🟡 | ❌ | ✅ | N/A | <!--TODO--> |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | 🟡 | ❌ | ✅ | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |
 
@@
 
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ✅ | ✅ | ❌ | ✅ | <!--TODO--> |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ✅ | ✅ | ❌ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |
 
@@
 
-**Reflections:** Large amounts of code duplication are non-ideal as they can:
+@hernandez_optimal_2015: <!--TODO-->
+
+@wood_value_2021: <!--TODO-->
+
+**Reflections:** <!--TODO: Update reflections (since have added Johnson, Hernandez and Wood) --> Large amounts of code duplication are non-ideal as they can:
 
@@
 
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ✅ | 🟡 | 🟡 | <!--TODO--> |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ❌ | ✅ | 🟡 | 🟡 | <!--TODO--> | <!--TODO--> | <!--TODO--> |
 
@@
 
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: |
-| 🟡 | ❌ | ❌ | ❌ | N/A | <!--TODO--> |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| 🟡 | ❌ | ❌ | ❌ | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |
 
@@
 
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: |
-| N/A | N/A | N/A | ❌ | N/A | <!--TODO--> |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| N/A | N/A | N/A | ❌ | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |
 
@@
 
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | ❌ | N/A | <!--TODO--> |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ❌ | ❌ | ❌ | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |
 
@@
 
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |
 
@@
 
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: |
-| 🟡 | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| 🟡 | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |
 
@@
 
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | ✅ | ✅ | <!--TODO--> |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ❌ | ❌ | ✅ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |
 
@@
 
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | 🟡 | N/A | N/A | <!--TODO--> |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ❌ | 🟡 | N/A | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |
 
@@
 
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ✅ | N/A | N/A | N/A | <!--TODO--> |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ✅ | N/A | N/A | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |
 
@@
 
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: |
-| ✅ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ✅ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |
 
@@
 
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | N/A | 🟡 | ❌ | N/A | <!--TODO--> |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | N/A | 🟡 | ❌ | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |
 
@@
 
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | ❌ | ❌ | <!--TODO--> |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ❌ | ❌ | ❌ | ❌ | <!--TODO--> | <!--TODO--> | <!--TODO--> |
 
@@
 
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | N/A | ❌ | N/A | <!--TODO--> |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ❌ | N/A | ❌ | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |
 
@@
 
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | 🟡 | ✅ | <!--TODO--> |
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ❌ | ❌ | 🟡 | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |
 
@@
 
-**Reflections:**
+@johnson_cost_2021: <!--TODO-->
+
+@hernandez_optimal_2015: <!--TODO-->
+
+@wood_value_2021: <!--TODO-->
+
+**Reflections:** <!--TODO: Update reflections (since have added Johnson, Hernandez and Wood) -->
 

### 2024-10-11 pages/repo_evaluation.qmd
docs(evaluation): add spaces for hernandez and wood results

@@
   'Anagnostou et al. 2022': [10, 0, 2, 0],
-  'Johnson et al. 2021': [0, 0, 0, 1]
+  'Johnson et al. 2021': [0, 0, 0, 1],
+  'Hernandez et al. 2015': [0, 0, 0, 1],
+  'Wood et al. 2021': [0, 0, 0, 1]
 }
@@
   'Anagnostou et al. 2022': [5, 0, 7, 0],
-  'Johnson et al. 2021': [0, 0, 0, 1]
+  'Johnson et al. 2021': [0, 0, 0, 1],
+  'Hernandez et al. 2015': [0, 0, 0, 1],
+  'Wood et al. 2021': [0, 0, 0, 1]
 }
@@
   'Anagnostou et al. 2022': [7, 0, 1, 0],
-  'Johnson et al. 2021': [0, 0, 0, 1]
+  'Johnson et al. 2021': [0, 0, 0, 1],
+  'Hernandez et al. 2015': [0, 0, 0, 1],
+  'Wood et al. 2021': [0, 0, 0, 1]
 }
@@
   'Anagnostou et al. 2022': [1, 1, 3, 0],
-  'Johnson et al. 2021': [0, 0, 0, 1]
+  'Johnson et al. 2021': [0, 0, 0, 1],
+  'Hernandez et al. 2015': [0, 0, 0, 1],
+  'Wood et al. 2021': [0, 0, 0, 1]
 }
@@
 * **S:** @shoaib_simulation_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-shoaib-2022/evaluation/badges.html" target="_blank">link to evaluation</a>
-* **H:** @huang_optimizing_2019  - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-huang-2019/evaluation/badges.html" target="_blank">link to evaluation</a>
+* **Hu:** @huang_optimizing_2019  - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-huang-2019/evaluation/badges.html" target="_blank">link to evaluation</a>
 * **L:** @lim_staff_2020 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-lim-2020/evaluation/badges.html" target="_blank">link to evaluation</a>
@@
 * **J:** @johnson_cost_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-johnson-2021/evaluation/badges.html" target="_blank">link to evaluation</a>
+* **He:** @hernandez_optimal_2015 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-hernandez-2015/evaluation/badges.html" target="_blank">link to evaluation</a>
+* **W:** @wood_value_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-wood-2021/evaluation/badges.html" target="_blank">link to evaluation</a>
 
-<!-- TODO: Add Johnson et al. 2021 -->
+<!-- TODO: Add Johnson et al. 2021, Hernandez et al. 2015 and Wood et al. 2021 -->
 
@@
 
-| Item | S | H | L | K | A | J |
-| - | - | - | - | - | - | - | - |
+| Item | S | Hu | L | K | A | J | He | W |
+| - | - | - | - | - | - | - | - | - | - |
 | **Criteria related to how artefacts are shared** |
@@
 | Reproduced within approximately one hour (excluding compute time) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
-: {tbl-colwidths="[70, 5, 5, 5, 5, 5, 5]"}
+: {tbl-colwidths="[60, 5, 5, 5, 5, 5, 5, 5, 5]"}
 
@@
 
-<!-- TODO: Add Johnson et al. 2021 -->
+<!-- TODO: Add Johnson et al. 2021, Hernandez et al. 2015 and Wood et al. 2021 -->
 
-| Item | S | H | L | K | A | J |
-| - | - | - | - | - | - | - | - |
+| Item | S | Hu | L | K | A | J | He | W |
+| - | - | - | - | - | - | - | - | - | - |
 | **“Open objects” badges** |
@@
 to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community)<br>• Artefacts are clearly documented and accompanied by a README file with step-by-step instructions on how to reproduce results in the manuscript | ❌ | ❌ | ❌ | ❌ | ❌ |
-: {tbl-colwidths="[70, 5, 5, 5, 5, 5, 5]"}
+: {tbl-colwidths="[60, 5, 5, 5, 5, 5, 5, 5, 5]"}
 
@@
 * **S:** @shoaib_simulation_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-shoaib-2022/evaluation/artefacts.html" target="_blank">link to evaluation</a>
-* **H:** @huang_optimizing_2019  - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-huang-2019/evaluation/artefacts.html" target="_blank">link to evaluation</a>
+* **Hu:** @huang_optimizing_2019  - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-huang-2019/evaluation/artefacts.html" target="_blank">link to evaluation</a>
 * **L:** @lim_staff_2020 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-lim-2020/evaluation/artefacts.html" target="_blank">link to evaluation</a>
@@
 * **J:** @johnson_cost_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-johnson-2021/evaluation/artefacts.html" target="_blank">link to evaluation</a>
+* **He:** @hernandez_optimal_2015 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-hernandez-2015/evaluation/artefacts.html" target="_blank">link to evaluation</a>
+* **W:** @wood_value_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-wood-2021/evaluation/artefacts.html" target="_blank">link to evaluation</a>
 
-<!-- TODO: Add Johnson et al. 2021 -->
+<!-- TODO: Add Johnson et al. 2021, Hernandez et al. 2015 and Wood et al. 2021 -->
 
-| Item | S | H | L | K | A | J |
-| - | - | - | - | - | - | - | - |
+| Item | S | Hu | L | K | A | J | He | W |
+| - | - | - | - | - | - | - | - | - | - |
 | **Essential components** |
@@
 | **Web app hosting**<br>Host web app online (e.g. Streamlit Community Cloud, ShinyApps hosting) | ❌ | ✅ | ❌ | ❌ | 🟡 |
-: {tbl-colwidths="[70, 5, 5, 5, 5, 5, 5]"}
+: {tbl-colwidths="[60, 5, 5, 5, 5, 5, 5, 5, 5]"}
 
@@
 
-<!-- TODO: Add Johnson et al. 2021 -->
+<!-- TODO: Add Johnson et al. 2021, Hernandez et al. 2015 and Wood et al. 2021 -->
 
@@
 * @johnson_cost_2021
+* @hernandez_optimal_2015 -
+* @wood_value_2021 -
 

### 2024-10-11 pages/reproduction.qmd
fix(reproduction): correct kim 2021 time
docs(evaluation): add spaces for hernandez and wood results

@@
 **@kim_modelling_2021:** Adapts a previously developed **R (Rcpp, expm, msm, foreach, iterators, doParallel)** model for abdominal aortic aneurysm (AAA) screening of men in England.
-The model is adapted/used to explore different approaches to resuming screening and surgical repair for AAA, as these survives were paused or substantially reduced during COVID-19 due to concerns about virus transmission.
+The model is adapted/used to explore different approaches to resuming screening and surgical repair for AAA, as these services were paused or substantially reduced during COVID-19 due to concerns about virus transmission.
 <a href="https://pythonhealthdatascience.github.io/stars-reproduce-kim-2021/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>
@@
 
+**@hernandez_optimal_2015:** TBC <!-- TODO -->
+
+**@wood_value_2021:** TBC <!-- TODO -->
+
 ## Scope
@@
 | Lim et al. 2020 | 9 items:<br>• 5 tables<br>• 4 figures | 9 out of 9 (100%) | 12h 27m |
-| Kim et al. 2021 | 10 items:<br>• 3 tables<br>• 6 figures<br>• 1 in-text result | 10 out of 10 (100%) | 13h 59m |
-| Anagnostou et al. 2022 | 1 item:<br>• 1 figure | 1 out of 1 (100%) | 2h 10m |
+| Kim et al. 2021 | 10 items:<br>• 3 tables<br>• 6 figures<br>• 1 in-text result | 10 out of 10 (100%) | 14h 42m |
+| Anagnostou et al. 2022 | 1 item:<br>• 1 figure | 1 out of 1 (100%) | 2h 11m |
 | Johnson et al. 2021 | 5 items:<br>• 1 table<br>• 4 figures | TBC | TBC |
+| Hernandez et al. 2015 | 8 items:<br>• 6 figures<br>• 2 tables | TBC | TBC |
+| Wood et al. 2021 | 5 items:<br>• 4 figures<br>• 1 table | TBC | TBC |
 
@@
 
-<!-- TODO: Add Johnson et al. 2021 once conducted reproduction -->
+<!-- TODO: Add Johnson et al. 2021, Hernandez et al. 2015 and Wood et al. 2021 once conducted reproduction -->
 
@@
 
+# Hernandez et al. 2015
+# TODO: Add times once completed reproduction
+
+# Wood et al. 2021
+# TODO: Add times once completed reproduction
+
 # Create list with the dataframes, labels and colours, to use for each plot
@@
     (df_ana, 'Anagnostou<br>et al. 2022', '#66ccee')
-    # 'Johnson et al. 2021', '#aa3377')
+    # (df_joh, 'Johnson et<br>al. 2021', '#aa3377'),
+    # (df_her, 'Hernandez<br>et al. 2015', '#117733'),
+    # (df_woo, 'Woord et al.<br>2021', '#882255')
 ]

### 2024-10-11 pages/protocol.qmd
docs(protocol): small clarification to minor deviations

@@
 However, given the many possible influences on the timings, this was considered negligble.<br><br>We also required consensus on whether items had been succesfully reproduced or not before moving on.
-In two cases, this was not done due to a two week period of annual leave where it wouldn't be possible to get a second opinion, and so I progressed with the evaluation and got consensus on reproductions afterwards.
+In some cases, this was not done, as other team members were not available (e.g.
+busy or on annual leave) and so could not yet give a second opinion, and so I progressed with the evaluation and got consensus on reproductions afterwards, once they were available.
 |
 | Organisation of the repository for the research compendium | In the protocol, we had planned that seperate folders were created for data, methods and outputs.
-This was generally followed but, if an alternative structure seemed more suitable (for example, if the original study already divided items well, but perhaps with different folder names or with multiple scripts folders or so on, we might have used that original structure, as it still served the purpose of being clear and easy to re-run, whilst reducing the number of differences compared with the original study).
+This was generally followed but, if an alternative structure seemed more suitable.
+For example, if the original study already divided items well, but perhaps with different folder names or with multiple scripts folders or so on, we might have used that original structure, as it still served the purpose of being clear and easy to re-run, whilst reducing the number of differences compared with the original study.
 |

### 2024-10-11 pages/other_studies.qmd
docs(other studies): add a few others to look into

@@
 * @hardwicke_analytic_2021
+* @monks_computer_2023 (although overlap - look at how many of mine are from the review - some were identified from that, but some were not)
+* @henderson_reproducibility_2024

### 2024-10-11 pages/protocol.qmd
docs(protocol): add deviation about source of papers

@@
 However, I was easily able to resolve this by setting the release to a prior commit, choosing the commit from that timepoint (between scope and reproduction), so it was as if it had been done at the time |
+| Identification of papers | Although X <!--TODO: Count numbers--> papers were identified from the review by @monks_computer_2023, X were identified from additional searches (informal, not systematic) |
 

### 2024-10-11 pages/reflections.qmd
docs(results): add extra TODO statements to results pages

@@
 * @wood_value_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-wood-2021/evaluation/reflections.html" target="_blank">link to reflections</a>
+
+<!-- TODO: Consider whether to make further attempts at managing to backdate R.
+Didn't manage before.
+E.g.
+`containerit` package.
+Although - is it necessary, if I succeeded without?
+Note, I always backdated the python environments.
+So, relatedly, TODO: Is it worth checking/trying with newest Python and seeing if they would work?</mark -->
+
+<!-- TODO: Add reflections related specifically to the reproduction package and second reproduction test parts of the work (i.e. after the reproduction) -->
+
+<!-- TODO: Once complete, carefully go over again and check everything is correct -->
 

### 2024-10-16 pages/reproduction.qmd
docs(results): add extra TODO statements to results pages
docs(reproductions): add hernandez and wood

@@
 ---
+
+<!-- TODO: Once complete, carefully go over again and check everything is correct -->
 
@@
 
-**@lim_staff_2020:** Uses **python (numpy and pandas)** to model the transmission of COVID-19 in a laboratory.
+**@lim_staff_2020:** Uses **python (NumPy and pandas)** to model the transmission of COVID-19 in a laboratory.
 It examines the proportion of staff infected in scenarios varying the: number of shifts per day; number of staff per shift; overall staff pool; shift patterns; secondary attack rate of the virus; introduction of protective measures (social distancing and personal protective equipment).
@@
 **@anagnostou_facs-charm_2022:** This paper includes two models - we have focussed just on the dynamiC Hospital wARd Management (CHARM) model.
-CHARM uses **Python (simpy)** to model intensive care units (ICU) in the COVID-19 pandemic (as well as subsequent stays in a recovery bed).
+CHARM uses **python (SimPy)** to model intensive care units (ICU) in the COVID-19 pandemic (as well as subsequent stays in a recovery bed).
 It includes three types of admission to the ICU (emergency, elective or COVID-19).
@@
 
-**@hernandez_optimal_2015:** TBC <!-- TODO -->
+**@hernandez_optimal_2015:** This study models Points-of-Dispensing (PODs) in New York City.
+These are sites set up during a public health emergency to dispense counter-measures.
+The authors use evolutionary algorithms combined with discrete-event simulation to explore optimal staff numbers with regards to resource use, wait time and throughput.
+They use **python** for most of the analysis (with **SimPy** for the simulation component), but **R** to produce the plots and tables for the paper.
+<a href="https://pythonhealthdatascience.github.io/stars-reproduce-hernandez-2015/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>
 
-**@wood_value_2021:** TBC <!-- TODO -->
+**@wood_value_2021:** This study uses discrete-event simulation (**R (base R, dplyr, tidyr)**) to explore the deaths and life years lost under different triage strategies for an intensive care unit, relative to a baseline strategy.
+The unit is modelled with 20 beds (varied from 10 to 200 in sensitivity analyses).
+Three different triage strategies are explored, under three different projected demand trajectories.
+<a href="https://pythonhealthdatascience.github.io/stars-reproduce-wood-2021/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>
 
@@
 | Anagnostou et al. 2022 | 1 item:<br>• 1 figure | 1 out of 1 (100%) | 2h 11m |
-| Johnson et al. 2021 | 5 items:<br>• 1 table<br>• 4 figures | TBC | TBC |
-| Hernandez et al. 2015 | 8 items:<br>• 6 figures<br>• 2 tables | TBC | TBC |
-| Wood et al. 2021 | 5 items:<br>• 4 figures<br>• 1 table | TBC | TBC |
+| Johnson et al. 2021 | 5 items:<br>• 1 table<br>• 4 figures | <!--TODO--> | <!--TODO--> |
+| Hernandez et al. 2015 | 8 items:<br>• 6 figures<br>• 2 tables | 1 out of 8 (12.5%) | 17h 56m |
+| Wood et al. 2021 | 5 items:<br>• 4 figures<br>• 1 table | 5 out of 5 (100%) | 3h 50m |
 
@@
 
-<!-- TODO: Add Johnson et al. 2021, Hernandez et al. 2015 and Wood et al. 2021 once conducted reproduction -->
+<!-- TODO: Add Johnson et al. 2021 once conducted reproduction -->
 
@@
 
-# Hernandez et al. 2015
-# TODO: Add times once completed reproduction
+# Hernandez et al. 2015 (1/8)
+time_her = [
+    [1076, 'Figure 5'], # Finished work, not completed, adjust to set to NaN
+    [696, 'Figure 6'],
+    [np.nan, 'Figure 7'],
+    [np.nan, 'Figure 8'],
+    [np.nan, 'Figure 9'],
+    [np.nan, 'Figure 10'],
+    [np.nan, 'Table 3'],
+    [np.nan, 'Table 4']]
+df_her = process_times(time_her, adjust='Figure 5')
 
 # Wood et al. 2021
-# TODO: Add times once completed reproduction
+time_woo = [
+    [170, 'Figure 4'],
+    [170, 'Table 4'],
+    [170, 'Figure 5'],
+    [170, 'Figure 6'],
+    [230, 'Figure 7']]
+df_woo = process_times(time_woo)
 
@@
     (df_kim, 'Kim et<br>al. 2021', '#ccbb44'),
-    (df_ana, 'Anagnostou<br>et al. 2022', '#66ccee')
+    (df_ana, 'Anagnostou<br>et al. 2022', '#66ccee'),
     # (df_joh, 'Johnson et<br>al. 2021', '#aa3377'),
-    # (df_her, 'Hernandez<br>et al. 2015', '#117733'),
-    # (df_woo, 'Woord et al.<br>2021', '#882255')
+    (df_her, 'Hernandez<br>et al. 2015', '#882255'),
+    (df_woo, 'Wood et al.<br>2021', '#117733')
 ]

### 2024-10-16 pages/reflections.qmd
docs(reflections): add wood 2021

@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |
+| ❌ | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> | <!--TODO--> | ❌ |
 
@@
 
-@wood_value_2021: <!--TODO-->
+@wood_value_2021: Not met. However, easily resolved based on imports to `.R` script.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | 🟡 | 🟡 | 🟡 | <!--TODO--> | <!--TODO--> | <!--TODO--> |
+| ❌ | ❌ | 🟡 | 🟡 | 🟡 | <!--TODO--> | <!--TODO--> | 🟡 |
 
@@
 @anagnostou_facs-charm_2022: Partially met (depending on how strict you are being).
-The Python version was stated in the paper, and the simpy version was stated in the complementary app repository (although neither were mentioned in the model repository itself).
+The Python version was stated in the paper, and the SimPy version was stated in the complementary app repository (although neither were mentioned in the model repository itself).
 
@@
 
-@wood_value_2021: <!--TODO-->
+@wood_value_2021: Partially met.
+States version of R but not package.
+Due to prior issues with backdating R, used latest versions.
+There were no issues using the latest versions of R and packages, but if there had been, it would be important to know what versions had previously been used and worked.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ✅ | ❌ | ✅ | ✅ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |
+| ✅ | ❌ | ✅ | ✅ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |
 
@@
 
-@wood_value_2021: <!--TODO-->
+@wood_value_2021: Fully met. Provided as a single `.R` file which ran the model with a for loop.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ✅ | ✅ | ✅ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |
+| ❌ | ✅ | ✅ | ✅ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |
 
@@
 
-@wood_value_2021: <!--TODO-->
+@wood_value_2021: Fully met. Changes inputs to run all scenarios from a single `.R` file.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | 🟡 | ❌ | ✅ | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |
+| ❌ | 🟡 | ❌ | ✅ | N/A | <!--TODO--> | <!--TODO--> | ✅ |
 
@@
 
-@wood_value_2021: <!--TODO-->
+@wood_value_2021: Fully met. All model parameters for the scenarios/sensitivity analysis could be varied from "outside" the model code itself.
 
@@
 Hence, have included as two seperate reflections.
+* Important to note that we evaluate this in the context of reproduction - and have not checked for hard-coded parameters outside the specified scenario analyses, but that someone may wish to alter if reusing the model for a different analysis/context/purpose.
+
+:::
+
+::: {.callout-warning icon=false collapse=true}
+
+## Use relative file paths
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | ✅ |
+
+@shoaib_simulation_2021: <!--TODO-->
+
+@huang_optimizing_2019: <!--TODO-->
+
+@lim_staff_2020: <!--TODO-->
+
+@kim_modelling_2021: <!--TODO-->
+
+@anagnostou_facs-charm_2022: <!--TODO-->
+
+@johnson_cost_2021: <!--TODO-->
+
+@hernandez_optimal_2015: <!--TODO-->
+
+@wood_value_2021: Fully met.
+Although I then changed things a bit as reorganised repository and prefer not to work with `setwd()`, these were set up in such a way that it would be really easy to correct file path, just by setting working directory at start of script.
+
+**Reflections:** <!--TODO: Update reflections (when add Shoaib, Huang, Lim, Kim and Wood) and then (since have added Johnson, Hernandez and Wood) -->
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ✅ | ✅ | ❌ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |
+| ❌ | ✅ | ✅ | ❌ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |
 
@@
 
-@johnson_cost_2021: Fully met.
+@anagnostou_facs-charm_2022: Fully met.
 
@@
 
-@wood_value_2021: <!--TODO-->
+@wood_value_2021: Fully met.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ✅ | 🟡 | 🟡 | <!--TODO--> | <!--TODO--> | <!--TODO--> |
+| ❌ | ❌ | ✅ | 🟡 | 🟡 | <!--TODO--> | <!--TODO--> | ❌ |
 
@@
 
-@wood_value_2021: <!--TODO-->
+@wood_value_2021: Not met. Very few comments, so for the small bit of the code that I did delve into, took a bit of working out what different variables referred to.
 
@@
 
-## Run time and memory usage
+## Run time, memory usage and file size
 
@@
 * @johnson_cost_2021: <!--TODO-->
+* @hernandez_optimal_2015: <!--TODO-->
+* @wood_value_2021: No changes made, but unlike other reproduction, didn't try to run at smaller amounts - just set it to run as-is over the weekend.
 
 For @kim_modelling_2021, an error appears to have been introduced with the aoorta diameter thresholds by switching between nested and unnested lists, which I’m anticipating was unresolved due to the long run times of the model meaning they weren’t all run in sequence at the end.
-
-@hernandez_optimal_2015: <!--TODO-->
-
-@wood_value_2021: <!--TODO-->
 
@@
 
+::: {.callout-warning icon=false collapse=true}
+
+## Avoid large file sizes if possible
+
+I have not evaluated like as a criteria, as a large file size is not inherently a bad thing, and might be difficult to avoid.
+However, when files are very large, this can make things trickier, such as with requiring compression and use of GitHub Large File Storage (LFS) for tracking, which has limits on the free tier.
+
+Regarding file sizes in each study:
+
+* @shoaib_simulation_2021: <!--TODO-->
+* @huang_optimizing_2019: <!--TODO-->
+* @lim_staff_2020: <!--TODO-->
+* @kim_modelling_2021: <!--TODO-->
+* @anagnostou_facs-charm_2022: <!--TODO-->
+* @johnson_cost_2021: <!--TODO-->
+* @hernandez_optimal_2015: <!--TODO-->
+* @wood_value_2021: Aggregate results files are small (327 kB), but raw results files are very large (2.38 GiB), and even when compressed to `.csv.gz` (128 MiB) require using of GitHub LFS
+
+**Reflections:** <!--TODO: Update reflections (when add Shoaib, Huang, Lim, Kim and Wood) and then (since have added Johnson, Hernandez and Wood) -->
+
+:::
+
 ::: {.callout-important icon=false collapse=true}
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| 🟡 | ❌ | ❌ | ❌ | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |
+| 🟡 | ❌ | ❌ | ❌ | N/A | <!--TODO--> | <!--TODO--> | 🟡 |
 
@@
 
-@wood_value_2021: <!--TODO-->
+@wood_value_2021: Partially met. In the paper, they state that it takes less than five minutes for each scenario, but this feels like half the picture, given the total run time was 48 hours.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| N/A | N/A | N/A | ❌ | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |
+| N/A | N/A | N/A | ❌ | N/A | <!--TODO--> | <!--TODO--> | N/A |
 
@@
 
+@johnson_cost_2021: <!--TODO-->
+
 @hernandez_optimal_2015: <!--TODO-->
 
-@wood_value_2021: <!--TODO-->
+@wood_value_2021: Not applicable. As stated in their prior paper, the model is constrained by processing time, not computer memory.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | ❌ | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |
+| ❌ | ❌ | ❌ | ❌ | N/A | <!--TODO--> | <!--TODO--> | ✅ |
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |
+| ❌ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| 🟡 | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |
+| 🟡 | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | ✅ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |
+| ❌ | ❌ | ❌ | ✅ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | 🟡 | N/A | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |
+| ❌ | ❌ | 🟡 | N/A | N/A | <!--TODO--> | <!--TODO--> | N/A |
 
@@
 
-@wood_value_2021: <!--TODO-->
+@wood_value_2021: Not applicable. All provided.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ✅ | N/A | N/A | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |
+| ❌ | ✅ | N/A | N/A | N/A | <!--TODO--> | <!--TODO--> | N/A |
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ✅ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |
+| ✅ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |
 
@@
 
-@wood_value_2021: <!--TODO-->
+@wood_value_2021: Outputs to `.csv` files.
 
@@
 
-@wood_value_2021: <!--TODO-->
+@wood_value_2021: Fully met. I didn't need to work with the output tables, but from looking at them now, they make sense.
 
@@
 
-@wood_value_2021: <!--TODO-->
+@wood_value_2021: Fully met. Sets seed based on replication number.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | N/A | 🟡 | ❌ | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |
+| ❌ | N/A | 🟡 | ❌ | N/A | <!--TODO--> | <!--TODO--> | ✅ |
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | ❌ | ❌ | <!--TODO--> | <!--TODO--> | <!--TODO--> |
+| ❌ | ❌ | ❌ | ❌ | ❌ | <!--TODO--> | <!--TODO--> | ✅ |
 
@@
 
-@wood_value_2021: <!--TODO-->
+@wood_value_2021: Fully met. Figures match article, with one minor exception that I had to add smoothing to the lines on one of the figures.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | N/A | ❌ | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |
+| ❌ | ❌ | N/A | ❌ | N/A | <!--TODO--> | <!--TODO--> | N/A |
 
@@
 
-@lim_staff_2020, @anagnostou_facs-charm_2022: Not applicable (no in-text results).
+@lim_staff_2020, @anagnostou_facs-charm_2022, @wood_value_2021: Not applicable (no in-text results).
 
@@
 @hernandez_optimal_2015: <!--TODO-->
-
-@wood_value_2021: <!--TODO-->
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | 🟡 | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |
+| ❌ | ❌ | ❌ | 🟡 | ✅ | <!--TODO--> | <!--TODO--> | ❌ |
 
@@
 
-@wood_value_2021: <!--TODO-->
+@wood_value_2021: Not met. No instructions, although it was fairly self explanatory (single script `master.R` to run, then processing scripts named after items in article e.g. `fig7.R`).
 

### 2024-10-16 pages/reflections.qmd
docs(reflections): add hernandez 2015

@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> | <!--TODO--> | ❌ |
+| ❌ | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> | 🟡 | ❌ |
 
@@
 
-@hernandez_optimal_2015: <!--TODO-->
+@hernandez_optimal_2015: Partially met. Some (but not all) of the required packages were listed in the paper.
 
@@
 * There are various options for listing the packages (e.g. comprehensive import statements, installation lines in the script, environment files).
+* Ideally mention this in repository, not just the paper.
 * This was a common issue.
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | 🟡 | 🟡 | 🟡 | <!--TODO--> | <!--TODO--> | 🟡 |
+| ❌ | ❌ | 🟡 | 🟡 | 🟡 | <!--TODO--> | 🟡 | 🟡 |
 
@@
 
-@hernandez_optimal_2015: <!--TODO-->
+@hernandez_optimal_2015: Partially. Versions of Python, R and some (but not all) packages given in the paper. Some versions weren't very specific (e.g. Python 2.7 v.s. something specific like 2.7.12)
 
@@
 * For Python, it was very easy to "backdate" the python and package versions. However, I found this very difficult to in R, and ended up always using the latest versions.
-* Versions are sometimes provided elsewhere (e.g. in paper, in other repositories), but would be handy to be in model repository itself
+* Versions are sometimes provided elsewhere (e.g. in paper, in other repositories), but would be handy to be in model repository itself.
+* Handy to provide specific versions too, particularly when there can be reasonably large changes between minor versions.
 * This was a very common issue.
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ✅ | ❌ | ✅ | ✅ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |
+| ✅ | ❌ | ✅ | ✅ | ✅ | <!--TODO--> | ✅ | ✅ |
 
@@
 
-@hernandez_optimal_2015: <!--TODO-->
+@hernandez_optimal_2015: Fully met. The model (python code) can be run from `main.py`.
 
@@
 
+<!--TODO: Consider overlap between some of these and how clear it is.
+I seperated to seperate out the script structure v.s.
+hard coding v.s.
+providing parameters and scenarios later.
+Consider whether evaluation for Shoaib below feels correct or not.
+-->
+
 ::: {.callout-warning icon=false collapse=true}
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ✅ | ✅ | ✅ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |
+| ❌ | ✅ | ✅ | ✅ | ✅ | <!--TODO--> | ✅ | ✅ |
 
@@
 Everything uses default inputs, and it designed in such a way that - if you wish to vary model parameters - you need to directly change these in the script itself.
-This meant you couldn't run multiple versions of the model using the same script.
-It also meant hidden errors were more likely (e.g.
-if miss changing a parameter somewhere, or input the wrong parameters and don’t realise).
 
@@
 
-@hernandez_optimal_2015: <!--TODO-->
+@hernandez_optimal_2015: Fully met. Model created from classes, which accept some inputs and can run the model.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | 🟡 | ❌ | ✅ | N/A | <!--TODO--> | <!--TODO--> | ✅ |
+| ❌ | 🟡 | ❌ | ✅ | N/A | <!--TODO--> | 🟡 | ✅ |
 
@@
 
-@hernandez_optimal_2015: <!--TODO-->
+@hernandez_optimal_2015: Partially met.
+Did not hard code, runs, population, generations, and percent pre-screened.
+However, did hard code other parameters like bi-objective v.s tri-objective model and bounding.
+Also, it was pretty tricky to change percent pre-screened, as it assumed you provided a `.txt` file for each %.
 
@@
 
+<!--TODO: Consider whether this is something to keep?
+Did any have an issue with relative file paths?
+Or was it more that I saw an issue with relative file paths that were tricky to change?
+Have mentioned this is a bit under "Saves output to a file"-->
+
 | @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | ✅ |
+| <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | ✅ | ✅ |
 
@@
 
-@hernandez_optimal_2015: <!--TODO-->
+@hernandez_optimal_2015: Fully met. Creates folder in current working directory based on date/time to store results.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ✅ | ✅ | ❌ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |
+| ❌ | ✅ | ✅ | ❌ | ✅ | <!--TODO--> | ✅ | ✅ |
 
@@
 
-@hernandez_optimal_2015: <!--TODO-->
+@hernandez_optimal_2015: Fully met.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ✅ | 🟡 | 🟡 | <!--TODO--> | <!--TODO--> | ❌ |
+| ❌ | ❌ | ✅ | 🟡 | 🟡 | <!--TODO--> | 🟡 | ❌ |
 
@@
 
-@hernandez_optimal_2015: <!--TODO-->
+@hernandez_optimal_2015: Partially met. There are some comments and doc-strings, but not comprehensively.
 
@@
 
-## Run time, memory usage and file size
+## Run time and memory usage
 
@@
 * @johnson_cost_2021: <!--TODO-->
-* @hernandez_optimal_2015: <!--TODO-->
+* @hernandez_optimal_2015: Add parallel processing, did not run one of the scenarios (it was very long, and hadn't managed to reproduce other parts of same figure regardless), and experimented with reducing parameters for evolutionary algorithm (but, in the end, ran with full parameters, though lower were helpful while working through and troubleshooting).
 * @wood_value_2021: No changes made, but unlike other reproduction, didn't try to run at smaller amounts - just set it to run as-is over the weekend.
@@
 
-::: {.callout-warning icon=false collapse=true}
-
-## Avoid large file sizes if possible
-
-I have not evaluated like as a criteria, as a large file size is not inherently a bad thing, and might be difficult to avoid.
-However, when files are very large, this can make things trickier, such as with requiring compression and use of GitHub Large File Storage (LFS) for tracking, which has limits on the free tier.
-
-Regarding file sizes in each study:
-
-* @shoaib_simulation_2021: <!--TODO-->
-* @huang_optimizing_2019: <!--TODO-->
-* @lim_staff_2020: <!--TODO-->
-* @kim_modelling_2021: <!--TODO-->
-* @anagnostou_facs-charm_2022: <!--TODO-->
-* @johnson_cost_2021: <!--TODO-->
-* @hernandez_optimal_2015: <!--TODO-->
-* @wood_value_2021: Aggregate results files are small (327 kB), but raw results files are very large (2.38 GiB), and even when compressed to `.csv.gz` (128 MiB) require using of GitHub LFS
-
-**Reflections:** <!--TODO: Update reflections (when add Shoaib, Huang, Lim, Kim and Wood) and then (since have added Johnson, Hernandez and Wood) -->
-
-:::
-
 ::: {.callout-important icon=false collapse=true}
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| 🟡 | ❌ | ❌ | ❌ | N/A | <!--TODO--> | <!--TODO--> | 🟡 |
+| ✅ | ❌ | ❌ | ❌ | N/A | <!--TODO--> | 🟡 | 🟡 |
 
-@shoaib_simulation_2021: Partially met. Run time stated in paper but not repository.
+@shoaib_simulation_2021: Fully met. Run time stated in paper (but not repository).
 
@@
 
-@kim_modelling_2021: Not met. A prior paper describing the model development mentions the run time, but not the current paper or repository.
+@kim_modelling_2021: Not met. A prior paper describing the model development mentions the run time, but not the current paper or repository, so this is easily missed.
 
@@
 
-@hernandez_optimal_2015: <!--TODO-->
+@hernandez_optimal_2015: Partially met.
+Some of the run times are mentioned in the paper, but not all, although this did help indicate that we would anticipate other s scenarios to similarly take hours to run.
 
@@
 And hard to know how long to expect, and whether it is without the capacities of your machine and so on.
+* Ideally include statement of run time in repository as well as paper.
+* Ideally include run time of all components of analysis (e.g. all scenarios).
 * Common issue.
@@
 
-@hernandez_optimal_2015: <!--TODO-->
+@hernandez_optimal_2015: <!--TODO: This had long run times but I don't know if it was computationally expensive or not. May need to run again for a while and see what memory usage is-->
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | ❌ | N/A | <!--TODO--> | <!--TODO--> | ✅ |
+| ❌ | ❌ | ❌ | ❌ | N/A | <!--TODO--> | ❌ | ✅ |
 
@@
 
-@hernandez_optimal_2015: <!--TODO-->
+@hernandez_optimal_2015: Not met. Took a while to figure out how to implement scenarios.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |
+| ❌ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | ✅ | ✅ |
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| 🟡 | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |
+| 🟡 | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> | ❌ | ✅ |
 
@@
 
-@hernandez_optimal_2015: <!--TODO-->
+@hernandez_optimal_2015: Not met.
+As agreed with the author, this is likely the primary reason for the discrepancy in these results - they are very close, and we see similar patterns, but not reproduced.
+Unfortunately, several parameters were wrong, and although we changed those we spotted, we anticipate there could be others we hadn't spotted that might explain the remaining discrepancies.
 
@@
 * This can introduce difficulties - when some parameters are wrong, you rely on the paper to check which parameters are correct or not, but if the paper doesn't mention every single parameter (which is reasonably likely, as this includes those not varied by scenarios), then you aren't able to be sure that the model you are running is correct.
+* This can make a really big difference, and be likely cause of managing to reproduce everything v.s. nothing, if it impacts all aspects of the results.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | ✅ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |
+| ❌ | ❌ | ❌ | ✅ | ✅ | <!--TODO--> | ❌ | ✅ |
 
@@
 
-@hernandez_optimal_2015: <!--TODO-->
+@hernandez_optimal_2015: Not met.
+The results have a large impact by the bounding set, but this was not mentioned in the paper or repository, and required me looking at the numbers in results and GitHub commit history to estimate the appropriate bounds to use.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | 🟡 | N/A | N/A | <!--TODO--> | <!--TODO--> | N/A |
+| ❌ | ❌ | 🟡 | N/A | N/A | <!--TODO--> | 🟡 | N/A |
 
@@
 
-@hernandez_optimal_2015: <!--TODO-->
+@hernandez_optimal_2015: Most parameters are relatively easily identified from the text or figure legends (though would be easier if provided in a table or similar).
+Parameter for bounding was not provided in paper.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ✅ | N/A | N/A | N/A | <!--TODO--> | <!--TODO--> | N/A |
+| ❌ | ✅ | N/A | N/A | N/A | <!--TODO--> | N/A | N/A |
 
@@
 
-@hernandez_optimal_2015: <!--TODO-->
+@hernandez_optimal_2015: Not applicable.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ✅ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |
+| ✅ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | ✅ | ✅ |
 
@@
 
-@hernandez_optimal_2015: <!--TODO-->
+@hernandez_optimal_2015: Fully met. Outputs to `.txt` files.
 
-@wood_value_2021: Outputs to `.csv` files.
+@wood_value_2021: Fully met. Outputs to `.csv` files.
 
@@
 
-@hernandez_optimal_2015: <!--TODO-->
+@hernandez_optimal_2015: Fully met. Straightforward with key information provided.
 
@@
 * Make it clear what each colum/category in the results table means, if it might not be immediately clear.
+
+:::
+
+::: {.callout-caution icon=false collapse=true}
+
+## Avoid large file sizes if possible
+
+I have not evaluated like as a criteria, as a large file size is not inherently a bad thing, and might be difficult to avoid.
+However, when files are very large, this can make things trickier, such as with requiring compression and use of GitHub Large File Storage (LFS) for tracking, which has limits on the free tier.
+
+Regarding file sizes in each study:
+
+* @shoaib_simulation_2021: Not relevant (results files **<35 kB**)
+* @huang_optimizing_2019: Provided code didn't save results to file.
+When I saved to file, these were large, so I compressed to `.csv.gz`, which made them small enough that GitHub was still happy (**26 MB**).
+* @lim_staff_2020: Provided code didn't save results to file. When I saved to file, these were small, so not relevant (results files **<60 kB**)
+* @kim_modelling_2021: Provided code didn't save results to file. When I saved to file, these were small, so not relevant (results files **<1 kB**)
+* @anagnostou_facs-charm_2022: Not relevant (results file **34 kB**)
+* @johnson_cost_2021: <!--TODO-->
+* @hernandez_optimal_2015: Not relevant (aggregate results files **<10 kB**).
+* @wood_value_2021: Aggregate results files are small (**327 kB**), but raw results files are very large (**2.38 GB**), and even when compressed to `.csv.gz` (**128 MB**) require using of GitHub LFS
+
+**Reflections:** <!--TODO: Update reflections once add Johnson -->
+
+* For most studies, this was not relevant, with outputs relatively small
+* I only really found this to be an issue when files exceeded GitHub threshold.
+[GitHub](https://docs.github.com/en/repositories/working-with-files/managing-large-files/about-large-files-on-github) give warning over 50 MB, blocks files over 100 MB, requiring you to use GitHub LFS.
+Recommends repositories ideally <1 GB and for sure < 5GB.
+[GitHub LFS](https://docs.github.com/en/repositories/working-with-files/managing-large-files/about-storage-and-bandwidth-usage) has limits on storage and bandwith use (1GB of each).
+
+:::
+
+::: {.callout-caution icon=false collapse=true}
+
+## Do not output excessive numbers of files
+
+I have not evaluated like as a criteria, as a large number of files is not inherently a bad thing, and might be difficult to avoid.
+
+Regarding number of files:
+
+* @shoaib_simulation_2021: Not relevant.
+* @huang_optimizing_2019: Not relevant.
+* @lim_staff_2020: Not relevant.
+* @kim_modelling_2021: Not relevant.
+* @anagnostou_facs-charm_2022: Not relevant.
+* @johnson_cost_2021: <!--TODO-->
+* @hernandez_optimal_2015: The default behaviour of the script was to output **lots of files** from each round (so you could easily have 90, 100, 200+ files), which were then **not** used in analysis (as it just depended on an aggregate results file).
+Although these individual files might be useful during quality control, as a default behaviour of the script, it could easily make the repository quite busy/littered with files.
+* @wood_value_2021: Not relevant.
+
+**Reflections:** <!--TODO: Update reflections once add Johnson -->
+
+* Outputting hundreds of files - particularly if they are not then used normally in analysis - can easily make repository cluttered/busy
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | ✅ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |
+| ❌ | ❌ | ❌ | ✅ | ✅ | <!--TODO--> | ✅ | ✅ |
 
@@
 
-@hernandez_optimal_2015: <!--TODO-->
+@hernandez_optimal_2015: Fully met. This ensured consistent results between runs of the script, which was really helpful.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | N/A | 🟡 | ❌ | N/A | <!--TODO--> | <!--TODO--> | ✅ |
+| ❌ | N/A | 🟡 | ❌ | N/A | <!--TODO--> | ❌ | ✅ |
 
@@
 
-@hernandez_optimal_2015: <!--TODO-->
+@hernandez_optimal_2015: Not met.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | ❌ | ❌ | <!--TODO--> | <!--TODO--> | ✅ |
+| ❌ | ❌ | ❌ | ❌ | ❌ | <!--TODO--> | 🟡 | ✅ |
 
@@
 
-@hernandez_optimal_2015: <!--TODO-->
+@hernandez_optimal_2015: Partially met.
+Provides a few example `ggplot`s, but these are not all the plots, nor exactly matching article, nor including any of the pre-processing required before the plots, and so could only serve as a starting point (though that was still really handy).
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | N/A | ❌ | N/A | <!--TODO--> | <!--TODO--> | N/A |
+| ❌ | ❌ | N/A | ❌ | N/A | N/A | N/A | N/A |
 
@@
 
-@lim_staff_2020, @anagnostou_facs-charm_2022, @wood_value_2021: Not applicable (no in-text results).
+@lim_staff_2020, @anagnostou_facs-charm_2022, @johnson_cost_2021, @hernandez_optimal_2015, @wood_value_2021: Not applicable (no in-text results).
 
-@johnson_cost_2021: <!--TODO-->
-
-@hernandez_optimal_2015: <!--TODO-->
-
-**Reflections:** <!--TODO: Update reflections (since have added Johnson, Hernandez and Wood) -->
+**Reflections:**
 
@@
 
-::: {.callout-warning icon=false collapse=true}
+::: {.callout-important icon=false collapse=true}
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | 🟡 | ✅ | <!--TODO--> | <!--TODO--> | ❌ |
+| ❌ | ❌ | ❌ | 🟡 | ✅ | <!--TODO--> | ❌ | ❌ |
 
@@
 
-Include tick marks/grid lines on figures, so it is easier to read across and judge whether a result is above or below a certain Y value.
+<!--TODO: Reflect whether any of these should be boxes above-->
 
-@anagnostou_facs-charm_2022: Included data dictionary for input parameters. Although I didn’t need this, this would have been great if I needed to change the input parameters at all.
+**Grid lines**. Include tick marks/grid lines on figures, so it is easier to read across and judge whether a result is above or below a certain Y value.
+
+**Data dictionaries**.
+@anagnostou_facs-charm_2022: Included data dictionary for input parameters.
+Although I didn’t need this, this would have been great if I needed to change the input parameters at all.
+
+**Unsupported versions**. @hernandez_optimal_2015: Due to the age of the work:
+
+* Some packages were no longer available on Conda and had to be installed from PyPI
+* The version of python was no longer supported which meant:
+    * Not supported by Jupyter Lab and Jupyter Notebook (so no `.ipynb` files, or Jupyter Lab on Docker)
+    * Not supported by VSCode (so had to use "tricks" to run it, involving using a pre-release version of Python on VSCode)
+    * Had to create Docker image from scratch (i.e. couldn't start from e.g. `miniconda3`)
+
+However, this is a slightly unavoidable problem unless you continue to maintain your code (which is ideal but not always feasible in a research environment).
+Realistically, if reusing this code for a new purpose, you would upgrade it to supported versions.
+
+**Original results files**. @hernandez_optimal_2015: Included some original results files, which was invaluable in identifying some of the parameters in the code that needed to be fixed.
+
+**Classes**. @hernandez_optimal_2015: Structured code into classes, which was nice to work with/amend.
 
@@
 * Include data dictionaries
+* If feasible, maintain code to avoid dependency on unsupported old versions of packages and languages
+* Ideally, include copies of your results, so can (a) compare against, (b) use to run analysis on, and (c) use in troubleshooting
 

### 2024-10-16 pages/repo_evaluation.qmd
docs(results): add extra TODO statements to results pages
docs(repo evaluation): add hernandez 2015 and wood 2021

@@
 
+<!-- TODO: Once complete, carefully go over again and check everything is correct -->
+
 ## Summary
 
-<!-- TODO: Add Johnson et al. 2021, Hernandez et al. 2015 and Wood et al. 2021 -->
+<!-- TODO: Add Johnson et al. 2021 -->
 
@@
   'Johnson et al. 2021': [0, 0, 0, 1],
-  'Hernandez et al. 2015': [0, 0, 0, 1],
-  'Wood et al. 2021': [0, 0, 0, 1]
+  'Hernandez et al. 2015': [3, 0, 9, 0],
+  'Wood et al. 2021': [4, 0, 8, 0]
 }
@@
   'Johnson et al. 2021': [0, 0, 0, 1],
-  'Hernandez et al. 2015': [0, 0, 0, 1],
-  'Wood et al. 2021': [0, 0, 0, 1]
+  'Hernandez et al. 2015': [0, 0, 12, 0],
+  'Wood et al. 2021': [5, 0, 7, 0]
 }
@@
   'Johnson et al. 2021': [0, 0, 0, 1],
-  'Hernandez et al. 2015': [0, 0, 0, 1],
-  'Wood et al. 2021': [0, 0, 0, 1]
+  'Hernandez et al. 2015': [2, 0, 6, 0],
+  'Wood et al. 2021': [2, 0, 6, 0]
 }
@@
   'Johnson et al. 2021': [0, 0, 0, 1],
-  'Hernandez et al. 2015': [0, 0, 0, 1],
-  'Wood et al. 2021': [0, 0, 0, 1]
+  'Hernandez et al. 2015': [0, 0, 5, 0],
+  'Wood et al. 2021': [0, 0, 5, 0]
 }
@@
 
-<!-- TODO: Add Johnson et al. 2021, Hernandez et al. 2015 and Wood et al. 2021 -->
+<!-- TODO: Add Johnson et al. 2021 -->
 
@@
 | **Criteria related to how artefacts are shared** |
-| Stored in a permanent archive that is publicly and openly accessible | ❌ | ❌ | ❌ | ❌ | ✅ |
-| Has a persistent identifier | ❌ | ❌ | ❌ | ❌ | ✅ |
-| Includes an open license | ❌ | ✅ | ❌ | ✅ | ✅ |
+| Stored in a permanent archive that is publicly and openly accessible | ❌ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | ❌ | ❌ |
+| Has a persistent identifier | ❌ | ❌ | ❌ | ❌ | ✅ |<!--TODO--> | ❌ | ❌ |
+| Includes an open license | ❌ | ✅ | ❌ | ✅ | ✅ |<!--TODO--> | ❌ | ❌ |
 | **Criteria related to what artefacts are shared** |
-| Artefacts are relevant to and contribute to the article’s results | ✅ | ✅ | ✅ | ✅ | ✅ |
-| Complete set of materials shared (as would be needed to fully reproduce article) | ❌ | ❌ | ❌ | ❌ | ❌ |
+| Artefacts are relevant to and contribute to the article’s results | ✅ | ✅ | ✅ | ✅ | ✅ |<!--TODO--> | ✅ | ✅ |
+| Complete set of materials shared (as would be needed to fully reproduce article) | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ✅ |
 | **Criteria related to the structure and documentation of the artefacts** |
-| Artefacts are well structured/organised (e.g. to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community) | ❌ | ❌ | ❌ | ✅ | ✅ |
-| Artefacts are sufficiently documented (i.e. to understand how it works, to enable it to be run, including package versions) | ❌ | ❌ | ❌ | ❌ | ✅ |
-| Artefacts are carefully documented (more than sufficient - i.e. to the extent that reuse and repurposing is facilitated - e.g. changing parameters, reusing for own purpose) | ❌ | ❌ | ❌ | ❌ | ✅ |
-| Artefacts are clearly documented and accompanied by a README file with step-by-step instructions on how to reproduce results in the manuscript | ❌ | ❌ | ❌ | ❌ | ✅ |
+| Artefacts are well structured/organised (e.g.
+to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community) | ❌ | ❌ | ❌ | ✅ | ✅ |<!--TODO--> | ✅ | ❌ |
+| Artefacts are sufficiently documented (i.e. to understand how it works, to enable it to be run, including package versions) | ❌ | ❌ | ❌ | ❌ | ✅ |<!--TODO--> | ❌ | ❌ |
+| Artefacts are carefully documented (more than sufficient - i.e.
+to the extent that reuse and repurposing is facilitated - e.g.
+changing parameters, reusing for own purpose) | ❌ | ❌ | ❌ | ❌ | ✅ |<!--TODO--> | ❌ | ❌ |
+| Artefacts are clearly documented and accompanied by a README file with step-by-step instructions on how to reproduce results in the manuscript | ❌ | ❌ | ❌ | ❌ | ✅ |<!--TODO--> | ❌ | ❌ |
 | **Criteria related to running and reproducing results** |
-| Scripts can be successfully executed | ✅ | ✅ | ✅ | ✅ | ✅ |
-| Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ |
-| Reproduced within approximately one hour (excluding compute time) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
+| Scripts can be successfully executed | ✅ | ✅ | ✅ | ✅ | ✅ |<!--TODO--> | ✅ | ✅ |
+| Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ |<!--TODO--> | ❌ | ✅ |
+| Reproduced within approximately one hour (excluding compute time) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
 : {tbl-colwidths="[60, 5, 5, 5, 5, 5, 5, 5, 5]"}
@@
 | **“Open objects” badges** |
-| **NISO "Open Research Objects (ORO)"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier<br>• Includes an open license | ❌ | ❌ | ❌ | ❌ | ✅ |
-| **NISO "Open Research Objects - All (ORO-A)"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier<br>• Includes an open license<br>• Complete set of materials shared (as would be needed to fully reproduce article) | ❌ | ❌ | ❌ | ❌ | ❌ |
-| **ACM "Artifacts Available"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier | ❌ | ❌ | ❌ | ❌ | ✅ |
+| **NISO "Open Research Objects (ORO)"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier<br>• Includes an open license | ❌ | ❌ | ❌ | ❌ | ✅ |<!--TODO--> | ❌ | ❌ |
+| **NISO "Open Research Objects - All (ORO-A)"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier<br>• Includes an open license<br>• Complete set of materials shared (as would be needed to fully reproduce article) | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ❌ |
+| **ACM "Artifacts Available"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier | ❌ | ❌ | ❌ | ❌ | ✅ |<!--TODO--> | ❌ | ❌ |
 | **COS "Open Code"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier<br>• Includes an open license<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Artefacts are sufficiently documented (i.e.
-to understand how it works, to enable it to be run, including package versions) | ❌ | ❌ | ❌ | ❌ | ❌ |
-| **IEEE "Code Available"**<br>• Complete set of materials shared (as would be needed to fully reproduce article) | ❌ | ❌ | ❌ | ❌ | ❌ |
+to understand how it works, to enable it to be run, including package versions) | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ❌ |
+| **IEEE "Code Available"**<br>• Complete set of materials shared (as would be needed to fully reproduce article) | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ✅ |
 | **"Object review" badges** |
 | **ACM "Artifacts Evaluated - Functional"**<br>• Artefacts are sufficiently documented (i.e.
-to understand how it works, to enable it to be run, including package versions)<br>• Artefacts are relevant to and contribute to the article’s results<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Scripts can be successfully executed | ❌ | ❌ | ❌ | ❌ | ❌ |
+to understand how it works, to enable it to be run, including package versions)<br>• Artefacts are relevant to and contribute to the article’s results<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Scripts can be successfully executed | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ❌ |
 | **ACM "Artifacts Evaluated - Reusable"**<br>• Artefacts are sufficiently documented (i.e.
@@
 changing parameters, reusing for own purpose)<br>• Artefacts are relevant to and contribute to the article's results<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Scripts can be successfully executed<br>• Artefacts are well structured/organised (e.g.
-to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community) | ❌ | ❌ | ❌ | ❌ | ❌ |
-| **IEEE "Code Reviewed"**<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Scripts can be successfully executed | ❌ | ❌ | ❌ | ❌ | ❌ |
+to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community) | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ❌ |
+| **IEEE "Code Reviewed"**<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Scripts can be successfully executed | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ✅ |
 | **"Reproduced" badges** |
-| **NISO "Results Reproduced (ROR-R)"**<br>• Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ |
-| **ACM "Results Reproduced"**<br>• Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ |
-| **IEEE "Code Reproducible"**<br>• Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ |
+| **NISO "Results Reproduced (ROR-R)"**<br>• Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ |<!--TODO--> | ❌ | ✅ |
+| **ACM "Results Reproduced"**<br>• Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ |<!--TODO--> | ❌ | ✅ |
+| **IEEE "Code Reproducible"**<br>• Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ |<!--TODO--> | ❌ | ✅ |
 | **Psychological Science "Computational Reproducibility"**<br>• Independent party regenerated results using the authors research artefacts<br>• Reproduced within approximately one hour (excluding compute time)<br>• Artefacts are well structured/organised (e.g.
-to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community)<br>• Artefacts are clearly documented and accompanied by a README file with step-by-step instructions on how to reproduce results in the manuscript | ❌ | ❌ | ❌ | ❌ | ❌ |
+to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community)<br>• Artefacts are clearly documented and accompanied by a README file with step-by-step instructions on how to reproduce results in the manuscript | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ❌ |
 : {tbl-colwidths="[60, 5, 5, 5, 5, 5, 5, 5, 5]"}
@@
 | **Essential components** |
-| **Open license**<br>Free and open-source software (FOSS) license (e.g. MIT, GNU Public License (GPL)) | ❌ | ✅ | ❌ | ✅ | ✅ |
-| **Dependency management**<br>Specify software libraries, version numbers and sources (e.g. dependency management tools like virtualenv, conda, poetry) | ❌ | ❌ | ❌ | 🟡 | ✅ |
-| **FOSS model**<br>Coded in FOSS language (e.g. R, Julia, Python) | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ |
+| **Open license**<br>Free and open-source software (FOSS) license (e.g. MIT, GNU Public License (GPL)) | ❌ | ✅ | ❌ | ✅ | ✅ |<!--TODO--> | ❌ | ❌ |
+| **Dependency management**<br>Specify software libraries, version numbers and sources (e.g. dependency management tools like virtualenv, conda, poetry) | ❌ | ❌ | ❌ | 🟡 | ✅ |<!--TODO--> | ❌ | ❌ |
+| **FOSS model**<br>Coded in FOSS language (e.g. R, Julia, Python) | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ |
 | **Minimum documentation**<br>Minimal instructions (e.g.
-in README) that overview (a) what model does, (b) how to install and run model to obtain results, and (c) how to vary parameters to run new experiments | ❌ | ❌ | ❌ | ✅ | ✅ |
-| **ORCID**<br>ORCID for each study author | ❌ | ❌ | ❌ | ❌ | ❌ |
-| **Citation information**<br>Instructions on how to cite the research artefact (e.g. CITATION.cff file) | ❌ | ❌ | ❌ | ❌ | ✅ |
-| **Remote code repository**<br>Code available in a remote code repository (e.g. GitHub, GitLab, BitBucket) | ✅ | ✅ | ✅ | ✅ | ✅ |
+in README) that overview (a) what model does, (b) how to install and run model to obtain results, and (c) how to vary parameters to run new experiments | ❌ | ❌ | ❌ | ✅ | ✅ |<!--TODO--> | ❌ | ❌ |
+| **ORCID**<br>ORCID for each study author | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ❌ |
+| **Citation information**<br>Instructions on how to cite the research artefact (e.g. CITATION.cff file) | ❌ | ❌ | ❌ | ❌ | ✅ |<!--TODO--> | ❌ | ❌ |
+| **Remote code repository**<br>Code available in a remote code repository (e.g. GitHub, GitLab, BitBucket) | ✅ | ✅ | ✅ | ✅ | ✅ |<!--TODO--> | ✅ | ✅ |
 | **Open science archive**<br>Code stored in an open science archive with FORCE11 compliant citation and guaranteed persistance of digital artefacts (e.g.
-Figshare, Zenodo, the Open Science Framework (OSF), and the Computational Modeling in the Social and Ecological Sciences Network (CoMSES Net)) | ❌ | ❌ | ❌ | ❌ | ✅ |
+Figshare, Zenodo, the Open Science Framework (OSF), and the Computational Modeling in the Social and Ecological Sciences Network (CoMSES Net)) | ❌ | ❌ | ❌ | ❌ | ✅ |<!--TODO--> | ❌ | ❌ |
 | **Optional components** |
@@
 via notebooks and markdown files, brought together using software like Quarto and Jupyter Book).
-Suggested content includes:<br>• Plain english summary of project and model<br>• Clarifying license<br>• Citation instructions<br>• Contribution instructions<br>• Model installation instructions<br>• Structured code walk through of model<br>• Documentation of modelling cycle using TRACE<br>• Annotated simulation reporting guidelines<br>• Clear description of model validation including its intended purpose | ❌ | ❌ | ❌ | ❌ | ❌ |
-| **Documentation hosting**<br>Host documentation (e.g. with GitHub pages, GitLab pages, BitBucket Cloud, Quarto Pub) | ❌ | ❌ | ❌ | ❌ | ❌ |
-| **Online coding environment**<br>Provide an online environment where users can run and change code (e.g. BinderHub, Google Colaboratory, Deepnote) | ❌ | ❌ | ❌ | ❌ | ❌ |
-| **Model interface**<br>Provide web application interface to the model so it is accessible to less technical simulation users | ❌ | ✅ | ❌ | ❌ | ✅ |
-| **Web app hosting**<br>Host web app online (e.g. Streamlit Community Cloud, ShinyApps hosting) | ❌ | ✅ | ❌ | ❌ | 🟡 |
+Suggested content includes:<br>• Plain english summary of project and model<br>• Clarifying license<br>• Citation instructions<br>• Contribution instructions<br>• Model installation instructions<br>• Structured code walk through of model<br>• Documentation of modelling cycle using TRACE<br>• Annotated simulation reporting guidelines<br>• Clear description of model validation including its intended purpose | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ❌ |
+| **Documentation hosting**<br>Host documentation (e.g. with GitHub pages, GitLab pages, BitBucket Cloud, Quarto Pub) | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ❌ |
+| **Online coding environment**<br>Provide an online environment where users can run and change code (e.g. BinderHub, Google Colaboratory, Deepnote) | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ❌ |
+| **Model interface**<br>Provide web application interface to the model so it is accessible to less technical simulation users | ❌ | ✅ | ❌ | ❌ | ✅ |<!--TODO--> | ❌ | ❌ |
+| **Web app hosting**<br>Host web app online (e.g. Streamlit Community Cloud, ShinyApps hosting) | ❌ | ✅ | ❌ | ❌ | 🟡 |<!--TODO--> | ❌ | ❌ |
 : {tbl-colwidths="[60, 5, 5, 5, 5, 5, 5, 5, 5]"}
@@
 * @anagnostou_facs-charm_2022 - 19m
-* @johnson_cost_2021
-* @hernandez_optimal_2015 -
-* @wood_value_2021 -
+* @johnson_cost_2021 - <!--TODO-->
+* @hernandez_optimal_2015 - 13m
+* @wood_value_2021 - 14m
 

### 2024-10-16 pages/paper_evaluation.qmd
docs(results): add extra TODO statements to results pages
docs(paper evaluation): add hernandez 2015 wood 2021

@@
   'Hernandez et al. 2015': [18, 2, 3, 1],
-  'Wood et al. 2021': [0, 0, 0, 1]
+  'Wood et al. 2021': [22, 2, 0, 0]
 }
@@
   'Johnson et al. 2021': [0, 0, 0, 1],
-  'Hernandez et al. 2015': [10, 0, 8, 0],
-  'Wood et al. 2021': [0, 0, 0, 1]
+  'Hernandez et al. 2015': [10, 0, 7, 1],
+  'Wood et al. 2021': [13, 0, 4, 1]
 }
@@
 
-<!-- TODO: Add Johnson et al. 2021, Hernandez et al. 2015 and Wood et al. 2021, and update after discussion of Kim et al. 2021 -->
+<!-- TODO: Add Johnson et al. 2021, and update after discussion of Kim et al. 2021 -->
 
@@
 | **Objectives** | 
-| **1.1 Purpose of the model**<br>Explain the background and objectives for the model | ✅ | ✅ | ✅ | ✅ | ✅ |
+| **1.1 Purpose of the model**<br>Explain the background and objectives for the model | ✅ | ✅ | ✅ | ✅ | ✅ | <!--TODO--> | ✅ | ✅ |
 | **1.2 Model outputs**<br>Define all quantitative performance measures that are reported, using equations where necessary.
 Specify how and when they are calculated during the model run along with how any measures of error such as confidence intervals are calculated.
-| 🟡 | ✅ | ✅ | ✅ | ✅ |
+| 🟡 | ✅ | ✅ | ✅ | ✅ | <!--TODO--> | ✅ | ✅ |
 | **1.3 Experimentation aims**<br>If the model has been used for experimentation, state the objectives that it was used to investigate.<br>(A) Scenario based analysis – Provide a name and description for each scenario, providing a rationale for the choice of scenarios and ensure that item 2.3 (below) is completed.<br>(B) Design of experiments – Provide details of the overall design of the experiments with reference to performance measures and their parameters (provide further details in data below).<br>(C) Simulation Optimisation – (if appropriate) Provide full details of what is to be optimised, the parameters that were included and the algorithm(s) that was be used.
 Where possible provide a citation of the algorithm(s).
-| ✅ | ✅ | ✅ | ✅ | N/A |
+| ✅ | ✅ | ✅ | ✅ | N/A | <!--TODO--> | ✅ | ✅ |
 | **Logic** |
@@
 The goal is to describe the breadth and depth of the model with respect to the system being studied.
-| ✅ | ✅ | ✅ | ✅ | ✅ |
-| **2.2 Base model logic**<br>Give details of the base model logic. Give additional model logic details sufficient to communicate to the reader how the model works. | ✅ | ✅ | ✅ | ✅ | ✅ |
+| ✅ | ✅ | ✅ | ✅ | ✅ | <!--TODO--> | ✅ | ✅ |
+| **2.2 Base model logic**<br>Give details of the base model logic.
+Give additional model logic details sufficient to communicate to the reader how the model works.
+| ✅ | ✅ | ✅ | ✅ | ✅ | <!--TODO--> | ✅ | ✅ |
 | **2.3 Scenario logic**<br>Give details of the logical difference between the base case model and scenarios (if any).
 This could be incorporated as text or where differences are substantial could be incorporated in the same manner as 2.2.
-| ✅ | ✅ | ✅ | ✅ | N/A |
+| ✅ | ✅ | ✅ | ✅ | N/A | <!--TODO--> | ✅ | ✅ |
 | **2.4 Algorithms**<br>Provide further detail on any algorithms in the model that (for example) mimic complex or manual processes in the real world (i.e.
@@
 Pseudo-code may be used to describe an algorithm.
-| ✅ | 🟡 | ✅ | 🟡 | ✅ |
+| ✅ | 🟡 | ✅ | 🟡 | ✅ | <!--TODO--> | ✅ | ✅ |
 | **2.5.1 Components - entities**<br>Give details of all entities within the simulation including a description of their role in the model and a description of all their attributes.
-| ✅ | ✅ | ✅ | ✅ | ✅ |
-| **2.5.2 Components - activities**<br>Describe the activities that entities engage in within the model. Provide details of entity routing into and out of the activity. | ✅ | ✅ | ✅ | ✅ | ✅ |
-| **2.5.3 Components - resources**<br>List all the resources included within the model and which activities make use of them. | ✅ | ✅ | N/A | N/A | ✅ |
+| ✅ | ✅ | ✅ | ✅ | ✅ | <!--TODO--> | ✅ | ✅ |
+| **2.5.2 Components - activities**<br>Describe the activities that entities engage in within the model.
+Provide details of entity routing into and out of the activity.
+| ✅ | ✅ | ✅ | ✅ | ✅ | <!--TODO--> | ✅ | ✅ |
+| **2.5.3 Components - resources**<br>List all the resources included within the model and which activities make use of them. | ✅ | ✅ | N/A | N/A | ✅ | <!--TODO--> | ✅ | ✅ |
 | **2.5.4 Components - queues**<br>Give details of the assumed queuing discipline used in the model (e.g.
@@
 Detail any delays or capacity constraints on the queues.
-| ✅ | ✅ | N/A | N/A | ✅ |
+| ✅ | ✅ | N/A | N/A | ✅ | <!--TODO--> | ✅ | ✅ |
 | **2.5.5 Components - entry/exit points**<br>Give details of the model boundaries i.e.
@@
 Detail the arrival mechanism (e.g.
-‘thinning’ to mimic a non-homogenous Poisson process or balking) | ✅ | ✅ | ✅ | ✅ | ✅ |
+‘thinning’ to mimic a non-homogenous Poisson process or balking) | ✅ | ✅ | ✅ | ✅ | ✅ | <!--TODO--> | ✅ | ✅ |
 | **Data** |
@@
 Provide, where possible, the link and DOI to the data or reference to published literature.<br>All data source descriptions should include details of the sample size, sample date ranges and use within the study.
-| ✅ | ✅ | ✅ | ✅ | ✅ |
+| ✅ | ✅ | ✅ | ✅ | ✅ | <!--TODO--> | ✅ | ✅ |
 | **3.2 Pre-processing**<br>Provide details of any data manipulation that has taken place before its use in the simulation, e.g.
 interpolation to account for missing data or the removal of outliers.
-| ✅ | N/A | N/A | ✅ | N/A |
+| ✅ | N/A | N/A | ✅ | N/A | <!--TODO--> | N/A | ✅ |
 | **3.3 Input parameters**<br>List all input variables in the model.
@@
 Give details of all time dependent parameters and correlation.<br>Clearly state:<br>• Base case data<br>• Data use in experimentation, where different from the base case.<br>• Where optimisation or design of experiments has been used, state the range of values that parameters can take.<br>• Where theoretical distributions are used, state how these were selected and prioritised above other candidate distributions.
-| 🟡 | 🟡 | ✅ | 🟡 | ✅ |
+| 🟡 | 🟡 | ✅ | 🟡 | ✅ | <!--TODO--> | ✅ | ✅ |
 | **3.4 Assumptions**<br>Where data or knowledge of the real system is unavailable what assumptions are included in the model?
 This might include parameter values, distributions or routing logic within the model.
-| ✅ | ❌ | ✅ | ✅ | ❌ |
+| ✅ | ❌ | ✅ | ✅ | ❌ | <!--TODO--> | ✅ | ✅ |
 | **Experimentation** |
@@
 Report whether initialisation of these variables is deterministic or stochastic.
-| 🟡 | ❌ | ❌ | 🟡 | ❌ |
-| **4.2 Run length**<br>Detail the run length of the simulation model and time units. | ✅ | ✅ | ✅ | ✅ | 🟡 |
+| 🟡 | ❌ | ❌ | 🟡 | ❌ | <!--TODO--> | ❌ | ✅ |
+| **4.2 Run length**<br>Detail the run length of the simulation model and time units. | ✅ | ✅ | ✅ | ✅ | 🟡 | <!--TODO--> | ✅ | ✅ |
 | **4.3 Estimation approach**<br>State the method used to account for the stochasticity: For example, two common methods are multiple replications or batch means.
@@
 For both procedures provide a justification for the methods used and the number of replications/size of batches.
-| 🟡 | 🟡 | ✅ | ✅ | ✅ |
+| 🟡 | 🟡 | ✅ | ✅ | ✅ | <!--TODO--> | ✅ | ✅ |
 | **Implementation** |
@@
 Python 3.5).<br>Where frameworks and libraries have been used provide all details including version numbers.
-| 🟡 | 🟡 | 🟡 | 🟡 | 🟡 |
+| 🟡 | 🟡 | 🟡 | 🟡 | 🟡 | <!--TODO--> | 🟡 | 🟡 |
 | **5.2 Random sampling**<br>State the algorithm used to generate random samples in the software/programming language used e.g.
 Mersenne Twister.<br>If common random numbers are used, state how seeds (or random number streams) are distributed among sampling processes.
-| ❌ | 🟡 | ❌ | ❌ | ❌ |
+| ❌ | 🟡 | ❌ | ❌ | ❌ | <!--TODO--> | ❌ | ✅ |
 | **5.3 Model execution**<br>State the event processing mechanism used e.g.
@@
 For parallel and distributed simulations the time management algorithms used.
-If the HLA is used then state the version of the standard, which run-time infrastructure (and version), and any supporting documents (FOMs, etc.) | 🟡 |❌ | ❌ | ❌ | ❌ |
+If the HLA is used then state the version of the standard, which run-time infrastructure (and version), and any supporting documents (FOMs, etc.) | 🟡 |❌ | ❌ | ❌ | ❌ | <!--TODO--> | ❌ | ✅ |
 | **5.4 System specification**<br>State the model run time and specification of hardware used.
@@
 For parallel, distributed and/or use grid or cloud computing, etc.
-state the details of all systems used in the implementation (processors, network, etc.) | ✅ | ❌ | 🟡 | 🟡 | ❌ |
+state the details of all systems used in the implementation (processors, network, etc.) | ✅ | ❌ | 🟡 | 🟡 | ❌ | <!--TODO--> | 🟡 | 🟡 |
 | **Code access** |
@@
 Provide, where possible, the link and DOIs to these.
-| ✅ | ✅ | ✅ | ✅ | ✅ |
+| ✅ | ✅ | ✅ | ✅ | ✅ | <!--TODO--> | ✅ | ✅ |
 : {tbl-colwidths="[60, 5, 5, 5, 5, 5, 5, 5, 5]"}
@@
 DES studies included different types of decision problems, eg, those listed in previously developed taxonomies.
-| ✅ | ✅ | ✅ | ✅ | ✅ |
+| ✅ | ✅ | ✅ | ✅ | ✅ | <!--TODO--> | ✅ | ✅ |
 | **2 Is the modeled healthcare setting/health condition clarified?**<br>...the physical context/scope (eg, a certain healthcare unit or a broader system) or disease spectrum simulated was described.
-| ✅ | ✅ | ✅ | ✅ | ✅ |
-| **3 Is the model structure described?**<br>...the model’s conceptual structure was described in the form of either graphical or text presentation. | ✅ | ✅ | ✅ | ✅ | ✅ |
-| **4 Is the time horizon given?**<br>...the time period covered by the simulation was reported. | ✅ | ✅ | ✅ | ✅ | ❌ |
-| **5 Are all simulated strategies/scenarios specified?**<br>...the comparators under test were described in terms of their components, corresponding variations, etc | ✅ | ✅ | ✅ | ✅ | N/A |
-| **6 Is the target population described?**<br>...the entities simulated and their main attributes were characterized. | ✅ | ❌ | ✅ | ✅ | 🟡 |
+| ✅ | ✅ | ✅ | ✅ | ✅ | <!--TODO--> | ✅ | ✅ |
+| **3 Is the model structure described?**<br>...the model’s conceptual structure was described in the form of either graphical or text presentation. | ✅ | ✅ | ✅ | ✅ | ✅ | <!--TODO--> | ✅ | ✅ |
+| **4 Is the time horizon given?**<br>...the time period covered by the simulation was reported. | ✅ | ✅ | ✅ | ✅ | ❌ | <!--TODO--> | ✅ | ✅ |
+| **5 Are all simulated strategies/scenarios specified?**<br>...the comparators under test were described in terms of their components, corresponding variations, etc | ✅ | ✅ | ✅ | ✅ | N/A | <!--TODO--> | ✅ | ✅ |
+| **6 Is the target population described?**<br>...the entities simulated and their main attributes were characterized. | ✅ | ❌ | ✅ | ✅ | 🟡 | <!--TODO--> | ✅ | ✅ |
 | **Paramaterisation and uncertainty assessment** |
-| **7 Are data sources informing parameter estimations provided?**<br>...the sources of all data used to inform model inputs were reported. | ✅ | ✅ | ✅ | ✅ | ✅ |
-| **8 Are the parameters used to populate model frameworks specified?**<br>...all relevant parameters fed into model frameworks were disclosed. | 🟡 | 🟡 | ✅ | ✅ | ✅ |
+| **7 Are data sources informing parameter estimations provided?**<br>...the sources of all data used to inform model inputs were reported. | ✅ | ✅ | ✅ | ✅ | ✅ | <!--TODO--> | ✅ | ✅ |
+| **8 Are the parameters used to populate model frameworks specified?**<br>...all relevant parameters fed into model frameworks were disclosed. | 🟡 | 🟡 | ✅ | ✅ | ✅ | <!--TODO--> | ✅ | ✅ |
 | **9 Are model uncertainties discussed?**<br>...the uncertainty surrounding parameter estimations and adopted statistical methods (eg, 95% confidence intervals or possibility distributions) were reported.
-| 🟡 | ❌ | ❌ | ❌ | ✅ |
+| 🟡 | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | ✅ | ✅ |
 | **10 Are sensitivity analyses performed and reported?**<br>...the robustness of model outputs to input uncertainties was examined, for example via deterministic (based on parameters’ plausible ranges) or probabilistic (based on a priori-defined probability distributions) sensitivity analyses, or both.
-| ✅ | ❌ | ✅ | ❌ | N/A |
+| ✅ | ❌ | ✅ | ❌ | N/A | <!--TODO--> | ❌ | ✅ |
 | **Validation** |
@@
 It was assumed that this type of validation should be conducted by external evaluators with no stake in the study.
-| ❌ | ❌ | ❌ | ❌ | ❌ |
-| **12 Is cross validation performed and reported**<br>...comparison across similar modeling studies which deal with the same decision problem was undertaken. | N/A | ❌ | ❌ | ✅ | ❌ |
-| **13 Is external validation performed and reported?**<br>...the modeler(s) examined how well the model’s results match the empirical data of an actual event modeled. | N/A | N/A | N/A | ✅ | ❌ |
+| ❌ | ❌ | ❌ | ❌ | ❌ | <!--TODO--> | ❌ | ❌ |
+| **12 Is cross validation performed and reported**<br>...comparison across similar modeling studies which deal with the same decision problem was undertaken.
+| N/A | ❌ | ❌ | ✅ | ❌ | <!--TODO--> | ❌ | ❌ |
+| **13 Is external validation performed and reported?**<br>...the modeler(s) examined how well the model’s results match the empirical data of an actual event modeled.
+| N/A | N/A | N/A | ✅ | ❌ | <!--TODO--> | ❌ | ❌ |
 | **14 Is predictive validation performed or attempted?**<br> ...the modeler(s) examined the consistency of a model’s predictions of a future event and the actual outcomes in the future.
 If this was not undertaken, it was assessed whether the reasons were discussed.
-| N/A | N/A | N/A | N/A | N/A |
+| N/A | N/A | N/A | N/A | N/A | <!--TODO--> | N/A | N/A |
 | **Generalisability and stakeholder involvement** |
 | **15 Is the model generalizability issue discussed?**<br>...the modeler(s) discussed the potential of the resulting model for being applicable to other settings/populations (single/multiple application).
-| ✅ | ✅ | ✅ | ❌ | 🟡 |
+| ✅ | ✅ | ✅ | ❌ | 🟡 | <!--TODO--> | ❌ | ✅ |
 | **16 Are decision makers or other stakeholders involved in modeling?**<br>...the modeler(s) reported in which part throughout the modeling process decision makers and other stakeholders (eg, subject experts) were engaged.
-| ❌ | ❌ | ❌ | ❌ | ✅ |
-| **17 Is the source of funding stated?**<br>...the sponsorship of the study was indicated. | ✅ | ❌ | ✅ | ✅ | ✅ |
-| **18 Are model limitations discussed?**<br>...limitations of the assessed model, especially limitations of interest to decision makers, were discussed. | ✅ | 🟡 | ✅ | ✅ | 🟡 |
+| ❌ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | ❌ | ❌ |
+| **17 Is the source of funding stated?**<br>...the sponsorship of the study was indicated. | ✅ | ❌ | ✅ | ✅ | ✅ | <!--TODO--> | ❌ | ✅ |
+| **18 Are model limitations discussed?**<br>...limitations of the assessed model, especially limitations of interest to decision makers, were discussed. | ✅ | 🟡 | ✅ | ✅ | 🟡 | <!--TODO--> | ✅ | ✅ |
 : {tbl-colwidths="[60, 5, 5, 5, 5, 5, 5, 5, 5]"}
@@
 
-<!-- TODO: Add johnson, hernandez, wood -->
+<!-- TODO: Add johnson -->
 
@@
 * @anagnostou_facs-charm_2022 - 53m
-* @johnson_cost_2021
-* @hernandez_optimal_2015
-* @wood_value_2021
+* @johnson_cost_2021 - <!--TODO-->
+* @hernandez_optimal_2015 - 1h 11m
+* @wood_value_2021 - 1h 24m
 

### 2024-10-16 pages/repo_evaluation.qmd
docs(repo evaluation): add reflections and scatter plots for the first two summary charts, and N/N reproduced to all chart labels

@@
 criteria_dict = {
-  'Shoaib and<br>Ramamohan 2021': [3, 0, 9, 0],
-  'Huang et al. 2019': [3, 0, 9, 0],
-  'Lim et al. 2020': [3, 0, 9, 0],
-  'Kim et al. 2021': [5, 0, 7, 0],
-  'Anagnostou et al. 2022': [10, 0, 2, 0],
-  'Johnson et al. 2021': [0, 0, 0, 1],
-  'Hernandez et al. 2015': [3, 0, 9, 0],
-  'Wood et al. 2021': [4, 0, 8, 0]
+  'Shoaib and Ramamohan<br>2021 (16/17)': [3, 0, 9, 0],
+  'Huang et al. 2019 (3/8)': [3, 0, 9, 0],
+  'Lim et al. 2020 (9/9)': [3, 0, 9, 0],
+  'Kim et al. 2021 (10/10)': [5, 0, 7, 0],
+  'Anagnostou et al. 2022 (1/1)': [10, 0, 2, 0],
+  'Johnson et al. 2021 (X/X)': [0, 0, 0, 1],
+  'Hernandez et al. 2015 (1/8)': [3, 0, 9, 0],
+  'Wood et al. 2021 (5/5)': [4, 0, 8, 0]
 }
@@
 ```
+
+::: {.callout icon=false collapse=true}
+
+## Reflections
+
+The studies meeting 33.3%, 41.7% and 83.3% of criteria were all fully reproduced.
+
+The remaining four studies met 25% of criteria, and ranged from 12.5% to 100% reproduced.
+
+However, I think it is more meaningful to actually look at what criteria were and were not met.
+
+```{python}
+import plotly.express as px
+
+# Percentage of items reproduced, and percentage of badge criteria met
+df = pd.DataFrame({
+  'Shoaib and Ramamohan 2021': [94, 25],
+  'Huang et al. 2019': [37.5, 25],
+  'Lim et al. 2020': [100, 25],
+  'Kim et al. 2021': [100, 41.7],
+  'Anagnostou et al. 2022': [100, 83.3],
+  #'Johnson et al. 2021': [],
+  'Hernandez et al. 2015': [12.5, 25],
+  'Wood et al. 2021': [100, 33.3]
+}).T.reset_index()
+df.columns = ['study', 'reproduce', 'criteria']
+
+px.scatter(df, x='criteria', y='reproduce',
+           hover_data={'study': True})
+```
+
+:::
 
@@
 badge_dict = {
-  'Shoaib and<br>Ramamohan 2021': [3, 0, 9, 0],
-  'Huang et al. 2019': [0, 0, 12, 0],
-  'Lim et al. 2020': [3, 0, 9, 0],
-  'Kim et al. 2021': [3, 0, 9, 0],
-  'Anagnostou et al. 2022': [5, 0, 7, 0],
-  'Johnson et al. 2021': [0, 0, 0, 1],
-  'Hernandez et al. 2015': [0, 0, 12, 0],
-  'Wood et al. 2021': [5, 0, 7, 0]
+  'Shoaib and Ramamohan<br>2021 (16/17)': [3, 0, 9, 0],
+  'Huang et al. 2019 (3/8)': [0, 0, 12, 0],
+  'Lim et al. 2020 (9/9)': [3, 0, 9, 0],
+  'Kim et al. 2021 (10/10)': [3, 0, 9, 0],
+  'Anagnostou et al. 2022 (1/1)': [5, 0, 7, 0],
+  'Johnson et al. 2021 (X/X)': [0, 0, 0, 1],
+  'Hernandez et al. 2015 (1/8)': [0, 0, 12, 0],
+  'Wood et al. 2021 (5/5)': [5, 0, 7, 0]
 }
@@
 ```
+
+::: {.callout icon=false collapse=true}
+
+## Reflections
+
+Not certain how meaningful these numbers are, as we have imbalanced numbers of different types of badge, and meeting certain popular criteria will quite weight what is met v.s. not.
+
+Feel that looking at the criteria met is a bit more meaningful?
+And then specific examples of how that translates into badges - e.g.
+none meeting ACM "Artifacts Evaluated - Functional" as requires xyz and these are commonly not met.
+
+```{python}
+import plotly.express as px
+
+# Percentage of items reproduced, and percentage of badges awarded
+df = pd.DataFrame({
+  'Shoaib and Ramamohan 2021': [94, 25],
+  'Huang et al. 2019': [37.5, 0],
+  'Lim et al. 2020': [100, 25],
+  'Kim et al. 2021': [100, 25],
+  'Anagnostou et al. 2022': [100, 41.7],
+  #'Johnson et al. 2021': [],
+  'Hernandez et al. 2015': [12.5, 0],
+  'Wood et al. 2021': [100, 41.7]
+}).T.reset_index()
+df.columns = ['study', 'reproduce', 'badges']
+
+px.scatter(df, x='badges', y='reproduce',
+           hover_data={'study': True})
+```
+
+:::
 
@@
 essential_dict = {
-  'Shoaib and<br>Ramamohan 2021': [2, 0, 6, 0],
-  'Huang et al. 2019': [2, 0, 6, 0],
-  'Lim et al. 2020': [2, 0, 6, 0],
-  'Kim et al. 2021': [4, 1, 3, 0],
-  'Anagnostou et al. 2022': [7, 0, 1, 0],
-  'Johnson et al. 2021': [0, 0, 0, 1],
-  'Hernandez et al. 2015': [2, 0, 6, 0],
-  'Wood et al. 2021': [2, 0, 6, 0]
+  'Shoaib and Ramamohan<br>2021 (16/17)': [2, 0, 6, 0],
+  'Huang et al. 2019 (3/8)': [2, 0, 6, 0],
+  'Lim et al. 2020 (9/9)': [2, 0, 6, 0],
+  'Kim et al. 2021 (10/10)': [4, 1, 3, 0],
+  'Anagnostou et al. 2022 (1/1)': [7, 0, 1, 0],
+  'Johnson et al. 2021 (X/X)': [0, 0, 0, 1],
+  'Hernandez et al. 2015 (1/8)': [2, 0, 6, 0],
+  'Wood et al. 2021 (5/5)': [2, 0, 6, 0]
 }
@@
 optional_dict = {
-  'Shoaib and<br>Ramamohan 2021': [0, 0, 5, 0],
-  'Huang et al. 2019': [2, 0, 3, 0],
-  'Lim et al. 2020': [0, 0, 5, 0],
-  'Kim et al. 2021': [0, 0, 5, 0],
-  'Anagnostou et al. 2022': [1, 1, 3, 0],
-  'Johnson et al. 2021': [0, 0, 0, 1],
-  'Hernandez et al. 2015': [0, 0, 5, 0],
-  'Wood et al. 2021': [0, 0, 5, 0]
+  'Shoaib and Ramamohan<br>2021 (16/17)': [0, 0, 5, 0],
+  'Huang et al. 2019 (3/8)': [2, 0, 3, 0],
+  'Lim et al. 2020 (9/9)': [0, 0, 5, 0],
+  'Kim et al. 2021 (10/10)': [0, 0, 5, 0],
+  'Anagnostou et al. 2022 (1/1)': [1, 1, 3, 0],
+  'Johnson et al. 2021 (X/X)': [0, 0, 0, 1],
+  'Hernandez et al. 2015 (1/8)': [0, 0, 5, 0],
+  'Wood et al. 2021 (5/5)': [0, 0, 5, 0]
 }

### 2024-10-17 pages/reflections.qmd
docs(reflections): add note about hernandez 2015 local dependency

@@
 
-@hernandez_optimal_2015: Partially met. Some (but not all) of the required packages were listed in the paper.
+@hernandez_optimal_2015: Partially met.
+Some (but not all) of the required packages were listed in the paper.
+Of particular note, this depended on having a local package `myutils/`, which was another GitHub repository from the author.
+This was not mentioned anywhere, and so required to notice this was needed.
 
@@
 * Ideally mention this in repository, not just the paper.
+* If there are local dependencies (e.g.
+other GitHub repositories), make sure to (a) mention and link to these repositories, so it is clear they are also required, and (b) include license/s in those repositories also, so they can be used.
 * This was a common issue.

### 2024-10-17 pages/repo_evaluation.qmd
docs(repo evaluation): add more reflections and charts

@@
 
+```{python}
+# Imports and function
+import plotly.express as px
+import pandas as pd
+from functions import eval_chart, plot_scatter
+```
+
 ## Summary
+
+**Unique badge criteria:**
 
@@
 
-**Unique badge criteria:**
-
 ```{python}
-import pandas as pd
-from functions import eval_chart
-
 # Create dataframe of results
@@
 
-::: {.callout icon=false collapse=true}
+::: {.callout icon=false collapse=false}
 
@@
 
-The studies meeting 33.3%, 41.7% and 83.3% of criteria were all fully reproduced.
+<!-- TODO: Add Johnson et al. 2021 -->
 
-The remaining four studies met 25% of criteria, and ranged from 12.5% to 100% reproduced.
+Four studies met 25% of criteria, and ranged from 12.5% to 100% reproduced.
+
+The remaining three studies were fully reproduced and met 33.3%, 41.7% and 83.3%.
 
@@
 ```{python}
-import plotly.express as px
-
-# Percentage of items reproduced, and percentage of badge criteria met
-df = pd.DataFrame({
-  'Shoaib and Ramamohan 2021': [94, 25],
-  'Huang et al. 2019': [37.5, 25],
-  'Lim et al. 2020': [100, 25],
-  'Kim et al. 2021': [100, 41.7],
-  'Anagnostou et al. 2022': [100, 83.3],
-  #'Johnson et al. 2021': [],
-  'Hernandez et al. 2015': [12.5, 25],
-  'Wood et al. 2021': [100, 33.3]
-}).T.reset_index()
-df.columns = ['study', 'reproduce', 'criteria']
-
-px.scatter(df, x='criteria', y='reproduce',
-           hover_data={'study': True})
+plot_scatter('Unique badge criteria met',
+             sho = 25,
+             hua = 25,
+             lim = 25,
+             kim = 41.7,
+             ana = 83.3,
+             her = 25,
+             woo = 33.3)
 ```
@@
 **Badges:**
+
+<!-- TODO: Add Johnson et al. 2021 -->
 
@@
 
-::: {.callout icon=false collapse=true}
+::: {.callout icon=false collapse=false}
 
 ## Reflections
+
+<!-- TODO: Add Johnson et al. 2021 -->
 
@@
 ```{python}
-import plotly.express as px
-
-# Percentage of items reproduced, and percentage of badges awarded
-df = pd.DataFrame({
-  'Shoaib and Ramamohan 2021': [94, 25],
-  'Huang et al. 2019': [37.5, 0],
-  'Lim et al. 2020': [100, 25],
-  'Kim et al. 2021': [100, 25],
-  'Anagnostou et al. 2022': [100, 41.7],
-  #'Johnson et al. 2021': [],
-  'Hernandez et al. 2015': [12.5, 0],
-  'Wood et al. 2021': [100, 41.7]
-}).T.reset_index()
-df.columns = ['study', 'reproduce', 'badges']
-
-px.scatter(df, x='badges', y='reproduce',
-           hover_data={'study': True})
+plot_scatter('Badges awarded',
+             sho = 25,
+             hua = 0,
+             lim = 25,
+             kim = 25,
+             ana = 41.7,
+             her = 0,
+             woo = 41.7)
 ```
@@
 **Essential components of STARS framework:**
+
+<!-- TODO: Add Johnson et al. 2021 -->
 
@@
 
+::: {.callout icon=false collapse=false}
+
+## Reflections
+
+<!-- TODO: Add Johnson et al. 2021 -->
+
+Similar to journal criteria (unsurprisingly, as looking at similar things) - most studies meet very few and have range of reproduction success. Two met more, and both were reproduced.
+
+I think, if we were to draw anything from this, it would be to reflect on exactly what criteria were and were not met, and why/how that impacted reproduction, in any way (either success or time).
+
+*Note: Just considers those fully met, in plot*
+
+```{python}
+plot_scatter('Essential STARS components met',
+             sho = 25,
+             hua = 25,
+             lim = 25,
+             kim = 50,
+             ana = 87.5,
+             her = 25,
+             woo = 25)
+```
+
+:::
+
 **Optional components of STARS framework:**
+
+<!-- TODO: Add Johnson et al. 2021 -->
 
@@
 ```
+
+::: {.callout icon=false collapse=false}
+
+## Reflections
+
+<!-- TODO: Add Johnson et al. 2021 -->
+
+This highlights how Huang meets the most criteria, but is only partially reproduced - but I think it is most interesting to consider why this is.
+
+*Note: Just considers those fully met, in plot*
+
+```{python}
+plot_scatter('Optional STARS components met',
+             sho = 0,
+             hua = 40,
+             lim = 0,
+             kim = 0,
+             ana = 20,
+             her = 0,
+             woo = 0)
+```
+
+:::
 
@@
 
-\
+::: {.callout icon=false collapse=false}
+
+## Reflections
+
+<!-- TODO: Update after Johnson et al. 2021 -->
+
+```{python}
+# Create dataframe of results
+col = ['fully', 'partially', 'not', 'na']
+criteria_dict = {
+  'Archive': [1, 0, 6, 0],
+  'ID': [1, 0, 6, 0],
+  'License': [3, 0, 4, 0],
+  'Relevant': [7, 0, 0, 0],
+  'Complete': [1, 0, 6, 0],
+  'Structured for reuse': [3, 0, 4, 0],
+  'Sufficient docs': [1, 0, 6, 0],
+  'Careful docs': [1, 0, 6, 0],
+  'Step-by-step README': [1, 0, 6, 0],
+  'Execute': [7, 0, 0, 0],
+  'Reproduced': [5, 0, 2, 0],
+  'One hour': [0, 0, 7, 0]
+}
+criteria_wide = pd.DataFrame(criteria_dict, index=col).T
+
+eval_chart(criteria_wide)
+```
+
+**Stored in a permanent archive that is publicly and openly accessible**: Fulfillment doesn't impact reproduction as I was able to get everything needed from the remote code repository (GitHub or GitLab).
+However, if these had been deleted from GitHub, it would have become invaluable.
+
+**Has a persistent identifier**: Fulfillment doesn't impact reproduction.
+
+**Includes an open license**: This had a big impact on our ability to complete reproductions, as we had to ask authors to add an open license to their work, to enable us to use it.
+Gladly, all authors we contacted kindly add these on request.
+However, it's worth noting that this was a relatively common issue, and one of the most important, since it completely prevents reuse if excluded.
+
+**Artefacts are relevant to and contribute to the article’s results**: All met (if not met, this would be a massive hindrance).
+
+**Complete set of materials shared (as would be needed to fully reproduce article)**: This had a really big impact on the reproduction.
+The main reason for longer times in reproduction was (a) code for scenarios not provided, and (b) code to process results into figures and tables not provided.
+
+**Artefacts are well structured/organised (e.g.
+to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community)**: In cases where this was not met, this was often related to hard-coding of parameters, or set up of code in a way that - alike hard-coding - made it much harder to reuse the model (in this context, to reuse them between different scenarios).
+
+**Artefacts are sufficiently documented (i.e.
+to understand how it works, to enable it to be run, including package versions)**: Only two studies had any form of documentation - these were READMEs for @kim_modelling_2021 and @anagnostou_facs-charm_2022 - but this criteria also required "package versions" which were uncommon.
+However, focusing on the READMEs, in both these cases it was great to have these, guiding on how to run the scripts, or on what each folder/file in the repository is.
+
+**Artefacts are carefully documented (more than sufficient - i.e.
+to the extent that reuse and repurposing is facilitated - e.g.
+changing parameters, reusing for own purpose)**: In @anagnostou_facs-charm_2022, they include a file `CHARM_INFO.md` alongside their README which walks through the input parameters for the model.
+I didn't need to change any of these for the reproduction, but would imagine this is to be very helpful if someone were to reuse the model.
+
+**Artefacts are clearly documented and accompanied by a README file with step-by-step instructions on how to reproduce results in the manuscript**: Whilst this was true for @anagnostou_facs-charm_2022, it should be noted that this was a very simple example, just requiring to run one script which quickly reproduces everything!
+I had been a bit uncertain on it, since the README doesn’t explicitly say how to make the figure, but it does provide instructions that lead you to regenerate the exact model results from the paper, and so I feel that it does provide instructions to reproduce results sufficiently (although would be more complete to include instructions for figure too - so if it weren’t a yes/no decision for badges, I would’ve said this was partially met).
+Ideally, studies would clearly outline how to reproduce results in full.
+
+**Scripts can be successfully executed**: This is true, though I did allow troubleshooting, which sometimes took a while.
+Hence, the importance of e.g.
+environments and scripts being provided in a runnable format (both covered on the [reflections page](reflections.qmd)), since these are the hurdles to successfully executing scripts.
+
+**Independent party regenerated results using the authors research artefacts**: On the [reproduction page](reproduction.qmd), I reflected (where possible) on what I thought the primary reasons were, for cases where I didn't manage to reproduce results despite troubleshooting.
+
+**Reproduced within approximately one hour (excluding compute time)**: In this study, this was pretty much impossible, since I followed a protocol of first setting up, reading the article, and so on.
+It is worth noting however that there were two studies that were quite quick to run, which I reflect about on the [reproduction page](reproduction.qmd).
+
+:::
 
@@
 : {tbl-colwidths="[60, 5, 5, 5, 5, 5, 5, 5, 5]"}
+
+::: {.callout icon=false collapse=false}
+
+## Reflections
+
+<!-- TODO: Update after Johnson et al. 2021 -->
+
+```{python}
+# Create dataframe of results
+col = ['fully', 'partially', 'not', 'na']
+badges_dict = {
+  'NISO “Open Research<br>Objects (ORO)”': [1, 0, 6, 0],
+  'NISO “Open Research<br>Objects - All (ORO-A)”': [0, 0, 7, 0],
+  'ACM “Artifacts<br>Available”': [1, 0, 6, 0],
+  'COS “Open Code”': [0, 0, 7, 0],
+  'IEEE “Code Available”': [1, 0, 6, 0],
+  'ACM “Artifacts<br>Evaluated - Functional”': [0, 0, 7, 0],
+  'ACM “Artifacts<br>Evaluated - Reusable”': [0, 0, 7, 0],
+  'IEEE “Code Reviewed”': [1, 0, 6, 0],
+  'NISO “Results<br>Reproduced (ROR-R)”': [5, 0, 2, 0],
+  'ACM “Results Reproduced”': [5, 0, 2, 0],
+  'IEEE “Code Reproducible”': [5, 0, 2, 0],
+  'Psychological Science<br>“Computational Reproducibility”': [0, 0, 7, 0],
+}
+badges_wide = pd.DataFrame(badges_dict, index=col).T
+
+eval_chart(badges_wide)
+```
+
+Only one study had **permanent archive (with persistent identifier)**, hence one being awarded *NISO “Open Research Objects (ORO)”* and *ACM “Artifacts Available”*.
+This was required by two other badges **as well as** sufficient documentation and/or complete set of materials.
+Since the one permanently archived study didn't meet these criteria, none were awarded the two badges: *NISO “Open Research Objects - All (ORO-A)”* or *COS “Open Code”*.
+
+A **complete set of materials** was required by *IEEE “Code Available”* and *IEEE “Code Reviewed”* - but this was only met by one study, as studies commonly did not include code for scenarios or creation of figures and tables.
+It was also required by *ACM “Artifacts Evaluated - Functional and Reusable”* badges, but since that one study didn't meet their **documentation** requirements, none were awarded these badges.
+
+Three badges had one criteria: **reproduction of results** - and hence, several studies received these (*NISO “Results Reproduced (ROR-R)”*, *ACM “Results Reproduced”*, *IEEE “Code Reproducible”*).
+However, it's worth noting that we allowed troubleshooting (since that was how we approached the reproductions), and that some of these studies might not have received these badges, if they have any requirements that exclude troubleshooting (which is likely).
+
+Besides the reproduction and documentation criteria, the final badge *Psychological Science “Computational Reproducibility”* was somewhat impossible to award since it required **reproduction within an hour**, which was somewhat impossible in our procedures, since we read the article and set-up etc beforehand.
+
+:::
 
@@
 
+::: {.callout icon=false collapse=false}
+
+## Reflections
+
+<!-- TODO: Update after Johnson et al. 2021 -->
+
+```{python}
+# Create dataframe of results
+col = ['fully', 'partially', 'not', 'na']
+stars_dict = {
+  'Open license': [3, 0, 4, 0],
+  'Dependency management': [1, 1, 5, 0],
+  'FOSS model': [8, 0, 0, 0],
+  'Minimum documentation': [2, 0, 5, 0],
+  'ORCID': [0, 0, 7, 0],
+  'Citation information': [1, 0, 6, 0],
+  'Remote code repository': [7, 0, 0, 0],
+  'Open science archive': [1, 0, 6, 0],
+  'Enhanced documentation': [0, 0, 7, 0],
+  'Documentation hosting': [0, 0, 7, 0],
+  'Online coding environment': [0, 0, 7, 0],
+  'Model interface': [2, 0, 5, 0],
+  'Web app hosting': [1, 1, 5, 0],
+}
+stars_wide = pd.DataFrame(stars_dict, index=col).T
+
+eval_chart(stars_wide)
+```
+
+As in badge criteria reflections: **open license**, **minimum documentation**, and **open science archive**.
+<!--TODO: Consider re minimum documentation: Kim met for STARS but not for badges.
+Double-check that decision-->
+
+**Dependency management**: This was pretty uncommon, and often took some troubleshooting at the start, to figure out which packages were needed, and certain versions.
+
+**FOSS model**: All met as requirement of our reproduction.
+
+**ORCID** and **citation information**: Doesn't impact reproduction in this case - but we do go to these from having found an article.
+In all cases, I emailed the authors, which requires finding contact information (generally via paper, sometimes from googling them to find new emails).
+
+**Remote code repository**: All met, most common way to share code.
+
+**Enhanced documentation**: Only two studies had any documentation, and neither met these extensive requirements.
+I anticipate - if any had met this - it would've made the reproduction very quick and easy!
+
+**Documentation hosting**: Not applicable, given only basic documentation.
+
+**Online coding environment**: None provided.
+I always intended to run on my own machine, so this might not have had much bearing in my case if provided, but would moreso for people who perhaps didn't have Python or R installed, and hopefully would have bypassed environment troubleshooting issues.
+
+**Model interface**: Two studies had applications, although in both cases, these weren't "outcomes" in scope of reproduction, nor did they produce them.
+
+**Web app hosting**: This was quite important.
+Both apps had been hosted, but one was hosted with a site that is no longer operational.
+In both cases, the app wasn't in "scope" although I did still view it and look into it for one as it was hosted and so could very easily - but for the other, I didn't view it, as I didn't go through the steps of running it locally, since it wasn't the focus.
+
+:::
+
 ## Timings
 
-<!-- TODO: Add Johnson et al. 2021, Hernandez et al. 2015 and Wood et al. 2021 -->
+<!-- TODO: Add Johnson et al. 2021 -->
 
@@
 * @wood_value_2021 - 14m
+
+::: {.callout icon=false collapse=false}
+
+## Reflections
+
+No particular comments, don't think we learn much from the timings here.
+
+:::
 

### 2024-10-17 pages/functions.py

@@ -255,3 +255,55 @@ def calculate_times(used_to_date, times, limit=True):
         # Find proportion out of 40 hours
         prop = round((total_min+used_to_date)/max*100, 1)
         print(f'Used {prop}% of 40 hours max')
+
+
+def plot_scatter(var, sho, hua, lim, kim, ana, her, woo):
+    '''
+    Create scatter plot of variable against reproduction success, with dot size
+    from time taken.
+
+    Parameters:
+    -----------
+    var: string
+        Name of variable to plot
+    sho: number
+        Value for Shoaib and Ramamohan 2021
+    hua: number
+        Value for Huang et al. 2019
+    lim: number
+        Value for Lim et al. 2020
+    kim: number
+        Value for Kim et al. 2021
+    ana: number
+        Value for Anagnostou et al. 2022
+    her: number
+        Value for Hernandez et al. 2015
+    woo: number
+        Value for Wood et al. 2021
+    '''
+    # Create data frame with columns for study, % items reproduced,
+    # time (minutes) spent on reproduction, and the input variable
+    df = pd.DataFrame({
+        'Shoaib and Ramamohan 2021': [94, 1694, sho],
+        'Huang et al. 2019': [37.5, 1450, hua],
+        'Lim et al. 2020': [100, 747, lim],
+        'Kim et al. 2021': [100, 875, kim],
+        'Anagnostou et al. 2022': [100, 130, ana],
+        # 'Johnson et al. 2021': [],
+        'Hernandez et al. 2015': [12.5, 1076, her],
+        'Wood et al. 2021': [100, 230, woo]
+    }).T.reset_index()
+    df.columns = ['study', 'reproduce', 'time', var]
+
+    # Create plot
+    fig = px.scatter(df, x=var, y='reproduce', size='time',
+                     hover_data={'study': True})
+    fig.update_layout(xaxis_range=[-10, 110],
+                      yaxis_range=[-10, 110],
+                      yaxis_title='Items reproduced',
+                      xaxis_ticksuffix='%',
+                      yaxis_ticksuffix='%')
+    fig['data'][0]['showlegend'] = True
+    fig['data'][0]['name'] = ('<b>Dot size:</b><br>Time spent<br>on ' +
+                              'reproduction<br>(smaller=quicker)')
+    return fig

### 2024-10-17 pages/relationship_reproduction_evaluation.qmd
chore(docs): add TODO to several pages

@@
 TODO: Add this page, to assess whether (and if so, how) there is a relationship between the evaluation (code and/or reporting) and how easy it was / able we were to reproduce
+
+TODO: I'm also interested actually particularly in relationship between "reflections" being met, and reproduction.
+
+*this could be more restructured into (a) reflections from evaluations, similar to as I have for reproductions, then supported by the side by side evidence, and then (b) adding that side by side evidence to the existing reflections from reproductions*
+
+TODO: For reflections on evaluations, add reflection that a lack of provision of ORCID or citation information didn't have a big impact here, as I was choosing repositories that I had found from papers, so I already at least knew who the paper authors were.
+Although that doesn't mean that any attempted citation of the repository itself would've necessarily been correct, depending on whether the author list would be the same.
+
+*add some scatter plots to repo evaluation but not sure how helpful they are*

### 2024-10-17 pages/reproduction.qmd
chore(docs): add TODO to several pages

@@
 
+::: {.callout icon=false collapse=false}
+
+## Reproduction reflections
+
+**TODO: Where possible, reflect on what I think to be the primary reason that didn't manage to fully reproduce despite troubleshooting, for the studies where this was the case**
+
+:::
+
+::: {.callout icon=false collapse=false}
+
+## Timing reflections
+
+**TODO: Reflect on these timings - what I think were the primary reason for things to be quicker or slower - and what I think was relevant/important** <!--e.g.
+models with run long times, experimenting with parameters to run it quicker, in order to more easily troubleshoot, else run for long time then discover xyz is wrong-->
+
+:::
+
 ## References

### 2024-10-17 pages/background.qmd
docs(background): add baker 2016
docs(background): add some extra background citations, and citations that inspired protocol

@@
 This included a review of code sharing practices and the development of the STARS framework.
+
+## General context
+
+@baker_1500_2016 - survey of 1576 researchers across disciplines, finding:
+
+* "More than 70% of researchers have tried and failed to reproduce another scientist's experiments"
+* "More than half have failed to reproduce their own experiments"
+* 52% "agree that there is a significant 'crisis' of reproducibility"
+* "Less than 31% think that failure to reproduce published results means that the result is probably wrong, and most say that they still trust the published literature"
+
+Differences between **reproduction** and **replication**
+
+* Reproduction - using their code
+* Replication - writing your own code
+
+@korbmacher_replication_2023 - great discussion of the **replication** crisis
+
+On the [protocol page](protocol.qmd), several reproducibility studies are mentioned, which were used to help inform the methods in our reproducibility assessments.
 

### 2024-10-17 pages/protocol.qmd
docs(background): add some extra background citations, and citations that inspired protocol

@@
 
+## Inspiration
+
+As cited in @heather_protocol_2024, the protocol was informed by several prior studies assessing computational reproducibility:
+
+* @krafczyk_learning_2021: Assessed the reproducibility of seven articles published in the Journal of Computational Physics.
+* @wood_push_2018 and @wood_replication_2018: Assessed the reproducibility of 109 published impact evaluations in low- and middle-income countries.
+Conducted in association with the replication programme of the International Initiative for Impact Evaluation (3ie).
+* @schwander_replication_2021: Assessed the reproducibility of four health economic obesity models.
+* @laurinavichyute_share_2022: Assessed the reproducibility of 118 articles published in the Journal of Memory and Language.
+* @konkol_computational_2019: Assessed the reproducibility of 41 geoscientific articles from Copernicus Publications and the Journal of Statistical Software.
+
+It was also informed by:
+
+* @ayllon_keeping_2021: Article with recommendations on keeping modelling notebooks to support completion of TRACE (TRAnsparent and Comprehensive model Evaluation) documents.
+* @berkeley_initiative_for_transparency_in_the_social_sciences_guide_2022: Guidelines on conducting reproductions of published social science research.
+* @mcmanus_can_2019: Article proposing several possible definitions for success in reproducing or replicating models in health economics.
+* @marwick_packaging_2018: Article recommending how to structure data analytical work as research compendiums using the R package structure.
+
 ## Major deviations from the protocol

### 2024-10-17 pages/other_studies.qmd
docs(other studies): add notes on samuel 2024

--- 2024-09-10 pages/other_studies.qmd
@@
 * @hardwicke_analytic_2021
+* @monks_computer_2023 (although overlap - look at how many of mine are from the review - some were identified from that, but some were not)
+* @henderson_reproducibility_2024
+* @samuel_computational_2024
+    * Reproduction success:
+        * 27,271 jupyter notebooks (2660 GitHub repositories, 3467 publications, majority python)
+        * 15,817 included dependencies in standard requirement files
+        * Of those, 10,388 could be installed successfully
+        * Of those, 1203 ran without error
+        * Of those, 879 produced results identical to those reported in the original notebook
+    * References several other studies that have attempted to re-run jupyter notebooks
+    * ModuleNotFoundError, ImportError and FileNotFounderError were the top 3 common exceptions
+    * Also used `flakenb` to look for code styling errors
+    * Implications:
+        * Low reproducibility as in prior studies
+        * Review processes don't pay attention to journal reproducibiltiy
+        * Common errors around dependencies... Use exiting approaches like requirements, conda and poetry
+        * Some journals, article types, levels of documentation and research fields had more reproduced notebooks than others.
+Worth considering procedures at those journals with most reproduced (**iScience**).
+Also, notebooks combining computation and narrative.
+        * Things go out of data... importance of pre-prints...
+        * Reproducibility badges, reproducibility platforms like REScience, nanopublications

### 2024-10-25 pages/repo_evaluation.qmd
docs(repo evaluation): add johnson 2021

@@
 
-<!-- TODO: Add Johnson et al. 2021 -->
-
 ```{python}
@@
   'Anagnostou et al. 2022 (1/1)': [10, 0, 2, 0],
-  'Johnson et al. 2021 (X/X)': [0, 0, 0, 1],
+  'Johnson et al. 2021 (4/5)': [4, 0, 8, 0],
   'Hernandez et al. 2015 (1/8)': [3, 0, 9, 0],
@@
 
-<!-- TODO: Add Johnson et al. 2021 -->
-
 Four studies met 25% of criteria, and ranged from 12.5% to 100% reproduced.
 
-The remaining three studies were fully reproduced and met 33.3%, 41.7% and 83.3%.
+Two studies met 33% of criteria, and these were 80% and 100% reproduced.
+
+The remaining two studies were fully reproduced and met 41.7% and 83.3% of criteria.
 
@@
              ana = 83.3,
+             joh = 33.3,
              her = 25,
@@
 **Badges:**
-
-<!-- TODO: Add Johnson et al. 2021 -->
 
@@
   'Anagnostou et al. 2022 (1/1)': [5, 0, 7, 0],
-  'Johnson et al. 2021 (X/X)': [0, 0, 0, 1],
+  'Johnson et al. 2021 (4/5)': [3, 0, 9, 0],
   'Hernandez et al. 2015 (1/8)': [0, 0, 12, 0],
@@
 
-<!-- TODO: Add Johnson et al. 2021 -->
+Not certain how meaningful these numbers are, as we have imbalanced numbers of different types of badge, and meeting certain popular criteria will weight what is met v.s. not.
 
-Not certain how meaningful these numbers are, as we have imbalanced numbers of different types of badge, and meeting certain popular criteria will quite weight what is met v.s. not.
+Feel that looking at the criteria met is a bit more meaningful? And then specific examples of how that translates into badges - e.g.
 
-Feel that looking at the criteria met is a bit more meaningful?
-And then specific examples of how that translates into badges - e.g.
-none meeting ACM "Artifacts Evaluated - Functional" as requires xyz and these are commonly not met.
+* None meeting ACM "Artifacts Evaluated - Functional" as requires xyz and these are commonly not met.
+* For several, they meet three badges, but those three badges have one criteria: reproducing results.
+
+Also, it's important to remember here that the criteria used for these were based on what could be found about each badge online, but we likely differences in our procedure (e.g.
+allowed troubleshooting for execution and reproduction, not under tight time pressure to complete).
+Moreover, we focus only on reproduction of the discrete-event simulation, and not on other aspects of the article.
+We cannot guarantee that the badges below would have been awarded in practice by these journals (and, in fact, know likely not for many).
 
@@
              ana = 41.7,
+             joh = 25,
              her = 0,
@@
 **Essential components of STARS framework:**
-
-<!-- TODO: Add Johnson et al. 2021 -->
 
@@
   'Anagnostou et al. 2022 (1/1)': [7, 0, 1, 0],
-  'Johnson et al. 2021 (X/X)': [0, 0, 0, 1],
+  'Johnson et al. 2021 (4/5)': [4, 2, 2, 0],
   'Hernandez et al. 2015 (1/8)': [2, 0, 6, 0],
@@
 
-<!-- TODO: Add Johnson et al. 2021 -->
-
-Similar to journal criteria (unsurprisingly, as looking at similar things) - most studies meet very few and have range of reproduction success. Two met more, and both were reproduced.
+Similar to journal criteria (unsurprisingly, as looking at similar things) - most studies meet very few and have wide range of reproduction success, from 12.5% to 100%.
+Three met more, and these were 80% to 100% reproduced.
 
@@
              ana = 87.5,
+             joh = 50,
              her = 25,
@@
 **Optional components of STARS framework:**
-
-<!-- TODO: Add Johnson et al. 2021 -->
 
@@
   'Anagnostou et al. 2022 (1/1)': [1, 1, 3, 0],
-  'Johnson et al. 2021 (X/X)': [0, 0, 0, 1],
+  'Johnson et al. 2021 (4/5)': [0, 0, 5, 0],
   'Hernandez et al. 2015 (1/8)': [0, 0, 5, 0],
@@
 
-<!-- TODO: Add Johnson et al. 2021 -->
-
 This highlights how Huang meets the most criteria, but is only partially reproduced - but I think it is most interesting to consider why this is.
@@
              ana = 20,
+             joh = 0,
              her = 0,
@@
 | **Criteria related to how artefacts are shared** |
-| Stored in a permanent archive that is publicly and openly accessible | ❌ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | ❌ | ❌ |
-| Has a persistent identifier | ❌ | ❌ | ❌ | ❌ | ✅ |<!--TODO--> | ❌ | ❌ |
-| Includes an open license | ❌ | ✅ | ❌ | ✅ | ✅ |<!--TODO--> | ❌ | ❌ |
+| Stored in a permanent archive that is publicly and openly accessible | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
+| Has a persistent identifier | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
+| Includes an open licence | ❌ | ✅ | ❌ | ✅ | ✅ | ✅ | ❌ | ❌ |
 | **Criteria related to what artefacts are shared** |
-| Artefacts are relevant to and contribute to the article’s results | ✅ | ✅ | ✅ | ✅ | ✅ |<!--TODO--> | ✅ | ✅ |
-| Complete set of materials shared (as would be needed to fully reproduce article) | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ✅ |
+| Artefacts are relevant to and contribute to the article’s results | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ |
+| Complete set of materials shared (as would be needed to fully reproduce article) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ✅ |
 | **Criteria related to the structure and documentation of the artefacts** |
-| Artefacts are well structured/organised (e.g.
-to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community) | ❌ | ❌ | ❌ | ✅ | ✅ |<!--TODO--> | ✅ | ❌ |
-| Artefacts are sufficiently documented (i.e. to understand how it works, to enable it to be run, including package versions) | ❌ | ❌ | ❌ | ❌ | ✅ |<!--TODO--> | ❌ | ❌ |
+| Artefacts are well structured/organised (e.g. to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community) | ❌ | ❌ | ❌ | ✅ | ✅ | ❌ | ✅ | ❌ |
+| Artefacts are sufficiently documented (i.e. to understand how it works, to enable it to be run, including package versions) | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
 | Artefacts are carefully documented (more than sufficient - i.e.
 to the extent that reuse and repurposing is facilitated - e.g.
-changing parameters, reusing for own purpose) | ❌ | ❌ | ❌ | ❌ | ✅ |<!--TODO--> | ❌ | ❌ |
-| Artefacts are clearly documented and accompanied by a README file with step-by-step instructions on how to reproduce results in the manuscript | ❌ | ❌ | ❌ | ❌ | ✅ |<!--TODO--> | ❌ | ❌ |
+changing parameters, reusing for own purpose) | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
+| Artefacts are clearly documented and accompanied by a README file with step-by-step instructions on how to reproduce results in the manuscript | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
 | **Criteria related to running and reproducing results** |
-| Scripts can be successfully executed | ✅ | ✅ | ✅ | ✅ | ✅ |<!--TODO--> | ✅ | ✅ |
-| Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ |<!--TODO--> | ❌ | ✅ |
+| Scripts can be successfully executed | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ |
+| Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ | ✅ | ❌ | ✅ |
 | Reproduced within approximately one hour (excluding compute time) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
@@
 
-<!-- TODO: Update after Johnson et al. 2021 -->
-
 ```{python}
@@
 criteria_dict = {
-  'Archive': [1, 0, 6, 0],
-  'ID': [1, 0, 6, 0],
-  'License': [3, 0, 4, 0],
-  'Relevant': [7, 0, 0, 0],
-  'Complete': [1, 0, 6, 0],
-  'Structured for reuse': [3, 0, 4, 0],
-  'Sufficient docs': [1, 0, 6, 0],
-  'Careful docs': [1, 0, 6, 0],
-  'Step-by-step README': [1, 0, 6, 0],
-  'Execute': [7, 0, 0, 0],
-  'Reproduced': [5, 0, 2, 0],
-  'One hour': [0, 0, 7, 0]
+  'Archive': [1, 0, 7, 0],
+  'ID': [1, 0, 7, 0],
+  'Licence': [4, 0, 4, 0],
+  'Relevant': [8, 0, 0, 0],
+  'Complete': [1, 0, 7, 0],
+  'Structured for reuse': [3, 0, 5, 0],
+  'Sufficient docs': [1, 0, 7, 0],
+  'Careful docs': [1, 0, 7, 0],
+  'Step-by-step README': [1, 0, 7, 0],
+  'Execute': [8, 0, 0, 0],
+  'Reproduced': [6, 0, 2, 0],
+  'One hour': [0, 0, 8, 0]
 }
@@
 
-**Includes an open license**: This had a big impact on our ability to complete reproductions, as we had to ask authors to add an open license to their work, to enable us to use it.
+**Includes an open licence**: This had a big impact on our ability to complete reproductions, as we had to ask authors to add an open licence to their work, to enable us to use it.
 Gladly, all authors we contacted kindly add these on request.
@@
 **Artefacts are well structured/organised (e.g.
-to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community)**: In cases where this was not met, this was often related to hard-coding of parameters, or set up of code in a way that - alike hard-coding - made it much harder to reuse the model (in this context, to reuse them between different scenarios).
+to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community)**: In cases where this was not met, this was often related to hard-coding of parameters, or set up of code in a way that - alike hard-coding - made it much harder to reuse the model (in this context, to reuse them between different scenarios) - or quite a busy/cluttered repository which was confusing to navigate.
 
 **Artefacts are sufficiently documented (i.e.
-to understand how it works, to enable it to be run, including package versions)**: Only two studies had any form of documentation - these were READMEs for @kim_modelling_2021 and @anagnostou_facs-charm_2022 - but this criteria also required "package versions" which were uncommon.
-However, focusing on the READMEs, in both these cases it was great to have these, guiding on how to run the scripts, or on what each folder/file in the repository is.
+to understand how it works, to enable it to be run, including package versions)**: Only three studies had any documentation - READMEs for @kim_modelling_2021, @anagnostou_facs-charm_2022 and @johnson_cost_2021 - but this criteria also required "package versions" which were uncommon.
+However, focusing on the READMEs, in each of these cases it was great to have these, guiding on how to run the scripts, or on what each folder/file in the repository is.
 
@@
 
-**Scripts can be successfully executed**: This is true, though I did allow troubleshooting, which sometimes took a while.
+**Scripts can be successfully executed**: This is true, though I did allow troubleshooting, which sometimes took a long while.
 Hence, the importance of e.g.
@@
 | **“Open objects” badges** |
-| **NISO "Open Research Objects (ORO)"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier<br>• Includes an open license | ❌ | ❌ | ❌ | ❌ | ✅ |<!--TODO--> | ❌ | ❌ |
-| **NISO "Open Research Objects - All (ORO-A)"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier<br>• Includes an open license<br>• Complete set of materials shared (as would be needed to fully reproduce article) | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ❌ |
-| **ACM "Artifacts Available"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier | ❌ | ❌ | ❌ | ❌ | ✅ |<!--TODO--> | ❌ | ❌ |
-| **COS "Open Code"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier<br>• Includes an open license<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Artefacts are sufficiently documented (i.e.
-to understand how it works, to enable it to be run, including package versions) | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ❌ |
-| **IEEE "Code Available"**<br>• Complete set of materials shared (as would be needed to fully reproduce article) | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ✅ |
+| **NISO "Open Research Objects (ORO)"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier<br>• Includes an open licence | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
+| **NISO "Open Research Objects - All (ORO-A)"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier<br>• Includes an open licence<br>• Complete set of materials shared (as would be needed to fully reproduce article) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
+| **ACM "Artifacts Available"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
+| **COS "Open Code"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier<br>• Includes an open licence<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Artefacts are sufficiently documented (i.e.
+to understand how it works, to enable it to be run, including package versions) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
+| **IEEE "Code Available"**<br>• Complete set of materials shared (as would be needed to fully reproduce article) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ✅ |
 | **"Object review" badges** |
 | **ACM "Artifacts Evaluated - Functional"**<br>• Artefacts are sufficiently documented (i.e.
-to understand how it works, to enable it to be run, including package versions)<br>• Artefacts are relevant to and contribute to the article’s results<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Scripts can be successfully executed | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ❌ |
+to understand how it works, to enable it to be run, including package versions)<br>• Artefacts are relevant to and contribute to the article’s results<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Scripts can be successfully executed | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
 | **ACM "Artifacts Evaluated - Reusable"**<br>• Artefacts are sufficiently documented (i.e.
@@
 changing parameters, reusing for own purpose)<br>• Artefacts are relevant to and contribute to the article's results<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Scripts can be successfully executed<br>• Artefacts are well structured/organised (e.g.
-to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community) | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ❌ |
-| **IEEE "Code Reviewed"**<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Scripts can be successfully executed | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ✅ |
+to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
+| **IEEE "Code Reviewed"**<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Scripts can be successfully executed | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ✅ |
 | **"Reproduced" badges** |
-| **NISO "Results Reproduced (ROR-R)"**<br>• Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ |<!--TODO--> | ❌ | ✅ |
-| **ACM "Results Reproduced"**<br>• Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ |<!--TODO--> | ❌ | ✅ |
-| **IEEE "Code Reproducible"**<br>• Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ |<!--TODO--> | ❌ | ✅ |
+| **NISO "Results Reproduced (ROR-R)"**<br>• Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ | ✅ | ❌ | ✅ |
+| **ACM "Results Reproduced"**<br>• Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ | ✅ | ❌ | ✅ |
+| **IEEE "Code Reproducible"**<br>• Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ | ✅ | ❌ | ✅ |
 | **Psychological Science "Computational Reproducibility"**<br>• Independent party regenerated results using the authors research artefacts<br>• Reproduced within approximately one hour (excluding compute time)<br>• Artefacts are well structured/organised (e.g.
-to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community)<br>• Artefacts are clearly documented and accompanied by a README file with step-by-step instructions on how to reproduce results in the manuscript | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ❌ |
+to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community)<br>• Artefacts are clearly documented and accompanied by a README file with step-by-step instructions on how to reproduce results in the manuscript | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
 : {tbl-colwidths="[60, 5, 5, 5, 5, 5, 5, 5, 5]"}
@@
 badges_dict = {
-  'NISO “Open Research<br>Objects (ORO)”': [1, 0, 6, 0],
-  'NISO “Open Research<br>Objects - All (ORO-A)”': [0, 0, 7, 0],
-  'ACM “Artifacts<br>Available”': [1, 0, 6, 0],
-  'COS “Open Code”': [0, 0, 7, 0],
-  'IEEE “Code Available”': [1, 0, 6, 0],
-  'ACM “Artifacts<br>Evaluated - Functional”': [0, 0, 7, 0],
-  'ACM “Artifacts<br>Evaluated - Reusable”': [0, 0, 7, 0],
-  'IEEE “Code Reviewed”': [1, 0, 6, 0],
-  'NISO “Results<br>Reproduced (ROR-R)”': [5, 0, 2, 0],
-  'ACM “Results Reproduced”': [5, 0, 2, 0],
-  'IEEE “Code Reproducible”': [5, 0, 2, 0],
-  'Psychological Science<br>“Computational Reproducibility”': [0, 0, 7, 0],
+  'NISO “Open Research<br>Objects (ORO)”': [1, 0, 7, 0],
+  'NISO “Open Research<br>Objects - All (ORO-A)”': [0, 0, 8, 0],
+  'ACM “Artifacts<br>Available”': [1, 0, 7, 0],
+  'COS “Open Code”': [0, 0, 8, 0],
+  'IEEE “Code Available”': [1, 0, 7, 0],
+  'ACM “Artifacts<br>Evaluated - Functional”': [0, 0, 8, 0],
+  'ACM “Artifacts<br>Evaluated - Reusable”': [0, 0, 8, 0],
+  'IEEE “Code Reviewed”': [1, 0, 7, 0],
+  'NISO “Results<br>Reproduced (ROR-R)”': [6, 0, 2, 0],
+  'ACM “Results Reproduced”': [6, 0, 2, 0],
+  'IEEE “Code Reproducible”': [6, 0, 2, 0],
+  'Psychological Science<br>“Computational Reproducibility”': [0, 0, 8, 0],
 }
@@
 A **complete set of materials** was required by *IEEE “Code Available”* and *IEEE “Code Reviewed”* - but this was only met by one study, as studies commonly did not include code for scenarios or creation of figures and tables.
-It was also required by *ACM “Artifacts Evaluated - Functional and Reusable”* badges, but since that one study didn't meet their **documentation** requirements, none were awarded these badges.
+It was also required by *ACM “Artifacts Evaluated - Functional and Reusable”* badges, but since that one study didn't meet their **documentation** requirements, none were awarded those badges.
 
@@
 
-Besides the reproduction and documentation criteria, the final badge *Psychological Science “Computational Reproducibility”* was somewhat impossible to award since it required **reproduction within an hour**, which was somewhat impossible in our procedures, since we read the article and set-up etc beforehand.
+The final badge *Psychological Science “Computational Reproducibility”* had several criteria, but of importance, one of those was to complete the **reproduction within an hour**.
+This was somewhat impossible in our procedures, since we read the article and set-up etc beforehand, and so none were awarded this badge.
 
@@
 | **Essential components** |
-| **Open license**<br>Free and open-source software (FOSS) license (e.g. MIT, GNU Public License (GPL)) | ❌ | ✅ | ❌ | ✅ | ✅ |<!--TODO--> | ❌ | ❌ |
-| **Dependency management**<br>Specify software libraries, version numbers and sources (e.g. dependency management tools like virtualenv, conda, poetry) | ❌ | ❌ | ❌ | 🟡 | ✅ |<!--TODO--> | ❌ | ❌ |
+| **Open licence**<br>Free and open-source software (FOSS) licence (e.g. MIT, GNU Public Licence (GPL)) | ❌ | ✅ | ❌ | ✅ | ✅ | ✅ | ❌ | ❌ |
+| **Dependency management**<br>Specify software libraries, version numbers and sources (e.g. dependency management tools like virtualenv, conda, poetry) | ❌ | ❌ | ❌ | 🟡 | ✅ | 🟡 | ❌ | ❌ |
 | **FOSS model**<br>Coded in FOSS language (e.g. R, Julia, Python) | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ |
 | **Minimum documentation**<br>Minimal instructions (e.g.
-in README) that overview (a) what model does, (b) how to install and run model to obtain results, and (c) how to vary parameters to run new experiments | ❌ | ❌ | ❌ | ✅ | ✅ |<!--TODO--> | ❌ | ❌ |
-| **ORCID**<br>ORCID for each study author | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ❌ |
-| **Citation information**<br>Instructions on how to cite the research artefact (e.g. CITATION.cff file) | ❌ | ❌ | ❌ | ❌ | ✅ |<!--TODO--> | ❌ | ❌ |
-| **Remote code repository**<br>Code available in a remote code repository (e.g. GitHub, GitLab, BitBucket) | ✅ | ✅ | ✅ | ✅ | ✅ |<!--TODO--> | ✅ | ✅ |
+in README) that overview (a) what model does, (b) how to install and run model to obtain results, and (c) how to vary parameters to run new experiments | ❌ | ❌ | ❌ | ✅ | ✅ | 🟡 | ❌ | ❌ |
+| **ORCID**<br>ORCID for each study author | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
+| **Citation information**<br>Instructions on how to cite the research artefact (e.g. CITATION.cff file) | ❌ | ❌ | ❌ | ❌ | ✅ | ✅ | ❌ | ❌ |
+| **Remote code repository**<br>Code available in a remote code repository (e.g. GitHub, GitLab, BitBucket) | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ |
 | **Open science archive**<br>Code stored in an open science archive with FORCE11 compliant citation and guaranteed persistance of digital artefacts (e.g.
-Figshare, Zenodo, the Open Science Framework (OSF), and the Computational Modeling in the Social and Ecological Sciences Network (CoMSES Net)) | ❌ | ❌ | ❌ | ❌ | ✅ |<!--TODO--> | ❌ | ❌ |
+Figshare, Zenodo, the Open Science Framework (OSF), and the Computational Modeling in the Social and Ecological Sciences Network (CoMSES Net)) | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
 | **Optional components** |
@@
 via notebooks and markdown files, brought together using software like Quarto and Jupyter Book).
-Suggested content includes:<br>• Plain english summary of project and model<br>• Clarifying license<br>• Citation instructions<br>• Contribution instructions<br>• Model installation instructions<br>• Structured code walk through of model<br>• Documentation of modelling cycle using TRACE<br>• Annotated simulation reporting guidelines<br>• Clear description of model validation including its intended purpose | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ❌ |
-| **Documentation hosting**<br>Host documentation (e.g. with GitHub pages, GitLab pages, BitBucket Cloud, Quarto Pub) | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ❌ |
-| **Online coding environment**<br>Provide an online environment where users can run and change code (e.g. BinderHub, Google Colaboratory, Deepnote) | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ❌ |
-| **Model interface**<br>Provide web application interface to the model so it is accessible to less technical simulation users | ❌ | ✅ | ❌ | ❌ | ✅ |<!--TODO--> | ❌ | ❌ |
-| **Web app hosting**<br>Host web app online (e.g. Streamlit Community Cloud, ShinyApps hosting) | ❌ | ✅ | ❌ | ❌ | 🟡 |<!--TODO--> | ❌ | ❌ |
+Suggested content includes:<br>• Plain english summary of project and model<br>• Clarifying licence<br>• Citation instructions<br>• Contribution instructions<br>• Model installation instructions<br>• Structured code walk through of model<br>• Documentation of modelling cycle using TRACE<br>• Annotated simulation reporting guidelines<br>• Clear description of model validation including its intended purpose | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
+| **Documentation hosting**<br>Host documentation (e.g. with GitHub pages, GitLab pages, BitBucket Cloud, Quarto Pub) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
+| **Online coding environment**<br>Provide an online environment where users can run and change code (e.g. BinderHub, Google Colaboratory, Deepnote) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
+| **Model interface**<br>Provide web application interface to the model so it is accessible to less technical simulation users | ❌ | ✅ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
+| **Web app hosting**<br>Host web app online (e.g. Streamlit Community Cloud, ShinyApps hosting) | ❌ | ✅ | ❌ | ❌ | 🟡 | ❌ | ❌ | ❌ |
 : {tbl-colwidths="[60, 5, 5, 5, 5, 5, 5, 5, 5]"}
@@
 stars_dict = {
-  'Open license': [3, 0, 4, 0],
-  'Dependency management': [1, 1, 5, 0],
+  'Open licence': [4, 0, 4, 0],
+  'Dependency management': [1, 2, 5, 0],
   'FOSS model': [8, 0, 0, 0],
-  'Minimum documentation': [2, 0, 5, 0],
-  'ORCID': [0, 0, 7, 0],
-  'Citation information': [1, 0, 6, 0],
-  'Remote code repository': [7, 0, 0, 0],
-  'Open science archive': [1, 0, 6, 0],
-  'Enhanced documentation': [0, 0, 7, 0],
-  'Documentation hosting': [0, 0, 7, 0],
-  'Online coding environment': [0, 0, 7, 0],
-  'Model interface': [2, 0, 5, 0],
-  'Web app hosting': [1, 1, 5, 0],
+  'Minimum documentation': [2, 1, 5, 0],
+  'ORCID': [0, 0, 8, 0],
+  'Citation information': [2, 0, 6, 0],
+  'Remote code repository': [8, 0, 0, 0],
+  'Open science archive': [1, 0, 7, 0],
+  'Enhanced documentation': [0, 0, 8, 0],
+  'Documentation hosting': [0, 0, 8, 0],
+  'Online coding environment': [0, 0, 8, 0],
+  'Model interface': [2, 0, 6, 0],
+  'Web app hosting': [1, 1, 6, 0],
 }
@@
 
-As in badge criteria reflections: **open license**, **minimum documentation**, and **open science archive**.
+These topics were covered in the badge criteria reflections: **open licence**, **minimum documentation**, and **open science archive**.
 <!--TODO: Consider re minimum documentation: Kim met for STARS but not for badges.
@@
 
-**Enhanced documentation**: Only two studies had any documentation, and neither met these extensive requirements.
+**Enhanced documentation**: Only three studies had any documentation, and neither met these extensive requirements.
 I anticipate - if any had met this - it would've made the reproduction very quick and easy!
@@
 
-<!-- TODO: Add Johnson et al. 2021 -->
-
 * @shoaib_simulation_2021 - 30m
@@
 * @anagnostou_facs-charm_2022 - 19m
-* @johnson_cost_2021 - <!--TODO-->
+* @johnson_cost_2021 - 20m
 * @hernandez_optimal_2015 - 13m

### 2024-10-25 pages/functions.py
docs(functions): add johnson to plot_scatter

@@ -257,7 +257,7 @@ def calculate_times(used_to_date, times, limit=True):
         print(f'Used {prop}% of 40 hours max')
 
 
-def plot_scatter(var, sho, hua, lim, kim, ana, her, woo):
+def plot_scatter(var, sho, hua, lim, kim, ana, joh, her, woo):
     '''
     Create scatter plot of variable against reproduction success, with dot size
     from time taken.
@@ -276,6 +276,8 @@ def plot_scatter(var, sho, hua, lim, kim, ana, her, woo):
         Value for Kim et al. 2021
     ana: number
         Value for Anagnostou et al. 2022
+    joh: number
+        Value for Johnson et al. 2021
     her: number
         Value for Hernandez et al. 2015
     woo: number
@@ -289,7 +291,7 @@ def plot_scatter(var, sho, hua, lim, kim, ana, her, woo):
         'Lim et al. 2020': [100, 747, lim],
         'Kim et al. 2021': [100, 875, kim],
         'Anagnostou et al. 2022': [100, 130, ana],
-        # 'Johnson et al. 2021': [],
+        'Johnson et al. 2021': [80, 1189, joh],
         'Hernandez et al. 2015': [12.5, 1076, her],
         'Wood et al. 2021': [100, 230, woo]
     }).T.reset_index()

### 2024-10-25 framework/stars_checklist.tex
chore(docs): correct licence spelling

@@
 \textbf{Essential components} &\tabularnewline
-Open license & \emph{Describe your implementation of this
+Open licence & \emph{Describe your implementation of this
 component}\tabularnewline
@@
 
-\paragraph{Open license}
+\paragraph{Open licence}
 
-Free and open-source software (FOSS) license (e.g. MIT, GNU Public
-License (GPL))
+Free and open-source software (FOSS) licence (e.g. MIT, GNU Public
+Licence (GPL))
 
@@
 \item
-  Clarifying license
+  Clarifying licence
 \item

### 2024-10-25 index.qmd
chore(docs): correct licence spelling

@@
 
-## License {.unnumbered}
+## Licence {.unnumbered}
 
-This book is licensed under a [Creative Commons Attribution 4.0 International (CC BY 4.0)](https://github.com/pythonhealthdatascience/stars_wp1_summary/blob/1a7e932013abd8e4810764b8925e98e9a6473844/LICENSE) license.
+This book is licensed under a [Creative Commons Attribution 4.0 International (CC BY 4.0)](https://github.com/pythonhealthdatascience/stars_wp1_summary/blob/1a7e932013abd8e4810764b8925e98e9a6473844/LICENSE) licence.
 
-[![License: CC BY 4.0](https://licensebuttons.net/l/by/4.0/80x15.png)](https://creativecommons.org/licenses/by/4.0/)
-[![License: CC BY 4.0](https://img.shields.io/badge/License-CC_BY_4.0-lightgrey.svg)](https://creativecommons.org/licenses/by/4.0/)
+[![Licence: CC BY 4.0](https://licensebuttons.net/l/by/4.0/80x15.png)](https://creativecommons.org/licenses/by/4.0/)
+[![Licence: CC BY 4.0](https://img.shields.io/badge/License-CC_BY_4.0-lightgrey.svg)](https://creativecommons.org/licenses/by/4.0/)

### 2024-10-25 pages/framework.qmd
chore(docs): add TODO to several pages
chore(docs): correct licence spelling

@@
 ---
+
+<!--TODO: Move this to stars_wp2-->
 
@@
 
-* Open license - available on about half, added on request for rest, a very important one as without it you technically cannot reuse someones code
+* Open licence - available on about half, added on request for rest, a very important one as without it you technically cannot reuse someones code
 * Complete materials - rarely, so alot of time spent on writing code and figuring out how best to do that

### 2024-10-25 pages/protocol.qmd
chore(docs): correct licence spelling

@@
 For this work, six published healthcare DES models were selected.
-These were models with publicly available code under an open license (either already available or add on request from the STARS team).
+These were models with publicly available code under an open licence (either already available or add on request from the STARS team).
 For each model, the follow stages of work were conducted:
@@
 
-* Informed authors about study and, if not available, asked if they would be happy to add an open license to their code
+* Informed authors about study and, if not available, asked if they would be happy to add an open licence to their code
 * Set up repository for reproduction with the article and code

### 2024-10-25 pages/reflections.qmd
docs(reflections): add tom's suggestion re: solutions for large file sizes
chore(docs): correct licence spelling

@@
 * If there are local dependencies (e.g.
-other GitHub repositories), make sure to (a) mention and link to these repositories, so it is clear they are also required, and (b) include license/s in those repositories also, so they can be used.
+other GitHub repositories), make sure to (a) mention and link to these repositories, so it is clear they are also required, and (b) include licence/s in those repositories also, so they can be used.
 * This was a common issue.
@@
 [GitHub LFS](https://docs.github.com/en/repositories/working-with-files/managing-large-files/about-storage-and-bandwidth-usage) has limits on storage and bandwith use (1GB of each).
+* **Reducing file size isn't the only solution**.
+In cases where you have large files, a good option can be storing it elsewhere and then pulling from there into your workflow - for example, storing in **zenodo** and fetching using [pooch](https://github.com/fatiando/pooch).
 

### 2024-10-25 pages/paper_evaluation.qmd
docs(paper evaluation): add johnson 2021

--- 2024-10-11 pages/paper_evaluation.qmd
@@
 
-<!-- TODO: Add Johnson et al. 2021, Hernandez et al. 2015 and Wood et al. 2021 -->
+<!-- TODO: add charts and reflections like I did for repo evaluation -->
 
@@
   'Anagnostou et al. 2022': [14, 2, 5, 3],
-  'Johnson et al. 2021': [0, 0, 0, 1],
+  'Johnson et al. 2021': [16, 1, 2, 5],
   'Hernandez et al. 2015': [18, 2, 3, 1],
-  'Wood et al. 2021': [0, 0, 0, 1]
+  'Wood et al. 2021': [22, 2, 0, 0]
 }
@@
   'Anagnostou et al. 2022': [8, 3, 4, 3],
-  'Johnson et al. 2021': [0, 0, 0, 1],
-  'Hernandez et al. 2015': [10, 0, 8, 0],
-  'Wood et al. 2021': [0, 0, 0, 1]
+  'Johnson et al. 2021': [15, 0, 2, 1],
+  'Hernandez et al. 2015': [10, 0, 7, 1],
+  'Wood et al. 2021': [13, 0, 4, 1]
 }
@@
 
-<!-- TODO: Add Johnson et al. 2021, Hernandez et al. 2015 and Wood et al. 2021, and update after discussion of Kim et al. 2021 -->
+<!-- TODO: update after discussion of Kim et al. 2021 -->
 
@@
 | **Objectives** | 
-| **1.1 Purpose of the model**<br>Explain the background and objectives for the model | ✅ | ✅ | ✅ | ✅ | ✅ |
+| **1.1 Purpose of the model**<br>Explain the background and objectives for the model | ✅ | ✅ | ✅ | ✅ | ✅ | ✅  | ✅ | ✅ |
 | **1.2 Model outputs**<br>Define all quantitative performance measures that are reported, using equations where necessary.
 Specify how and when they are calculated during the model run along with how any measures of error such as confidence intervals are calculated.
-| 🟡 | ✅ | ✅ | ✅ | ✅ |
+| 🟡 | ✅ | ✅ | ✅ | ✅ | ✅  | ✅ | ✅ |
 | **1.3 Experimentation aims**<br>If the model has been used for experimentation, state the objectives that it was used to investigate.<br>(A) Scenario based analysis – Provide a name and description for each scenario, providing a rationale for the choice of scenarios and ensure that item 2.3 (below) is completed.<br>(B) Design of experiments – Provide details of the overall design of the experiments with reference to performance measures and their parameters (provide further details in data below).<br>(C) Simulation Optimisation – (if appropriate) Provide full details of what is to be optimised, the parameters that were included and the algorithm(s) that was be used.
 Where possible provide a citation of the algorithm(s).
-| ✅ | ✅ | ✅ | ✅ | N/A |
+| ✅ | ✅ | ✅ | ✅ | N/A | ✅  | ✅ | ✅ |
 | **Logic** |
@@
 The goal is to describe the breadth and depth of the model with respect to the system being studied.
-| ✅ | ✅ | ✅ | ✅ | ✅ |
-| **2.2 Base model logic**<br>Give details of the base model logic. Give additional model logic details sufficient to communicate to the reader how the model works. | ✅ | ✅ | ✅ | ✅ | ✅ |
+| ✅ | ✅ | ✅ | ✅ | ✅ | ✅  | ✅ | ✅ |
+| **2.2 Base model logic**<br>Give details of the base model logic. Give additional model logic details sufficient to communicate to the reader how the model works. | ✅ | ✅ | ✅ | ✅ | ✅ | ✅  | ✅ | ✅ |
 | **2.3 Scenario logic**<br>Give details of the logical difference between the base case model and scenarios (if any).
 This could be incorporated as text or where differences are substantial could be incorporated in the same manner as 2.2.
-| ✅ | ✅ | ✅ | ✅ | N/A |
+| ✅ | ✅ | ✅ | ✅ | N/A | ✅  | ✅ | ✅ |
 | **2.4 Algorithms**<br>Provide further detail on any algorithms in the model that (for example) mimic complex or manual processes in the real world (i.e.
@@
 Pseudo-code may be used to describe an algorithm.
-| ✅ | 🟡 | ✅ | 🟡 | ✅ |
+| ✅ | 🟡 | ✅ | 🟡 | ✅ | ✅  | ✅ | ✅ |
 | **2.5.1 Components - entities**<br>Give details of all entities within the simulation including a description of their role in the model and a description of all their attributes.
-| ✅ | ✅ | ✅ | ✅ | ✅ |
-| **2.5.2 Components - activities**<br>Describe the activities that entities engage in within the model. Provide details of entity routing into and out of the activity. | ✅ | ✅ | ✅ | ✅ | ✅ |
-| **2.5.3 Components - resources**<br>List all the resources included within the model and which activities make use of them. | ✅ | ✅ | N/A | N/A | ✅ |
+| ✅ | ✅ | ✅ | ✅ | ✅ | ✅  | ✅ | ✅ |
+| **2.5.2 Components - activities**<br>Describe the activities that entities engage in within the model.
+Provide details of entity routing into and out of the activity.
+| ✅ | ✅ | ✅ | ✅ | ✅ | ✅  | ✅ | ✅ |
+| **2.5.3 Components - resources**<br>List all the resources included within the model and which activities make use of them. | ✅ | ✅ | N/A | N/A | ✅ | N/A | ✅ | ✅ |
 | **2.5.4 Components - queues**<br>Give details of the assumed queuing discipline used in the model (e.g.
@@
 Detail any delays or capacity constraints on the queues.
-| ✅ | ✅ | N/A | N/A | ✅ |
+| ✅ | ✅ | N/A | N/A | ✅ | N/A | ✅ | ✅ |
 | **2.5.5 Components - entry/exit points**<br>Give details of the model boundaries i.e.
@@
 Detail the arrival mechanism (e.g.
-‘thinning’ to mimic a non-homogenous Poisson process or balking) | ✅ | ✅ | ✅ | ✅ | ✅ |
+‘thinning’ to mimic a non-homogenous Poisson process or balking) | ✅ | ✅ | ✅ | ✅ | ✅ | ✅  | ✅ | ✅ |
 | **Data** |
@@
 Provide, where possible, the link and DOI to the data or reference to published literature.<br>All data source descriptions should include details of the sample size, sample date ranges and use within the study.
-| ✅ | ✅ | ✅ | ✅ | ✅ |
+| ✅ | ✅ | ✅ | ✅ | ✅ | ✅  | ✅ | ✅ |
 | **3.2 Pre-processing**<br>Provide details of any data manipulation that has taken place before its use in the simulation, e.g.
 interpolation to account for missing data or the removal of outliers.
-| ✅ | N/A | N/A | ✅ | N/A |
+| ✅ | N/A | N/A | ✅ | N/A | N/A | N/A | ✅ |
 | **3.3 Input parameters**<br>List all input variables in the model.
@@
 Give details of all time dependent parameters and correlation.<br>Clearly state:<br>• Base case data<br>• Data use in experimentation, where different from the base case.<br>• Where optimisation or design of experiments has been used, state the range of values that parameters can take.<br>• Where theoretical distributions are used, state how these were selected and prioritised above other candidate distributions.
-| 🟡 | 🟡 | ✅ | 🟡 | ✅ |
+| 🟡 | 🟡 | ✅ | 🟡 | ✅ | ✅  | ✅ | ✅ |
 | **3.4 Assumptions**<br>Where data or knowledge of the real system is unavailable what assumptions are included in the model?
 This might include parameter values, distributions or routing logic within the model.
-| ✅ | ❌ | ✅ | ✅ | ❌ |
+| ✅ | ❌ | ✅ | ✅ | ❌ | ✅  | ✅ | ✅ |
 | **Experimentation** |
@@
 Report whether initialisation of these variables is deterministic or stochastic.
-| 🟡 | ❌ | ❌ | 🟡 | ❌ |
-| **4.2 Run length**<br>Detail the run length of the simulation model and time units. | ✅ | ✅ | ✅ | ✅ | 🟡 |
+| 🟡 | ❌ | ❌ | 🟡 | ❌ | ✅  | ❌ | ✅ |
+| **4.2 Run length**<br>Detail the run length of the simulation model and time units. | ✅ | ✅ | ✅ | ✅ | 🟡 | ✅  | ✅ | ✅ |
 | **4.3 Estimation approach**<br>State the method used to account for the stochasticity: For example, two common methods are multiple replications or batch means.
@@
 For both procedures provide a justification for the methods used and the number of replications/size of batches.
-| 🟡 | 🟡 | ✅ | ✅ | ✅ |
+| 🟡 | 🟡 | ✅ | ✅ | ✅ | N/A | ✅ | ✅ |
 | **Implementation** |
@@
 Python 3.5).<br>Where frameworks and libraries have been used provide all details including version numbers.
-| 🟡 | 🟡 | 🟡 | 🟡 | 🟡 |
+| 🟡 | 🟡 | 🟡 | 🟡 | 🟡 | 🟡 | 🟡 | 🟡 |
 | **5.2 Random sampling**<br>State the algorithm used to generate random samples in the software/programming language used e.g.
 Mersenne Twister.<br>If common random numbers are used, state how seeds (or random number streams) are distributed among sampling processes.
-| ❌ | 🟡 | ❌ | ❌ | ❌ |
+| ❌ | 🟡 | ❌ | ❌ | ❌ | N/A | ❌ | ✅ |
 | **5.3 Model execution**<br>State the event processing mechanism used e.g.
@@
 For parallel and distributed simulations the time management algorithms used.
-If the HLA is used then state the version of the standard, which run-time infrastructure (and version), and any supporting documents (FOMs, etc.) | 🟡 |❌ | ❌ | ❌ | ❌ |
+If the HLA is used then state the version of the standard, which run-time infrastructure (and version), and any supporting documents (FOMs, etc.) | 🟡 |❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ✅ |
 | **5.4 System specification**<br>State the model run time and specification of hardware used.
@@
 For parallel, distributed and/or use grid or cloud computing, etc.
-state the details of all systems used in the implementation (processors, network, etc.) | ✅ | ❌ | 🟡 | 🟡 | ❌ |
+state the details of all systems used in the implementation (processors, network, etc.) | ✅ | ❌ | 🟡 | 🟡 | ❌ | ❌ | 🟡 | 🟡 |
 | **Code access** |
@@
 Provide, where possible, the link and DOIs to these.
-| ✅ | ✅ | ✅ | ✅ | ✅ |
+| ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ |
 : {tbl-colwidths="[60, 5, 5, 5, 5, 5, 5, 5, 5]"}
@@
 DES studies included different types of decision problems, eg, those listed in previously developed taxonomies.
-| ✅ | ✅ | ✅ | ✅ | ✅ |
+| ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ |
 | **2 Is the modeled healthcare setting/health condition clarified?**<br>...the physical context/scope (eg, a certain healthcare unit or a broader system) or disease spectrum simulated was described.
-| ✅ | ✅ | ✅ | ✅ | ✅ |
-| **3 Is the model structure described?**<br>...the model’s conceptual structure was described in the form of either graphical or text presentation. | ✅ | ✅ | ✅ | ✅ | ✅ |
-| **4 Is the time horizon given?**<br>...the time period covered by the simulation was reported. | ✅ | ✅ | ✅ | ✅ | ❌ |
-| **5 Are all simulated strategies/scenarios specified?**<br>...the comparators under test were described in terms of their components, corresponding variations, etc | ✅ | ✅ | ✅ | ✅ | N/A |
-| **6 Is the target population described?**<br>...the entities simulated and their main attributes were characterized. | ✅ | ❌ | ✅ | ✅ | 🟡 |
+| ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ |
+| **3 Is the model structure described?**<br>...the model’s conceptual structure was described in the form of either graphical or text presentation. | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ |
+| **4 Is the time horizon given?**<br>...the time period covered by the simulation was reported. | ✅ | ✅ | ✅ | ✅ | ❌ | ✅ | ✅ | ✅ |
+| **5 Are all simulated strategies/scenarios specified?**<br>...the comparators under test were described in terms of their components, corresponding variations, etc | ✅ | ✅ | ✅ | ✅ | N/A | ✅ | ✅ | ✅ |
+| **6 Is the target population described?**<br>...the entities simulated and their main attributes were characterized. | ✅ | ❌ | ✅ | ✅ | 🟡 | ✅ | ✅ | ✅ |
 | **Paramaterisation and uncertainty assessment** |
-| **7 Are data sources informing parameter estimations provided?**<br>...the sources of all data used to inform model inputs were reported. | ✅ | ✅ | ✅ | ✅ | ✅ |
-| **8 Are the parameters used to populate model frameworks specified?**<br>...all relevant parameters fed into model frameworks were disclosed. | 🟡 | 🟡 | ✅ | ✅ | ✅ |
+| **7 Are data sources informing parameter estimations provided?**<br>...the sources of all data used to inform model inputs were reported. | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ |
+| **8 Are the parameters used to populate model frameworks specified?**<br>...all relevant parameters fed into model frameworks were disclosed. | 🟡 | 🟡 | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ |
 | **9 Are model uncertainties discussed?**<br>...the uncertainty surrounding parameter estimations and adopted statistical methods (eg, 95% confidence intervals or possibility distributions) were reported.
-| 🟡 | ❌ | ❌ | ❌ | ✅ |
+| 🟡 | ❌ | ❌ | ❌ | ✅ | N/A | ✅ | ✅ |
 | **10 Are sensitivity analyses performed and reported?**<br>...the robustness of model outputs to input uncertainties was examined, for example via deterministic (based on parameters’ plausible ranges) or probabilistic (based on a priori-defined probability distributions) sensitivity analyses, or both.
-| ✅ | ❌ | ✅ | ❌ | N/A |
+| ✅ | ❌ | ✅ | ❌ | N/A | ✅ | ❌ | ✅ |
 | **Validation** |
@@
 It was assumed that this type of validation should be conducted by external evaluators with no stake in the study.
-| ❌ | ❌ | ❌ | ❌ | ❌ |
-| **12 Is cross validation performed and reported**<br>...comparison across similar modeling studies which deal with the same decision problem was undertaken. | N/A | ❌ | ❌ | ✅ | ❌ |
-| **13 Is external validation performed and reported?**<br>...the modeler(s) examined how well the model’s results match the empirical data of an actual event modeled. | N/A | N/A | N/A | ✅ | ❌ |
+| ❌ | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ |
+| **12 Is cross validation performed and reported**<br>...comparison across similar modeling studies which deal with the same decision problem was undertaken. | N/A | ❌ | ❌ | ✅ | ❌ | ✅ | ❌ | ❌ |
+| **13 Is external validation performed and reported?**<br>...the modeler(s) examined how well the model’s results match the empirical data of an actual event modeled.
+| N/A | N/A | N/A | ✅ | ❌ | ✅ | ❌ | ❌ |
 | **14 Is predictive validation performed or attempted?**<br> ...the modeler(s) examined the consistency of a model’s predictions of a future event and the actual outcomes in the future.
 If this was not undertaken, it was assessed whether the reasons were discussed.
-| N/A | N/A | N/A | N/A | N/A |
+| N/A | N/A | N/A | N/A | N/A | ❌ | N/A | N/A |
 | **Generalisability and stakeholder involvement** |
 | **15 Is the model generalizability issue discussed?**<br>...the modeler(s) discussed the potential of the resulting model for being applicable to other settings/populations (single/multiple application).
-| ✅ | ✅ | ✅ | ❌ | 🟡 |
+| ✅ | ✅ | ✅ | ❌ | 🟡 | ✅ | ❌ | ✅ |
 | **16 Are decision makers or other stakeholders involved in modeling?**<br>...the modeler(s) reported in which part throughout the modeling process decision makers and other stakeholders (eg, subject experts) were engaged.
-| ❌ | ❌ | ❌ | ❌ | ✅ |
-| **17 Is the source of funding stated?**<br>...the sponsorship of the study was indicated. | ✅ | ❌ | ✅ | ✅ | ✅ |
-| **18 Are model limitations discussed?**<br>...limitations of the assessed model, especially limitations of interest to decision makers, were discussed. | ✅ | 🟡 | ✅ | ✅ | 🟡 |
+| ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
+| **17 Is the source of funding stated?**<br>...the sponsorship of the study was indicated. | ✅ | ❌ | ✅ | ✅ | ✅ | ✅ | ❌ | ✅ |
+| **18 Are model limitations discussed?**<br>...limitations of the assessed model, especially limitations of interest to decision makers, were discussed. | ✅ | 🟡 | ✅ | ✅ | 🟡 | ✅ | ✅ | ✅ |
 : {tbl-colwidths="[60, 5, 5, 5, 5, 5, 5, 5, 5]"}
@@
 ## Timings
-
-<!-- TODO: Add johnson, hernandez, wood -->
 
@@
 * @anagnostou_facs-charm_2022 - 53m
-* @johnson_cost_2021
-* @hernandez_optimal_2015
-* @wood_value_2021
+* @johnson_cost_2021 - 1h 32m
+* @hernandez_optimal_2015 - 1h 11m
+* @wood_value_2021 - 1h 24m
+
+## Use of reporting guidelines
+
+<!--TODO: Add a similar thing for whether the article was reporting on/building on analysis using a model previously reported, and cite the paper -->
+<!--TODO: In cases where they did, mention whether and what reporting guidelines prior study used -->
+<!--TODO: Look at relationship between these two things (prior paper and reporting guidelines) and how many meet -->
+
+Regarding whether each study mentioned using reporting guidelines:
+
+* @shoaib_simulation_2021 - ❌
+* @huang_optimizing_2019 - ❌
+* @lim_staff_2020 - ❌
+* @kim_modelling_2021 - ❌
+* @anagnostou_facs-charm_2022 - ❌
+* @johnson_cost_2021 - ✅ Consolidated Health Economic Evaluation Reporting Standards (CHEERS) - @husereau_consolidated_2013
+* @hernandez_optimal_2015 - ❌
+* @wood_value_2021 - ✅ STRESS-DES: Strengthening The Reporting of Empirical Simulation Studies (Discrete-Event Simulation) - @monks_strengthening_2019
 

### 2024-10-25 pages/paper_evaluation.qmd
docs(paper evaluation): add some more charts and STRESS-DES reflections

@@
 
-<!-- TODO: add charts and reflections like I did for repo evaluation -->
-
 **STRESS-DES:**
@@
 import pandas as pd
-from functions import eval_chart
+from functions import eval_chart, plot_scatter
 
@@
 ```
+
+::: {.callout icon=false collapse=false}
+
+## Reflections
+
+Of the applicable criteria, all studies fully met at least 60% (and many others still partially met).
+
+I don't think we learn much in relation to items reproduced, and that it is more interesting to consider which criteria were met and whether this aided the reproduction or not.
+
+*Note. This plots the proportion of **applicable** criteria that were **fully met***.
+
+```{python}
+plot_scatter('STRESS-DES criteria met',
+             sho = (17/24)*100,
+             hua = (14/23)*100,
+             lim = (16/21)*100,
+             kim = (15/22)*100,
+             ana = (14/21)*100,
+             joh = (16/19)*100,
+             her = (18/23)*100,
+             woo = (22/24)*100)
+```
+
+:::
 
@@
 ```
+
+::: {.callout icon=false collapse=false}
+
+## Reflections
+
+The proportion of applicable criteria met was lower for this checklist.
+
+However, I again think it's most relevant to consider which criteria were met, rather than draw conclusions from this chart.
+
+*Note. This plots the proportion of **applicable** criteria that were **fully met***.
+
+```{python}
+plot_scatter('STRESS-DES criteria met',
+             sho = (11/15)*100,
+             hua = (7/16)*100,
+             lim = (12/16)*100,
+             kim = (12/17)*100,
+             ana = (8/15)*100,
+             joh = (15/17)*100,
+             her = (10/17)*100,
+             woo = (13/17)*100)
+```
+
+:::
 
@@
 
+::: {.callout icon=false collapse=false}
+
+## Reflections
+
+```{python}
+# Create dataframe of results
+col = ['fully', 'partially', 'not', 'na']
+criteria_dict = {
+  '1.1 Purpose': [8, 0, 0, 0],
+  '1.2 Outputs': [7, 1, 0, 0],
+  '1.3 Aims': [7, 0, 0, 1],
+  '2.1 Diagram': [8, 0, 0, 0],
+  '2.2 Base logic': [8, 0, 0, 0],
+  '2.3 Scenarios': [7, 0, 0, 1],
+  '2.4 Algorithms': [6, 2, 0, 0],
+  '2.5.1 Entities': [8, 0, 0, 0],
+  '2.5.2 Activities': [8, 0, 0, 0],
+  '2.5.3 Resources': [5, 0, 0, 3],
+  '2.5.4 Queues': [5, 0, 0, 3],
+  '2.5.5 Entry/Exit': [8, 0, 0, 0],
+  '3.1 Data sources': [8, 0, 0, 0],
+  '3.2 Pre-processing': [3, 0, 0, 5],
+  '3.3 Inputs': [5, 3, 0, 0],
+  '3.4 Assumptions': [6, 0, 2, 0],
+  '4.1 Initialisation': [2, 2, 4, 0],
+  '4.2 Run length': [7, 1, 0, 0],
+  '4.3 Estimation': [5, 2, 0, 1],
+  '5.1 Language': [0, 8, 0, 0],
+  '5.2 Random': [1, 1, 5, 1],
+  '5.3 Execution': [1, 1, 6, 0],
+  '5.4 System': [1, 4, 3, 0],
+  '6.1 Sharing': [8, 0, 0, 0]
+}
+criteria_wide = pd.DataFrame(criteria_dict, index=col).T
+
+eval_chart(criteria_wide)
+```
+
+I find this chart a really helpful visualisation, to see what is commonly being met, things that are often not applicable, and things often not met.
+
+Below, I've reflected on the impact of each criteria being fulfilled, on the reproduction.
+I've also identified where I feel I've been a bit more lax in my evaluation.
+<!-- TODO: Consider - is this an issue?
+Should I revisit those and be more strict?
+-->
+
+**1.1 Purpose of the model**<br>Explain the background and objectives for the model.
+
+* Pretty basic requirement that all meet (unsurprisingly).
+
+**1.2 Model outputs**<br>Define all quantitative performance measures that are reported, using equations where necessary.
+Specify how and when they are calculated during the model run along with how any measures of error such as confidence intervals are calculated.
+
+* One paper was rated as "partially met" as many of the outcomes used were not defined.
+* For those marked fully met, this was mainly based on them mentioning or being pretty clear about what the outcomes were, but wasn't super strict - ie.
+didn't require equations, or to specify how and when they were calculated.
+* Whilst this is important, the raw/basic outcomes themselves were generally pretty straightforward, and issues with outputs more-so related to:
+  * Which output to use from the results table (if unclear names, or similar names)
+  * How to apply any required transformations
+
+**1.3 Experimentation aims**<br>If the model has been used for experimentation, state the objectives that it was used to investigate.<br>(A) Scenario based analysis – Provide a name and description for each scenario, providing a rationale for the choice of scenarios and ensure that item 2.3 (below) is completed.<br>(B) Design of experiments – Provide details of the overall design of the experiments with reference to performance measures and their parameters (provide further details in data below).<br>(C) Simulation Optimisation – (if appropriate) Provide full details of what is to be optimised, the parameters that were included and the algorithm(s) that was be used.
+Where possible provide a citation of the algorithm(s).
+
+* In all seven papers with scenarios, these were described. Didn't necessarily provide a "name" for each scenario, nor a "rationale" for the choice of scenarios, but did describe them.
+* Although the description of the scenario can feel clear from the paper, when the code was not provided, it could be quick tricky and time-consuming to work out how to appropriately change the code, in order to implement the scenario.
+
+**2.1 Base model overview diagram**<br>Describe the base model using appropriate diagrams and description.
+This could include one or more process flow, activity cycle or equivalent diagrams sufficient to describe the model to readers.
+Avoid complicated diagrams in the main text.
+The goal is to describe the breadth and depth of the model with respect to the system being studied.
+
+* All papers included a diagram, which was great.
+
+**2.2 Base model logic**<br>Give details of the base model logic. Give additional model logic details sufficient to communicate to the reader how the model works.
+
+* Pretty basic requirement that all meet (unsurprisingly).
+
+**2.3 Scenario logic**<br>Give details of the logical difference between the base case model and scenarios (if any).
+This could be incorporated as text or where differences are substantial could be incorporated in the same manner as 2.2.
+
+* Overlap with 1.3 (implicit in describing 1.3, that would describe this).
+
+**2.4 Algorithms**<br>Provide further detail on any algorithms in the model that (for example) mimic complex or manual processes in the real world (i.e.
+scheduling of arrivals/ appointments/ operations/ maintenance, operation of a conveyor system, machine breakdowns, etc.).
+Sufficient detail should be included (or referred to in other published work) for the algorithms to be reproducible.
+Pseudo-code may be used to describe an algorithm.
+
+* Those partially met are for describing some but not all of the algorithms.
+However, it is worth noting that it could be hard to actually ensure all relevant algorithms were described, if I hadn't identified them in the more complex models.
+
+**2.5.1 Components - entities**<br>Give details of all entities within the simulation including a description of their role in the model and a description of all their attributes.
+
+* Pretty basic requirement that all meet (unsurprisingly, as implicit in description of model / logic)
+
+**2.5.2 Components - activities**<br>Describe the activities that entities engage in within the model. Provide details of entity routing into and out of the activity.
+
+* Pretty basic requirement that all meet (unsurprisingly, as implicit in description of model / logic)
+* Didn't necessarily require explicit description of routing.
+
+**2.5.3 Components - resources**<br>List all the resources included within the model and which activities make use of them.
+
+* Generally seem to be mentioned when included, particularly as often form part of output (e.g. resource utilisation)
+* When not mentioned (and based on known structure of model), assume not relevant.
+
+**2.5.4 Components - queues**<br>Give details of the assumed queuing discipline used in the model (e.g.
+First in First Out, Last in First Out, prioritisation, etc.).
+Where one or more queues have a different discipline from the rest, provide a list of queues, indicating the queuing discipline used for each.
+If reneging, balking or jockeying occur, etc., provide details of the rules.
+Detail any delays or capacity constraints on the queues.
+
+* As for 2.5.3
+
+**2.5.5 Components - entry/exit points**<br>Give details of the model boundaries i.e.
+all arrival and exit points of entities.
+Detail the arrival mechanism (e.g.
+‘thinning’ to mimic a non-homogenous Poisson process or balking).
+
+* Generally fairly implicit
+* Overlap with 2.4 algorithms, and hence didn't necessarily mark this down if not full detail of arrival mechanism.
+
+**3.1 Data sources**<br>List and detail all data sources.
+Sources may include:<br>• Interviews with stakeholders,<br>• Samples of routinely collected data,<br>• Prospectively collected samples for the purpose of the simulation study,<br>• Public domain data published in either academic or organisational literature.
+Provide, where possible, the link and DOI to the data or reference to published literature.<br>All data source descriptions should include details of the sample size, sample date ranges and use within the study.
+
+* All meet.
+
+**3.2 Pre-processing**<br>Provide details of any data manipulation that has taken place before its use in the simulation, e.g. interpolation to account for missing data or the removal of outliers.
+
+* Often had to assume that none occurred if none described.
+
+**3.3 Input parameters**<br>List all input variables in the model.
+Provide a description of their use and include parameter values.
+For stochastic inputs provide details of any continuous, discrete or empirical distributions used along with all associated parameters.
+Give details of all time dependent parameters and correlation.<br>Clearly state:<br>• Base case data<br>• Data use in experimentation, where different from the base case.<br>• Where optimisation or design of experiments has been used, state the range of values that parameters can take.<br>• Where theoretical distributions are used, state how these were selected and prioritised above other candidate distributions.
+
+* This was very important as it allows to check that the code parameters were correct as - in several cases - the provided code did not include the base case parameters as described.
+When missing from the paper, it was not possible to check them.
+
+**3.4 Assumptions**<br>Where data or knowledge of the real system is unavailable what assumptions are included in the model?
+This might include parameter values, distributions or routing logic within the model.
+
+* Although not relevant for reproduction, would be very relevant for reuse and validity
+
+**4.1 Initialisation**<br>Report if the system modelled is terminating or non-terminating.
+State if a warm-up period has been used, its length and the analysis method used to select it.
+For terminating systems state the stopping condition.<br>State what if any initial model conditions have been included, e.g., pre-loaded queues and activities.
+Report whether initialisation of these variables is deterministic or stochastic.
+
+* Often not reported, and would be handy as it's a pretty basic/fundamental aspect to the model that would help readers to have better understanding of how the model is working.
+
+**4.2 Run length**<br>Detail the run length of the simulation model and time units.
+
+* Important to mention for same reasons as 3.3
+
+**4.3 Estimation approach**<br>State the method used to account for the stochasticity: For example, two common methods are multiple replications or batch means.
+Where multiple replications have been used, state the number of replications and for batch means, indicate the batch length and whether the batch means procedure is standard, spaced or overlapping.
+For both procedures provide a justification for the methods used and the number of replications/size of batches.
+
+* The description of this criteria is quite confusing - generally just focussed on identifying whether it was multiple replications or a big run, and then if the numbers used were justified.
+* Partially met cases are those with replications that are not justified.
+
+<!--TODO: Check Lim 2020 - think it should be changed to partially met, as no justification mentioned -->
+
+**5.1 Software or programming language**<br>State the operating system and version and build number.<br>State the name, version and build number of commercial or open source DES software that the model is implemented in.<br>State the name and version of general-purpose programming languages used (e.g.
+Python 3.5).<br>Where frameworks and libraries have been used provide all details including version numbers.
+
+* Will often mentioned the programming language, but not operating system or version numbers
+* This was pretty handy, when versions were given, for cases where no versions were given in the repository itself - although ideally, versions could just simply be there.
+
+**5.2 Random sampling**<br>State the algorithm used to generate random samples in the software/programming language used e.g.
+Mersenne Twister.<br>If common random numbers are used, state how seeds (or random number streams) are distributed among sampling processes.
+
+* Frequently not described, despite some of the studies having implemented and used seeds.
+
+<!--TODO: Check Huang 2019, looks like I've answered with arrival sampling, but that is not relevant here - but does indicate that the wording here is a little confusing perhaps -->
+
+**5.3 Model execution**<br>State the event processing mechanism used e.g.
+three phase, event, activity, process interaction.<br>*Note that in some commercial software the event processing mechanism may not be published.
+In these cases authors should adhere to item 5.1 software recommendations.*<br>State all priority rules included if entities/activities compete for resources.<br>If the model is parallel, distributed and/or use grid or cloud computing, etc., state and preferably reference the technology used.
+For parallel and distributed simulations the time management algorithms used.
+If the HLA is used then state the version of the standard, which run-time infrastructure (and version), and any supporting documents (FOMs, etc.)
+
+* Often not mentioned event processing machnism
+* This is a very long list of requirements in one category, and I found a bit difficult to evaluate, e.g. to check against all criteria
+
+**5.4 System specification**<br>State the model run time and specification of hardware used.
+This is particularly important for large scale models that require substantial computing power.
+For parallel, distributed and/or use grid or cloud computing, etc.
+state the details of all systems used in the implementation (processors, network, etc.)
+
+* Model run time was really important to mention, but often not given.
+Particularly important for the models with longer run times, to know what to expect - including in light of reuse, and perhaps short times being necessary in certain contexts - or here, when troubleshooting, to know I might need to try lower numbers first while getting it working
+* Overlaps with 5.3 parallel and 5.1 operating system.
+
+**6.1 Computer model sharing statement**<br>Describe how someone could obtain the model described in the paper, the simulation software and any other associated software (or hardware) needed to reproduce the results.
+Provide, where possible, the link and DOIs to these.
+
+* This is inevitable/selection bias, given we chose papers that had links to code.
+
+:::
+
 ## DES checklist derived from ISPOR-SDM

### 2024-10-25 pages/reflections.qmd
docs(reflections): add summary chart + johnson (both W.I.P.)

@@
 title: "Reflections from reproductions"
+echo: False
 bibliography: ../references.bib
@@
 
+## Summary
+
+<!--TODO: Add stacked bar summary chart -->
+
+```{python}
+import pandas as pd
+from functions import eval_chart
+
+# Create dataframe of results
+col = ['fully', 'partially', 'not', 'na']
+criteria_dict = {
+  'List packages': [2, 3, 3, 0],
+  'Provide versions': [0, 6, 2, 0],
+  'Model in "runnable" format': [7, 0, 1, 0],
+  'Run programmatically': [0, 0, 0, 0],
+  '''Don't hard code scenario param.''': [0, 0, 0, 0],
+  'Relative file paths': [0, 0, 0, 0],
+  'Avoid duplication': [0, 0, 0, 0],
+  'Sufficient comments': [0, 0, 0, 0],
+  'Quicker (?)': [0, 0, 0, 1],
+  'If slow, state run time': [0, 0, 0, 0],
+  'If comp. exp., state usage + alt.': [0, 0, 0, 0],
+  'Provide scenario code': [0, 0, 0, 0],
+  'Provide all required outputs': [0, 0, 0, 0],
+  'Include correct parameters': [0, 0, 0, 0],
+  'Provide all required parameters': [0, 0, 0, 0],
+  'If not, clearly state in paper': [0, 0, 0, 0],
+  'If process param., provide calc.': [0, 0, 0, 0],
+  'Save output to file': [0, 0, 0, 0],
+  'Understandable output tables': [0, 0, 0, 0],
+  'Avoid large files (?)': [0, 0, 0, 1],
+  'Not excessive output files': [0, 0, 0, 0],
+  'Use seeds': [0, 0, 0, 0],
+  'Code to make tables': [0, 0, 0, 0],
+  'Code to make figures': [0, 0, 0, 0],
+  'Code to process in-text results': [0, 0, 0, 0],
+  'Run instructions': [0, 0, 0, 0],
+}
+criteria_wide = pd.DataFrame(criteria_dict, index=col).T
+
+eval_chart(criteria_wide)
+```
+
 ## Environment
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> | 🟡 | ❌ |
+| ❌ | ❌ | 🟡 | ✅ | ✅ | 🟡 | 🟡 | ❌ |
 
@@
 
-@johnson_cost_2021: <!--TODO-->
+@johnson_cost_2021: Partially met. `DESCRIPTION` file accompanying `epicR` package contained some but not all dependencies.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | 🟡 | 🟡 | 🟡 | <!--TODO--> | 🟡 | 🟡 |
+| ❌ | ❌ | 🟡 | 🟡 | 🟡 | 🟡 | 🟡 | 🟡 |
 
@@
 
-@johnson_cost_2021: <!--TODO-->
+@johnson_cost_2021: Partially met. R version given in paper. `DESCRIPTION` file contains minimum versions for some but not all packages.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ✅ | ❌ | ✅ | ✅ | ✅ | <!--TODO--> | ✅ | ✅ |
+| ✅ | ❌ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ |
 

### 2024-10-25 pages/relationship_reproduction_evaluation.qmd
docs(discussion): add various TODO and ideas for discussion

@@
 ---
+
+TODO: Add somewhere in discussion comments about subjectivity and reproduction and how the nature of what is being plot and so on can impact - e.g.
+health economic costs and qalys look super similar, but when turn into incremental to calculate ICER and INMB, tiny different result in big changes.
 
@@
 *add some scatter plots to repo evaluation but not sure how helpful they are*
+
+TODO: Find right place for this reflection: The test-run stage after making compendium helped us to spot run issues that I hadn't noticed, mainly from having not completely tested absolutely everything before pushing.
+For example, Hernandez et al.
+2015, and there was at least one other example too.
+Shows importance of having someone else check things - easy to leave in small mistakes that mean it doesn't run.
+
+TODO: Make a paper with STRESS specific reflections - so ensure these are incorporated in others, then have discussion page where I walk through STRESS and, based on what I have found, suggest what was helpful in framework, what was missing, and so on.
+
+* Consider: which of my reflections pertain to what is in the article, v.s.
+what is in the repository - e.g.
+the scenarios being used is important in both - but mine is actually referring more to the repository, hence relevant to STARS more-so than STARS
+
+TODO: Add reflection from doing evaluations that likely not perfect, can be hard to find things in a paper, may have made mistakes, did have second person check to try and help with this, but that is why it can be so helpful to actually provide a completed framework, that highlights key reporting points for a given study, and where to look, particularly as things get more complicated with appendices and prior papers to refer back to for information.
+
+TODO: Limitation of this work, not reuse, although did sometimes dig into some more than other to figure out how to code scenarios, which is similar to scenarios, but for some could just stay top level.
+Hence, in many cases, can't truly say if information provided was sufficient for that deep understanding of what it is doing and so on.
+
+TODO: Consider, would there be any relevant literature related to time spent to try and get someone elses code mentioned - like how Andy mentioned there would be a max amount of time that someone in the NHS would reasonably spend troubleshooting
+
+TODO: Include reflection that here is what was helpful for reuse, but some aspects of things are not helpful for reuse, but are helpful for other purposes - e.g.
+validity checks - e.g.
+web applications.

### 2024-10-25 pages/reproduction.qmd
docs(reproduction): add johnson

@@
 
-**@johnson_cost_2021:** TBC <!-- TODO: Add Johnson -->
+**@johnson_cost_2021:** This study uses a previously validated discrete-event simulation model, EPIC: Evaluation Platform in chronic obstructive pulmonary disease (COPD).
+The model is written in **C++** with an **R** interface, using R scripts for execution.
+The model is adapted to evaluate the cost-effectiveness of 16 COPD case detection strategies in primary care, comparing costs, quality-adjusted life years (QALYs), incremental cost-effectiveness ratios (ICER), and incremental net monetary benefits (INMB) across scenarios.
+Sensitivity analyses are also conducted.
+<a href="https://pythonhealthdatascience.github.io/stars-reproduce-johnson-2021/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>
 
@@
 | Anagnostou et al. 2022 | 1 item:<br>• 1 figure | 1 out of 1 (100%) | 2h 11m |
-| Johnson et al. 2021 | 5 items:<br>• 1 table<br>• 4 figures | <!--TODO--> | <!--TODO--> |
+| Johnson et al. 2021 | 5 items:<br>• 1 table<br>• 4 figures | 4 out of 5 (80%) | 19h 49m |
 | Hernandez et al. 2015 | 8 items:<br>• 6 figures<br>• 2 tables | 1 out of 8 (12.5%) | 17h 56m |
@@
 
-<!-- TODO: Add Johnson et al. 2021 once conducted reproduction -->
+<!--TODO: Consider changing this figure to have lines straight directly connecting points rather than steps, as that would prevent overlap between hernandez and wood?
+However, time to event data is usually plot like that.
+-->
 
@@
 # Johnson et al. 2021
-# TODO: Add times once completed reproduction
+time_joh = [
+    [1124, 'Table 3'],
+    [1124, 'Figure 3'],
+    [1189, 'Figure 4'],
+    [np.nan, 'Appendix 6'],
+    [1157, 'Appendix 7']]
+df_joh = process_times(time_joh)
 
@@
     (df_ana, 'Anagnostou<br>et al. 2022', '#66ccee'),
-    # (df_joh, 'Johnson et<br>al. 2021', '#aa3377'),
+    (df_joh, 'Johnson et<br>al. 2021', '#aa3377'),
     (df_her, 'Hernandez<br>et al. 2015', '#882255'),

### 2024-10-25 pages/paper_evaluation.qmd
docs(paper evaluation): add previous report checklist, some W.I.P charts, and structure for ISPOR-SDM reflections

@@
 
+::: {.callout icon=false collapse=false}
+
+## Reflections
+
+```{python}
+# Create dataframe of results
+col = ['fully', 'partially', 'not', 'na']
+criteria_dict = {
+  '1 Decision problem': [8, 0, 0, 0],
+  '2 Setting/condition': [8, 0, 0, 0],
+  '3 Structure': [8, 0, 0, 0],
+  '4 Time horizon': [7, 0, 1, 0],
+  '5 Scenarios': [7, 0, 0, 1],
+  '6 Population': [6, 1, 1, 0],
+  '7 Data sources': [8, 0, 0, 0],
+  '8 Inputs': [6, 2, 0, 0],
+  '9 Uncertainty': [3, 1, 3, 1],
+  '10 Sensitivity': [4, 0, 3, 1],
+  '11 Face val.': [1, 0, 7, 0],
+  '12 Cross val.': [2, 0, 5, 1],
+  '13 External val.': [2, 0, 3, 3],
+  '14 Predictive val.': [0, 0, 1, 7],
+  '15 Generalisability': [5, 1, 2, 0],
+  '16 Stakeholders': [1, 0, 7, 0],
+  '17 Funding': [6, 0, 2, 0],
+  '18 Limitations': [6, 2, 0, 0]
+}
+criteria_wide = pd.DataFrame(criteria_dict, index=col).T
+
+eval_chart(criteria_wide)
+```
+
+These guidelines have quite a different focus from STRESS-DES.
+STRESS-DES is very focused on what and how modelling work is performed.
+These guidelines do cover that, but have quite alot of focus on validity of the work, and good practice (e.g.
+stating funding, involving stakeholders).
+
+<!--TODO: Add reflections on each of the elements -->
+
+**1 Is the focused health-related decision problem clarified?**<br>...the decision problem under investigation was defined.
+DES studies included different types of decision problems, eg, those listed in previously developed taxonomies.
+
+*
+
+**2 Is the modeled healthcare setting/health condition clarified?**<br>...the physical context/scope (eg, a certain healthcare unit or a broader system) or disease spectrum simulated was described.
+
+*
+
+**3 Is the model structure described?**<br>...the model’s conceptual structure was described in the form of either graphical or text presentation.
+
+*
+
+**4 Is the time horizon given?**<br>...the time period covered by the simulation was reported.
+
+*
+
+**5 Are all simulated strategies/scenarios specified?**<br>...the comparators under test were described in terms of their components, corresponding variations, etc
+
+*
+
+**6 Is the target population described?**<br>...the entities simulated and their main attributes were characterized.
+
+*
+
+**7 Are data sources informing parameter estimations provided?**<br>...the sources of all data used to inform model inputs were reported.
+
+*
+
+**8 Are the parameters used to populate model frameworks specified?**<br>...all relevant parameters fed into model frameworks were disclosed.
+
+*
+
+**9 Are model uncertainties discussed?**<br>...the uncertainty surrounding parameter estimations and adopted statistical methods (eg, 95% confidence intervals or possibility distributions) were reported.
+
+*
+
+**10 Are sensitivity analyses performed and reported?**<br>...the robustness of model outputs to input uncertainties was examined, for example via deterministic (based on parameters’ plausible ranges) or probabilistic (based on a priori-defined probability distributions) sensitivity analyses, or both.
+
+*
+
+**11 Is face validity evaluated and reported?**<br>...it was reported that the model was subjected to the examination on how well model designs correspond to the reality and intuitions.
+It was assumed that this type of validation should be conducted by external evaluators with no stake in the study.
+
+*
+
+**12 Is cross validation performed and reported**<br>...comparison across similar modeling studies which deal with the same decision problem was undertaken.
+
+*
+
+**13 Is external validation performed and reported?**<br>...the modeler(s) examined how well the model’s results match the empirical data of an actual event modeled.
+
+*
+
+**14 Is predictive validation performed or attempted?**<br> ...the modeler(s) examined the consistency of a model’s predictions of a future event and the actual outcomes in the future.
+If this was not undertaken, it was assessed whether the reasons were discussed.
+
+*
+
+**15 Is the model generalizability issue discussed?**<br>...the modeler(s) discussed the potential of the resulting model for being applicable to other settings/populations (single/multiple application).
+
+*
+
+**16 Are decision makers or other stakeholders involved in modeling?**<br>...the modeler(s) reported in which part throughout the modeling process decision makers and other stakeholders (eg, subject experts) were engaged.
+
+*
+
+**17 Is the source of funding stated?**<br>...the sponsorship of the study was indicated.
+
+* Good practice, usually a journal requirement, although some did not have.
+
+**18 Are model limitations discussed?**<br>...limitations of the assessed model, especially limitations of interest to decision makers, were discussed.
+
+*
+
+:::
+
 ## Timings
@@
 
-<!--TODO: Add a similar thing for whether the article was reporting on/building on analysis using a model previously reported, and cite the paper -->
-<!--TODO: In cases where they did, mention whether and what reporting guidelines prior study used -->
-<!--TODO: Look at relationship between these two things (prior paper and reporting guidelines) and how many meet -->
-
 Regarding whether each study mentioned using reporting guidelines:
@@
 
+<!--TODO: Add reflections on this, and relationship between these and then e.g. how many of the reporting guidelines were met -->
+
+```{python}
+import plotly.express as px
+
+# For each study, define (a) whether use a previously reported model, and (b) proportion of applicable STRESS-DES fully met
+previous_stress =  [
+  (0, (17/24)*100),
+  (0, (14/23)*100),
+  (0, (16/21)*100),
+  (0, (15/22)*100),
+  (0, (14/21)*100),
+  (1, (16/19)*100),
+  (0, (18/23)*100),
+  (1, (22/24)*100)
+]
+
+# Get x and y values
+x, y = zip(*previous_stress)
+
+fig = px.scatter(x=x, y=y)
+fig.show()
+```
+
+## Uses a previously reported model
+
+Regarding whether each study was using a previously reported model:
+
+* @shoaib_simulation_2021 - No
+* @huang_optimizing_2019 - No
+* @lim_staff_2020 - No
+* @kim_modelling_2021 - Yes - previously described by @glover_discrete_2018 and @thompson_screening_2018
+* @anagnostou_facs-charm_2022 - No
+* @johnson_cost_2021 - Yes - `EPIC` model previously described by @sadatsafavi_development_2019
+* @hernandez_optimal_2015 - No
+* @wood_value_2021 - Yes - previously described by @wood_covid-19_2020
+
+<!--TODO: Add reflections on this, and relationship between these and then e.g. how many of the reporting guidelines were met -->
+
+```{python}
+import plotly.express as px
+
+# For each study, define (a) whether use a previously reported model, and (b) proportion of applicable STRESS-DES fully met
+previous_stress =  [
+  (0, (17/24)*100),
+  (0, (14/23)*100),
+  (0, (16/21)*100),
+  (1, (15/22)*100),
+  (0, (14/21)*100),
+  (1, (16/19)*100),
+  (0, (18/23)*100),
+  (1, (22/24)*100)
+]
+
+# Get x and y values
+x, y = zip(*previous_stress)
+
+fig = px.scatter(x=x, y=y)
+fig.show()
+```
+
+<!--TODO: Improve this plot so (a) it's not a massive gap between the bars, (b) it's a function used for this and above rather than duplicate code, (c) so we have ones for STRESS and ISPOR -->
+
+<!-- TODO: consider, did the previously reported model also use reporting guidelines? -->
+
 ## References

### 2024-11-04 pages/reproduction.qmd
docs(reproduction): add reflections on reproduction success and timings

@@
 
-<!--TODO: Consider changing this figure to have lines straight directly connecting points rather than steps, as that would prevent overlap between hernandez and wood?
-However, time to event data is usually plot like that.
+<!--Note: In this figure, Hernandez and Wood overlap.
+Although we would typically have stepped lines like this for time-to-event data, I did explore switching to diagonals to avoid the overlap, but then realised we just get the same issue except with Johnson and Hernandez almost exactly overlapping.
 -->
@@
 
-**TODO: Where possible, reflect on what I think to be the primary reason that didn't manage to fully reproduce despite troubleshooting, for the studies where this was the case**
+For the studies where I didn't manage to fully reproduce results despite troubleshooting, my reflections on what I think to be the primary reason for not managing to reproduce results in each case were:
+
+**@shoaib_simulation_2021:** No specific suggestions - had to write code to run scenarios and process results, so it could be that I hadn't done this all exactly the same as in the original study.
+
+**@huang_optimizing_2019:** No specific suggestions - had to write code to run scenarios and process results, so it could be that I hadn't done this all exactly the same as in the original study.
+
+**@johnson_cost_2021:** No specific suggestions - although note that their results on GitHub appeared to likewise have the same discrepancy compared with the article, so it appears there might have been a minor change to the code/parameters made from that used to produce the article figure that might explain this.
+
+**@hernandez_optimal_2015:** This appears likely to be due to a parameter somewhere being not quite right.
+Ivan Hernandez suggested that it could be a random seed or that the optimisation doesn't have enough runs - although was using the same seed and played around with run number.
+The other suggestion was that the version on GitHub might not have exactly the right version of inputs - and interestingly, he had an earlier version of the paper that had more similar results (our discrepancy was in range on Y axis, and he had an earlier version with range of 0 to 15000).
+This reaffirms that a minor parameter difference is the likely reason for the discrepancy, with that having impacted across nearly all the results.
 
@@
 
-**TODO: Reflect on these timings - what I think were the primary reason for things to be quicker or slower - and what I think was relevant/important** <!--e.g.
-models with run long times, experimenting with parameters to run it quicker, in order to more easily troubleshoot, else run for long time then discover xyz is wrong-->
+There was a large amount of variation in the time each reproduction took. For each study, I have also reflected on what I think were the primary reasons behind things being quicker or slower:
+
+**@shoaib_simulation_2021** - 28h 14m:
+
+* This had lots of items to reproduce (17)
+* Took me longer than usual to set up environment as needed specific package versions and had some confusion around package `statistics` which is base but I had mixed up with one that can be imported from conda/pypi
+* Most of the time was dedicated to identifying parameters for each scenario, writing code to run the scenarios (and run these programmatically), and writing code to process the results into figures and tables.
+
+**@huang_optimizing_2019** - 24h 10m:
+
+* Time-consuming aspects were modifying the code from the app so I could run it, writing code for each scenario, and writing code for figures (it took me quite a whiole to work out transformations for axes and how to standardise density)
+
+**@lim_staff_2020** - 12h 27m:
+
+* Lots of time was spent setting up model so could run programmatically, writing code for scenarios, and writing code to produce figures.
+
+**@kim_modelling_2021** - 14h 42m:
+
+* Time-consuming aspect was largely writing code to produce tables and figures (including figuring out how to process).
+
+**@anagnostou_facs-charm_2022** - 2h 11m:
+
+* This only had one item to reproduce.
+* It required very little troubleshooting - just had to write code to produce figure, although it was relatively simple.
+
+**@johnson_cost_2021** - 19h 49m:
+
+* Most time was spent on writing code for sensitivity analysis, and to produce tables and figures (which included working out which results tables / columns / scenarios to use, how to transform columns, and how to calculate features like efficiency frontier)
+
+**@hernandez_optimal_2015** - 17h 56m:
+
+* Time-consuming aspects were writing code for scenarios and for figures and tables, and troubleshooting parameter discrepancies.
+
+**@wood_value_2021** - 3h 50m:
+
+* Ran quick as code for model didn't require troubleshooting (included all correct parameters and scenarios), and as they provided code to produce the figures and tables.
+
+Regarding run time of the models themselves, for longer models, I sometimes experimented with parameters to run it quicker, in order to more easily troubleshoot, else I would run for a long time and then discover XYZ is wrong.
+Although the model run time itself is not included in the times, it is important to note, as some models took several days, and so in practice, this would impact on someone if they were trying to run a model within a short amount of time.
+
+Regarding the reproduction run times, I think the main reflection from above is that including code with correct parameters and scenarios, and code to make the figures and tables, has a really big impact.
 

### 2024-11-04 pages/reflections.qmd
docs(reflections): add johnson 2021 reflections

@@
 <!--TODO: Add Johnson et al. 2021, Hernandez et al. 2015 and Wood et al. 2021 reflections once have finished reproduction -->
+
+<!--TODO: Check all the notes on Johnson's reflections page are captured below, and that there weren't any new categories to add-->
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ✅ | ✅ | ✅ | ✅ | <!--TODO--> | ✅ | ✅ |
+| ❌ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ |
 
@@
 
-@johnson_cost_2021: <!--TODO-->
+@johnson_cost_2021: Fully met. Creates a list of `input` which are then used by a `run()` function.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | 🟡 | ❌ | ✅ | N/A | <!--TODO--> | 🟡 | ✅ |
+| ❌ | 🟡 | ❌ | ✅ | N/A | ✅ | 🟡 | ✅ |
 
@@
 
-@johnson_cost_2021: <!--TODO-->
+@johnson_cost_2021: Fully met. All model parameters could be varied from "outside" the model code itself, as they were provided as changeable inputs to the model.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | ✅ | ✅ |
+| <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | N/A | ✅ | ✅ |
 
@@
 
-@johnson_cost_2021: <!--TODO-->
+@johnson_cost_2021: Not applicable.
+All inputs defined within script.
+Outputs are not specifically saved to a file (just that the .md and image files were automatically saved when the .Rmd file was knit).
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ✅ | ✅ | ❌ | ✅ | <!--TODO--> | ✅ | ✅ |
+| ❌ | ✅ | ✅ | ❌ | ✅ | ❌ | ✅ | ✅ |
 
@@
 
-@johnson_cost_2021: <!--TODO-->
+@johnson_cost_2021: Not met.
+There was alot of duplication when running each scenario.
+This meant, when amending these for the sensitivity analysis, I would need to change the same parameter 12 times within the script, and for changes to all, changing it 12 times in 14 duplicate scripts.
+Hence, it was simpler to write an R script to do this than change it directly, but for base case, I had to make sure I carefully changed everything in both files.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ✅ | 🟡 | 🟡 | <!--TODO--> | 🟡 | ❌ |
+| ❌ | ❌ | ✅ | 🟡 | 🟡 | ❌ | 🟡 | ❌ |
 
@@
 
-@johnson_cost_2021: <!--TODO-->
+@johnson_cost_2021: Not met. Very few comments in the `Case_Detection_Results...Rmd` files, which were the code files provided.
 
@@
 * @anagnostou_facs-charm_2022: Model was super quick which made it really easy to run and re-run each time
-* @johnson_cost_2021: <!--TODO-->
+* @johnson_cost_2021: Experimented with using a fewer number of agents for troubleshooting (although ultimately had to run with full number to reproduce results), and ran the scripts in parallel by opening seperate terminals simultaneously.
+Note: Long run time also meant it took a longer time to do this reproduction - although we excluded computation time in our timings, it just meant e.g.
+when I made a mistake in coding of scenario analysis and had to re-run, I had to wait another day or two for that to finish before I could resume.
 * @hernandez_optimal_2015: Add parallel processing, did not run one of the scenarios (it was very long, and hadn't managed to reproduce other parts of same figure regardless), and experimented with reducing parameters for evolutionary algorithm (but, in the end, ran with full parameters, though lower were helpful while working through and troubleshooting).
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ✅ | ❌ | ❌ | ❌ | N/A | <!--TODO--> | 🟡 | 🟡 |
+| ✅ | ❌ | ❌ | ❌ | N/A | ✅ | 🟡 | 🟡 |
 
@@
 
-@johnson_cost_2021: <!--TODO-->
+@johnson_cost_2021: Fully met.
+In the README, they state the the run time with 100 million agents is 16 hours, which was very handy to know, as I then just got stuck in running with fewer agents while troubleshooting.
 
@@
 
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| N/A | N/A | N/A | ❌ | N/A | <!--TODO--> | <!--TODO--> | N/A |
+<!--TODO: Consider whether this should be done like a checklist like this?
+As actually, I could run a simple version (e.g.
+serial or one at a time) without issue, but starts taking up more memory with parallel stuff.-->
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| N/A | N/A | N/A | ❌ | N/A | ❌ | <!--TODO--> | N/A |
 
@@
 
-@johnson_cost_2021: <!--TODO-->
+@johnson_cost_2021: Not met.
+It becomes more computationally expensive if try to run lots at once in simultaneous terminals.
+Didn't try running one on local machine with full parameter due to long run time making it infeasible, but knowing my system specs, it should have been able to if did.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | ❌ | N/A | <!--TODO--> | ❌ | ✅ |
+| ❌ | ❌ | ❌ | ❌ | N/A | 🟡 | ❌ | ✅ |
 
@@
 
-@johnson_cost_2021: <!--TODO-->
+@johnson_cost_2021: Partially met. Has all base case scenarios, but not sensitivity analysis.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | ✅ | ✅ |
+| ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ✅ | ✅ |
 
@@
 
-@johnson_cost_2021: <!--TODO-->
+@johnson_cost_2021: Note met.
+It has an output that is in "per 1000" and, although it outputs the columns required to calculate this, I found it very tricky to work out which columns to use and how to transform them to get this output, and so feel this is not met (as feels like a seperate output, and not something simple like a mean, and as it felt so tricky to work out).
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| 🟡 | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> | ❌ | ✅ |
+| 🟡 | ❌ | 🟡 | ✅ | ✅ | ✅ | ❌ | ✅ |
 
@@
 
-@johnson_cost_2021: <!--TODO-->
+@johnson_cost_2021: Fully met. Base case parameters all correct.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | ✅ | ✅ | <!--TODO--> | ❌ | ✅ |
+| ❌ | ❌ | ❌ | ✅ | ✅ | ✅ | ❌ | ✅ |
 
@@
 
-@johnson_cost_2021: <!--TODO-->
+@johnson_cost_2021: Fully met. Could determine appropriate parameters for sensitivity analysis from description in article.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | 🟡 | N/A | N/A | <!--TODO--> | 🟡 | N/A |
+| ❌ | ❌ | 🟡 | N/A | N/A | ✅ | 🟡 | N/A |
 
@@
 
-@johnson_cost_2021: <!--TODO-->
+@johnson_cost_2021: Fully met. All parameters clearly in the two figures presenting the sensitivity analysis, and didn't have to look elsewhere beyond that.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ✅ | N/A | N/A | N/A | <!--TODO--> | N/A | N/A |
+| ❌ | ✅ | N/A | N/A | N/A | N/A | N/A | N/A |
 
@@
 
-@johnson_cost_2021: <!--TODO-->
+@johnson_cost_2021: Not applicable. No processing of parameters required.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ✅ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | ✅ | ✅ |
+| ✅ | ❌ | ❌ | ❌ | ✅ | ❌ | ✅ | ✅ |
 
@@
 
-@johnson_cost_2021: <!--TODO-->
+@johnson_cost_2021: Not met. Outputs to dataframe/s that are not saved as files (although can see within the kept `.md` file from knitting).
 
@@
 
-@johnson_cost_2021: <!--TODO-->
+@johnson_cost_2021: Not met. I had mistakes and confusion figuring out which results tables I needed, which columns to use, and which scenarios to use from the tables.
 
@@
 * @anagnostou_facs-charm_2022: Not relevant (results file **34 kB**)
-* @johnson_cost_2021: <!--TODO-->
+* @johnson_cost_2021: Provided code didn't save results to file. When I saved to `.csv` files, these were small, so not relevant (results files **<3.6kB**)
 * @hernandez_optimal_2015: Not relevant (aggregate results files **<10 kB**).
@@
 * @anagnostou_facs-charm_2022: Not relevant.
-* @johnson_cost_2021: <!--TODO-->
+* @johnson_cost_2021: Not relevant.
 * @hernandez_optimal_2015: The default behaviour of the script was to output **lots of files** from each round (so you could easily have 90, 100, 200+ files), which were then **not** used in analysis (as it just depended on an aggregate results file).
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | ✅ | ✅ | <!--TODO--> | ✅ | ✅ |
+| ❌ | ❌ | ❌ | ✅ | ✅ | ✅ | ✅ | ✅ |
 
@@
 
-@johnson_cost_2021: <!--TODO-->
+@johnson_cost_2021: Fully met. At start of script, authors `set.seed(333)`.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | N/A | 🟡 | ❌ | N/A | <!--TODO--> | ❌ | ✅ |
+| ❌ | N/A | 🟡 | ❌ | N/A | ❌ | ❌ | ✅ |
 
@@
 
-@johnson_cost_2021: <!--TODO-->
+@johnson_cost_2021: Not met. Had to write code to generate tables, which took me a while as I got confused over thinks like which tables / columns / scenarios to use.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | ❌ | ❌ | <!--TODO--> | 🟡 | ✅ |
+| ❌ | ❌ | ❌ | ❌ | ❌ | 🟡 | 🟡 | ✅ |
 
@@
 
-@johnson_cost_2021: <!--TODO-->
+@johnson_cost_2021: Partially met.
+For Figure 3, most of the required code for the figure was provided, which was super helpful.
+However, this wasn't complete, and for all others figures, I had to start from scratch writing the code.
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | 🟡 | ✅ | <!--TODO--> | ❌ | ❌ |
+| ❌ | ❌ | ❌ | 🟡 | ✅ | ✅ | ❌ | ❌ |
 
@@
 
-@johnson_cost_2021: <!--TODO-->
+@johnson_cost_2021: Fully met. README has mini description of model and clear instructions on how to install and run the model.
 
@@
 
+**Version history and releases**.
+@johnson_cost_2021 had commits to their GitHub repository after the publication date.
+It wasn't clear which version aligned with the publication.
+However, the most recent commits add clear README instructions to the repository.
+We decided to use the latest version of the repository, but it would have beneficial to have releases/versions/a change log that would help to outline the commit history in relation to the publication and any subsequent changes.
+
+<!--TODO: update or remove this summary-->
+
 **Reflections:**

### 2024-11-04 pages/reflections.qmd
docs(reflections): completed summary diagrams, relative file paths and comp. expensive models

@@
 
-<!--TODO: Add stacked bar summary chart -->
+This summary excludes:
+
+* "Quicker models are easier to work with"
+* "For computationally expensive models, state memory usage and provide alternatives for lower spec machines"
+* "Avoid large file sizes if possible"
+* "Do not output excessive numbers of files"
+* "Other"
 
@@
   'Model in "runnable" format': [7, 0, 1, 0],
-  'Run programmatically': [0, 0, 0, 0],
-  '''Don't hard code scenario param.''': [0, 0, 0, 0],
-  'Relative file paths': [0, 0, 0, 0],
-  'Avoid duplication': [0, 0, 0, 0],
-  'Sufficient comments': [0, 0, 0, 0],
-  'Quicker (?)': [0, 0, 0, 1],
-  'If slow, state run time': [0, 0, 0, 0],
-  'If comp. exp., state usage + alt.': [0, 0, 0, 0],
-  'Provide scenario code': [0, 0, 0, 0],
-  'Provide all required outputs': [0, 0, 0, 0],
-  'Include correct parameters': [0, 0, 0, 0],
-  'Provide all required parameters': [0, 0, 0, 0],
-  'If not, clearly state in paper': [0, 0, 0, 0],
-  'If process param., provide calc.': [0, 0, 0, 0],
-  'Save output to file': [0, 0, 0, 0],
-  'Understandable output tables': [0, 0, 0, 0],
-  'Avoid large files (?)': [0, 0, 0, 1],
-  'Not excessive output files': [0, 0, 0, 0],
-  'Use seeds': [0, 0, 0, 0],
-  'Code to make tables': [0, 0, 0, 0],
-  'Code to make figures': [0, 0, 0, 0],
-  'Code to process in-text results': [0, 0, 0, 0],
-  'Run instructions': [0, 0, 0, 0],
+  'Can run some programmatically': [7, 0, 1, 0],
+  '''Don't hard code scenario param.''': [3, 2, 2, 1],
+  'Relative file paths': [5, 0, 0, 3],
+  'Avoid duplication': [5, 0, 3, 0],
+  'Sufficient comments': [1, 3, 4, 0],
+  'If slow, state run time': [2, 2, 3, 1],
+  'Provide scenario code': [1, 1, 5, 1],
+  'Provide all required outputs': [3, 0, 5, 0],
+  'Include correct parameters': [4, 2, 2, 0],
+  'Provide all required parameters': [4, 0, 4, 0],
+  'If not, clearly state in paper': [1, 2, 2, 3],
+  'If process param., provide calc.': [1, 0, 1, 6],
+  'Save output to file': [4, 0, 4, 0],
+  'Understandable output tables': [5, 0, 3, 0],
+  'Use seeds': [5, 0, 3, 0],
+  'Code to make tables': [1, 1, 4, 2],
+  'Code to make figures': [1, 2, 5, 0],
+  'Code to process in-text results': [0, 0, 3, 5],
+  'Run instructions': [2, 1, 5, 0],
 }
@@
 Or was it more that I saw an issue with relative file paths that were tricky to change?
-Have mentioned this is a bit under "Saves output to a file"-->
-
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | N/A | ✅ | ✅ |
-
-@shoaib_simulation_2021: <!--TODO-->
-
-@huang_optimizing_2019: <!--TODO-->
-
-@lim_staff_2020: <!--TODO-->
-
-@kim_modelling_2021: <!--TODO-->
-
-@anagnostou_facs-charm_2022: <!--TODO-->
+Have mentioned this is a bit under "Saves output to a file".
+Although maybe it doesn't have to be an issue to mention it - can just be a positive, that noticed all used?-->
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ✅ | N/A | N/A | ✅ | ✅ | N/A | ✅ | ✅ |
+
+@shoaib_simulation_2021: Fully met. Just provides file path, so file is saved into current/run directory.
+
+@huang_optimizing_2019: Not applicable. All inputs defined within script. Outputs were not saved to file/s.
+
+@lim_staff_2020: Not applicable. All inputs defined within script. Outputs were not saved to file/s.
+
+@kim_modelling_2021: Fully met. Uses relative file paths for sourcing model and input parameters (gets current directory, then navigates from there).
+
+@anagnostou_facs-charm_2022: Fully met. Uses relative imports of local code files.
 
@@
 Outputs are not specifically saved to a file (just that the .md and image files were automatically saved when the .Rmd file was knit).
+EpicR is package import.
 
@@
 
-<!--TODO: Consider whether this should be done like a checklist like this?
-As actually, I could run a simple version (e.g.
-serial or one at a time) without issue, but starts taking up more memory with parallel stuff.-->
-
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| N/A | N/A | N/A | ❌ | N/A | ❌ | <!--TODO--> | N/A |
-
-@shoaib_simulation_2021, @huang_optimizing_2019, and @lim_staff_2020: Not applicable. Didn't find it to be too computationally expensive for my machine.
-
-@kim_modelling_2021: Not met.
-Unable to run on my machine (`serial` took too long to run (would have to leave laptop on for many many hours which isn't feasible), and `parallel` was too computationally expensive and crashed the machine (with the original number of people)).
+As I felt this was relatively subjective, as depending on what I felt to be "computationally expensive", as I didn't record the memory usage of all models, it felt unfair to do this as a checklist, and so have just informally noted below:
+
+* @shoaib_simulation_2021, @huang_optimizing_2019, and @lim_staff_2020: Not applicable. Didn't find it to be too computationally expensive for my machine.
+* @kim_modelling_2021: Unable to run on my machine (`serial` took too long to run (would have to leave laptop on for many many hours which isn't feasible), and `parallel` was too computationally expensive and crashed the machine (with the original number of people)).
 This is not mentioned in the repository or paper, but only referred to in a prior publication.
 Would've been handy if it included suggestions like reducing number of people and so on (which is what I had to do to feasibly run it).
-
-@anagnostou_facs-charm_2022: Not applicable. Runs in seconds.
-
-@johnson_cost_2021: Not met.
-It becomes more computationally expensive if try to run lots at once in simultaneous terminals.
+* @anagnostou_facs-charm_2022: Not applicable. Runs in seconds.
+* @johnson_cost_2021: It becomes more computationally expensive if try to run lots at once in simultaneous terminals.
 Didn't try running one on local machine with full parameter due to long run time making it infeasible, but knowing my system specs, it should have been able to if did.
-
-@hernandez_optimal_2015: <!--TODO: This had long run times but I don't know if it was computationally expensive or not. May need to run again for a while and see what memory usage is-->
-
-@wood_value_2021: Not applicable. As stated in their prior paper, the model is constrained by processing time, not computer memory.
+* @hernandez_optimal_2015: This had long run times but I don't know if it was computationally expensive or not - I just know that I didn't run into any issues (but I didn't record memory usage, so its possible a lower-specced machine might).
+* @wood_value_2021: Not applicable. As stated in their prior paper, the model is constrained by processing time, not computer memory.
 

### 2024-11-04 pages/reproduction.qmd
docs(reproduction): add model run times

@@
 
-## Scope
+## Scope and reproduction
 
@@
 
-## Time to completion
+::: {.callout icon=false collapse=false}
+
+## Reproduction reflections
+
+For the studies where I didn't manage to fully reproduce results despite troubleshooting, my reflections on what I think to be the primary reason for not managing to reproduce results in each case were:
+
+**@shoaib_simulation_2021:** No specific suggestions - had to write code to run scenarios and process results, so it could be that I hadn't done this all exactly the same as in the original study.
+
+**@huang_optimizing_2019:** No specific suggestions - had to write code to run scenarios and process results, so it could be that I hadn't done this all exactly the same as in the original study.
+
+**@johnson_cost_2021:** No specific suggestions - although note that their results on GitHub appeared to likewise have the same discrepancy compared with the article, so it appears there might have been a minor change to the code/parameters made from that used to produce the article figure that might explain this.
+
+**@hernandez_optimal_2015:** This appears likely to be due to a parameter somewhere being not quite right.
+Ivan Hernandez suggested that it could be a random seed or that the optimisation doesn't have enough runs - although was using the same seed and played around with run number.
+The other suggestion was that the version on GitHub might not have exactly the right version of inputs - and interestingly, he had an earlier version of the paper that had more similar results (our discrepancy was in range on Y axis, and he had an earlier version with range of 0 to 15000).
+This reaffirms that a minor parameter difference is the likely reason for the discrepancy, with that having impacted across nearly all the results.
+
+:::
+
+## Time to complete reproductions
 
@@
 
-## Reproduction reflections
-
-For the studies where I didn't manage to fully reproduce results despite troubleshooting, my reflections on what I think to be the primary reason for not managing to reproduce results in each case were:
-
-**@shoaib_simulation_2021:** No specific suggestions - had to write code to run scenarios and process results, so it could be that I hadn't done this all exactly the same as in the original study.
-
-**@huang_optimizing_2019:** No specific suggestions - had to write code to run scenarios and process results, so it could be that I hadn't done this all exactly the same as in the original study.
-
-**@johnson_cost_2021:** No specific suggestions - although note that their results on GitHub appeared to likewise have the same discrepancy compared with the article, so it appears there might have been a minor change to the code/parameters made from that used to produce the article figure that might explain this.
-
-**@hernandez_optimal_2015:** This appears likely to be due to a parameter somewhere being not quite right.
-Ivan Hernandez suggested that it could be a random seed or that the optimisation doesn't have enough runs - although was using the same seed and played around with run number.
-The other suggestion was that the version on GitHub might not have exactly the right version of inputs - and interestingly, he had an earlier version of the paper that had more similar results (our discrepancy was in range on Y axis, and he had an earlier version with range of 0 to 15000).
-This reaffirms that a minor parameter difference is the likely reason for the discrepancy, with that having impacted across nearly all the results.
-
-:::
-
-::: {.callout icon=false collapse=false}
-
 ## Timing reflections
@@
 
+## Model run times
+
+For reference, the run times for the models are detailed below.
+It's worth being aware that these are not compared on a "level playing field" as they were run on different machines, and with/without parallel processing or parallel terminals.
+
+| Study | Machine specs | Model run time | Additional details |
+| --- | --- | --- | --- |
+| @shoaib_simulation_2021 | Intel Core i7-12700H with 32GB RAM running Ubuntu 22.04.4 Linux | **22 minutes 26 seconds** | This is based on the combined runtime of the notebooks which use 10 replications (rather than 100) and parallel processing, but with each notebook run seperately.
+|
+| @huang_optimizing_2019 | Intel Core i7-12700H with 32GB RAM running Ubuntu 22.04.4 Linux | **29 minutes 10 seconds** | Combined time from notebooks run seperately. |
+| @lim_staff_2020 | Intel Core i7-12700H with 32GB RAM running Ubuntu 22.04.4 Linux | **49 minutes and 17 seconds** |
+| @kim_modelling_2021 | Intel Core i9-13900K with 81GB RAM running Pop!_OS 22.04 Linux | **6 hours 53 minutes** |We reduced the number of patients in the simulation from 10 million to 1 million, to improve run times.
+Note, you can expect the runtime to be **notably longer** on machines with lower specs than this.
+For example, I ran surveillance scenario 0 on an Intel Core i7-12700H with 32GB RAM running Ubuntu 22.04.4 Linux.
+The runtime increased from **4 minutes 28 seconds** up to **21 minutes 59 seconds**.
+|
+| @anagnostou_facs-charm_2022 | Intel Core i7-12700H with 32GB RAM running Ubuntu 22.04.4 Linux | **Only a few seconds**. |
+| @johnson_cost_2021 | Intel Core i9-13900K with 81GB RAM running Pop!_OS 22.04 Linux | **At least 1 day 11 hours** | It was run from the command line via multiple terminals simultaneously - hence, the exact times are impacted by the number being ran at once.
+The base case scenarios were ran at the same time, and took an overall total time of **20 hours 40 minutes**.
+The sensitivity analysis scenario were all ran at the same time, and took an overall total of **1 day 10 hours 57 minutes**.
+Four files (scenarios 2 and 3) had to be re-run seperately after fixing a mistake, and when just those were run, the total was **21 hours 26 minutes** (quicker than when they were run as part of the full set of scenarios, when they took up to 1.3 days).
+Based on this, if you were to run all scenarios at once in parallel in seperate terminals, you could expect a run time of **at least 1 day 11 hours**, but would be higher than that (since the more run at once, the lower it takes, as you can see from the scenario 2 and 3 times above).
+|
+| @hernandez_optimal_2015| Intel Core i9-13900K with 81GB RAM running Pop!_OS 22.04 Linux | **9 hours 16 minutes** | This involved running the models within each experiment in parallel, but each of the experiment files seperately.
+If these are run at the same time (which I could do without issue), then you will be able to run them all within **4 hours 28 minutes** (the longest experiment) (or a little longer, due to slowing speeds from running at once).
+Also, this has excluded one of the variants for Experiment 3, which I did not run as it had a very long run time (quoted to be 27 hours in the article) and as, regardless, I had not managed to reproduce the other sub-plots in the figure for that experiment.
+|
+| @wood_value_2021 | Intel Core i9-13900K with 81GB RAM running Pop!_OS 22.04 Linux | **48 hours 25 minutes** | It ran in a single loop, so required the computer to remain on for that time.
+This time includes all scenarios - but, for just the base scenario, the run time was **2 hours 3 minutes**.
+|
+: {tbl-colwidths="[20, 20, 20, 40]"}
+
 ## References

### 2024-11-04 pages/reflections.qmd
docs(reflections): update reflections for each item, now that have add hernandez wood and johnson

@@
 With each section, I have created a table which evaluates whether the facilitators were fully met (✅), partially met (🟡), not met (❌) or not applicable (N/A) for each study.
-
-<!--TODO: Add Johnson et al. 2021, Hernandez et al. 2015 and Wood et al. 2021 reflections once have finished reproduction -->
-
-<!--TODO: Check all the notes on Johnson's reflections page are captured below, and that there weren't any new categories to add-->
 
@@
 
+<!-- TODO: From Tom - So much great work and interesting findings.
+We need to move towards some headlines and take aways for the community.
+Mayybe there are some high level groupings of your findings?
+e.g.
+
+* Study reporting
+* Model structuring and functionality
+* Analysis pipeline
+
+Or perhaps:
+
+* Evidence supporting the use of reporting guidelines
+    * as in - reporting guidelines state this should info be included and you found it v.difficult or impossible to reproduce without it.?
+-->
+
 ## Summary
 
-This summary excludes:
-
-* "Quicker models are easier to work with"
-* "For computationally expensive models, state memory usage and provide alternatives for lower spec machines"
-* "Avoid large file sizes if possible"
-* "Do not output excessive numbers of files"
-* "Other"
+This is a summary of all the items that were evaluated (with ✅🟡❌) below.
 
@@
 
-**Reflections:** <!--TODO: Update reflections (since have added Johnson, Hernandez and Wood) -->
+**Reflections:**
 
 * The `import` statements can be sufficient in indicating all the packages required but this is not always the case if there are "hidden"/unmentioned dependencies that don't get imported
-* There are various options for listing the packages (e.g. comprehensive import statements, installation lines in the script, environment files).
+* There are various options for listing the packages (e.g. comprehensive import statements, installation lines in the script, environment files, package DESCRIPTION file).
 * Ideally mention this in repository, not just the paper.
@@
 
-**Reflections:** <!--TODO: Update reflections (since have added Johnson, Hernandez and Wood) -->
+**Reflections:**
 
@@
 
-@johnson_cost_2021: <!--TODO-->
+@johnson_cost_2021: Fully met. Model provided as a package (which is an R interface for the C++ model).
 
@@
 :::
-
-<!--TODO: Consider overlap between some of these and how clear it is.
-I seperated to seperate out the script structure v.s.
-hard coding v.s.
-providing parameters and scenarios later.
-Consider whether evaluation for Shoaib below feels correct or not.
--->
 
@@
 * This was an uncommon issue.
+* Note, this just refers to the basic set-up, with items below like hard coding parameters also being very important in this context.
 
@@
 @hernandez_optimal_2015: Partially met.
-Did not hard code, runs, population, generations, and percent pre-screened.
+Did not hard code runs, population, generations, and percent pre-screened.
 However, did hard code other parameters like bi-objective v.s tri-objective model and bounding.
@@
 
-**Reflections:** <!--TODO: Update reflections (since have added Johnson, Hernandez and Wood) -->
+**Reflections:**
 
 * It can be quite difficult to change parameters that are hard coded into the model. Ideally, all the parameters that a user might want to change should be easily changeable and not hard coded.
-* This is a somewhat common issue.
+* This is a relatively common issue.
 * There is overlap between this and whether the code for scenarios is provided (as typically, the code for scenario is conditionally changing parameter values, although this can be facilitated by not hard coding the parameters, so you call need to change the values from "outside" the model code, rather than making changes to the model functions themselves).
@@
 ## Use relative file paths
-
-<!--TODO: Consider whether this is something to keep?
-Did any have an issue with relative file paths?
-Or was it more that I saw an issue with relative file paths that were tricky to change?
-Have mentioned this is a bit under "Saves output to a file".
-Although maybe it doesn't have to be an issue to mention it - can just be a positive, that noticed all used?-->
 
@@
 
-**Reflections:** <!--TODO: Update reflections (when add Shoaib, Huang, Lim, Kim and Wood) and then (since have added Johnson, Hernandez and Wood) -->
+**Reflections:**
+
+* This was not an issue for any studies - but included to note this was a "facilitator", as would have needed to amend if they weren't.
 
@@
 
-**Reflections:** <!--TODO: Update reflections (since have added Johnson, Hernandez and Wood) --> Large amounts of code duplication are non-ideal as they can:
+**Reflections:** Large amounts of code duplication are non-ideal as they can:
 
@@
 * Increase the likelihood of introducing mistakes
+* Make it trickier to set up scenarios/sensitivity analyses
 
@@
 * Good to have consistent comments and docstrings throughout (i.e. on all scripts, on not just some of them)
+* Common issue
 
@@
     * Relatedly, it is good practice to re-run all scripts before finishing up, as then you can spot any errors like the one mentioned for @kim_modelling_2021
-* Common issue (to varying degrees - i.e. taking 20 minutes, up to taking several hours).
+* Common issue (to varying degrees - i.e. taking 20 minutes, up to taking several hours or even day/s).
 
@@
 
-**Reflections:** <!--TODO: Update reflections (since have added Johnson, Hernandez and Wood) -->
+**Reflections:**
 
 * Some models are so computationally expensive that it may be simply impossible to run it a feasible length of time without a high powered machine.
+* Handy to mention memory requirements so someone with lower spec machine can ensure they would be able to run it.
 * If a model is computationally expensive, it would be good to provide suggested alternatives that allow it to be run on lower spec machines
@@
 
-@johnson_cost_2021: Fully met. Could determine appropriate parameters for sensitivity analysis from description in article.
+@johnson_cost_2021: Fully met. Could determine appropriate parameters for sensitivity analysis from figures in article.
 
@@
 * Make it clear what each colum/category in the results table means, if it might not be immediately clear.
+* Make differences between seperate results tables clear.
 
@@
 
-**Reflections:** <!--TODO: Update reflections once add Johnson -->
-
-* For most studies, this was not relevant, with outputs relatively small
+**Reflections:**
+
+* For most studies, this was not relevant, with outputs relatively small.
 * I only really found this to be an issue when files exceeded GitHub threshold.
@@
 
+<!--TODO: Move this to other, or move things from other up here into their own boxes -->
+
 ## Do not output excessive numbers of files
 
-I have not evaluated like as a criteria, as a large number of files is not inherently a bad thing, and might be difficult to avoid.
+I have not evaluated this as a criteria, as a large number of files is not inherently a bad thing, and might be difficult to avoid.
 
@@
 
-**Reflections:** <!--TODO: Update reflections once add Johnson -->
+**Reflections:**
 
@@
 * It can be really quite simple to include seeds.
+* Over half of the studies did include seed control in their code.
 
@@
 | ❌ | N/A | 🟡 | ❌ | N/A | ❌ | ❌ | ✅ |
-
-<!--TODO: Lim 2020... I think from memory that this output tables  similar to the paper, but I then changed them as that format was difficult to compare/work with -->
 
@@
 
-**Reflections:** <!--TODO: Update reflections (since have added Johnson, Hernandez and Wood) -->
-
-* It can take a bit of time to do this processing, so very handy for it to be provided.
+**Reflections:**
+
+* It can take a bit of time to do this processing, and it can be tricky/confusing to do correctly, so very handy for it to be provided.
 * Common issue.
@@
 It was also unclear and a bit tricky to work out how to standardise the density in the figures (since it is only described in the text and no formula/calculations are provided there or in the code).
-<!-- TODO: Consider whether this should be split into another box (i.e.
-about providing the processing?) -->
 
@@
 
-**Reflections:** <!--TODO: Update reflections (since have added Johnson, Hernandez and Wood) -->
+**Reflections:**
 
 * It can take a bit of time to do this processing, particularly if the figure involves any transformations (and less so if the figure is simple), so very handy for it to be provided.
+* Also, handy if the full code can be provided for all figures (although partial code is more helpful than none at all).
 * Common issue.
@@
 * Provide code to calculate in-text results
+* Universal issue, for those with in-text results not otherwise captured in tables and figures
+
+:::
+
+## Documentation
+
+::: {.callout-important icon=false collapse=true}
+
+## Include instructions on how to run the model/script
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ❌ | ❌ | 🟡 | ✅ | ✅ | ❌ | ❌ |
+
+@shoaib_simulation_2021: Not met. No instructions, although is just a single script that you run.
+
+@huang_optimizing_2019: Not met. Not provided in runnable form but, regardless, no instructions for running it as it is provided (as a web application - i.e. no info on how to get that running).
+
+@lim_staff_2020: Not met. No instructions, although is just a single script that you run.
+
+@kim_modelling_2021: Partially met. README tells you which folder has the scripts you need, although nothing further. Although all you need to do is run them.
+
+@anagnostou_facs-charm_2022: Fully met. Clear README with instructions on how to run the model was really helpful.
+
+@johnson_cost_2021: Fully met. README has mini description of model and clear instructions on how to install and run the model.
+
+@hernandez_optimal_2015: Not met.
+
+@wood_value_2021: Not met. No instructions, although it was fairly self explanatory (single script `master.R` to run, then processing scripts named after items in article e.g. `fig7.R`).
+
+**Reflections:**
+
+* Even if as simple as running a script, include instructions on how to do so
+* In simpler projects (e.g. single script), this can be less of a problem.
 * Common issue
@@
 
-## Documentation
-
-::: {.callout-important icon=false collapse=true}
-
-## Include instructions on how to run the model/script
-
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | 🟡 | ✅ | ✅ | ❌ | ❌ |
-
-@shoaib_simulation_2021: Not met. No instructions, although is just a single script that you run.
-
-@huang_optimizing_2019: Not met. Not provided in runnable form but, regardless, no instructions for running it as it is provided (as a web application - i.e. no info on how to get that running).
-
-@lim_staff_2020: Not met. No instructions, although is just a single script that you run.
-
-@kim_modelling_2021: Partially met. README tells you which folder has the scripts you need, although nothing further. Although all you need to do is run them.
-
-@anagnostou_facs-charm_2022: Fully met. Clear README with instructions on how to run the model was really helpful.
-
-@johnson_cost_2021: Fully met. README has mini description of model and clear instructions on how to install and run the model.
-
-@hernandez_optimal_2015: Not met.
-
-@wood_value_2021: Not met. No instructions, although it was fairly self explanatory (single script `master.R` to run, then processing scripts named after items in article e.g. `fig7.R`).
-
-**Reflections:** <!--TODO: Update reflections (since have added Johnson, Hernandez and Wood) -->
-
-* Even if as simple as running a script, include instructions on how to do so
-* Common issue
-
-:::
-
 ## Other
-
-<!--TODO: Reflect whether any of these should be boxes above-->
 
@@
 
-<!--TODO: update or remove this summary-->
-
-**Reflections:**
-
-* Include grid lines
-* Include data dictionaries
-* If feasible, maintain code to avoid dependency on unsupported old versions of packages and languages
-* Ideally, include copies of your results, so can (a) compare against, (b) use to run analysis on, and (c) use in troubleshooting
-
 ## References

### 2024-11-04 pages/reflections.qmd
docs(reflections): moved excess files to other

@@
 
-::: {.callout-caution icon=false collapse=true}
-
-<!--TODO: Move this to other, or move things from other up here into their own boxes -->
-
-## Do not output excessive numbers of files
-
-I have not evaluated this as a criteria, as a large number of files is not inherently a bad thing, and might be difficult to avoid.
-
-Regarding number of files:
-
-* @shoaib_simulation_2021: Not relevant.
-* @huang_optimizing_2019: Not relevant.
-* @lim_staff_2020: Not relevant.
-* @kim_modelling_2021: Not relevant.
-* @anagnostou_facs-charm_2022: Not relevant.
-* @johnson_cost_2021: Not relevant.
-* @hernandez_optimal_2015: The default behaviour of the script was to output **lots of files** from each round (so you could easily have 90, 100, 200+ files), which were then **not** used in analysis (as it just depended on an aggregate results file).
-Although these individual files might be useful during quality control, as a default behaviour of the script, it could easily make the repository quite busy/littered with files.
-* @wood_value_2021: Not relevant.
-
-**Reflections:**
-
-* Outputting hundreds of files - particularly if they are not then used normally in analysis - can easily make repository cluttered/busy
-
-:::
-
 ## Seeds
@@
 
+**Excessive number of files**.
+For @hernandez_optimal_2015 the default behaviour of the script was to output lots of files from each round (so you could easily have 90, 100, 200+ files), which were then not used in analysis (as it just depended on an aggregate results file).
+Although these individual files might be useful during quality control, as a default behaviour of the script, it could easily make the repository quite busy/littered with files.
+
 **Classes**. @hernandez_optimal_2015: Structured code into classes, which was nice to work with/amend.

### 2024-11-04 pages/reflections.qmd
docs(reflections+framework): add toms comments from shared hackmd file

@@
 * The `import` statements can be sufficient in indicating all the packages required but this is not always the case if there are "hidden"/unmentioned dependencies that don't get imported
+    * Tom: Given that import statements are not always enough, then I would argue more is needed.
+    * Tom: Useful to know that `renv` "detects" dependencies listed as imports in scripts.
 * There are various options for listing the packages (e.g. comprehensive import statements, installation lines in the script, environment files, package DESCRIPTION file).
@@
 
+## Be aware of potential system dependencies
+
+There can also be system dependencies, which will vary between systems, and may not be obvious if researchers already have these installed.
+We identified these when setting up the docker environments (which act like "fresh installs"):
+
+* @shoaib_simulation_2021, @lim_staff_2020, @anagnostou_facs-charm_2022 - no dependencies
+* @huang_optimizing_2019, @kim_modelling_2021, @johnson_cost_2021 and @wood_value_2021 - libcurl4-openssl-dev, libssl-dev, libxml2-dev, libglpk-dev, libicu-dev - as well as `tk` for Johnson et al.
+2021
+* @hernandez_optimal_2015 - wget, build-essential, libssl-dev, libffi-dev, libbz2-dev, libreadline-dev, libsqlite3-dev, zlib1g-dev, libncurses5-dev, libgdbm-de, libnss3-dev, tk-dev, liblzma-dev, libsqlite3-dev, lzma, ca-certificates, curl, git
+
+Although it would be unreasonable for authors to be aware of and list all system dependencies, given they may not be aware of them, this does show the benefit of creating something like docker in identifying them and making note of them within the docker files.
+
+This issue was specific to (a) R studies, and (b) the study with an unsupported version of Python that required building it from source in the docker file.
+
+:::
+
+::: {.callout-note icon=false collapse=true}
+
 ## Provide versions
@@
 The Python version was stated in the paper, and the SimPy version was stated in the complementary app repository (although neither were mentioned in the model repository itself).
+Requirements file just contains one thing - `simpy` - with no version.
 
@@
 * This was a very common issue.
+* Tom: For R, we are sort of moving towards a pre-built container for an R reproducible pipeline
+    * Response: Though being aware that it is possible to successfully reproduce without backdating - didn't run into issues with it for the R models - though that doesn't mean you wouldn't - but it is a sort of "characteristic" of R, that it is *supposed* to be less changeable than Python in this regard.
+Though obviously no guarantees.
+And not a fair comparison, as I didn't try to run the Python ones without backdating.
 
@@
 * If you are presenting the results of a model, then provide the code for that model in a "runnable" format.
-* This was an uncommon issue.
+* This was an **uncommon** issue.
 
@@
 
-* This was not an issue for any studies - but included to note this was a "facilitator", as would have needed to amend if they weren't.
+* This was not an issue for any studies - but included to note this was a "facilitator", as would have needed to amend if they weren't (and Tom noted that this is a common problem that he runs into elsewhere).
 
@@
 
-@shoaib_simulation_2021: Not met.
-The model often contained very similar blocks of code before or after warm-up.
-This has the potential to introduce mistakes - with a suspected (although unconfirmed) mistake being that the lower boundary for the doctor consultation times in configuration 1 differed before and after warm-up.
+@shoaib_simulation_2021: Not met. The model often contained very similar blocks of code before or after warm-up.
 
@@
 * Common issue
+* Tom: I guess this one isn't strictly necessary for reproducibility.
+The main issue was that the studies required a fair bit of manual work to get them to reproduce the results from teh mixed issues you listed above.
+This is sort of a "failsafe option" for reproducibility or perhaps more relevant for reuse/adaptation.
 
@@
 
-For @kim_modelling_2021, an error appears to have been introduced with the aoorta diameter thresholds by switching between nested and unnested lists, which I’m anticipating was unresolved due to the long run times of the model meaning they weren’t all run in sequence at the end.
+In one of the studies, there was a minor error which needed fixing, which we anticipated to likely be present due to long run times meaning the model wasn't all run in sequence at the end.
 
@@
 * Common issue (to varying degrees - i.e. taking 20 minutes, up to taking several hours or even day/s).
+* Tom: Long run times are inevitable for some models, but this does suggest that some extra work to build confidence the model is working is expected is beneficial, like one or a small set of verification scenarios that are quick to run.
 
@@
 * Common issue.
+* Tom: This supports the inclusion of section 5.4 in the STRESS-DES guidelines
+    * Response: But think it is also important that this is in the repository itself, and not just the paper.
 
@@
 * Not a common problem - only relevant to computationally expensive models
+* Tom: Agree it makes sense to report this, and is captured in reporting guidelines like STRESS-DES.
 
@@
 * Time consuming and tricky to resolve
+* Tom: This is a headline. Also, links to importance of reproducible analytical pipelines (RAP) for simulation.
 
@@
 if its just plotting a mean or simple calculation, then didn't consider that here) (however, combined with other criteria, we do want them to provide code to calculate outputs, so we would want them to provide that anyway)
+* Tom: This is a headline.
+I suspect we can find supporting citations elsewhere from other fields.
+Its a reporting guideline thing too, but in natural language things can get very ambiguous still!
+Would be good to make that point as well I think.
 
@@
 * This can make a really big difference, and be likely cause of managing to reproduce everything v.s. nothing, if it impacts all aspects of the results.
+* Tom: I think this comes back to minimum verification as well. I think the "at least for one scenario" idea of yours is excellent.
 
@@
 * Provide all required parameters
+* Tom: Evidence to support STRESS-DES 3.3
 
@@
 * Provide parameters in a table (including for each scenario), as it can be difficult/ambiguous to interpret them from the text, and hard to spot them too.
+    * Tom: The ambiguity of the natural language for scenarios was an important finding.
 * Be sure to mention every parameter that gets changed (e.g. for @lim_staff_2020, as there wasn't a default `staff_per_shift` across all scenarios, but not stated for the scenario, had to guess it).
+* Tom: Evidence to support STRESS-DES 3.3
 
@@
 * If you are going to be mentioning the "pre-processed" values at all, then its important to include the calculation (ideally in the code, as that is the clearest demonstration of exactly what you did)
+* Tom: This is a very good point for RAP.
 
@@
 * Make differences between seperate results tables clear.
+* Tom: In a RAP for simulation world we have a env + model + script that gets you to the exact results table you see in the paper and this isn't a problem (although more time consuiming to setup).
 
@@
 In cases where you have large files, a good option can be storing it elsewhere and then pulling from there into your workflow - for example, storing in **zenodo** and fetching using [pooch](https://github.com/fatiando/pooch).
+    * Tom: Approach with zenodo seems sensible.
+There's a simple workflow for submitting to a journal with this approach as well.
+Plus scenarios/scripts can link to raw datafiles on zenodo for comparion.
 
@@
 * Over half of the studies did include seed control in their code.
+* Tom: There seems little argument against doing this.
+worth noting that commerical software does this for you and possibly explains why authors didn't do this themselves if that was their background (lack of knowledge?).
+* Tom: Note simpy is independent of any sampling mechanism.
+We could just use python's random module and set a single seed if needed (although you lose CRN) and we can setup our models so that we only need to set a single seed.
+* Tom: A key part of STARS 2.0 for reproducibility
 
@@
 ## Code to produce article results
+
+This is a common problem across all item types, and a key part of STARS 2.0 for reproducibility.
 
@@
 * Common issue
+* Tom: Evidence for STARS essential component of minimum documentation.
 
@@
 
+Tom: This is interesting - and you wonder if it would still be possible (given the "tricks" I followed) in another 10 years time.
+
 **Original results files**. @hernandez_optimal_2015: Included some original results files, which was invaluable in identifying some of the parameters in the code that needed to be fixed.
@@
 Although these individual files might be useful during quality control, as a default behaviour of the script, it could easily make the repository quite busy/littered with files.
+
+* Tom reflected that this is more of a general housekeeping issue. He agrees and says its ok to do this, but perhaps they need a run mode that does not produce these verification files
 

### 2024-11-04 pages/paper_evaluation.qmd
docs(paper evaluation): correction to huang and lim stress-des, and removing addressed TODO

@@
   'Shoaib and<br>Ramamohan 2021': [17, 6, 1, 0],
-  'Huang et al. 2019': [14, 6, 3, 1],
-  'Lim et al. 2020': [16, 2, 3, 3],
+  'Huang et al. 2019': [14, 5, 4, 1],
+  'Lim et al. 2020': [15, 3, 3, 3],
   'Kim et al. 2021': [15, 5, 2, 2],
@@
              hua = (14/23)*100,
-             lim = (16/21)*100,
+             lim = (15/21)*100,
              kim = (15/22)*100,
@@
 
-<!-- TODO: update after discussion of Kim et al. 2021 -->
-
 | Item | S | Hu | L | K | A | J | He | W |
@@
 For both procedures provide a justification for the methods used and the number of replications/size of batches.
-| 🟡 | 🟡 | ✅ | ✅ | ✅ | N/A | ✅ | ✅ |
+| 🟡 | 🟡 | 🟡 | ✅ | ✅ | N/A | ✅ | ✅ |
 | **Implementation** |
@@
 Mersenne Twister.<br>If common random numbers are used, state how seeds (or random number streams) are distributed among sampling processes.
-| ❌ | 🟡 | ❌ | ❌ | ❌ | N/A | ❌ | ✅ |
+| ❌ | ❌ | ❌ | ❌ | ❌ | N/A | ❌ | ✅ |
 | **5.3 Model execution**<br>State the event processing mechanism used e.g.
@@
   '4.2 Run length': [7, 1, 0, 0],
-  '4.3 Estimation': [5, 2, 0, 1],
+  '4.3 Estimation': [4, 3, 0, 1],
   '5.1 Language': [0, 8, 0, 0],
-  '5.2 Random': [1, 1, 5, 1],
+  '5.2 Random': [1, 0, 6, 1],
   '5.3 Execution': [1, 1, 6, 0],
@@
 Below, I've reflected on the impact of each criteria being fulfilled, on the reproduction.
-I've also identified where I feel I've been a bit more lax in my evaluation.
-<!-- TODO: Consider - is this an issue?
-Should I revisit those and be more strict?
--->
+I've also identified where I feel I've been a bit more lax in my evaluation - indeed, the "subjective" nature of this evaluation is a limitation - although did (a) get consensus on uncertainties and unmet, and (b) revisit alongside other evaluations when writing this section, which helped me identify a few inconsistent decisions between studies within the evaluation, which I then addressed.
 
@@
 
-<!--TODO: Check Lim 2020 - think it should be changed to partially met, as no justification mentioned -->
-
 **5.1 Software or programming language**<br>State the operating system and version and build number.<br>State the name, version and build number of commercial or open source DES software that the model is implemented in.<br>State the name and version of general-purpose programming languages used (e.g.
@@
 * Frequently not described, despite some of the studies having implemented and used seeds.
-
-<!--TODO: Check Huang 2019, looks like I've answered with arrival sampling, but that is not relevant here - but does indicate that the wording here is a little confusing perhaps -->
+* Initially incorrectly addressed this in one of my evaluations, accidentally adding notes on the sampling of arrivals, rather than specifically on random samples.
+Have noted this to be clear that it was possible to misinterpret (although that may be more a mistake of my own!
+and not one others would necessarily make.)
 
@@
 * **W:** @wood_value_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-wood-2021/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>
-
-<!-- TODO: update after discussion of Kim et al. 2021 -->
 

### 2024-11-05 pages/functions.py
feat(functions): add reporting_scatter()

@@ -257,6 +257,9 @@ def calculate_times(used_to_date, times, limit=True):
         print(f'Used {prop}% of 40 hours max')
 
 
+# TODO: Check the values used are still corrected, as there were some minor
+# amendments made to evaluations
+
 def plot_scatter(var, sho, hua, lim, kim, ana, joh, her, woo):
     '''
     Create scatter plot of variable against reproduction success, with dot size
@@ -308,4 +311,65 @@ def plot_scatter(var, sho, hua, lim, kim, ana, joh, her, woo):
     fig['data'][0]['showlegend'] = True
     fig['data'][0]['name'] = ('<b>Dot size:</b><br>Time spent<br>on ' +
                               'reproduction<br>(smaller=quicker)')
+    return fig
+
+
+def reporting_scatter(var, reporting, sho, hua, lim, kim, ana, joh, her, woo):
+    '''
+    Creates a scatter plot showing proportion of reporting guideline (STRESS-DES
+    or the guideline derived from ISPOR-SDM) that was fully met, against a
+    categorical variable (e.g. whether used reporting guidelines, whether model
+    has been described previously).
+
+    Parameters:
+    -----------
+    var: string
+        Name of variable to plot
+    reporting: string
+        Name of reporting guidelines to plot - 'stress' or 'ispor'
+    sho: number
+        Value for Shoaib and Ramamohan 2021
+    hua: number
+        Value for Huang et al. 2019
+    lim: number
+        Value for Lim et al. 2020
+    kim: number
+        Value for Kim et al. 2021
+    ana: number
+        Value for Anagnostou et al. 2022
+    joh: number
+         Value for Johnson et al. 2021
+    her: number
+        Value for Hernandez et al. 2015
+    woo: number
+        Value for Wood et al. 2021
+    '''
+    # Alongside categorical variable, lists the proportion of each guideline
+    # that was fully met (out of all the applicable categories)
+    df =  pd.DataFrame({
+        'Shoaib and Ramamohan 2021': [sho, (17/24)*100, (11/15)*100],
+        'Huang et al. 2019': [hua, (14/23)*100, (7/16)*100],
+        'Lim et al. 2020': [lim, (16/21)*100, (12/16)*100],
+        'Kim et al. 2021': [kim, (15/22)*100, (12/17)*100],
[…]

### 2024-11-05 pages/paper_evaluation.qmd
docs(paper evaluation): add ispor-sdm reflections, and charts for use of reporting guidelines or previously reported model

@@
 ```{python}
-plot_scatter('STRESS-DES criteria met',
+plot_scatter('ISPOR-SDM criteria met',
              sho = (11/15)*100,
@@
 
-These guidelines have quite a different focus from STRESS-DES.
+These guidelines have quite a **different focus** from STRESS-DES.
 STRESS-DES is very focused on what and how modelling work is performed.
@@
 stating funding, involving stakeholders).
-
-<!--TODO: Add reflections on each of the elements -->
+This is important, as **different checklists can be important** - and although practice is typically to use one practice, referring to more than one could also be beneficial.
 
@@
 
-*
+* Pretty basic requirement that all meet (unsurprisingly).
 
@@
 
-*
+* There was only one study where this was not stated (@anagnostou_facs-charm_2022), though this didn't impact the reproduction itself, for this study I was simply able to run the code and pretty much get the result required with minimal troubleshooting.
 
@@
 
-*
+* All papers with scenarios described them.
+As reflected for STRESS-DES, though the description of the scenario can feel clear from the paper, when the code was not provided, it could be quick tricky and time-consuming to work out how to appropriately change the code, in order to implement the scenario.
 
@@
 
-*
+* Fulfilment didn't impact the reproduction as this is more about interpretation/validity/etc.
 
@@
 
-*
+* All met, although it's worth noting that I didn't check that *every* single parameter's data source was stated (and indeed, its likely some were not) - simply whether I could identified that at least some were.
 
@@
 
-*
+* This was quite important for the reproduction as it allows us to check the parameters in the code are correct.
+When I identified that there were some discrepancies between the article and code, then in cases where a parameter was not given in the article, I couldn't be sure if it was correct or not in the code, as there was nothing to compare against.
 
@@
 
-*
+* Some don't (but worth noting this doesn't have impact on reproduction - beyond just these being additional values/lines in plot that we are trying to reproduce)
 
@@
 
-*
+* Some performed, some mentioned but no results presented, and some didn't mention at all. One explained it to not be relevant.
 
@@
 
-*
+* Rare (only one completed) - but didn't impact reproduction as this is more related to validity
 
@@
 
-*
+* Rare (only two completed) - but didn't impact reproduction as this is more related to validity
 
@@
 
-*
+* Rare (only two completed) - although some argue not applicable - but didn't impact reproduction as this is more related to validity
 
@@
 
-*
+* Generally not applicable - but didn't impact reproduction as this is more related to validity
 
@@
 
-*
+* More than half did discuss this - but didn't impact reproduction as this is more related to reuse
 
@@
 
-*
+* Rare (only one mentioned) - but didn't impact reproduction as this is more related to validity
 
@@
 
-* Good practice, usually a journal requirement, although some did not have.
+* Good practice, usually a journal requirement, although some did not have - but didn't impact reproduction.
 
@@
 
-*
+* Most discuss limitations (didn't really assess how comprehensive these were though, except in two cases where they only had a very general or hint towards limitations) - but didn't impact reproduction.
 
@@
 
+::: {.callout icon=false collapse=false}
+
+## Reflections
+
+It sometimes took quite a while to find all this information from the articles - and we acknowledge there's a chance that it is provided somewhere in the article but I missed it.
+For both of these reasons, we see the value in actually attaching a completed reporting checklist, clearly laying out key information about the model and study.
+
+:::
+
 ## Use of reporting guidelines
@@
 
-<!--TODO: Add reflections on this, and relationship between these and then e.g. how many of the reporting guidelines were met -->
+Although this is only a small sample, its interesting to note that the two studies that used reporting guidelines both had the highest proportion of fully met criteria in either reporting guideline.
 
 ```{python}
-import plotly.express as px
+from functions import reporting_scatter
 
-# For each study, define (a) whether use a previously reported model, and (b) proportion of applicable STRESS-DES fully met
-previous_stress =  [
-  (0, (17/24)*100),
-  (0, (14/23)*100),
-  (0, (16/21)*100),
-  (0, (15/22)*100),
-  (0, (14/21)*100),
-  (1, (16/19)*100),
-  (0, (18/23)*100),
-  (1, (22/24)*100)
-]
-
-# Get x and y values
-x, y = zip(*previous_stress)
-
-fig = px.scatter(x=x, y=y)
+for guide in ['stress', 'ispor']:
+    fig = reporting_scatter(
+        'Used reporting guidelines', reporting=guide,
+        sho=0, hua=0, lim=0, kim=0, ana=0, joh=1, her=0, woo=1)
     fig.show()
@@
 
-<!--TODO: Add reflections on this, and relationship between these and then e.g. how many of the reporting guidelines were met -->
+Again, a small sample, but this time a weaker pattern.
+We note that the two studies that used reporting guidelines are the same that are previously reported models here, alongside one other study which was previously reported but did not use reporting guidelines in this instance, and has a lower proportion of criteria that were fully met.
 
 ```{python}
-import plotly.express as px
-
-# For each study, define (a) whether use a previously reported model, and (b) proportion of applicable STRESS-DES fully met
-previous_stress =  [
-  (0, (17/24)*100),
-  (0, (14/23)*100),
-  (0, (16/21)*100),
-  (1, (15/22)*100),
-  (0, (14/21)*100),
-  (1, (16/19)*100),
-  (0, (18/23)*100),
-  (1, (22/24)*100)
-]
-
-# Get x and y values
-x, y = zip(*previous_stress)
-
-fig = px.scatter(x=x, y=y)
+for guide in ['stress', 'ispor']:
+    fig = reporting_scatter(
+        'Model reported previously', reporting=guide,
+        sho=0, hua=0, lim=0, kim=1, ana=0, joh=1, her=0, woo=1)
     fig.show()
@@
 
-<!--TODO: Improve this plot so (a) it's not a massive gap between the bars, (b) it's a function used for this and above rather than duplicate code, (c) so we have ones for STRESS and ISPOR -->
-
-<!-- TODO: consider, did the previously reported model also use reporting guidelines? -->
-
 ## References

### 2024-11-05 pages/results_discussion.qmd
docs(results discussion): add rough notes on key results and grouping results into categories

---
title: "Results discussion"
bibliography: ../references.bib
---

This page has rough notes that are blurry between results / discussion. It is from me reading ove rmy results section and trying to pull out key points or things I want to mention, and trying to group reflections into categories.

## Headlines / key findings / things want to emphasise

**Timings**. Timings varied alot. RESULT: 2h11 to 28h14.

DISCUSS: Variation due to -

* Time consuming:
    * Write code for scenarios/sensitivity analysis
    * Write code for tables/figures
    * Included troubleshooting mismatch parameters, working out how to change code for scenarios, working out appropriate transformations for processing, and which columns to use, and so on.
* The two quickest studies (by a long shot - <4h v.s. all others >12h) I feel were quick as
    * They required very little troubleshooting (didn't need any or only needed alittle coding from me)
    * Also, simplicity too - they had scope of 1 or 5 items - all others had 5 to 17.

What I think were key factors in not being able to fully reproduce some studies (and hence, these are headline findings):

* **Code containing wrong parameters**.
* **Having to write code for (a) scenarios, and (b) to process results (tables, figures, in-text)**
* These related to badges: complete set of materials

**Open license** (badges and STARS) - couldn't do without.

## Other important things to mention

Different checklists have different focuses... STRESS-DES focuses on what and how modelling work is performed... derived from ISPOR-SDM checklist is more related to validity type stuff...

Whether or not a study was fully reproduced or not doesn't necessarily mean it was "good" or "bad". Did lots of troubleshooting for some before fully reproduced. And sometimes, couldn't reproduce for simple reasons, like likely parameter being wrong impacting lal results.

## Other minor things to mention

Badges not awarded for not having combination of things required e.g. archive + docs, or complete + docs. Many got basic one of reproducing results, but I allowed troubleshooting - yet they may not - particularly HOURS of troubleshooting.

Article evaluation sometimes took quite a while... limitation that may not be perfect... those that used guidelines did better... emphasis importance of (a) using guidelines and (b) attaching completed guidelines

Meeting STARS optional wasn't helpful for reproduction (but would be for reuse)

## Grouping reflections from reproduction and evaluation into categories

### Model structuring and functionality

**feels important for reuse**

* Runnable
* Programmatic
    * E.g. classes... but WITH inputs... as had example using classes but all hard coded so not programmatic so using classes isn't magic fix, just a way of doing, so maybe don't mention
* Don't hard code
* Relative file paths
* Avoid duplication
* Sufficient comments
* Save outputs to file
* Understandable output
    * Data dictionaries (relevant to inputs and outputs).
    * Badges: careful documentation.
* Avoid large file sizes
* Excessive file number
* Instructions on how to run
    * STARS and badges: documentation (sufficient, minimal and step by step)
* Quicker model
    * State memory use
    * State run time
    * STRESS: Run time. Found really important for this to be mentioned (particularly relevant when considering reuse too) and should be in article AND repository.

### Analysis pipeline

**Feels important** for being able to get same results but then if someone has to troubleshoot then model structuring and functionality ones become important too.

* Packages
    * STARS: Dependency management
* System dependencies
* Versions
    * Badges: documentation
    * STRESS: software. handy when mentioned in article - but would ideally be in repository
* Scenario code
    * ISPOR and STRESS: May describe in paper but if code not provided can still be tricky and time consuming to implement. Implementation of scenarios impacted by model structure e.g. programmatic, don't hard code, sufficient comments.
* Outputs calculated
* Corrected parameters
* Required parameters
    * ISPOR and STRESS: Input parameters - this was VERY important to be reported as it allows us to check code parameters are correct. When missing from paper, not possible to check
* Code for tables, figures and in-text results
    * Impacted by model structure e.g. understandable output
* Seeds
* Original results files
* GitHub history and releases

### Other

* Open license
    * On ALL repositories required
* Unsupported versions

### Study reporting

See above...

Really important to be in article:

* STRESS: Run time
* ISPOR and STRESS: Input parameters

Handy to be in article but should ideally be in code:

* STRESS: software
* Scenario code ISPOR and STRESS

### 2024-11-05 pages/results_discussion.qmd
docs(results discussion): add pipeline diagram

@@
 ---
+
+## Reflections
+
+Reflections from the reproduction and evaluation are broadly grouped into two categories:
+
+* **Analysis pipeline**
+* **Model structure and functionality**
+
+A few additional general reflections are under **other**.
+
+### Analysis pipeline
+
+![Analysis pipeline diagram](../images/pipeline.png){.lightbox}
+
+These are important for reproduction. If need to troubleshoot, then model structure and functionality are particularly useful (e.g. writing code for results is impacted by understandable output)...
+
+Links to evaluation:
+
+* Packages - STARS: dependency management
+* Versions - Badges: documentation. STRESS: software (handy when mentioned in article but would ideally be in repository)
+* Scenario - ISPOR and STRESS: scenario (may describe in paper but if code not provided can still be tricky and time consuming to implement.
+Implementation of scenarios impacted by model structure e.g.
+programmatic, don't hard code, sufficient comments)
+* Required parameters - ISPOR and STRESS: input parameters (this was VERY important to be reported as it allows us to check code parameters are correct. When missing from paper, not possible to check)
+
+### Model structure and functionality
+
+## ROUGH NOTES TO SORT BELOW
 
@@
 
-### Analysis pipeline
-
-**Feels important** for being able to get same results but then if someone has to troubleshoot then model structuring and functionality ones become important too.
-
-* Packages
-    * STARS: Dependency management
-* System dependencies
-* Versions
-    * Badges: documentation
-    * STRESS: software. handy when mentioned in article - but would ideally be in repository
-* Scenario code
-    * ISPOR and STRESS: May describe in paper but if code not provided can still be tricky and time consuming to implement.
-Implementation of scenarios impacted by model structure e.g.
-programmatic, don't hard code, sufficient comments.
-* Outputs calculated
-* Corrected parameters
-* Required parameters
-    * ISPOR and STRESS: Input parameters - this was VERY important to be reported as it allows us to check code parameters are correct. When missing from paper, not possible to check
-* Code for tables, figures and in-text results
-    * Impacted by model structure e.g. understandable output
-* Seeds
-* Original results files
-* GitHub history and releases
-
 ### Other
@@
 * Scenario code ISPOR and STRESS
+
+Regarding **relationship between reproduction and evaluation**, in terms of article reporting, these feel like the key things. In terms of repository contents, the key things feel like - see above...
+
+* STARS and badges: documentation (sufficient, minimal, step by step, careful)
+    * Instructions on how to run
+    * Understandable output e.g. data dictionaries
+    * Versions
+* STARS: dependency management
+
+Hence, instead of having **study reporting** category or mentioning above, would describe seperately in own section.

### 2024-11-05 pages/results_discussion.qmd
docs(results dicussion): tidied up from rough notes to neater

@@
 
-## ROUGH NOTES TO SORT BELOW
+TODO: TURN INTO DIAGRAM (like have done for analysis pipeline)
 
-This page has rough notes that are blurry between results / discussion.
-It is from me reading ove rmy results section and trying to pull out key points or things I want to mention, and trying to group reflections into categories.
+* Runnable
+* Programmatic
+    * E.g. classes... but WITH inputs... as had example using classes but all hard coded so not programmatic so using classes isn't magic fix, just a way of doing, so maybe don't mention
+* Don't hard code
+* Relative file paths
+* Avoid duplication
+* Sufficient comments
+* Save outputs to file
+* Understandable output
+    * Data dictionaries (relevant to inputs and outputs).
+* Avoid large file sizes
+* Excessive file number
+* Instructions on how to run
+* Quicker model
+    * State memory use
+    * State run time
 
-## Headlines / key findings / things want to emphasise
+These are important for reuse - but also pipeline stuff! As they (a) make reproduction easier and (b) are important when troubleshooting.
 
-**Timings**. Timings varied alot. RESULT: 2h11 to 28h14.
+Links to evaluation:
 
-DISCUSS: Variation due to -
+* Data dictionaries - Badges: careful documentation
+* Instructions on how to run - STARS and Badges: documentation (sufficient, minimal and step by step)
+* Run time - STRESS: run time (found really important for this to be mentioned (particularly relevant when considering reuse too) and should be in article AND repository)
 
-* Time consuming:
-    * Write code for scenarios/sensitivity analysis
-    * Write code for tables/figures
-    * Included troubleshooting mismatch parameters, working out how to change code for scenarios, working out appropriate transformations for processing, and which columns to use, and so on.
-* The two quickest studies (by a long shot - <4h v.s. all others >12h) I feel were quick as
-    * They required very little troubleshooting (didn't need any or only needed alittle coding from me)
-    * Also, simplicity too - they had scope of 1 or 5 items - all others had 5 to 17.
+### Other
 
-What I think were key factors in not being able to fully reproduce some studies (and hence, these are headline findings):
+These didn't fit into the two categories above:
 
-* **Code containing wrong parameters**.
-* **Having to write code for (a) scenarios, and (b) to process results (tables, figures, in-text)**
-* These related to badges: complete set of materials
+* **Open license**
+    * On ALL repositories required
+* **Unsupported versions**
 
-**Open license** (badges and STARS) - couldn't do without.
+## Headline findings
 
-## Other important things to mention
+Whilst above captures the reflections, I've also pulled out a few **headline** findings.
+
+The four most important things:
+
+1. **Using correct parameters in code**
+2. **Including code for all scenarios**
+3. **Include code to create tables, figures and in-text results**
+4. **Open license**
+
+Why were these the most fundamental?
+
+**Using the code**. Open license  (4) is fundamentally important - can't reuse code without it. In several studies, had to ask authors to add license (all kindly agreed).
+
+**Timing**. Timings varied alot, from 2h11 to 28h14
+
+* Six slower studies (>12h)
+    * I think main reasons for time were: troubleshooting wrong parameters (1), writing code for scenarios (2), and creating tables/figures/in-text results (3) (including appropriate transformations, which columns to use, and so on).
+    * Scope could be larger (5 to 17 items)
+* Two quicker studies (<4h)
+    * Both required very little troubleshooting (e.g. only small amount of coding)
+    * Scope was also simple (1 or 5 items)
+
+**Reproduction success**. I think main reasons were having wrong parameters (1), not having code for scenarios (2) and not having code for results (3).
+
+Links to evaluation:
+
+* Badges and STARS: open license
+* Badges: complete set of materials
+
+## Relationship between reproduction and evaluation
+
+Regarding relationship between reproduction and evaluation, in terms of article reporting, these feel like the key things that impacted reproduction...
+
+### Article
+
+Really important to be in article:
+
+* STRESS: Run time
+* ISPOR and STRESS: Input parameters
+
+Handy to be in article but should ideally be in code:
+
+* STRESS: software
+* Scenario code ISPOR and STRESS
+
+### Repository
+
+* STARS and badges: documentation (sufficient, minimal, step by step, careful)
+    * Instructions on how to run
+    * Understandable output e.g. data dictionaries
+    * Versions
+* STARS: dependency management
+
+## Other things I wanted to mention
 
@@
 And sometimes, couldn't reproduce for simple reasons, like likely parameter being wrong impacting lal results.
-
-## Other minor things to mention
 
@@
 Meeting STARS optional wasn't helpful for reproduction (but would be for reuse)
-
-## Grouping reflections from reproduction and evaluation into categories
-
-### Model structuring and functionality
-
-**feels important for reuse**
-
-* Runnable
-* Programmatic
-    * E.g. classes... but WITH inputs... as had example using classes but all hard coded so not programmatic so using classes isn't magic fix, just a way of doing, so maybe don't mention
-* Don't hard code
-* Relative file paths
-* Avoid duplication
-* Sufficient comments
-* Save outputs to file
-* Understandable output
-    * Data dictionaries (relevant to inputs and outputs).
-    * Badges: careful documentation.
-* Avoid large file sizes
-* Excessive file number
-* Instructions on how to run
-    * STARS and badges: documentation (sufficient, minimal and step by step)
-* Quicker model
-    * State memory use
-    * State run time
-    * STRESS: Run time. Found really important for this to be mentioned (particularly relevant when considering reuse too) and should be in article AND repository.
-
-### Other
-
-* Open license
-    * On ALL repositories required
-* Unsupported versions
-
-### Study reporting
-
-See above...
-
-Really important to be in article:
-
-* STRESS: Run time
-* ISPOR and STRESS: Input parameters
-
-Handy to be in article but should ideally be in code:
-
-* STRESS: software
-* Scenario code ISPOR and STRESS
-
-Regarding **relationship between reproduction and evaluation**, in terms of article reporting, these feel like the key things. In terms of repository contents, the key things feel like - see above...
-
-* STARS and badges: documentation (sufficient, minimal, step by step, careful)
-    * Instructions on how to run
-    * Understandable output e.g. data dictionaries
-    * Versions
-* STARS: dependency management
-
-Hence, instead of having **study reporting** category or mentioning above, would describe seperately in own section.

### 2024-11-05 pages/results_discussion.qmd
docs(results discussion): add model structure and functionality diagram, and tidied link between reproduction and evaluation

@@
 
+::: {.callout-note}
+
+## What is on this page?
+
+* Reflections from the reproduction and evaluation, broadly grouped into two categories
+* Headline findings
+* Relationship between reproduction and evaluation
+* Some other things I want to mention
+
+:::
+
 ## Reflections
-
-Reflections from the reproduction and evaluation are broadly grouped into two categories:
-
-* **Analysis pipeline**
-* **Model structure and functionality**
-
-A few additional general reflections are under **other**.
 
@@
 
-![Analysis pipeline diagram](../images/pipeline.png){.lightbox}
+These are important for reproduction. If need to troubleshoot, then model structure and functionality are particularly useful - e.g.:
 
-These are important for reproduction. If need to troubleshoot, then model structure and functionality are particularly useful (e.g. writing code for results is impacted by understandable output)...
+* Writing code for scenarios is impacted by: programmatic, don't hard code, sufficient comments
+* Writing code for results is impacted by: understandable output
 
-Links to evaluation:
+"Reflections" in this group:
+
+!["Reflections" in the group "Analysis Pipeline"](../images/pipeline.png){.lightbox}
+
+::: {.callout-note collapse="true"}
+
+## Links to evaluation
+
+Hence, these are included in relationship between reproduction and evaluation below
 
 * Packages - STARS: dependency management
-* Versions - Badges: documentation. STRESS: software (handy when mentioned in article but would ideally be in repository)
-* Scenario - ISPOR and STRESS: scenario (may describe in paper but if code not provided can still be tricky and time consuming to implement.
-Implementation of scenarios impacted by model structure e.g.
-programmatic, don't hard code, sufficient comments)
-* Required parameters - ISPOR and STRESS: input parameters (this was VERY important to be reported as it allows us to check code parameters are correct. When missing from paper, not possible to check)
+* Versions - Badges: documentation, and STRESS: software
+* Scenario - ISPOR and STRESS: scenario, and Badges: complete set of materials
+* Required parameters - ISPOR and STRESS: input parameters
+
+:::
 
@@
 
-TODO: TURN INTO DIAGRAM (like have done for analysis pipeline)
-
-* Runnable
-* Programmatic
-    * E.g. classes... but WITH inputs... as had example using classes but all hard coded so not programmatic so using classes isn't magic fix, just a way of doing, so maybe don't mention
-* Don't hard code
-* Relative file paths
-* Avoid duplication
-* Sufficient comments
-* Save outputs to file
-* Understandable output
-    * Data dictionaries (relevant to inputs and outputs).
-* Avoid large file sizes
-* Excessive file number
-* Instructions on how to run
-* Quicker model
-    * State memory use
-    * State run time
-
 These are important for reuse - but also pipeline stuff! As they (a) make reproduction easier and (b) are important when troubleshooting.
 
-Links to evaluation:
+Note: Data dictionaries are relevant to inputs and outputs.
+
+!["Reflections" in the group "Model structure and functionality"](../images/structure_function.png){.lightbox}
+
+::: {.callout-note collapse="true"}
+
+## Links to evaluation
+
+Hence, these are included in relationship between reproduction and evaluation below
 
@@
 * Instructions on how to run - STARS and Badges: documentation (sufficient, minimal and step by step)
-* Run time - STRESS: run time (found really important for this to be mentioned (particularly relevant when considering reuse too) and should be in article AND repository)
+* Run time - STRESS: run time
+
+:::
 
@@
 * **Unsupported versions**
+
+::: {.callout-note collapse="true"}
+
+## Links to evaluation
+
+Hence, these are included in relationship between reproduction and evaluation below
+
+* Badges and STARS: open license
+
+:::
 
@@
 
-**Using the code**. Open license  (4) is fundamentally important - can't reuse code without it. In several studies, had to ask authors to add license (all kindly agreed).
+> **Using the code**. Open license  (4) is fundamentally important - can't reuse code without it. In several studies, had to ask authors to add license (all kindly agreed).
 
-**Timing**. Timings varied alot, from 2h11 to 28h14
+> **Timing**. Timings varied alot, from 2h11 to 28h14
+> 
+> * Six slower studies (>12h)
+>     * I think main reasons for time were: troubleshooting wrong parameters (1), writing code for scenarios (2), and creating tables/figures/in-text results (3) (including appropriate transformations, which columns to use, and so on).
+>     * Scope could be larger (5 to 17 items)
+> * Two quicker studies (<4h)
+>     * Both required very little troubleshooting (e.g. only small amount of coding)
+>     * Scope was also simple (1 or 5 items)
 
-* Six slower studies (>12h)
-    * I think main reasons for time were: troubleshooting wrong parameters (1), writing code for scenarios (2), and creating tables/figures/in-text results (3) (including appropriate transformations, which columns to use, and so on).
-    * Scope could be larger (5 to 17 items)
-* Two quicker studies (<4h)
-    * Both required very little troubleshooting (e.g. only small amount of coding)
-    * Scope was also simple (1 or 5 items)
-
-**Reproduction success**. I think main reasons were having wrong parameters (1), not having code for scenarios (2) and not having code for results (3).
-
-Links to evaluation:
-
-* Badges and STARS: open license
-* Badges: complete set of materials
+> **Reproduction success**. I think main reasons were having wrong parameters (1), not having code for scenarios (2) and not having code for results (3).
 
@@
 
-Really important to be in article:
+**Really important to be in article:**
 
 * STRESS: Run time
+    * Found this very useful when mentioned, and a bit frustrating when not and later realise its a long run time.
+Want in both article and repository as whether someone finds repository from article or vice versa, want them to have right expectations up front of run requirements for this model
 * ISPOR and STRESS: Input parameters
+    * This was VERY important to be reported as it allows us to check code parameters are correct. When missing from paper, not possible to check
 
-Handy to be in article but should ideally be in code:
+**Handy to be in article but should ideally be in repository:**
 
@@
 * Scenario code ISPOR and STRESS
+    * May describe in paper but if code not provided can still be tricky and time consuming to implement
 

### 2024-11-06 pages/results_discussion.qmd
docs(results discussion): adding some of tom's comments, and section with evidence for frmaework components

@@
 
+(Addressing Tom's suggestion - "Maybe there are some high level groupings of your findings? e.g. Study reporting; Model structuring and functionality; Analysis pipeline")
+
 ### Analysis pipeline
@@
 
-"Reflections" in this group:
+Notes:
+
+* Tom: Key for STARS 2.0: seeds
 
@@
 
-Note: Data dictionaries are relevant to inputs and outputs.
+Notes:
+
+* Data dictionaries are relevant to inputs and outputs.
+* Some of these can become "less of an issue" for reproduction if there is a reproducible analytical pipeline, as don't need to delve into it and troubleshoot (but are still relevant for reuse).
 
@@
 
+Many of these headlines link to the importance of reproducible analytical pipelines (RAP) for simulation.
+
 Why were these the most fundamental?
@@
 Regarding relationship between reproduction and evaluation, in terms of article reporting, these feel like the key things that impacted reproduction...
+
+(Also addressing Tom's suggestion: "Evidence supporting the use of reporting guidelines...
+as in - reporting guidelines state this should info be included and you found it v.difficult or impossible to reproduce without it")
 
@@
 
+## Evidence for framework components
+
+Reflections:
+
+* "Include instructions on how to run the model/script" --> Evidence for STARS essential component minimum documentation
+* "For slow models, state the expected run time" --> Evidence for STRESS-DES 5.4
+* "For computationally expensive models, state memory usage and provide alternatives for lower spec machines" --> Evidence for STRESS-DES
+* "Provide all the required parameters" and "If not provided in the script, then *clearly* present all parameters in the paper" --> Evidence for STRESS-DES 3.3
+
 ## Other things I wanted to mention

### 2024-11-06 pages/compendium.qmd
docs(discussion): addressed or reorganised discussion TODO. e.g. made page of limitations.

---
title: "Reflections from research compendium and test-run"
bibliography: ../references.bib
---

After completing the reproduction and evaluation, the final stage involved organising the `reproduction/` folder into a mini "research compendium", and having a test-run of this by a second STARS team member.

## Reflections

The test-run stage after making compendium helped us to spot run issues that I hadn't noticed, mainly from having not completely tested absolutely everything before pushing. For example, Hernandez et al. 2015, and there was at least one other example too. Shows importance of having someone else check things - easy to leave in small mistakes that mean it doesn't run.

### 2024-11-06 pages/framework.qmd
docs(reflections+framework): add toms comments from shared hackmd file
docs(discussion): addressed or reorganised discussion TODO. e.g. made page of limitations.

@@
 
+<!--TODO: Divide this into STARS framework and STRESS framework reflections-->
+
 <!--TODO: Consider implications of:
@@
 
-## Contents of the framework
+<!--TODO: Make a paper with STRESS specific reflections - so ensure these are incorporated in others, then have discussion page where I walk through STRESS and, based on what I have found, suggest what was helpful in framework, what was missing, and so on.
+
+* Consider: which of my reflections pertain to what is in the article, v.s.
+what is in the repository - e.g.
+the scenarios being used is important in both - but mine is actually referring more to the repository, hence relevant to STARS more-so than STARS-->
+
+## Contents of the STARS framework
 
@@
 
+* Tom: Agree this is a good idea
+
 ## Reflections from the evaluations

### 2024-11-06 pages/limitations.qmd
docs(discussion): addressed or reorganised discussion TODO. e.g. made page of limitations.

---
title: "Limitations"
bibliography: ../references.bib
---

## Subjective reproduction success

As acknowledged in the protocol, reproduction success is a subjective decision.

* Where helpful, did compare numbers and absolute / percent difference, but this can be heavily impacted by scales (e.g. if comparing 0.1 0.2 0.3, will see much larger percentage differences than comparing 10 15 20, but actually one might be more meaningful than other, depending on what the underlying scale etc is.)
* Nature of what is being plot can have a big impact - e.g. for one study, health economic costs and QALYs look super similar, but when calculate ICER and INMB, tiny differences result in huge changes

## Reuse v.s. reproduction

I did not try to reuse studies for new context. Although for some studies, I did have to dig into the code quite alot to work out how to set up scenarios and process results, and I would argue that is similar to reuse (as I was trying to adapt it for a new scenario). However, for some other studies, this was not necessary and for those I just had a more top-level/basic interaction with the code (and didn't have to delve). Hence, in many cases, can't truly say if information provided was sufficient for that deep understanding of what it is doing and so on, but in some cases I can a bit more.

## Human error in evaluation

Evaluations are likely imperfect. Can be hard to find things in a paper, may have made mistakes, to help with this did:

* Have a second person look at uncertain or unmet criteria
* Revist all the evaluations side-by-side once complete to check for any inconsistent decisions between them

However, this does highlight how it can be so helpful to actually provide a completed framework, that highlights key reporting points for a given study, and where to look, particularly as things get more complicated with appendices and prior papers to refer back to for information.

## Focus on reproduction

I'm not sure if this is a limitation? But certaintly its worth baring in mind that things I have flagged as being really important for the reproductions were indeed for reproductions, and not for reuse. As mentioned above, for some studies I did veer more into "reuse territory", but for others not.

There will be things that were not helpful for the reproduction, but would be helpful for reuse, e.g.

* Validity information in the article
* Web applications

### 2024-11-06 pages/other_studies.qmd
chore(docs): correct licence spelling
docs(discussion): addressed or reorganised discussion TODO. e.g. made page of limitations.

@@
 **In-progress**
+
+TODO: Consider, would there be any relevant literature related to time spent to try and get someone elses code mentioned - like how Andy mentioned there would be a max amount of time that someone in the NHS would reasonably spend troubleshooting
 
@@
     * use seeds, and report seed you used
-    * make all code and data available with an appropriate license
+    * make all code and data available with an appropriate licence
     * include master script that runs in computations in publication

### 2024-11-06 pages/background.qmd
docs(general): minor bits / tidying / removing resolved TODO

@@
 
+<!--TODO: Write this up, currently just some notes and ideas - or, could leave as notes.-->
+
 @baker_1500_2016 - survey of 1576 researchers across disciplines, finding:
@@
 * Replication - writing your own code
+
+(I.e. terminology I researched previously, **computational reproducibiltiy** etc, similar to how lots of articles define it, e.g. @samuel_computational_2024).
 
@@
 
-* Open license
+* Open licence
 * Dependency management

### 2024-11-06 pages/reflections.qmd
docs(general): minor bits / tidying / removing resolved TODO

@@
 * @wood_value_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-wood-2021/evaluation/reflections.html" target="_blank">link to reflections</a>
-
-<!-- TODO: Consider whether to make further attempts at managing to backdate R.
-Didn't manage before.
-E.g.
-`containerit` package.
-Although - is it necessary, if I succeeded without?
-Note, I always backdated the python environments.
-So, relatedly, TODO: Is it worth checking/trying with newest Python and seeing if they would work?</mark -->
-
-<!-- TODO: Add reflections related specifically to the reproduction package and second reproduction test parts of the work (i.e. after the reproduction) -->
-
-<!-- TODO: Once complete, carefully go over again and check everything is correct -->
-
-<!-- TODO: From Tom - So much great work and interesting findings.
-We need to move towards some headlines and take aways for the community.
-Mayybe there are some high level groupings of your findings?
-e.g.
-
-* Study reporting
-* Model structuring and functionality
-* Analysis pipeline
-
-Or perhaps:
-
-* Evidence supporting the use of reporting guidelines
-    * as in - reporting guidelines state this should info be included and you found it v.difficult or impossible to reproduce without it.?
--->
 
@@
 Though obviously no guarantees.
-And not a fair comparison, as I didn't try to run the Python ones without backdating.
+And **not a fair comparison, as I didn't try to run the Python ones without backdating**.
 

### 2024-11-06 pages/repo_evaluation.qmd
docs(general): minor bits / tidying / removing resolved TODO

@@
 
-<!-- TODO: Add Johnson et al. 2021 -->
-
 In this section and below, the criteria for each study are marked as either being fully met (✅), partially met (🟡), not met (❌) or not applicable (N/A).
@@
 
-<!-- TODO: Add Johnson et al. 2021 -->
-
 | Item | S | Hu | L | K | A | J | He | W |
@@
 ## Reflections
-
-<!-- TODO: Update after Johnson et al. 2021 -->
 
@@
 These topics were covered in the badge criteria reflections: **open licence**, **minimum documentation**, and **open science archive**.
-<!--TODO: Consider re minimum documentation: Kim met for STARS but not for badges.
-Double-check that decision-->
 
@@
 
-**ORCID** and **citation information**: Doesn't impact reproduction in this case - but we do go to these from having found an article.
-In all cases, I emailed the authors, which requires finding contact information (generally via paper, sometimes from googling them to find new emails).
+**ORCID** and **citation information**: Doesn't impact reproduction in this case - but:
+
+* We do go to these from having found an article. I was choosing repositories that I had found from papers, so I already at least knew who the paper authors were.
+* In all cases, I emailed the authors, which requires finding contact information (generally via paper, sometimes from googling them to find new emails).
+* Any attempted citation of the repository itself would've necessarily been correct, depending on whether the author list would be the same as in the paper, if you relied on the paper without citation information.
 

### 2024-11-06 pages/functions.py

@@ -316,10 +316,10 @@ def plot_scatter(var, sho, hua, lim, kim, ana, joh, her, woo):
 
 def reporting_scatter(var, reporting, sho, hua, lim, kim, ana, joh, her, woo):
     '''
-    Creates a scatter plot showing proportion of reporting guideline (STRESS-DES
-    or the guideline derived from ISPOR-SDM) that was fully met, against a
-    categorical variable (e.g. whether used reporting guidelines, whether model
-    has been described previously).
+    Creates a scatter plot showing proportion of reporting guideline
+    (STRESS-DES or guideline derived from ISPOR-SDM) that was fully met,
+    against a categorical variable (e.g. whether used reporting guidelines, or
+    whether model has been described previously).
 
     Parameters:
     -----------
@@ -346,7 +346,7 @@ def reporting_scatter(var, reporting, sho, hua, lim, kim, ana, joh, her, woo):
     '''
     # Alongside categorical variable, lists the proportion of each guideline
     # that was fully met (out of all the applicable categories)
-    df =  pd.DataFrame({
+    df = pd.DataFrame({
         'Shoaib and Ramamohan 2021': [sho, (17/24)*100, (11/15)*100],
         'Huang et al. 2019': [hua, (14/23)*100, (7/16)*100],
         'Lim et al. 2020': [lim, (16/21)*100, (12/16)*100],

### 2024-11-06 pages/limitations.qmd
docs(limitations): tidied

@@
 
-As acknowledged in the protocol, reproduction success is a subjective decision.
+As noted in the research protocol, the assessment of **reproduction success** involves **subjective judgment**.
 
-* Where helpful, did compare numbers and absolute / percent difference, but this can be heavily impacted by scales (e.g.
-if comparing 0.1 0.2 0.3, will see much larger percentage differences than comparing 10 15 20, but actually one might be more meaningful than other, depending on what the underlying scale etc is.)
-* Nature of what is being plot can have a big impact - e.g. for one study, health economic costs and QALYs look super similar, but when calculate ICER and INMB, tiny differences result in huge changes
+We sometimes looked at **absolute and percentage difference** betweeen our reproduction and the original results.
+However, these could be **significantly influenced by the scale** used.
+For instance, comparing values like 0.1, 0.2, and 0.3 results in larger percentage differences than comparing values such as 10, 15, and 20, even though the latter comparison might hold more practical significance depending on the context.
+
+The **nature of the metrics being analyzed** also affected outcomes.
+For example, in the health economic study, costs and Quality-Adjusted Life Years (QALYs) appeared similar in value.
+However, when using them to calculating the Incremental Cost-Effectiveness Ratio (ICER) and the Incremental Net Monetary Benefit (INMB), even **minor variations in the costs and QALYs resulted in substantial differences in the ICER and INMB**.
 
@@
 
-I did not try to reuse studies for new context.
-Although for some studies, I did have to dig into the code quite alot to work out how to set up scenarios and process results, and I would argue that is similar to reuse (as I was trying to adapt it for a new scenario).
-However, for some other studies, this was not necessary and for those I just had a more top-level/basic interaction with the code (and didn't have to delve).
-Hence, in many cases, can't truly say if information provided was sufficient for that deep understanding of what it is doing and so on, but in some cases I can a bit more.
+This study **did not attempt to reuse** the model/s in new contexts.
+Despite this, for some studies, I did have to examine the underlying code extensively to understand how to implement the scenarios or process the results.
+This troubleshooting process was **similar to reuse**, as I was attempting to **adapt the model code to run a new scenario**.
+However, for other studies, I could quite easily run the model and didn't need to delve into the code.
+
+As such, I would not have been able to consistently assess whether the repository provided sufficient information for a comprehensive understanding of the model, necessary for reuse.
+As such, the focus is moreso on **reproduction** and what was necessary/helpful/unnecessary for that.
+
+It's important to note that features I didn't as important for reproduction were indeed specific to reproduction, not to reuse.
+As such, certain **elements that weren't essential for reproduction might still be highly valuable for reuse** (and, we know, often would be), such as:
+
+* Validity information from the article
+* Web applications
 
@@
 
-Evaluations are likely imperfect. Can be hard to find things in a paper, may have made mistakes, to help with this did:
+The evaluations (in particular, of the articles) are likely to be **imperfect**. It can be difficult to locate information in the papers and errors may have occurred. To help mitigate this we:
 
-* Have a second person look at uncertain or unmet criteria
-* Revist all the evaluations side-by-side once complete to check for any inconsistent decisions between them
+* Had a **second person** look at uncertain or unmet criteria
+* Revisited all the evaluations **side-by-side** once complete to check for any inconsistent decisions between them
 
-However, this does highlight how it can be so helpful to actually provide a completed framework, that highlights key reporting points for a given study, and where to look, particularly as things get more complicated with appendices and prior papers to refer back to for information.
-
-## Focus on reproduction
-
-I'm not sure if this is a limitation?
-But certaintly its worth baring in mind that things I have flagged as being really important for the reproductions were indeed for reproductions, and not for reuse.
-As mentioned above, for some studies I did veer more into "reuse territory", but for others not.
-
-There will be things that were not helpful for the reproduction, but would be helpful for reuse, e.g.
-
-* Validity information in the article
-* Web applications
+However, this potential for error - as well as the time taken to complete these evaluations - does highlight how it can be so helpful to actually **provide a completed reporting guidelines framework**, which highlights key reporting points for each study and indicates where to find specific information.
+This can become especially helpful as studies become more complex with **longer articles**, or details often spread across **several appendices** or **earlier papers**.

### 2024-11-06 pages/compendium.qmd
docs(compendium): add reflections related to compendium and test-run

@@
 
-## Reflections
+## Reflections related to compendium
 
-The test-run stage after making compendium helped us to spot run issues that I hadn't noticed, mainly from having not completely tested absolutely everything before pushing.
-For example, Hernandez et al.
-2015, and there was at least one other example too.
-Shows importance of having someone else check things - easy to leave in small mistakes that mean it doesn't run.
+**Organisation:**
+
+* No one right way to organise. If it was already pretty good, I left it (e.g. Kim et al. 2021). However, for lots of them, I did change organise to e.g. `scripts/`, `inputs/`, `outputs/`
+
+**Tests:**
+
+* When creating the tests, since many of the models had long run times, my intention was often just to create a **"mini-run" of the model** that allows someone to quickly and easily check if they can run some aspect of the model (without needing to try the whole one with long run time).
+* The tests created **provide examples** of how can set up tests in Python and R, doing something basic like comparing dataframes or CSV files between runs.
+Indeed, it took a little bit of time to get set up initially with tests working as I want, but once figured for one, I could **reuse** like a template for the next.
+* Sometimes had to amend model to be able to run tests - e.g. for Wood et al. 2021, test wouldn't work if model was run with parallel processing
+* Also, an example of Johnson et al.
+2021 where I couldn't get the model to work correctly within a test (despite no visible errors), and so went with the solution of making a normal .R script that operates like a test but without the `testthat` package
+
+**GitHub actions:**
+
+* Wasn't able to successfully build a quarto book using GitHub actions if it required both Python and R (in which case, had to push from local)
+
+**Docker:**
+
+* This sometimes took rather alot of troubleshooting, and could sometimes be quite tricky.
+However, once resolved (Python, R, and later a older Python), I could then just **reuse** previous dockerfiles like a template (although sometimes still some troubleshooting still needed).
+
+## Reflections related to test-run
+
+The test-run stage after making compendium helped us to **spot run issues** that I hadn't noticed, mainly from having not completely tested absolutely everything before pushing. For example:
+
+* Shoaib and Ramamohan 2022 - there was an authentication error when trying to pull the docker image from GitHub Container Registry, as I was missing some of the steps related to personal access tokens
+* Hernandez et al.
+2015 - though the test worked locally, it did not work on docker.
+This was related to imports, and resolved by adding `__init__.py` files, but I hadn't noticed as hadn't checked the test on docker.
+* Lim et al. 2020 - one of the files failed to run as I hadn't uploaded some of the required data
+
+Shows importance of having someone else check things - **easy to leave in small mistakes** that mean it doesn't run.
+In general, having something like this to check your code is a really **handy practice**, if possible.
+
+The test-run stage also helped highlight **things that weren't clear**.
+For example, I had a test that took a few minutes to run, and whilst running your console is blank.
+He was unsure if this was an error - so I then add a section to the README that explained what to expect to see when running those tests.
+
+Also, **likely errors** people will encounter - for example, by not having a particular environment active or not being in the right folder when trying to run something - and so I then made sure to clarify this in the README.
+
+When running test-runs on a fresh machine, Tom often found there were **operating system dependencies** he had to install for R.
+Also, examples like Huang et al.
+2019 were Tom looked to run on his virtual machine but that only allocates 4GB RAM and the model used 8GB RAM so he had to use a different machine - hence, also helping highlight **memory requirements**.

### 2024-11-06 pages/protocol.qmd
docs(protocol): add extra "reflections" stage

@@
 However, I was easily able to resolve this by setting the release to a prior commit, choosing the commit from that timepoint (between scope and reproduction), so it was as if it had been done at the time |
-| Identification of papers | Although X <!--TODO: Count numbers--> papers were identified from the review by @monks_computer_2023, X were identified from additional searches (informal, not systematic) |
+| Identification of papers | Although 7 papers were identified from the review by @monks_computer_2023, 1 was identified from additional searches (informal, not systematic) - this was so we could find an older paper.
+|
+| Reflections | I effectivelly created an "additional" stage, which was to create a page of reflections on the reproduction (barriers and faciliators).
+This was not formally part of the original protocol, but implicit.
+|
 

### 2024-11-06 pages/other_studies.qmd
docs(other studies): add some more studies, with notes on some of them

@@
         * Reproducibility badges, reproducibility platforms like REScience, nanopublications
+
+And some relevant articles/discussions:
+
+* @hrynaszkiewicz_survey_2021
+    * Survey in Autumn 2020 of previous authors and other registered users with PLOS Computational Biology
+    * 214 complete responses
+    * Lots had papers where code was not shared - reasons inc (1) takes too much time to prepare code for sharing, (2) software and systems dependencies (3) concerns with my ability to prepare the code for sharing (4) I needed to protect intellectual property, etc...
+    * More likely to submit to journal if mandatory code sharing policy (moreso for ECR)
+    * Low mean satisfication score for accessing others code (44.0)
+* @cadwallader_survey_2022
+    * Survey in Spring 2021 of previous authors and other registers used with PLOS computational biology related disciplines
+    * 188 complete responses
+    * Questions on
+        * How often look at code associated with research articles
+        * Whether have encountered different methods of code sharing
+        * How useful found different methods of accessing code - **link to code repository was rated most useful - with code "available upon request" least useful**.
+When explaining why link was most useful, common reasons were: (**a) ability to see new versions of code (b) quick access to code (c) good documentation/README (d) practicality (e) reproduction of results (f) established**.
+For sharing via notebooks, like ability to explore code and reproduction of results.
+For archived code, like that it gives long term access.
+        * Features of code notebooks that are useful when accessing/reading code, highest ranked: (1) having all code, data and figures in one place, (2) knowing code is running in right environment (3) ability to interact inline with code in browser (4) ability to uncover data point by hovering over point in graph ...etc
+        * Satisifcation and importance scores of factors associated with sharing code
+        * Time spent preparing and sharing code
+        * Extra time willing to spend to make code easier to read and run
+* @noauthor_revisiting_2022
+    * Initiative from Nature Machine Intelligence to have new article type **"Reusability Report"** where researchers try code from article in journal and try running it, applying to new data or tweaking or extending it
+* @mejba_evolution_2023
+    * Lists **benefits of code reuse**: increase **productivity**, improved code quality, reduced errors, cost efficiency, faster time-to-market, **knowledge sharing**, scalability, sustainability, innovation
+    * Lists challenges of code reuse: **understanding reused code**, integration issues, incompatability, maintaining and updating reused code, **licensing and ownership**, security risks, quality control, overhead, dependency management
+    * Gives solutions to changes e.g. understanding reused code --> **comprehensive documentation**
+    * Strategies for effective code reuse...
+modular design, use of libraries and frameworks, design patterns, object oriented programming, apis and microservices, code documentation, automated testing, refactoring, code reviews, ci/cd
+    * Lists security implications of code reuse, and best practices for security
+    * Impacts of code reuse on software development lifecycle:
+        * Planning and analysis - **reuse code can reduce time and resources required, although crucial to check code compatability, quality and security to meet needs**
+        * Design - design of code can facilitate reuse
+        * Implementation - reuse snippets, lirbaries, etc.
+        * Testing - reused code can have benefit of being previously tests so less bugs, more stable software, but will need rigorous re test
+        * Deployment - if code has depenedencies, need to manage properly eg docker
+        * Maintenance - if reused code well understood and well documentation can make maintence easier
+* @dupre_beyond_2022
+    * <https://theplosblog.plos.org/2022/05/uphold-the-code/> describes the article, saying " DuPree and colleagues draw a distinction between the scholarly article, which they argue functions as a kind of preview or entrypoint to the research, and the real scholarly work.
+That is, the methods researchers develop (in this case software and code), and the data they gather and analyze in order to produce a result.
+It’s this data and code which forms the core of the research, the fulcrum on which everything else turns.
+For that reason, code not only deserves a place in the literature, it is required in order to fully understand and appreciate the scholarship."
+    * Article is about "**hybrid research objects**" - i.e.
+multiple content types, so narrative text plus at least one of: code, data, and/or computation.
+Can link in data/code availability statements.
+Publisher may require those linked objects to meet specific standards and include as part of review process.
+"Hope to see more hybrid research objects where each linked object is formatted with domain-relevant standards...
+and bi-directionally linked using persistent identifiers"
+    * Article then talks about interactive research objects, with everything all in one place, like "executable research articles", RMArkdown, Jupyter Book, Binder, Pangeo, NeuroLibre
+* @benureau_re-run_2018
+    * https://www.frontiersin.org/journals/neuroinformatics/articles/10.3389/fninf.2017.00069/full#B22
+    * "In conclusion, the R3 **(reproducible) form should be accepted as the minimum scientific standard** (Wilson et al., 2017). "
+* @wilson_good_2017
+    * https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1005510
+* @gomes_why_2022
+    * https://royalsocietypublishing.org/doi/full/10.1098/rspb.2022.1113
+    * Figure 1 is a nice visualisation
+* @connolly_software_2023
+    * https://par.nsf.gov/servlets/purl/10510561
+* https://www.nature.com/articles/nn.4550

### 2024-11-06 pages/other_studies.qmd
docs(other studies): table of reproduction studies, and more notes on some other papers

@@
 
-TODO: Consider, would there be any relevant literature related to time spent to try and get someone elses code mentioned - like how Andy mentioned there would be a max amount of time that someone in the NHS would reasonably spend troubleshooting
+TODO: Consider, would there be any relevant literature related to time spent to try and get someone elses code mentioned - like how Andy mentioned there would be a max amount of time that someone in the NHS would reasonably spend troubleshooting --> *struggled to find anything, so maybe just something to mention in general in discussion*
 
@@
 
+## Studies that assessed reproducibility
+
+Summary of studies that have assessed reproducibility:
+
+| Study | Focus | N | 
+| - | - | - |
+| @krafczyk_learning_2021 | Articles from *Journal of Computational Physics* | 7 |
+| @wood_push_2018 | Impact evaluations in low- and middle-income countries | 109 |
+| @schwander_replication_2021 | Health economic obesity models | 4 |
+| @laurinavichyute_share_2022 | Articles in the *Journal of Memory and Language* | 59 |
+| @konkol_computational_2019 | Geoscientific articles | 31 |
+| @hardwicke_analytic_2021 | Articles in *Psychological Science* | 25 |
+| @henderson_reproducibility_2024 | Infectious disease models | 200 |
+| @samuel_computational_2024 | Jupyter notebooks associated with publications | 3467 publications, from which 27,271 jupyter notebooks were downloaded for further analysis |
+
+The amount they reproduce and so on isn't directly comparable as alot of variation in methods (e.g.
+amount of troubleshooting allowed, how decided something is reproduced or not, and so on).
 *not sure if want to be comparing the actual proportions reproduced...
@@
 
-Starting points:
-
 * @krafczyk_learning_2021 - results are recommendations based on experiences, which were:
-    * can see completion in figure 1
+    * can see completion in figure 1, but focus is very much on the learnings rather than % reproduced and so on
     * being clear on links between article, code and data (e.g. which code uses which data, and which parts of code made each bit of article)
@@
 * @hardwicke_analytic_2021
-* @monks_computer_2023 (although overlap - look at how many of mine are from the review - some were identified from that, but some were not)
 * @henderson_reproducibility_2024
@@
 
-And some relevant articles/discussions:
+## Other relevant articles for introduction and/or discussion
 
+* @monks_computer_2023 - see summary in **introduction**
 * @hrynaszkiewicz_survey_2021
@@
 and bi-directionally linked using persistent identifiers"
-    * Article then talks about interactive research objects, with everything all in one place, like "executable research articles", RMArkdown, Jupyter Book, Binder, Pangeo, NeuroLibre
+    * Article then talks about interactive research objects, with everything all in one place, like "executable research articles", RMarkdown, Jupyter Book, Binder, Pangeo, NeuroLibre
 * @benureau_re-run_2018
-    * https://www.frontiersin.org/journals/neuroinformatics/articles/10.3389/fninf.2017.00069/full#B22
+    * They use terms from **Goble 2016**.
+They then show a simple python example which they progressively modify to meet these criteria.
+**Really nice paper!
+Could be good in introduction and elsewhere?**
+        * **R1: Re-runnable** (executable)
+            * "it is impossible to write future-proof code...
+modernizing an unmaintained ten-year-old code can reveal itself to be an arduous and expensive undertaking—and precarious...
+more straightforward solution is to recreate the old execution environment.
+For this to happen however, the dependencies in terms of systems, software, and libraries must be made clear enough."
+        * **R2: Repeatable** (produce the same result more than once)
+            * "it often comes down to controlling the initialization of the pseudo-random number generators (RNG)." --> **importance of seeds**
+        * **R3: Reproducible** (allow an investigator to reobtain published results)
+            * Explicit dependencies and operating system
+            * "includes pre-processing, post-processing, and plotting code"
+            * good practice to include short unit tests that verify reproduction
+            * code and input data and result data should all be made available
+        * **R4: Reusable** (easy to use, understand and modify)
+            * comments and documentation
+            * "reusability can represent an expensive endeavor if undertaken as an afterthought"
+            * simple things that improve reusability:
+                * avoid hardcoded values or magic numbers
+                * changes to code behaviour should be via modifiable parameters rather than commenting/uncommenting - so (a) conditions are recorded as parameters, and (b) can have seperate scripts to run and produce results
+        * **R5: Replicable** ("act as an available reference for any ambiguity in the algorithmic descriptions of the article")
+            * "replicating implies writing a new code matching the conceptual description of the article, in order to reobtain the same result"
+            * whilst this relies on the article, you will inveitably have ambiguities in the article, and so "Replication efforts use the paper first, and then the reproducible code that comes along with it whenever the paper falls short of being precise enough."
     * "In conclusion, the R3 **(reproducible) form should be accepted as the minimum scientific standard** (Wilson et al., 2017). "
 * @wilson_good_2017
-    * https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1005510
+    * Supplements the "**Best Practices for Scientific Computing" article** by giving a minimum set of "**good enough**" things to do
+    * Box 1 summarises the practices which are grouped into:
+        * Data management (e.g. saving data, documenting steps, tidy data)
+        * Software (eg. writing organising sharing scripts)
+        * Collaboration (eg. make it easier for collaborators to understand and contribute)
+        * Project organisation (eg. organise artefacts to ease discvoery and understanding)
+        * Tracking changes (i.e. record how components of project change over time)
+        * Manuscripts (eg. write manuscript with audit trail - so either history/change tracking, or version control)
 * @gomes_why_2022
-    * https://royalsocietypublishing.org/doi/full/10.1098/rspb.2022.1113
-    * Figure 1 is a nice visualisation
+    * **Figure 1** is a nice 
+    * **Barriers**
+        * Knowledge barriers - unsure about process, complex or manual workflows, large data files, insecurity, do not see value
+        * Reuse concerns - inappropriate use, rights, sensitive content, transient storage
+        * Disincentives - scooping, lack of time, lack of incentives
 * @connolly_software_2023
-    * https://par.nsf.gov/servlets/purl/10510561
-* https://www.nature.com/articles/nn.4550
+    * 3Rs of software enginerring: "readability (human understandable codes), resilience (fails rarely/gracefully), and reuse (can easily be used by others and can be embedded in other software)"
+    * Walks through some practices...
+version control, software design, computer programming or coding, quality assurance, packaging and deployment, user documentation, team management, user engagement
+* @eglen_toward_2017
+    * Simple guidelines for code sharing: version control, persistent URLs, license, etiquette, documentation, tools, case studies, data, standards, tests, user supoprt
+    * Tests - "We recommend including **test suites demonstrating that the code is producing the correct results**37.
+These tests can be at a low level (testing each individual function, called unit testing) or at a higher level (for example, testing that the program yields correct answers on simulated data)38." - and can link with **continuous integration** so automatically run and fail if change made to code that fails it

### 2024-11-07 pages/other_studies.qmd
docs(other studies): adding lots more examples of studies that assessed reproducibility

@@
 
-**In-progress**
-
-TODO: Consider, would there be any relevant literature related to time spent to try and get someone elses code mentioned - like how Andy mentioned there would be a max amount of time that someone in the NHS would reasonably spend troubleshooting --> *struggled to find anything, so maybe just something to mention in general in discussion*
-
-TODO: Add page comparing our findings to other studies. This could include:
-
-* Studies that have gone through this same process of finding barriers in reproductions
-* Studies that recommend how to share code (although, it might be simpler to just start with that first bullet and then decide whether to do both)
-
-*Do we also compare the evaluation results?
-Or do we just use that in context of barriers?* (e.g.
-@schwander_replication_2021 and @zhang_reporting_2020 for reporting...
-@laurinavichyute_share_2022 for code...)
-
 ## Studies that assessed reproducibility
 
-Summary of studies that have assessed reproducibility:
+### Summary of studies
 
-| Study | Focus | N | 
-| - | - | - |
-| @krafczyk_learning_2021 | Articles from *Journal of Computational Physics* | 7 |
-| @wood_push_2018 | Impact evaluations in low- and middle-income countries | 109 |
-| @schwander_replication_2021 | Health economic obesity models | 4 |
-| @laurinavichyute_share_2022 | Articles in the *Journal of Memory and Language* | 59 |
-| @konkol_computational_2019 | Geoscientific articles | 31 |
-| @hardwicke_analytic_2021 | Articles in *Psychological Science* | 25 |
-| @henderson_reproducibility_2024 | Infectious disease models | 200 |
-| @samuel_computational_2024 | Jupyter notebooks associated with publications | 3467 publications, from which 27,271 jupyter notebooks were downloaded for further analysis |
+| Study | Focus | Articles that tried running code from | Brief summary |
+| - | - | - | - |
+| @chang_is_2022 | Macroeconomics articles | 59 | Of 67 articles, 6 use confidential data and 2 use software they don't have, leaving 59.
+Of those, replicate 22 without author assistance and 29 with.
+(Note: no access to article - based on abstract).
+|
+| @eubank_lessons_2016 | Articles in the Quarterly Journal of Political Science which underwent in-house replication review | 24 | Of the 24, 4 didn't require modifications, 13 had code that would run without error, 8 were missing code for results in paper, 7 had no installation directions for dependencies, 14 (58%) had results in paper that differed from code-generated |
+| @galiani_incentives_2017 | Economics articles | Unclear | Of 203 included articles, 76% published any data or code.
+For those that had data and code, 54% of data manipulation code and 61% of "estimation code" could run without major modifications.
+They found 14% articles fully replicable (raw data to results) and 37% partially (estimated data to results) |
+| @konkol_computational_2019 | Geoscientific articles | 41 | Of 41 (R), 2 ran without issue, 33 had resolvable issues, 2 were partially executable, and 4 could not resolve issues.
+Author assistance for several (e.g.
+pointing out solutions, sending additional code and data).
+|
+| @krafczyk_learning_2021 | Articles from Journal of Computational Physics | 7 | Attempt to reproduce 7, allow troubleshooting up to 40 hours, success only described via viewing in a figure |
+| @henderson_reproducibility_2024 | Infectious disease models | 67 | 200 (100 random, 100 most highly cited).
+Not reproducible if properietary software/data inaccessible.
+For random, 19 had code and data.
+Of those, 4 completedly reproduced and 8 partially.
+For highly cited, 48 had code and data.
+Of those, 11 completely reproduced and 22 partially.
+|
+| @mccullough_lessons_2006 | Articles from Journal of Money, Credit and Banking | 58 | Of 266 articles, 193 should have archive entries, but only 69 did.
+Of those 69, should have code and data, but found only data for 11 of them (i.e.
+no code).
+Attempted to use supplied data and code of remaining 58 to reproduce published results.
+Allowed minor troubleshooting.
+|
+| @obels_analysis_2020 | Registered Reports in psychology | 36 | Of 62 articles, 36 had data and code. Could run 31 and reproduced main results for 21. |
+| @samuel_computational_2024 | Jupyter notebooks associated with publications | 15,817 | 3467 publications, from which 27,271 jupyter notebooks were downloaded for further analysis.
+Of those, 22,578 were Python and 15,817 had dependencies declared in standard file.
+Attempted to re-run those automatically.
+10,388 installed dependencies successfully.
+Of those, 1203 ran without error - and then 879 had results identical to original, 324 differed |
+| @stagge_assessing_2019 | Hydrology and water resources articles | 20 | Looked at data, model and code availability in 360 articles.
+Of those, 20 had required data/code/directions available for reproduction.
+Fully reproduce 4, partially reproduced 2, couldn't reproduce 2, and found 10 actually didn't have all the required artefacts.
+Allowed minor troubleshooting (e.g.
+folder/file locations) |
+| @stockemer_data_2018 | Political science articles | 71 | Looked for data/code in 145 articles, then emailed authors to ask for it.
+Received data and code for 71.
+For those, ran code, and success in reproducing apx.
+70%.
+|
+| @stodden_enabling_2018 | Articles from Journal of Computational Physics | 55 | Precursor to @krafczyk_learning_2021.
+Of 306 articles, 55 had code.
+Spent max 4 hours on them, managed to reproduce some struff for 18, but didn't complete any.
+|
+| @wood_push_2018 | Impact evaluations in low- and middle-income countries | 50 | Of 109, 27 ran to produced comparable results.
+59 refused to provide replications files.
+Of remaining 23, 3 had propreitrary data, 15 had incomplete replication files, and 5 had minor differences in results.
+|
+: {tbl-colwidths="[20, 25, 15, 40]"}
 
-The amount they reproduce and so on isn't directly comparable as alot of variation in methods (e.g.
-amount of troubleshooting allowed, how decided something is reproduced or not, and so on).
-*not sure if want to be comparing the actual proportions reproduced...
-or maybe do, but important to bare in mind what is being compared and what define as success...
-e.g.
-some include studies that haven't shared the code*
+Examples that use code and/or description in article (i.e. dont' *require* code):
+
+* @laurinavichyute_share_2022 - Articles in the Journal of Memory and Language - Look at data sharing in 59 articles before and 59 articles after a policy is in place.
+For the 59 after policy, attempted to reproduced.
+8 had inaccessible data.
+Under strict criteria, reproduced 20 (34%).
+Under lenient criteria, 33 (56%).
+* @hardwicke_data_2018 - 35 articles, two team members attempted for each article, used available data and information in article or any other additional documentation
+* @hardwicke_analytic_2021 - Articles in Psychological Science - 25 evaluated - initially 16 had at least one "major numerical discprenancy", after troubleshooting with/without authors, 37 discrepancnies remained from 789 checked values
+* @ostermann_advancing_2017 - reproducibility required full data set + executable tools or precise step-by-step instructions
+
+Examples that reuses data and repeats analysis "exactly as described in report" with clarification if needed:
+
+* @schwander_replication_2021 - 4 health economic obesity models
+* @naudet_data_2018
+* @raff_step_2019
+* @artner_reproducibility_2021
+* @maassen_reproducibility_2020
+
+### Which studies are most relevant? How do they compare?
+
+Note: It is difficult to make comparisons between all these studies due to the large variation in methods (such as amount of troubleshooting allowed, or thresholds for deciding something is reproduced).
+As such, the actual percentage reproduced is difficult to compare.
+
+However, this section does try to pull out the more relevant studies (in terms of their focus and/or methods), and consider the **similarities and differences** to our work (e.g.
+broadly considering reproduction findings, but focusing particularly on **issues encountered** and **recommendations made**).
+
+<!--TODO: Write this section -->
+
+**Similar focus**: @henderson_reproducibility_2024
+
+* Infectious disease models (i.e. models, health)
+
+::: {.callout-note collapse="true"}
+
+## Some old rough notes
 
@@
         * "Several self-created regression equations were introduced but without details on how to apply/solve the provided regressions correctly"
-* @laurinavichyute_share_2022
-* @konkol_computational_2019
-* @hardwicke_analytic_2021
+    * "We **investigated whether the CHEERS score might be predictive for the success of model replication**, but this was not the case, with scores ranging from 18 to 20.
+The non-successful replication case study 1 rated a score of 19 (the maximum possible CHEERS score is 24).
+A **comparable finding was observed by another research team that investigated the Phillips checklist** [24] in the context of model replication; they found that the Phillips checklist was not reliable for ensuring that studies are replicable [2]." They then **propose changes** to CHEERS that might help with replicability
 * @henderson_reproducibility_2024
@@
         * Reproducibility badges, reproducibility platforms like REScience, nanopublications
+
+:::
+
+## Studies that evaluated research artefacts and/or articles
+
+<!--TODO: Look into this -->
+
+e.g. @schwander_replication_2021 and @zhang_reporting_2020 for reporting... @laurinavichyute_share_2022 for code...
 
@@
 These tests can be at a low level (testing each individual function, called unit testing) or at a higher level (for example, testing that the program yields correct answers on simulated data)38." - and can link with **continuous integration** so automatically run and fail if change made to code that fails it
+* @gil_toward_2016
+    * Proposed checklits for things to include in paper, grouped into categories of:
+        * Data accessibility
+        * Data documentation
+        * Software accessibility
+        * Software documentation
+        * Provenance documentation
+        * Methods documentation
+        * Authors identification
+    * Suggest papers enriched with metadata/artefacts
+
+## Journal procedures
+
+<!--TODO: Finish this -->
+
+*Psychological Science*
+
+*Quarterly Journal of Political Science* in-house replication review - @eubank_lessons_2016
+
+*Cortex* Verification Reports - @chambers_verification_2020
+
+@galiani_incentives_2017 surveys journals about policies on sharing data and code
+
+Journal of Memory and Language  - open data and code policy, requiring code and data to be released
+
+Vadose Zone Journal - "Reproducible Research" programme where code and data is published alongside article - @skaggs_reproducible_2015

### 2024-11-12 pages/reproduction.qmd
feat(reproduction): save times figure to png
feat(reproduction): add linestyles and alt legend to time-to-completion non-interactive

@@
 # Create list with the dataframes, labels and colours, to use for each plot
+# Include alternative label for article with % reproduced and time
+# (rather than names), and a linestyle
 to_plot = [
-    (df_sho, 'Shoaib and<br>Ramamohan<br>2022', '#ee6677'),
-    (df_hua, 'Huang et<br>al. 2019', '#228833'),
-    (df_lim, 'Lim et<br>al. 2020', '#4477aa'),
-    (df_kim, 'Kim et<br>al. 2021', '#ccbb44'),
-    (df_ana, 'Anagnostou<br>et al. 2022', '#66ccee'),
-    (df_joh, 'Johnson et<br>al. 2021', '#aa3377'),
-    (df_her, 'Hernandez<br>et al. 2015', '#882255'),
-    (df_woo, 'Wood et al.<br>2021', '#117733')
+    (
+        df_ana,
+        'Anagnostou<br>et al. 2022',
+        '#882255',
+        '100% (1/1), 2h 11m',
+        (0, (1, 1))
+    ),
+    (
+        df_woo,
+        'Wood et al.<br>2021',
+        '#117733',
+        '100% (5/5), 3h 50m',
+        '--'
+    ),
+    (
+        df_lim,
+        'Lim et<br>al. 2020',
+        '#4477aa',
+        '100% (9/9), 12h 27m',
+        '-.'
+    ),
+    (
+        df_kim,
+        'Kim et<br>al. 2021',
+        '#ccbb44',
+        '100% (10/10), 14h 42m',
+        ':'
+    ),
+    (
+        df_her,
+        'Hernandez<br>et al. 2015',
+        '#aa3377',
+        '12.5% (1/8), 17h 56m',
+        '-'
+    ),
+    (
+        df_joh,
+        'Johnson et<br>al. 2021',
+        '#66ccee',
+        '80% (4/5), 19h 49m',
+        (0, (3, 1, 1, 1, 1, 1))
+    ),
+    (
+        df_hua,
+        'Huang et<br>al. 2019',
+        '#228833',
+        '37.5% (3/8), 24h 10m',
+        (0, (3, 3, 1, 3, 1, 3))
+    ),
+    (
+        df_sho,
+        'Shoaib and<br>Ramamohan<br>2022',
+        '#ee6677',
+        '94% (16/17), 28h 14m',
+        (5, (10, 3))
+    )
 ]
@@
 for x in to_plot:
-    success_static(x[0], ax, x[1], x[2])
+    success_static(x[0], ax, x[1], x[2], ls=x[4])
 
@@
 plt.show()
+```
+
+Version of non-interactive figure used in article:
+
+```{python}
+# Create figure object
+fig, ax = plt.subplots(figsize=(8, 4))
+
+# Loop through and add lines for each reproduction
+for x in to_plot:
+    success_static(x[0], ax, label=x[3], colour=x[2], ls=x[4])
+
+# Amend appearance
+plt.xlim(0, 30)
+plt.ylim(0, 100)
+plt.xlabel('Time elapsed (hours)')
+plt.ylabel('Percentage of items reproduced')
+ax.yaxis.set_major_formatter(mtick.PercentFormatter())
+ax.legend(loc='center left', bbox_to_anchor=(1, 0.5))
+
+# Save figure (to use in article)
+plt.tight_layout()
+plt.savefig('../images/article_times.png', dpi=300)
 ```

### 2024-11-12 pages/functions.py

@@ -114,7 +114,7 @@ def success_interactive(times_df, fig, label, colour):
             '%{hovertext}<br>Time: %{x:.1f} hours<br>Completion: %{y:.1f}%')))
 
 
-def success_static(times_df, ax, label, colour):
+def success_static(times_df, ax, label, colour, ls):
     '''
     Create static/non-interactive plot of time-to-completion
 
@@ -128,8 +128,11 @@ def success_static(times_df, ax, label, colour):
         Label for the line
     colour : string
         Colour of line
+    ls : string or tuple
+        Line style
     '''
-    ax.plot(times_df['hours'], times_df['ecdf'], marker='.', markevery=2,
+    ax.plot(times_df['hours'], times_df['ecdf'],
+            marker='.', markevery=2, linestyle=ls,
             label=label.replace('<br>', '\n'), color=colour)
 
 

### 2024-11-14 pages/other_studies.qmd
docs(discussion): add some more studies

@@
 |
+| @stodden_empirical_2018 | Articles from Science before and after policy change around code sharing | 22 | After policy was 204 articles - could identify artefacts themselves for 24, but contacted authors for 180, of which 131 replied - of which got data/code for 65/180 (36\%).
+From looking at the then total of 89 article artefacts, anticipated 56 to looked potentially reproducible.
+Chose 22 of them and were able to replicate results in publication for all except one (large dataset and software no longer acccesible).
+Issues in those thought not to reproduce were missing scripts, documentation, or parameters.
+Few papers cited visualisation tools, even when visualisation in article were important.
+|
 | @wood_push_2018 | Impact evaluations in low- and middle-income countries | 50 | Of 109, 27 ran to produced comparable results.
@@
 : {tbl-colwidths="[20, 25, 15, 40]"}
+
+Examples that just try and run code but don't check results:
+
+* @trisovic_large-scale_2022 - R code from the Harvard Dataverse repository | 9000 unique R files from 2000+ replication packages - with interesting oobservations about basic code cleaning, whether there's documentation and comments, and some stuff about **backwards compatability of R** and how it does become non-compatabile
 
@@
 Vadose Zone Journal - "Reproducible Research" programme where code and data is published alongside article - @skaggs_reproducible_2015
+
+## References

### 2024-11-14 pages/results_discussion.qmd
docs(general): minor bits / tidying / removing resolved TODO
chore(general): minor changes

@@
 ---
-
-::: {.callout-note}
-
-## What is on this page?
-
-* Reflections from the reproduction and evaluation, broadly grouped into two categories
-* Headline findings
-* Relationship between reproduction and evaluation
-* Some other things I want to mention
-
-:::
 
@@
 Meeting STARS optional wasn't helpful for reproduction (but would be for reuse)
+
+Importance of the timings.
+It often took alot of time to get something working.
+That is likely not feasible in practice.
+Andy anecdotally commented on the max amount of time that someone in the NHS would likely spend on something troubleshooting before moving on.

### 2024-11-18 pages/paper_evaluation.qmd
feat(paper evaluation): alternative scores and relationship with reproduction

@@
 import pandas as pd
-from functions import eval_chart, plot_scatter
+import plotly.express as px
+from functions import eval_chart, plot_scatter, calculate_scores
 
@@
 
-Of the applicable criteria, all studies fully met at least 60% (and many others still partially met).
+Of the applicable criteria, all studies fully met at least 60% (and many others still partially met) (`score_fully`).
 
-I don't think we learn much in relation to items reproduced, and that it is more interesting to consider which criteria were met and whether this aided the reproduction or not.
-
-*Note. This plots the proportion of **applicable** criteria that were **fully met***.
+Looking at the quality score suggested (`score`), we see no relationship between reporting quality and reproduction sucess.
+This remains the case when using other scoring systems used in other papers (`score_schwander` and `score_zhang`).
 
 ```{python}
-plot_scatter('STRESS-DES criteria met',
-             sho = (17/24)*100,
-             hua = (14/23)*100,
-             lim = (15/21)*100,
-             kim = (15/22)*100,
-             ana = (14/21)*100,
-             joh = (16/19)*100,
-             her = (18/23)*100,
-             woo = (22/24)*100)
+def check_reporting(df):
+  '''
+  Check the reporting quality of each study with different scoring systems
+
+  Parameters:
+  -----------
+  df : pandas dataframe
+    Dataframe with counts of fully, partially, not met and na items
+  '''
+  # Add reproduction success
+  df['reproduce'] = [94, 37.5, 100, 100, 100, 80, 12.5, 100]
+
+  # Calculating some reporting quality scores
+  scores = calculate_scores(df).rename_axis('study').reset_index()
+  display(scores)
+
+  # Plot relationship of score with reproduction success
+  for score in ['score', 'score_fully', 'score_schwander', 'score_zhang']:
+    fig = px.scatter(scores, x=score, y='reproduce', hover_data={'study': True})
+    fig.update_layout(xaxis_range=[-10, 110],
+                      yaxis_range=[-10, 110],
+                      yaxis_title='Items reproduced',
+                      xaxis_ticksuffix='%',
+                      yaxis_ticksuffix='%')
+    fig.show()
+
+check_reporting(stress_wide)
 ```
@@
 
-The proportion of applicable criteria met was lower for this checklist.
+The proportion of applicable criteria met was lower for this checklist (`score_fully`).
 
-However, I again think it's most relevant to consider which criteria were met, rather than draw conclusions from this chart.
-
-*Note. This plots the proportion of **applicable** criteria that were **fully met***.
+Same conclusions as for STRESS.
 
 ```{python}
-plot_scatter('ISPOR-SDM criteria met',
-             sho = (11/15)*100,
-             hua = (7/16)*100,
-             lim = (12/16)*100,
-             kim = (12/17)*100,
-             ana = (8/15)*100,
-             joh = (15/17)*100,
-             her = (10/17)*100,
-             woo = (13/17)*100)
+check_reporting(ispor_wide)
 ```

### 2024-11-18 pages/functions.py

@@ -260,6 +260,37 @@ def calculate_times(used_to_date, times, limit=True):
         print(f'Used {prop}% of 40 hours max')
 
 
+def calculate_scores(df):
+    '''
+    Calculate different reporting quality scores
+
+    Parameters:
+    -----------
+    df : pandas dataframe
+      Dataframe with columns for counts of fully, partially and not met items
+    '''
+    # Score: fully 1, partially 0.5, find as proportion of all applicable
+    df['score'] = (
+        (df['fully'] + df['partially'] / 2) /
+        (df['fully'] + df['partially'] + df['not']) * 100)
+
+    # Score: proportion fully met
+    df['score_fully'] = (
+        df['fully'] /
+        (df['fully'] + df['partially'] + df['not']) * 100)
+
+    # Score: As in Schwander - fully 1, partially 0.5, not or na 0
+    df['score_schwander'] = (
+        (df['fully'] + df['partially'] / 2) /
+        (df['fully'] + df['partially'] + df['not'] + df['na']) * 100)
+
+    # Score: As in Zhang - proportion of items fully met out of all (inc na)
+    df['score_zhang'] = (
+        df['fully'] /
+        (df['fully'] + df['partially'] + df['not'] + df['na']) * 100)
+    return df
+
+
 # TODO: Check the values used are still corrected, as there were some minor
 # amendments made to evaluations
 

### 2024-11-18 pages/paper_evaluation.qmd
feat(paper evaluation): add mean of scores

@@
 
+With similar conclusions from `score` and `score_fully`, I think it's sensible to present `score_fully` as that is the simplest interpretation.
+
 ```{python}
@@
   display(scores)
+  print("Mean values...")
+  display(scores.apply(pd.to_numeric, errors="coerce").mean())
 

### 2024-11-20 pages/badges.qmd
feat(badges): add badges page with revised, more specific criteria for badges

---
title: "Badges"
echo: False
bibliography: ../references.bib
---

There are several different badges with similar criteria. For clarity, a summary provides a comparison in the key criteria between these badges, and then the quoted criteria for each are here laid out in full.

A set of criteria was outlined in the protocol and used for the evaluation, but this was since revisited, revised and re-evaluated, to ensure the evaluation is **more specific** to the unique criteria of each badge (and not over-simplified).

## Summary

### "Open objects" badges

| Criteria | ACM Artifacts Available | NISO ORO | NISO ORO-A | COS Open Code | IEEE Code Available |
| - | - | - | - | - | - |
| Artefacts are archived in a repository that is: (a) public (b) guarantees persistence (c) gives a unique identifier (e.g. DOI) | ✅ | ✅ | ✅ | ✅ | ❌ |
| Open licence | ❌ | ✅ | ✅ | ✅ | ❌ |
| Complete (all relevant artefacts are available) | ❌ | ❌ | ✅ | ❌ | ✅ |
| Sufficient explanation to "understand how the code is used and relates to the reported methodology, including information about versions of software, systems, and packages." | ❌ | ❌ | ❌ | ✅ | ❌ |
: {tbl-colwidths="[50, 10, 10, 10, 10, 10]"}

### "Object review" badges

| Criteria | ACM Artifacts Evaluated - Functional | ACM Artifacts Evaluated - Reusable | IEEE Code Reviewed |
| - | - | - | - |
| Documentation with: (a) inventory of artefacts (b) sufficient description for artefacts to be exercised | ✅ | ✅ | ❌ |
| Artefacts relevant to paper | ✅ | ✅ | ❌ |
| Complete (all relevant artefacts are available) | ✅ | ✅ | ✅ |
| Scripts can be executed | ✅ | ✅ | ✅ |
| Artefacts are "carefully documented and well-structured to the extent that reuse and repurposing is facilitated", adhering to norms and standards | ❌ | ✅ | ❌ |
: {tbl-colwidths="[50, 16.66, 16.66, 16.66]"}

### "Reproduced" badges

Across all badges, whether explicitly stated or not, assuming that:

* Reproduced meaning agreement within tolerance deemed acceptable given context (e.g. not change main claims)
* Reproduction is within a reasonable time frame (assuming this to mean no more than a few hours, at the very most)
* Minor troubleshooting is reasonable (e.g. set up of right environment), but nothing extensive

| Criteria | ACM Results Reproduced | NISO ROR-R | IEEE Code Reproducible | Psychological Science Computational Reproducibility |
| - | - | - | - | - |
| Reproduced results (assuming (a) acceptably similar (b) reasonabe time frame (c) only minor troubleshooting) | ✅ | ✅ | ✅ | ✅ |
| README file with step-by-step instructions to run analysis | ❌ | ❌ | ❌ | ✅ |
| Dependencies (e.g. package versions) stated | ❌ | ❌ | ❌ | ✅ |
| Clear how output of analysis corrsponds to article | ❌ | ❌ | ❌ | ✅ |
: {tbl-colwidths="[50, 12.5, 12.5, 12.5, 12.5]"}

## Full criteria

### Association for Computing Machinery (ACM)

#### Artifacts Available

> "Author-created artifacts relevant to this paper have been placed on a **publically accessible archival repository**. A **DOI or link** to this repository along with a **unique identifier** for the object is provided.
> 
> * We do not mandate the use of specific repositories. Publisher repositories (such as the ACM Digital Library), institutional repositories, or open commercial repositories (e.g., figshare or Dryad) are acceptable. In all cases, repositories used to archive data should have a declared plan to enable **permanent accessibility**. Personal web pages are not acceptable for this purpose.
> * Artifacts **do not need to have been formally evaluated** in order for an article to receive this badge. In addition, they **need not be complete** in the sense described above. They simply need to be relevant to the study and add value beyond the text in the article. Such artifacts could be something as simple as the data from which the figures are drawn, or as complex as a complete software system under study."
> 
> @association_for_computing_machinery_acm_artifact_2020

#### Artifacts Evaluated - Functional

> "The artifacts associated with the research are found to be documented, consistent, complete, exercisable, and include appropriate evidence of verification and validation.
>
> * Documented: At minimum, an **inventory of artifacts** is included, and **sufficient description provided to enable the artifacts to be exercised**.
> * Consistent: The artifacts are **relevant** to the associated paper, and contribute in some inherent way to the generation of its main results.
> * Complete: To the extent possible, **all components relevant to the paper in question are included**. (Proprietary artifacts need not be included. If they are required to exercise the package then this should be documented, along with instructions on how to obtain them. **Proxies for proprietary data should be included** so as to demonstrate the analysis.)
> * Exercisable: Included scripts and/or software used to generate the results in the associated paper **can be successfully executed**, and included data can be accessed and appropriately manipulated."

#### Artifacts Evaluated - Reusable

> "The artifacts associated with the paper are of a quality that significantly exceeds minimal functionality. That is, they have all the qualities of the Artifacts Evaluated – Functional level, but, in addition, they are very **carefully documented and well-structured** to the extent that **reuse and repurposing is facilitated**. In particular, **norms and standards** of the research community for artifacts of this type are strictly adhered to."

#### Results Reproduced

> "The **main results** of the paper have been obtained in a subsequent study by a person or team **other than the authors**, **using, in part, artifacts provided by the author**."
>
> "...exact...reproduction of results is not required, or even expected. Instead, the **results must be in agreement to within a tolerance deemed acceptable for experiments of the given type**. In particular, differences in the results should **not change the main claims** made in the paper."
>
> For reproduced (or replicated) badges, "...a **peer-reviewed publication** which reports the replication or reproduction must be submitted as evidence, and if awarded, the **badge will contain a link to this paper**."

### National Information Standards Organisation (NISO)

#### Open Research Objects (ORO) and Open Research Objects - All (ORO-A)

> "This badge signals that author-created digital objects used in the research (including data and code) are **permanently archived** in a **public repository** that assigns a **global identifier** and **guarantees persistence**, and are made available via standard **open licenses** that maximize artifact availability.
>
> If **all relevant research objects are made available**, the badge is designated by a modifier, e.g., ORO-A. This badge signals that the research publication is reproducible (as described in the NASEM Report).
> 
> Notes:
>
> 1. This is akin to author-supplied supplemental materials, shared under a standard public license such as an Open Science Initiative (OSI)–approved license for software or a Creative Commons license or public domain dedication for data and other materials.
> 2. This definition corresponds to the Association for Computing Machinery (ACM) “Artifacts Available” badge, and to the combined Center for Open Science (COS) “Open Data” and “Open Materials” (pertaining to digital objects) badges. (See Appendix A.)
> 3. The determination of what objects are “relevant” to a research publication is in the hands of the editorial board or leadership members of the community, in addition to the authors themselves.
> 4. For physical objects relevant to the research, the metadata about the object should be made available."
>
> @niso_reproducibility_badging_and_definitions_working_group_reproducibility_2021

#### Research Objects Reviewed (ROR)

This badge was not included, as it doesn't have specific criteria to review against, and simply states that artefacts should be "reviewed according to the criteria provided by the badge issuer" (@niso_reproducibility_badging_and_definitions_working_group_reproducibility_2021).

#### Results Reproduced (ROR-R)

> "This badge signals that an additional step was taken or facilitated by the badge issuer (e.g., publisher, trusted third-party certifier) to certify that an independent party has regenerated computational results using the author-created research objects, methods, code, and conditions of analysis. Results Reproduced assumes that the research objects were **also reviewed**. For this reason, a possible distinction for this badge could be as a tag on the ROR badge: ROR-R. This Recommended Practice has adopted the National Academies of Sciences Engineering Medicine, definition of Reproducibility: “We define reproducibility to mean computational reproducibility— obtaining **consistent results using the same input data, computational steps, methods, code, and conditions of analysis**.”"
>
> @niso_reproducibility_badging_and_definitions_working_group_reproducibility_2021

### Center for Open Science (COS)

#### Open Code

> "The Open Analytic Code badge is earned by making publicly available the analytical code needed to reproduce the reported analyses.
>
> Criteria:
>
> * Digitally-shareable code is **publicly available** on an open-access **repository** (e.g., university repository, a registration on the Open Science Framework, or an independent repository at www.re3data.org). The code must be provided in a format that is **time-stamped, immutable, and permanent**. It must also have an associated **persistent identifier such as a DOI**. Note that the code itself may not have a distinct identifier, but rather be included in a repository with related files that is under one distinct identifier.
> * The code has an **open license** allowing others to copy, distribute, and make use of the code while allowing the licensor to retain credit and copyright as applicable.
> * **Sufficient explanation** is present for an independent researcher to understand **how the code is used and relates to the reported methodology, including information about versions of software, systems, and packages**."
>
> @blohowiak_badges_2023

### Institute of Electrical and Electronics Engineers (IEEE)

#### Code Available

> "The code and/or datasets, including any associated data and documentation, provided by the authors is reasonable and **complete** and can potentially be used to support reproducibility of the published results."
>
> @institute_of_electrical_and_electronics_engineers_ieee_about_2024

#### Code Reviewed

> "The code and/or datasets, including any associated data and documentation, provided by the authors is reasonable and **complete**, **runs to produce the outputs described**, and can support reproducibility of the published results."
>
> @institute_of_electrical_and_electronics_engineers_ieee_about_2024

#### Code Reproducible

> "This badge signals that an additional step was taken or facilitated to certify that an **independent party** has **regenerated computational results using the author-created research objects, methods, code, and conditions of analysis**. Reproducible assumes that the research objects were **also reviewed**."
>
> @institute_of_electrical_and_electronics_engineers_ieee_about_2024

### Psychological Science

#### Computational Reproducibility

> "All manuscripts submitted to Psychological Science are expected to be computationally reproducible. That is, a reader should be able to **run the authors’ analysis scripts on the authors’ data and reproduce the results reported in the manuscript, tables, and figures**. As part of the STAR review after conditional acceptance, we will conduct computational reproducibility checks.
>
> To ensure their work is computationally reproducible, authors should accompany analysis scripts with a **README file that provides clear step-by-step instructions** for repeating the analyses. Any **software dependencies (e.g., package versions) should be identified**. Authors should make **clear how the output of the analysis scripts corresponds to the results reported in the manuscript**. We strongly encourage authors to perform a reproducibility check within their own team before submitting a manuscript, as this will reduce delays at the conditional acceptance stage."
>
> @association_for_psychological_science_aps_psychological_2023
>
> "The Computational Reproducibility Badge will be awarded when authors take the necessary steps to ensure that reported results can be independently reproduced, **within a reasonable time frame**, by the STAR team. This is a standard that we expect from all articles submitted to Psychological Science; however, we appreciate that the community may currently lack the resources and skills required to write reproducible manuscripts. With that in mind, we are identifying and collating resources (see Educational Resources section) to help the community build the capacity to meet this standard. Eventually, we plan to make verified computational reproducibility a blanket requirement for all empirical articles."
>
> @hardwicke_transparency_2024

## References

### 2024-11-20 pages/badges.qmd
chore(badges): minor tweak to wording

@@
 | Open licence | ❌ | ✅ | ✅ | ✅ | ❌ |
-| Complete (all relevant artefacts are available) | ❌ | ❌ | ✅ | ❌ | ✅ |
-| Sufficient explanation to "understand how the code is used and relates to the reported methodology, including information about versions of software, systems, and packages." | ❌ | ❌ | ❌ | ✅ | ❌ |
+| Complete (all artefacts that would be needed for reproduction) | ❌ | ❌ | ✅ | ❌ | ✅ |
+| Documents (a) how code is used (b) how it relates to article (c) software, systems, packages and versions | ❌ | ❌ | ❌ | ✅ | ❌ |
 : {tbl-colwidths="[50, 10, 10, 10, 10, 10]"}
@@
 | - | - | - | - |
-| Documentation with: (a) inventory of artefacts (b) sufficient description for artefacts to be exercised | ✅ | ✅ | ❌ |
+| Documents (a) inventory of artefacts (b) sufficient description for artefacts to be exercised | ✅ | ✅ | ❌ |
 | Artefacts relevant to paper | ✅ | ✅ | ❌ |
-| Complete (all relevant artefacts are available) | ✅ | ✅ | ✅ |
-| Scripts can be executed | ✅ | ✅ | ✅ |
+| Complete (all artefacts that would be needed for reproduction) | ✅ | ✅ | ✅ |
+| Scripts can be successfully executed | ✅ | ✅ | ✅ |
 | Artefacts are "carefully documented and well-structured to the extent that reuse and repurposing is facilitated", adhering to norms and standards | ❌ | ✅ | ❌ |

### 2024-11-20 pages/badges.qmd
chore(badges): minor tweaks

@@
 | Dependencies (e.g. package versions) stated | ❌ | ❌ | ❌ | ✅ |
-| Clear how output of analysis corrsponds to article | ❌ | ❌ | ❌ | ✅ |
+| Clear how output of analysis corresponds to article | ❌ | ❌ | ❌ | ✅ |
 : {tbl-colwidths="[50, 12.5, 12.5, 12.5, 12.5]"}
@@
 >
-> @association_for_psychological_science_aps_psychological_2023
+> @association_for_psychological_science_aps_psychological_2024
 >

### 2024-11-20 pages/protocol.qmd
docs(protocol): changes language from deviations to modifications
chore(badges): minor tweaks

@@
         * Center for Open Science (COS) (@blohowiak_badges_2023)
-        * Institute of Electrical and Electronics Engineers (IEEE) (@institute_of_electrical_and_electronics_engineers_ieee_about_nodate)
-        * Psychological Science (@hardwicke_transparency_2023 and @association_for_psychological_science_aps_psychological_2023)
+        * Institute of Electrical and Electronics Engineers (IEEE) (@institute_of_electrical_and_electronics_engineers_ieee_about_2024)
+        * Psychological Science (@hardwicke_transparency_2023 and @association_for_psychological_science_aps_psychological_2024)
     * Recommendations from the pilot STARS framework for the sharing of code and associated materials from discrete-event simulation models (@monks_towards_2024).
@@
 
-## Major deviations from the protocol
+## Modifications from the protocol
 
-There was one major deviation from the protocol...
+There was one major change from the protocol...
 
@@
 
-## Minor deviations from the protocol
-
-There were some minor deviations from the protocol, which are explained below...
+There were also some minor changes, which are explained below...
 

### 2024-11-20 pages/repo_evaluation.qmd
chore(references): update hardwicke year
chore(badges): minor tweaks

@@
 
-**Institute of Electrical and Electronics Engineers (IEEE)** (@institute_of_electrical_and_electronics_engineers_ieee_about_nodate)
+**Institute of Electrical and Electronics Engineers (IEEE)** (@institute_of_electrical_and_electronics_engineers_ieee_about_2024)
 
@@
 
-**Psychological Science** (@hardwicke_transparency_2023 and @association_for_psychological_science_aps_psychological_2023)
+**Psychological Science** (@hardwicke_transparency_2024 and @association_for_psychological_science_aps_psychological_2024)
 

### 2024-11-21 pages/repo_evaluation.qmd
feat(badges): update following redoing of badge evaluation

@@
 
-*Caveat: Please note that these criteria are based on available information about each badge online, and that we have likely differences in our procedure (e.g.
-allowed troubleshooting for execution and reproduction, not under tight time pressure to complete).
+*Caveat: Please note that these criteria are based on available information about each badge online.
 Moreover, we focus only on reproduction of the discrete-event simulation, and not on other aspects of the article.
@@
 criteria_dict = {
-  'Shoaib and Ramamohan<br>2021 (16/17)': [3, 0, 9, 0],
+  'Shoaib and Ramamohan<br>2021 (16/17)': [2, 0, 10, 0],
   'Huang et al. 2019 (3/8)': [3, 0, 9, 0],
-  'Lim et al. 2020 (9/9)': [3, 0, 9, 0],
+  'Lim et al. 2020 (9/9)': [2, 0, 10, 0],
   'Kim et al. 2021 (10/10)': [5, 0, 7, 0],
-  'Anagnostou et al. 2022 (1/1)': [10, 0, 2, 0],
+  'Anagnostou et al. 2022 (1/1)': [8, 0, 4, 0],
   'Johnson et al. 2021 (4/5)': [4, 0, 8, 0],
-  'Hernandez et al. 2015 (1/8)': [3, 0, 9, 0],
+  'Hernandez et al. 2015 (1/8)': [2, 0, 10, 0],
   'Wood et al. 2021 (5/5)': [4, 0, 8, 0]
@@
 
-Four studies met 25% of criteria, and ranged from 12.5% to 100% reproduced.
-
-Two studies met 33% of criteria, and these were 80% and 100% reproduced.
-
-The remaining two studies were fully reproduced and met 41.7% and 83.3% of criteria.
-
-However, I think it is more meaningful to actually look at what criteria were and were not met.
+No clear relationship. I think it is more meaningful to actually look at what criteria were and were not met.
 
@@
 plot_scatter('Unique badge criteria met',
-             sho = 25,
+             sho = 16.7,
              hua = 25,
-             lim = 25,
+             lim = 16.7,
              kim = 41.7,
-             ana = 83.3,
+             ana = 66.7,
              joh = 33.3,
-             her = 25,
+             her = 16.7,
              woo = 33.3)
@@
 badge_dict = {
-  'Shoaib and Ramamohan<br>2021 (16/17)': [3, 0, 9, 0],
+  'Shoaib and Ramamohan<br>2021 (16/17)': [0, 0, 12, 0],
   'Huang et al. 2019 (3/8)': [0, 0, 12, 0],
-  'Lim et al. 2020 (9/9)': [3, 0, 9, 0],
-  'Kim et al. 2021 (10/10)': [3, 0, 9, 0],
-  'Anagnostou et al. 2022 (1/1)': [5, 0, 7, 0],
-  'Johnson et al. 2021 (4/5)': [3, 0, 9, 0],
+  'Lim et al. 2020 (9/9)': [0, 0, 12, 0],
+  'Kim et al. 2021 (10/10)': [0, 0, 12, 0],
+  'Anagnostou et al. 2022 (1/1)': [3, 0, 9, 0],
+  'Johnson et al. 2021 (4/5)': [0, 0, 12, 0],
   'Hernandez et al. 2015 (1/8)': [0, 0, 12, 0],
@@
 
-Also, it's important to remember here that the criteria used for these were based on what could be found about each badge online, but we likely differences in our procedure (e.g.
-allowed troubleshooting for execution and reproduction, not under tight time pressure to complete).
-Moreover, we focus only on reproduction of the discrete-event simulation, and not on other aspects of the article.
-We cannot guarantee that the badges below would have been awarded in practice by these journals (and, in fact, know likely not for many).
-
 ```{python}
 plot_scatter('Badges awarded',
-             sho = 25,
+             sho = 0,
              hua = 0,
-             lim = 25,
-             kim = 25,
-             ana = 41.7,
-             joh = 25,
+             lim = 0,
+             kim = 0,
+             ana = 25,
+             joh = 0,
              her = 0,
@@
 | **Criteria related to how artefacts are shared** |
-| Stored in a permanent archive that is publicly and openly accessible | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
-| Has a persistent identifier | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
-| Includes an open licence | ❌ | ✅ | ❌ | ✅ | ✅ | ✅ | ❌ | ❌ |
+| Artefacts are archived in a repository that is: (a) public (b) guarantees persistence (c) gives a unique identifier (e.g. DOI) | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
+| Open licence | ❌ | ✅ | ❌ | ✅ | ✅ | ✅ | ❌ | ❌ |
 | **Criteria related to what artefacts are shared** |
-| Artefacts are relevant to and contribute to the article’s results | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ |
-| Complete set of materials shared (as would be needed to fully reproduce article) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ✅ |
+| Complete (all relevant artefacts available) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ✅ |
+| Artefacts relevant to paper | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ |
 | **Criteria related to the structure and documentation of the artefacts** |
-| Artefacts are well structured/organised (e.g. to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community) | ❌ | ❌ | ❌ | ✅ | ✅ | ❌ | ✅ | ❌ |
-| Artefacts are sufficiently documented (i.e. to understand how it works, to enable it to be run, including package versions) | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
-| Artefacts are carefully documented (more than sufficient - i.e.
-to the extent that reuse and repurposing is facilitated - e.g.
-changing parameters, reusing for own purpose) | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
-| Artefacts are clearly documented and accompanied by a README file with step-by-step instructions on how to reproduce results in the manuscript | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
+| Documents (a) how code is used (b) how it relates to article (c) software, systems, packages and versions | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
+| Documents (a) inventory of artefacts (b) sufficient description for artefacts to be exercised | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ | ❌ |
+| Artefacts are carefully documented and well-structured to the extent that reuse and repurposing is facilitated, adhering to norms and standards | ❌ | ❌ | ❌ | ✅ | ✅ | ❌ | ❌ | ❌ |
+| README file with step-by-step instructions to run analysis | ❌ | ❌ | ❌ | ❌ | ✅ | ✅ | ❌ | ❌ |
+| Dependencies (e.g. package versions) stated | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
+| Clear how output of analysis corresponds to article | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ✅ |
 | **Criteria related to running and reproducing results** |
 | Scripts can be successfully executed | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ |
-| Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ | ✅ | ❌ | ✅ |
-| Reproduced within approximately one hour (excluding compute time) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
+| Reproduced results (assuming (a) acceptably similar (b) reasonable time frame (c) only minor troubleshooting) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ✅ |
 : {tbl-colwidths="[60, 5, 5, 5, 5, 5, 5, 5, 5]"}
@@
   'Archive': [1, 0, 7, 0],
-  'ID': [1, 0, 7, 0],
   'Licence': [4, 0, 4, 0],
+  'Complete': [1, 0, 7, 0],
   'Relevant': [8, 0, 0, 0],
-  'Complete': [1, 0, 7, 0],
-  'Structured for reuse': [3, 0, 5, 0],
-  'Sufficient docs': [1, 0, 7, 0],
-  'Careful docs': [1, 0, 7, 0],
-  'Step-by-step README': [1, 0, 7, 0],
+  'Docs use/relate/software': [1, 0, 7, 0],
+  'Docs inventory': [1, 0, 7, 0],
+  'README step-by-step': [2, 0, 6, 0],
+  'Dependencies': [1, 0, 7, 0],
+  'Output ~ Article': [1, 0, 7, 0],
   'Execute': [8, 0, 0, 0],
-  'Reproduced': [6, 0, 2, 0],
-  'One hour': [0, 0, 8, 0]
+  'Reproduced': [1, 0, 7, 0],
 }
@@
 
-**Stored in a permanent archive that is publicly and openly accessible**: Fulfillment doesn't impact reproduction as I was able to get everything needed from the remote code repository (GitHub or GitLab).
+**Artefacts are archived in a repository that is: (a) public (b) guarantees persistence (c) gives a unique identifier (e.g.
+DOI)**: Fulfillment doesn't impact reproduction as I was able to get everything needed from the remote code repository (GitHub or GitLab).
 However, if these had been deleted from GitHub, it would have become invaluable.
 
-**Has a persistent identifier**: Fulfillment doesn't impact reproduction.
-
-**Includes an open licence**: This had a big impact on our ability to complete reproductions, as we had to ask authors to add an open licence to their work, to enable us to use it.
+**Open licence**: This had a big impact on our ability to complete reproductions, as we had to ask authors to add an open licence to their work, to enable us to use it.
 Gladly, all authors we contacted kindly add these on request.
@@
 
-**Artefacts are relevant to and contribute to the article’s results**: All met (if not met, this would be a massive hindrance).
-
-**Complete set of materials shared (as would be needed to fully reproduce article)**: This had a really big impact on the reproduction.
+**Complete (all relevant artefacts available)**: This had a really big impact on the reproduction.
 The main reason for longer times in reproduction was (a) code for scenarios not provided, and (b) code to process results into figures and tables not provided.
 
-**Artefacts are well structured/organised (e.g.
-to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community)**: In cases where this was not met, this was often related to hard-coding of parameters, or set up of code in a way that - alike hard-coding - made it much harder to reuse the model (in this context, to reuse them between different scenarios) - or quite a busy/cluttered repository which was confusing to navigate.
+**Artefacts relevant to paper**: All met (if not met, this would be a massive hindrance).
 
-**Artefacts are sufficiently documented (i.e.
-to understand how it works, to enable it to be run, including package versions)**: Only three studies had any documentation - READMEs for @kim_modelling_2021, @anagnostou_facs-charm_2022 and @johnson_cost_2021 - but this criteria also required "package versions" which were uncommon.
-However, focusing on the READMEs, in each of these cases it was great to have these, guiding on how to run the scripts, or on what each folder/file in the repository is.
+**Documents (a) how code is used (b) how it relates to article (c) software, systems, packages and versions** / **Documents (a) inventory of artefacts (b) sufficient description for artefacts to be exercised** / **Artefacts are carefully documented and well-structured to the extent that reuse and repurposing is facilitated, adhering to norms and standards** / **README file with step-by-step instructions to run analysis**:
 
-**Artefacts are carefully documented (more than sufficient - i.e.
-to the extent that reuse and repurposing is facilitated - e.g.
-changing parameters, reusing for own purpose)**: In @anagnostou_facs-charm_2022, they include a file `CHARM_INFO.md` alongside their README which walks through the input parameters for the model.
+* All really handy. In cases where this was not met, this was often related to having quite a busy/cluttered repository which was confusing to navigate, with minimal documentation.
+* In @anagnostou_facs-charm_2022, they include a file `CHARM_INFO.md` alongside their README which walks through the input parameters for the model.
 I didn't need to change any of these for the reproduction, but would imagine this is to be very helpful if someone were to reuse the model.
-
-**Artefacts are clearly documented and accompanied by a README file with step-by-step instructions on how to reproduce results in the manuscript**: Whilst this was true for @anagnostou_facs-charm_2022, it should be noted that this was a very simple example, just requiring to run one script which quickly reproduces everything!
+* Only three studies had any documentation - READMEs for @kim_modelling_2021, @anagnostou_facs-charm_2022 and @johnson_cost_2021.
+However, focusing on the READMEs, in each of these cases it was great to have these, guiding on how to run the scripts, or on what each folder/file in the repository is - although one didn't have step-by-step instructions, as requested.
+* Whilst @anagnostou_facs-charm_2022 did meet criteria, it should be noted that this was a very simple example, just requiring to run one script which quickly reproduces everything!
 I had been a bit uncertain on it, since the README doesn’t explicitly say how to make the figure, but it does provide instructions that lead you to regenerate the exact model results from the paper, and so I feel that it does provide instructions to reproduce results sufficiently (although would be more complete to include instructions for figure too - so if it weren’t a yes/no decision for badges, I would’ve said this was partially met).
@@
 
-**Scripts can be successfully executed**: This is true, though I did allow troubleshooting, which sometimes took a long while.
+**Dependencies (e.g. package versions) stated**: Important and impacts analysis, takes a while to work out otherwise.
+
+**Clear how output of analysis corresponds to article**: This is handy - clear link between analysis and items in paper.
+
+**Scripts can be successfully executed**: This is true, though I did allow troubleshooting.
 Hence, the importance of e.g.
@@
 
-**Independent party regenerated results using the authors research artefacts**: On the [reproduction page](reproduction.qmd), I reflected (where possible) on what I thought the primary reasons were, for cases where I didn't manage to reproduce results despite troubleshooting.
-
-**Reproduced within approximately one hour (excluding compute time)**: In this study, this was pretty much impossible, since I followed a protocol of first setting up, reading the article, and so on.
+**Reproduced results (assuming (a) acceptably similar (b) reasonable time frame (c) only minor troubleshooting)**: On the [reproduction page](reproduction.qmd), I reflected (where possible) on what I thought the primary reasons were, for cases where I didn't manage to reproduce results despite troubleshooting.
 It is worth noting however that there were two studies that were quite quick to run, which I reflect about on the [reproduction page](reproduction.qmd).
@@
 | **“Open objects” badges** |
-| **NISO "Open Research Objects (ORO)"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier<br>• Includes an open licence | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
-| **NISO "Open Research Objects - All (ORO-A)"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier<br>• Includes an open licence<br>• Complete set of materials shared (as would be needed to fully reproduce article) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
-| **ACM "Artifacts Available"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
-| **COS "Open Code"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier<br>• Includes an open licence<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Artefacts are sufficiently documented (i.e.
-to understand how it works, to enable it to be run, including package versions) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
-| **IEEE "Code Available"**<br>• Complete set of materials shared (as would be needed to fully reproduce article) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ✅ |
+| **ACM "Artifacts Available"**<br>• Artefacts are archived in a repository that is: (a) public (b) guarantees persistence (c) gives a unique identifier (e.g. DOI) | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
+| **NISO "Open Research Objects (ORO)"**<br>• Artefacts are archived in a repository that is: (a) public (b) guarantees persistence (c) gives a unique identifier (e.g.
+DOI)<br>• Open licence | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
+| **NISO "Open Research Objects - All (ORO-A)"**<br>• Artefacts are archived in a repository that is: (a) public (b) guarantees persistence (c) gives a unique identifier (e.g.
+DOI)<br>• Open licence<br>• Complete (all relevant artefacts available) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
+| **COS "Open Code"**<br>• Artefacts are archived in a repository that is: (a) public (b) guarantees persistence (c) gives a unique identifier (e.g.
+DOI)<br>• Open licence<br>• Documents (a) how code is used (b) how it relates to article (c) software, systems, packages and versions | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
+| **IEEE "Code Available"**<br>• Complete (all relevant artefacts available) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ✅ |
 | **"Object review" badges** |
-| **ACM "Artifacts Evaluated - Functional"**<br>• Artefacts are sufficiently documented (i.e.
-to understand how it works, to enable it to be run, including package versions)<br>• Artefacts are relevant to and contribute to the article’s results<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Scripts can be successfully executed | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
-| **ACM "Artifacts Evaluated - Reusable"**<br>• Artefacts are sufficiently documented (i.e.
-to understand how it works, to enable it to be run, including package versions)<br>• Artefacts are carefully documented (more than sufficient - i.e.
-to the extent that reuse and repurposing is facilitated - e.g.
-changing parameters, reusing for own purpose)<br>• Artefacts are relevant to and contribute to the article's results<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Scripts can be successfully executed<br>• Artefacts are well structured/organised (e.g.
-to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
-| **IEEE "Code Reviewed"**<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Scripts can be successfully executed | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ✅ |
+| **ACM "Artifacts Evaluated - Functional"**<br>• Documents (a) inventory of artefacts (b) sufficient description for artefacts to be exercised<br>• Artefacts relevant to paper<br>• Complete (all relevant artefacts available)<br>• Scripts can be successfully executed | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
+| **ACM "Artifacts Evaluated - Reusable"**<br>• Documents (a) inventory of artefacts (b) sufficient description for artefacts to be exercised<br>• Artefacts relevant to paper<br>• Complete (all relevant artefacts available)<br>• Scripts can be successfully executed<br>• Artefacts are carefully documented and well-structured to the extent that reuse and repurposing is facilitated, adhering to norms and standards | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
+| **IEEE "Code Reviewed"**<br>• Complete (all relevant artefacts available)<br>• Scripts can be successfully executed | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ✅ |
 | **"Reproduced" badges** |
-| **NISO "Results Reproduced (ROR-R)"**<br>• Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ | ✅ | ❌ | ✅ |
-| **ACM "Results Reproduced"**<br>• Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ | ✅ | ❌ | ✅ |
-| **IEEE "Code Reproducible"**<br>• Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ | ✅ | ❌ | ✅ |
-| **Psychological Science "Computational Reproducibility"**<br>• Independent party regenerated results using the authors research artefacts<br>• Reproduced within approximately one hour (excluding compute time)<br>• Artefacts are well structured/organised (e.g.
-to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community)<br>• Artefacts are clearly documented and accompanied by a README file with step-by-step instructions on how to reproduce results in the manuscript | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
+| **ACM "Results Reproduced"**<br>• Reproduced results (assuming (a) acceptably similar (b) reasonable time frame (c) only minor troubleshooting) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ✅ |
+| **NISO "Results Reproduced (ROR-R)"**<br>• Reproduced results (assuming (a) acceptably similar (b) reasonable time frame (c) only minor troubleshooting) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ✅ |
+| **IEEE "Code Reproducible"**<br>• Reproduced results (assuming (a) acceptably similar (b) reasonable time frame (c) only minor troubleshooting) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ✅ |
+| **Psychological Science "Computational Reproducibility"**<br>• Reproduced results (assuming (a) acceptably similar (b) reasonable time frame (c) only minor troubleshooting)<br>• README file with step-by-step instructions to run analysis<br>• Dependencies (e.g.
+package versions) stated<br>• Clear how output of analysis corresponds to article | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
 : {tbl-colwidths="[60, 5, 5, 5, 5, 5, 5, 5, 5]"}
@@
 badges_dict = {
+  'ACM “Artifacts<br>Available”': [1, 0, 7, 0],
   'NISO “Open Research<br>Objects (ORO)”': [1, 0, 7, 0],
   'NISO “Open Research<br>Objects - All (ORO-A)”': [0, 0, 8, 0],
-  'ACM “Artifacts<br>Available”': [1, 0, 7, 0],
-  'COS “Open Code”': [0, 0, 8, 0],
+  'COS “Open Code”': [1, 0, 7, 0],
   'IEEE “Code Available”': [1, 0, 7, 0],
@@
   'IEEE “Code Reviewed”': [1, 0, 7, 0],
-  'NISO “Results<br>Reproduced (ROR-R)”': [6, 0, 2, 0],
-  'ACM “Results Reproduced”': [6, 0, 2, 0],
-  'IEEE “Code Reproducible”': [6, 0, 2, 0],
+  'ACM “Results Reproduced”': [1, 0, 7, 0],
+  'NISO “Results<br>Reproduced (ROR-R)”': [1, 0, 7, 0],
+  'IEEE “Code Reproducible”': [1, 0, 7, 0],
   'Psychological Science<br>“Computational Reproducibility”': [0, 0, 8, 0],
@@
 
-Only one study had **permanent archive (with persistent identifier)**, hence one being awarded *NISO “Open Research Objects (ORO)”* and *ACM “Artifacts Available”*.
-This was required by two other badges **as well as** sufficient documentation and/or complete set of materials.
-Since the one permanently archived study didn't meet these criteria, none were awarded the two badges: *NISO “Open Research Objects - All (ORO-A)”* or *COS “Open Code”*.
+Only one study had **permanent archive (with persistent identifier)**, hence one being awarded *NISO “Open Research Objects (ORO)”*, *ACM “Artifacts Available”* and *COS “Open Code”*.
+However, that study did not receive *NISO “Open Research Objects - All (ORO-A)”* as artefacts were not complete.
 
@@
 
-Three badges had one criteria: **reproduction of results** - and hence, several studies received these (*NISO “Results Reproduced (ROR-R)”*, *ACM “Results Reproduced”*, *IEEE “Code Reproducible”*).
-However, it's worth noting that we allowed troubleshooting (since that was how we approached the reproductions), and that some of these studies might not have received these badges, if they have any requirements that exclude troubleshooting (which is likely).
-
-The final badge *Psychological Science “Computational Reproducibility”* had several criteria, but of importance, one of those was to complete the **reproduction within an hour**.
-This was somewhat impossible in our procedures, since we read the article and set-up etc beforehand, and so none were awarded this badge.
-
+Three badges had one criteria: **reproduction of results** - but with assumptions - and only one study met this (with 100% reproduction PLUS meeting the assumptions).
 :::
@@
 
+Revisiting and redoing evaluation for badges was only 2-3 minutes per study, and have just stuck with the original evaluation timings above.
+
 ::: {.callout icon=false collapse=false}

### 2024-11-21 pages/repo_evaluation.qmd
feat(badges): create table for article

@@
 
+```{python}
+# Create dataframe of results
+col = ['fully', 'partially', 'not', 'na']
+badges_dict = {
+  'open_acm': [1, 0, 7, 0],
+  'open_niso': [1, 0, 7, 0],
+  'open_niso_all': [0, 0, 8, 0],
+  'open_cos': [1, 0, 7, 0],
+  'open_ieee': [1, 0, 7, 0],
+  'review_acm_functional': [0, 0, 8, 0],
+  'review_acm_reusable': [0, 0, 8, 0],
+  'review_ieee': [1, 0, 7, 0],
+  'reproduce_acm': [1, 0, 7, 0],
+  'reproduce_niso': [1, 0, 7, 0],
+  'reproduce_ieee': [1, 0, 7, 0],
+  'reproduce_psy': [0, 0, 8, 0],
+}
+badges_wide = pd.DataFrame(badges_dict, index=col).T
+
+# Full badge names
+badge_names = {
+    # Open objects
+    'open_acm': 'ACM “Artifacts<br>Available”',
+    'open_niso': 'NISO “Open Research<br>Objects (ORO)”',
+    'open_niso_all': 'NISO “Open Research<br>Objects - All (ORO-A)”',
+    'open_cos': 'COS “Open Code”',
+    'open_ieee': 'IEEE “Code Available”',
+    # Object review
+    'review_acm_functional': 'ACM “Artifacts<br>Evaluated - Functional”',
+    'review_acm_reusable': 'ACM “Artifacts<br>Evaluated - Reusable”',
+    'review_ieee': 'IEEE “Code Reviewed”',
+    # Results reproduced
+    'reproduce_acm': 'ACM “Results Reproduced”',
+    'reproduce_niso': 'NISO “Results<br>Reproduced (ROR-R)”',
+    'reproduce_ieee': 'IEEE “Code Reproducible”',
+    'reproduce_psy': 'Psychological Science<br>“Computational Reproducibility”'
+}
+
+# Replace with full badge names
+badges_fig = badges_wide.copy()
+badges_fig.index = badges_fig.index.map(badge_names)
+
+# Create figure
+eval_chart(badges_fig)
+```
+
 Only one study had **permanent archive (with persistent identifier)**, hence one being awarded *NISO “Open Research Objects (ORO)”*, *ACM “Artifacts Available”* and *COS “Open Code”*.
@@
 Three badges had one criteria: **reproduction of results** - but with assumptions - and only one study met this (with 100% reproduction PLUS meeting the assumptions).
+:::
+
+::: {.callout icon=false collapse=false}
+
+## Badges summary tables for the article
+
+```{python}
+# Criteria and their definitions
+criteria = {
+    'archive': 'Artefacts are archived in a repository that is: (a) public (b) guarantees persistence (c) gives a unique identifier (e.g. DOI)',
+    'licence': 'Open licence',
+    'complete': 'Complete (all relevant artefacts available)',
+    'docs1': 'Documents (a) how code is used (b) how it relates to article (c) software, systems, packages and versions',
+    'docs2': 'Documents (a) inventory of artefacts (b) sufficient description for artefacts to be exercised',
+    'relevant': 'Artefacts relevant to paper',
+    'execute': 'Scripts can be successfully executed',
+    'careful': 'Artefacts are carefully documented and well-structured to the extent that reuse and repurposing is facilitated, adhering to norms and standards',
+    'reproduce': 'Reproduced results (assuming (a) acceptably similar (b) reasonable time frame (c) only minor troubleshooting)',
+    'readme': 'README file with step-by-step instructions to run analysis',
+    'dependencies': 'Dependencies (e.g. package versions) stated',
+    'correspond': 'Clear how output of analysis corresponds to article'
+}
+
+# Criteria required by each badge
+badges = {
+    # Open objects
+    'open_acm': ['archive'],
+    'open_niso': ['archive', 'licence'],
+    'open_niso_all': ['archive', 'licence', 'complete'],
+    'open_cos': ['archive', 'licence', 'docs1'],
+    'open_ieee': ['complete'],
+    # Object review
+    'review_acm_functional': ['docs2', 'relevant', 'complete', 'execute'],
+    'review_acm_reusable': ['docs2', 'relevant', 'complete', 'execute', 'careful'],
+    'review_ieee': ['complete', 'execute'],
+    # Results reproduced
+    'reproduce_acm': ['reproduce'],
+    'reproduce_niso': ['reproduce'],
+    'reproduce_ieee': ['reproduce'],
+    'reproduce_psy': ['reproduce', 'readme', 'dependencies', 'correspond']
+}
+
+# Find proportion fully met, then use to make "met criteria" column
+badges_table = badges_wide.copy()
+badges_table['percent'] = round((badges_table['fully'] / 8)*100, 2)
+badges_table['met_criteria'] = badges_table['fully'].astype(str) + '/8 (' + badges_table['percent'].astype(str) + '%)'
+
+# Create a column with criteria for each badge
+badges_table['criteria'] = badges_table.index.map(
+    lambda badge: '<br>'.join(
+        f"• {criteria[crit]}" for crit in badges[badge]
+    )
+)
+
+# Replace with full badge names, then filter and relabel columns
+badges_table.index = badges_table.index.map(badge_names)
+badges_table.index.name = 'Badge'
+badges_table = badges_table[['criteria', 'met_criteria']].rename(
+  columns={'criteria': 'Criteria', 'met_criteria': 'Studies that met criteria'}
+)
+badges_table
+```
+
 :::

### 2024-11-21 pages/repo_evaluation.qmd
chore(badges): save to csv

@@
 )
+
+# Save to CSV and show
+badges_table.to_csv('../data/badges_table.csv')
 badges_table

### 2024-11-28 pages/paper_evaluation.qmd
feat(images): making eval_charts (a) save to png, (b) colourblind friendly, (c) percentage overlaid

@@
 
+```{python}
+# Imports and functions
+import pandas as pd
+import plotly.express as px
+import plotly.express as px
+import plotly.io as pio
+from functions import eval_chart, plot_scatter, calculate_scores
+```
+
 ## Summary
@@
 ```{python}
-import pandas as pd
-import plotly.express as px
-from functions import eval_chart, plot_scatter, calculate_scores
-
 # Create dataframe of results
@@
 
-eval_chart(stress_wide)
+eval_chart(stress_wide).show(config={'displayModeBar': False})
 ```
@@
 
-eval_chart(ispor_wide)
+eval_chart(ispor_wide).show(config={'displayModeBar': False})
 ```
@@
 
-eval_chart(criteria_wide)
+# Create figure
+stress_chart = eval_chart(criteria_wide)
+
+# Display figure
+stress_chart.show(config={'displayModeBar': False})
+
+# Save figure as 300DPI static image for use in article
+pio.write_image(stress_chart, '../images/stress_criteria.png',
+                width=2.8*300, height=2.5*300, scale=1)
 ```
@@
 
-eval_chart(criteria_wide)
+# Create figure
+ispor_chart = eval_chart(criteria_wide)
+
+# Display figure
+ispor_chart.show(config={'displayModeBar': False})
+
+# Save figure as 300DPI static image for use in article
+pio.write_image(ispor_chart, '../images/ispor_criteria.png',
+                width=2.5*300, height=2*300, scale=1)
+
 ```

### 2024-11-28 pages/repo_evaluation.qmd
feat(images): making eval_charts (a) save to png, (b) colourblind friendly, (c) percentage overlaid

@@
 import plotly.express as px
+import plotly.io as pio
 import pandas as pd
@@
 
-eval_chart(criteria_wide)
+eval_chart(criteria_wide).show(config={'displayModeBar': False})
 ```
@@
 
-eval_chart(badge_wide)
+eval_chart(badge_wide).show(config={'displayModeBar': False})
 ```
@@
 
-eval_chart(essential_wide)
+eval_chart(essential_wide).show(config={'displayModeBar': False})
 ```
@@
 
-eval_chart(optional_wide)
+eval_chart(optional_wide).show(config={'displayModeBar': False})
 ```
@@
 
-eval_chart(badges_wide)
+eval_chart(badges_wide).show(config={'displayModeBar': False})
 ```
@@
 # Create figure
-eval_chart(badges_fig)
+eval_chart(badges_fig).show(config={'displayModeBar': False})
 ```
@@
 
-eval_chart(stars_wide)
+# Create figure
+stars_chart = eval_chart(stars_wide)
+
+# Display figure
+stars_chart.show(config={'displayModeBar': False})
+
+# Save figure as 300DPI static image for use in article
+pio.write_image(stars_chart, '../images/stars_criteria.png',
+                width=2.5*300, height=1.8*300, scale=1)
 ```

### 2024-11-28 pages/functions.py

@@ -165,17 +165,18 @@ def eval_chart(df):
         x='percent',
         y='guideline',
         color='result',
-        color_discrete_map={'fully': '#06a94d',
+        color_discrete_map={'fully': '#56ae77',
                             'partially': '#ffd68c',
                             'not': '#ff9999',
-                            'na': '#d1dcea'},
+                            'na': '#f4f7fa'},
         orientation='h',
         hover_data={
             'count': True,
             'percent': False,
             'percentage': True,
             'guideline': False,
-            'result': False})
+            'result': False},
+        text='percentage')
 
     # Amend x axis label and ticks
     fig.update_layout(xaxis=dict(
@@ -197,8 +198,7 @@ def eval_chart(df):
                 'not': 'Not met', 'na': 'Not applicable'}
     fig.for_each_trace(lambda t: t.update(name=newnames[t.name]))
 
-    # Show without toolbar
-    fig.show(config={'displayModeBar': False})
+    return fig
 
 
 def min_hour(time):

### 2024-11-28 pages/paper_evaluation.qmd
fix(images): modified scale so images are 300 dpi at 14cm width

@@
 pio.write_image(stress_chart, '../images/stress_criteria.png',
-                width=2.8*300, height=2.5*300, scale=1)
+                width=2.8*300, height=2.5*300, scale=1.97)
 ```
@@
 pio.write_image(ispor_chart, '../images/ispor_criteria.png',
-                width=2.5*300, height=2*300, scale=1)
+                width=2.5*300, height=2*300, scale=2.2)
 

### 2024-11-28 pages/repo_evaluation.qmd
fix(images): modified scale so images are 300 dpi at 14cm width

@@
 pio.write_image(stars_chart, '../images/stars_criteria.png',
-                width=2.5*300, height=1.8*300, scale=1)
+                width=2.5*300, height=1.8*300, scale=2.2)
 ```

### 2024-12-03 pages/paper_evaluation.qmd
docs(various): tweaks to images (white space, labels), protocol (organisation) and references.bib

@@
 
+# Reduce white space
+stress_chart.update_layout(
+    margin=dict(l=0, r=0, t=10, b=0)
+)
+
 # Save figure as 300DPI static image for use in article
@@
   '10 Sensitivity': [4, 0, 3, 1],
-  '11 Face val.': [1, 0, 7, 0],
-  '12 Cross val.': [2, 0, 5, 1],
-  '13 External val.': [2, 0, 3, 3],
-  '14 Predictive val.': [0, 0, 1, 7],
+  '11 Face validity': [1, 0, 7, 0],
+  '12 Cross validity': [2, 0, 5, 1],
+  '13 External validity': [2, 0, 3, 3],
+  '14 Predictive validity': [0, 0, 1, 7],
   '15 Generalisability': [5, 1, 2, 0],
@@
 ispor_chart.show(config={'displayModeBar': False})
+
+# Reduce white space
+ispor_chart.update_layout(
+    margin=dict(l=0, r=0, t=10, b=0)
+)
 

### 2024-12-03 pages/protocol.qmd
docs(various): tweaks to images (white space, labels), protocol (organisation) and references.bib

@@
         * Institute of Electrical and Electronics Engineers (IEEE) (@institute_of_electrical_and_electronics_engineers_ieee_about_2024)
-        * Psychological Science (@hardwicke_transparency_2023 and @association_for_psychological_science_aps_psychological_2024)
+        * Psychological Science (@hardwicke_transparency_2024 and @association_for_psychological_science_aps_psychological_2024)
     * Recommendations from the pilot STARS framework for the sharing of code and associated materials from discrete-event simulation models (@monks_towards_2024).
@@
 
-There was one major change from the protocol...
+There were two main changes from the protocol...
 
@@
 |
-
-There were also some minor changes, which are explained below...
-
-| Deviation | Description and reason for the change |
-| --- | --- |
 | Using the latest software packages | In the protocol, I had planned that - if no versions were provided  we select a version of the software and each package that is closest to but still prior to the date of the code archive or paper publication.
@@
 As such, I used the latest versions of R and each package for those studies |
+
+There were also some very minor changes, which are explained below...
+
+| Deviation | Description and reason for the change |
+| --- | --- |
 | Using percentage difference in results to help decided reproduction success | This is not particularly deviation, as I did explore this, but I ultimately found it very unhelpful, as the percentage difference could be greatly impacted by scale (for example, 0.1 vs 0.2 would appear much greater than 3 vs 4, but the actual meaning of these differences might be similar (e.g.

### 2024-12-03 pages/paper_evaluation.qmd
feat(table): generate table of applicable criteria for stars/reporting

@@
 import plotly.io as pio
-from functions import eval_chart, plot_scatter, calculate_scores
+from functions import (eval_chart, plot_scatter, calculate_scores,
+                       calculate_percentage, extract_reproduced)
 ```
@@
 stress_dict = {
-  'Shoaib and<br>Ramamohan 2021': [17, 6, 1, 0],
-  'Huang et al. 2019': [14, 5, 4, 1],
-  'Lim et al. 2020': [15, 3, 3, 3],
-  'Kim et al. 2021': [15, 5, 2, 2],
-  'Anagnostou et al. 2022': [14, 2, 5, 3],
-  'Johnson et al. 2021': [16, 1, 2, 5],
-  'Hernandez et al. 2015': [18, 2, 3, 1],
-  'Wood et al. 2021': [22, 2, 0, 0]
+  'Shoaib and<br>Ramamohan 2021 (16/17)': [17, 6, 1, 0],
+  'Huang et al. 2019 (3/8)': [14, 5, 4, 1],
+  'Lim et al. 2020 (9/9)': [15, 3, 3, 3],
+  'Kim et al. 2021 (10/10)': [15, 5, 2, 2],
+  'Anagnostou et al. 2022 (1/1)': [14, 2, 5, 3],
+  'Johnson et al. 2021 (4/5)': [16, 1, 2, 5],
+  'Hernandez et al. 2015 (1/8)': [18, 2, 3, 1],
+  'Wood et al. 2021 (5/5)': [22, 2, 0, 0]
 }
@@
 ispor_dict = {
-  'Shoaib and<br>Ramamohan 2021': [11, 2, 2, 3],
-  'Huang et al. 2019': [7, 2, 7, 2],
-  'Lim et al. 2020': [12, 0, 4, 2],
-  'Kim et al. 2021': [12, 0, 5, 1],
-  'Anagnostou et al. 2022': [8, 3, 4, 3],
-  'Johnson et al. 2021': [15, 0, 2, 1],
-  'Hernandez et al. 2015': [10, 0, 7, 1],
-  'Wood et al. 2021': [13, 0, 4, 1]
+  'Shoaib and<br>Ramamohan 2021 (16/17)': [11, 2, 2, 3],
+  'Huang et al. 2019 (3/8)': [7, 2, 7, 2],
+  'Lim et al. 2020 (9/9)': [12, 0, 4, 2],
+  'Kim et al. 2021 (10/10)': [12, 0, 5, 1],
+  'Anagnostou et al. 2022 (1/1)': [8, 3, 4, 3],
+  'Johnson et al. 2021 (4/5)': [15, 0, 2, 1],
+  'Hernandez et al. 2015 (1/8)': [10, 0, 7, 1],
+  'Wood et al. 2021 (5/5)': [13, 0, 4, 1]
 }
@@
 check_reporting(ispor_wide)
+```
+
+:::
+
+::: {.callout icon=false collapse=false}
+
+## Table with proportion of applicable reporting criteria that were fully met
+
+This is part of a table used in the journal article:
+
+```{python}
+# Calculate essential and optional percentages
+report_df = pd.DataFrame({
+    'stress': calculate_percentage(stress_wide),
+    'generic': calculate_percentage(ispor_wide)
+})
+
+# Calculate percentage and items in scope
+report_df['percentage'], report_df['num'], report_df['denom'] = zip(
+  *report_df.index.to_series().apply(extract_reproduced))
+
+# Sort by percentage and then by number of items in scope
+report_df = report_df.sort_values(by=['percentage', 'denom'],
+                                  ascending=[False, False])
+
+# Create formatted column with % and n/n reproduced
+report_df['reproduction'] = report_df.apply(
+    lambda row: f"{row['percentage']}% ({row['num']}/{row['denom']})", axis=1
+)
+
+# Filter to relevant columns, save and display
+report_applicable = report_df[['reproduction', 'stress', 'generic']]
+report_applicable.to_csv('../data/applicable_report.csv')
+report_applicable
 ```

### 2024-12-03 pages/repo_evaluation.qmd
docs(various): tweaks to images (white space, labels), protocol (organisation) and references.bib
feat(table): generate table of applicable criteria for stars/reporting

@@
 import pandas as pd
-from functions import eval_chart, plot_scatter
+from functions import (eval_chart, plot_scatter,
+                       calculate_percentage, extract_reproduced)
 ```
@@
              woo = 0)
+```
+
+:::
+
+::: {.callout icon=false collapse=false}
+
+## Table with proportion of applicable STARS criteria that were fully met
+
+This is part of a table used in the journal article:
+
+```{python}
+# Calculate essential and optional percentages
+stars_df = pd.DataFrame({
+    'stars_essential': calculate_percentage(essential_wide),
+    'stars_optional': calculate_percentage(optional_wide)
+})
+
+# Calculate percentage and items in scope
+stars_df['percentage'], stars_df['num'], stars_df['denom'] = zip(
+  *stars_df.index.to_series().apply(extract_reproduced))
+
+# Sort by percentage and then by number of items in scope
+stars_df = stars_df.sort_values(by=['percentage', 'denom'],
+                                ascending=[False, False])
+
+# Create formatted column with % and n/n reproduced
+stars_df['reproduction'] = stars_df.apply(
+    lambda row: f"{row['percentage']}% ({row['num']}/{row['denom']})", axis=1
+)
+
+# Filter to relevant columns, save and display
+stars_applicable = stars_df[['reproduction', 'stars_essential', 'stars_optional']]
+stars_applicable.to_csv('../data/applicable_stars.csv')
+stars_applicable
 ```
@@
 
+# Reduce white space
+stars_chart.update_layout(
+    margin=dict(l=0, r=0, t=10, b=0)
+)
+
 # Save figure as 300DPI static image for use in article

### 2024-12-03 pages/functions.py

@@ -3,6 +3,7 @@ import numpy as np
 import pandas as pd
 from plotly import graph_objects as go
 import plotly.express as px
+import re
 
 
 def process_times(time_list, adjust=False):
@@ -407,3 +408,38 @@ def reporting_scatter(var, reporting, sho, hua, lim, kim, ana, joh, her, woo):
                       yaxis_title=ylab)
 
     return fig
+
+
+def calculate_percentage(df):
+    '''
+    Calculate of fully met criteria, out of all applicable criteria.
+
+    Parameters:
+    -----------
+    df : Dataframe containing 'fully', 'partially' and 'not' columns
+
+    Returns:
+    --------
+    Series contained calculate percentage as string rounded to int with '%' symbol.
+    '''
+    total = df[['fully', 'partially', 'not']].sum(axis=1)
+    return (df['fully'] / total * 100).round().astype(int).astype(str) + '%'
+
+
+def extract_reproduced(x):
+    '''
+    Extract count of items reproduced and total items in scope for each study,
+    and convert to percentage.
+
+    Parameters:
+    -----------
+    x : String including a format of 'X/Y' (e.g. '16/17')
+
+    Returns:
+    --------
+    Tuple containing the percentage, numerator and denominator
+    '''
+    nums = re.search(r'(\d+)/(\d+)', x)
+    num, denom = int(nums.group(1)), int(nums.group(2))
+    percentage = round(num / denom * 100, 1)
+    return percentage, num, denom

### 2024-12-03 pages/protocol.qmd
docs(protocol): tweak wording

@@
 
-These are summarised below, and deviations from the protocol are also described.
+These are summarised below, and modifications from the protocol are also described.
 
@@
 
-| Deviation | Description and reason for the change |
+| Modification | Description and reason for the change |
 | --- | --- |
@@
 
-| Deviation | Description and reason for the change |
+| Modification | Description and reason for the change |
 | --- | --- |
-| Using percentage difference in results to help decided reproduction success | This is not particularly deviation, as I did explore this, but I ultimately found it very unhelpful, as the percentage difference could be greatly impacted by scale (for example, 0.1 vs 0.2 would appear much greater than 3 vs 4, but the actual meaning of these differences might be similar (e.g.
+| Using percentage difference in results to help decided reproduction success | I did explore this, but I ultimately found it very unhelpful, as the percentage difference could be greatly impacted by scale (for example, 0.1 vs 0.2 would appear much greater than 3 vs 4, but the actual meaning of these differences might be similar (e.g.
 both might be considered a small difference) depending on the scale used and what is being compared - whilst in another context with a different scale, 0.1 vs 0.2 might actually reflect a huge difference!).

### 2024-12-03 pages/paper_evaluation.qmd
docs(quarto): address TODO and tweak 94% to 94.1%

@@
 ---
-
-<!-- TODO: Once complete, carefully go over again and check everything is correct -->
 
@@
   # Add reproduction success
-  df['reproduce'] = [94, 37.5, 100, 100, 100, 80, 12.5, 100]
+  df['reproduce'] = [94.1, 37.5, 100, 100, 100, 80, 12.5, 100]
 

### 2024-12-03 pages/reproduction.qmd
feat(reproduction): add pale grid lines
docs(quarto): address TODO and tweak 94% to 94.1%

@@
 | --- | --- | --- | --- |
-| Shoaib and Ramamohan 2022 | 17 items:<br>• 1 table<br>• 9 figures<br>• 7 in-text results | 16 out of 17 (94%) | 28h 14m |
+| Shoaib and Ramamohan 2022 | 17 items:<br>• 1 table<br>• 9 figures<br>• 7 in-text results | 16 out of 17 (94.1%) | 28h 14m |
 | Huang et al. 2019 | 8 items:<br>• 5 figures<br>• 3 in-text results | 3 out of 8 (37.5%) | 24h 10m |
@@
         '#ee6677',
-        '94% (16/17), 28h 14m',
+        '94.1% (16/17), 28h 14m',
         (5, (10, 3))
@@
 ax.legend(loc='center left', bbox_to_anchor=(1, 0.5))
+plt.grid(alpha=0.2)
 

### 2024-12-03 pages/functions.py

@@ -292,9 +292,6 @@ def calculate_scores(df):
     return df
 
 
-# TODO: Check the values used are still corrected, as there were some minor
-# amendments made to evaluations
-
 def plot_scatter(var, sho, hua, lim, kim, ana, joh, her, woo):
     '''
     Create scatter plot of variable against reproduction success, with dot size
@@ -324,7 +321,7 @@ def plot_scatter(var, sho, hua, lim, kim, ana, joh, her, woo):
     # Create data frame with columns for study, % items reproduced,
     # time (minutes) spent on reproduction, and the input variable
     df = pd.DataFrame({
-        'Shoaib and Ramamohan 2021': [94, 1694, sho],
+        'Shoaib and Ramamohan 2021': [94.1, 1694, sho],
         'Huang et al. 2019': [37.5, 1450, hua],
         'Lim et al. 2020': [100, 747, lim],
         'Kim et al. 2021': [100, 875, kim],

### 2024-12-06 pages/reproduction.qmd
feat(figure): Remove line types on time-to-reproduction figure

@@
         '#882255',
-        '100% (1/1), 2h 11m',
-        (0, (1, 1))
+        '100% (1/1), 2h 11m'
     ),
@@
         '#117733',
-        '100% (5/5), 3h 50m',
-        '--'
+        '100% (5/5), 3h 50m'
     ),
@@
         '#4477aa',
-        '100% (9/9), 12h 27m',
-        '-.'
+        '100% (9/9), 12h 27m'
     ),
@@
         '#ccbb44',
-        '100% (10/10), 14h 42m',
-        ':'
+        '100% (10/10), 14h 42m'
+    ),
+    (
+        df_sho,
+        'Shoaib and<br>Ramamohan<br>2022',
+        '#ee6677',
+        '94.1% (16/17), 28h 14m'
+    ),
+    (
+        df_joh,
+        'Johnson et<br>al. 2021',
+        '#228833',
+        '80% (4/5), 19h 49m'
+    ),
+    (
+        df_hua,
+        'Huang et<br>al. 2019',
+        '#66ccee',
+        '37.5% (3/8), 24h 10m'
     ),
@@
         '#aa3377',
-        '12.5% (1/8), 17h 56m',
-        '-'
-    ),
-    (
-        df_joh,
-        'Johnson et<br>al. 2021',
-        '#66ccee',
-        '80% (4/5), 19h 49m',
-        (0, (3, 1, 1, 1, 1, 1))
-    ),
-    (
-        df_hua,
-        'Huang et<br>al. 2019',
-        '#228833',
-        '37.5% (3/8), 24h 10m',
-        (0, (3, 3, 1, 3, 1, 3))
-    ),
-    (
-        df_sho,
-        'Shoaib and<br>Ramamohan<br>2022',
-        '#ee6677',
-        '94.1% (16/17), 28h 14m',
-        (5, (10, 3))
+        '12.5% (1/8), 17h 56m'
     )
@@
 for x in to_plot:
-    success_static(x[0], ax, x[1], x[2], ls=x[4])
+    success_static(x[0], ax, x[1], x[2])
 
@@
 for x in to_plot:
-    success_static(x[0], ax, label=x[3], colour=x[2], ls=x[4])
+    success_static(x[0], ax, label=x[3], colour=x[2])
 

### 2024-12-06 pages/functions.py

@@ -115,7 +115,7 @@ def success_interactive(times_df, fig, label, colour):
             '%{hovertext}<br>Time: %{x:.1f} hours<br>Completion: %{y:.1f}%')))
 
 
-def success_static(times_df, ax, label, colour, ls):
+def success_static(times_df, ax, label, colour):
     '''
     Create static/non-interactive plot of time-to-completion
 
@@ -129,11 +129,9 @@ def success_static(times_df, ax, label, colour, ls):
         Label for the line
     colour : string
         Colour of line
-    ls : string or tuple
-        Line style
     '''
     ax.plot(times_df['hours'], times_df['ecdf'],
-            marker='.', markevery=2, linestyle=ls,
+            marker='.', markevery=2,
             label=label.replace('<br>', '\n'), color=colour)
 
 

### 2024-12-10 pages/reflections.qmd
feat(images): making eval_charts (a) save to png, (b) colourblind friendly, (c) percentage overlaid
docs(quarto): address TODO and tweak 94% to 94.1%
docs(reflections): reorganised to match order and categories in article

@@
 
-<!-- TODO: Once complete, carefully go over again and check everything is correct -->
-
-This page describes the facilitators for each reproduction (and, conversely, the barriers to the reproduction, in their absence).
+This page describes the facilitators and barriers encountered in each reproduction, presented as a series of recommendations. These are grouped into two themes:
+
+* Recommendations to support reproduction
+* Recommendations to facilitate troubleshooting
+
 With each section, I have created a table which evaluates whether the facilitators were fully met (✅), partially met (🟡), not met (❌) or not applicable (N/A) for each study.
@@
 
-eval_chart(criteria_wide)
+eval_chart(criteria_wide).show(config={'displayModeBar': False})
 ```
 
-## Environment
+## Recommendations to support reproduction.
+
+### Set-up
 
@@
 
-## List required packages
+## Share code with an open licence
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ✅ | ❌ | ✅ | ✅ | ✅ | ❌ | ❌ |
+
+Absence of licence prevents legal reuse of code for reproduction.
+
+:::
+
+::: {.callout-note icon=false collapse=true}
+
+## Link publication to a specific version of the code
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| | | | | | ❌ | | |
+
+<!--TODO: Check if any other studies had commits after publication-->
+
+@johnson_cost_2021: Not met.
+Had commits to their GitHub repository after the publication date.
+It wasn't clear which version aligned with the publication.
+However, the most recent commits add clear README instructions to the repository.
+We decided to use the latest version of the repository, but it would have beneficial to have releases/versions/a change log that would help to outline the commit history in relation to the publication and any subsequent changes.
+
+:::
+
+::: {.callout-note icon=false collapse=true}
+
+## List required packages and versions
+
+### Packages and versions
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ❌ | 🟡 | 🟡 | 🟡 | 🟡 | 🟡 | 🟡 |
+
+### Packages
 
@@
 
-:::
-
-::: {.callout-note icon=false collapse=true}
-
-## Be aware of potential system dependencies
-
-There can also be system dependencies, which will vary between systems, and may not be obvious if researchers already have these installed.
-We identified these when setting up the docker environments (which act like "fresh installs"):
-
-* @shoaib_simulation_2021, @lim_staff_2020, @anagnostou_facs-charm_2022 - no dependencies
-* @huang_optimizing_2019, @kim_modelling_2021, @johnson_cost_2021 and @wood_value_2021 - libcurl4-openssl-dev, libssl-dev, libxml2-dev, libglpk-dev, libicu-dev - as well as `tk` for Johnson et al.
-2021
-* @hernandez_optimal_2015 - wget, build-essential, libssl-dev, libffi-dev, libbz2-dev, libreadline-dev, libsqlite3-dev, zlib1g-dev, libncurses5-dev, libgdbm-de, libnss3-dev, tk-dev, liblzma-dev, libsqlite3-dev, lzma, ca-certificates, curl, git
-
-Although it would be unreasonable for authors to be aware of and list all system dependencies, given they may not be aware of them, this does show the benefit of creating something like docker in identifying them and making note of them within the docker files.
-
-This issue was specific to (a) R studies, and (b) the study with an unsupported version of Python that required building it from source in the docker file.
-
-:::
-
-::: {.callout-note icon=false collapse=true}
-
-## Provide versions
+### Versions
 
@@
 
-## Structure of code and scripts
+### Running the model
+
+::: {.callout-tip icon=false collapse=true}
+
+## Provide code for all scenarios and/or sensitivity analyses
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ❌ | ❌ | ❌ | N/A | 🟡 | ❌ | ✅ |
+
+@shoaib_simulation_2021: Not met.
+There were several instances where it took quite a while to understand how and where to modify the code in order to run scenarios (e.g.
+no arrivals, transferring admin work, reducing doctor intervention in deliveries).
+
+@huang_optimizing_2019: Not met.
+Set up a notebook to programmatically run the model scenarios.
+It took alot of work to modify and write code that could run the scenarios, and I often made mistakes in my interpretation for the implementation of scenarios, which could be avoided if code for those scenarios was provided.
+
+@lim_staff_2020: Not met.
+Several parameters or scenarios were not incorporated in the code, and had to be added (e.g.
+with conditional logic to skip or change code run, removing hard-coding, adding parameters to existing).
+
+@kim_modelling_2021: Not met. Took alot of work to change model from for loop to function, to set all parameters as inputs (some were hard coded), and add conditional logic of scenarios when required.
+
+@anagnostou_facs-charm_2022: Not applicable. No scenarios.
+
+@johnson_cost_2021: Partially met. Has all base case scenarios, but not sensitivity analysis.
+
+@hernandez_optimal_2015: Not met. Took a while to figure out how to implement scenarios.
+
+@wood_value_2021: Fully met.
+
+**Reflections:**
+
+* Common issue
+* Time consuming and tricky to resolve
+* Tom: This is a headline. Also, links to importance of reproducible analytical pipelines (RAP) for simulation.
+
+:::
+
+::: {.callout-tip icon=false collapse=true}
+
+## Ensure model parameters are correct
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| 🟡 | ❌ | 🟡 | ✅ | ✅ | ✅ | ❌ | ✅ |
+
+@shoaib_simulation_2021: Partially met. Script is set with parameters for base configuration 1, with the exception of number of replications.
+
+@huang_optimizing_2019: Not met. The baseline model in the script did not match the baseline model (or any scenario) in the paper, so had to modify parameters.
+
+@lim_staff_2020: Partially met.
+The included parameters were corrected, but the baseline scenario included varying staff strength to 2, and the provided code only varied 4 and 6.
+I had to add some code that enabled it to run with staff strength 2 (as there were an error that occured if you tried to set that).
+
+@kim_modelling_2021: Fully met.
+
+@anagnostou_facs-charm_2022: Fully met.
+
+@johnson_cost_2021: Fully met. Base case parameters all correct.
+
+@hernandez_optimal_2015: Not met.
+As agreed with the author, this is likely the primary reason for the discrepancy in these results - they are very close, and we see similar patterns, but not reproduced.
+Unfortunately, several parameters were wrong, and although we changed those we spotted, we anticipate there could be others we hadn't spotted that might explain the remaining discrepancies.
+
+@wood_value_2021: Fully met.
+
+**Reflections:**
+
+* At least provide a script that can run the baseline model as in the paper (even if not providing the scenarios)
+* This can introduce difficulties - when some parameters are wrong, you rely on the paper to check which parameters are correct or not, but if the paper doesn't mention every single parameter (which is reasonably likely, as this includes those not varied by scenarios), then you aren't able to be sure that the model you are running is correct.
+* This can make a really big difference, and be likely cause of managing to reproduce everything v.s. nothing, if it impacts all aspects of the results.
+* Tom: I think this comes back to minimum verification as well. I think the "at least for one scenario" idea of yours is excellent.
+
+:::
+
+::: {.callout-note icon=false collapse=true}
+
+## Control randomness
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ❌ | ❌ | ✅ | ✅ | ✅ | ✅ | ✅ |
+
+@shoaib_simulation_2021: Not met.
+The lack of seeds wasn't actually a barrier to the reproduction though due to the replication number.
+I later add seeds so my results could be reproduced, and found that the ease of setting seeds with salabim was a greater facilitator to the work.
+I only had to change one or two lines of code to then get consistent results between runs (unlike other simulation software like SimPy where you have to consider the use of seeds by different sampling functions).
+Moreover, by default, salabim would have set a seed (although overridden by original authors to enable them to run replications).
+
+@huang_optimizing_2019: Not met.
+It would have been beneficial to include seeds, as there was a fair amount of variability, so with seeds I could then I could be sure that my results do not differ from the original simply due to randomness.
+
+@lim_staff_2020: Not met.
+The results obtained looked very similar to the original article, with minimal differences that I felt to be within the expected variation from the model stochasticity.
+However, if seeds had been present, we would have been able to say with certainty.
+I did not feel I needed to add seeds during the reproduction to get the same results.
+
+@kim_modelling_2021: Fully met. Included a seed, although I don't get identical results as I had to reduce number of people in simulation.
+
+@anagnostou_facs-charm_2022: Fully met.
+The authors included a random seed so the results I got were identical to the original (so no need for any subjectivity in deciding whether its similar enough, as I could perfectly reproduce).
+
+@johnson_cost_2021: Fully met. At start of script, authors `set.seed(333)`.
+
+@hernandez_optimal_2015: Fully met. This ensured consistent results between runs of the script, which was really helpful.
+
+@wood_value_2021: Fully met. Sets seed based on replication number.
+
+**Reflections:**
+
+* Depending on your model and the outputs/type of output you are looking at, the lack of seeds can have varying impacts on the appearance of your results, and can make the subjective judgement of whether results are consistent harder (if discrepancies could be attributed to not having consistent seeds or not).
+* It can be really quite simple to include seeds.
+* Over half of the studies did include seed control in their code.
+* Tom: There seems little argument against doing this.
+worth noting that commerical software does this for you and possibly explains why authors didn't do this themselves if that was their background (lack of knowledge?).
+* Tom: Note simpy is independent of any sampling mechanism.
+We could just use python's random module and set a single seed if needed (although you lose CRN) and we can setup our models so that we only need to set a single seed.
+* Tom: A key part of STARS 2.0 for reproducibility
+
+:::
+
+### Outputs
+
+::: {.callout-tip icon=false collapse=true}
+
+## Include code to calculate all required model outputs
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ✅ | ✅ |
+
+@shoaib_simulation_2021: Not met. Had to add some outputs and calculations (e.g. proportion of childbirth cases referred, standard deviation)
+
+@huang_optimizing_2019: Not met.
+It has a complicated output (standardised density of patient in queue) that I was never certain on whether I correctly calculated.
+Although it outputs the columns required to calculate it, due its complexity, I feel this was not met, as it feels like a whole new output in its own right (and not just something simple like a mean).
+
+@lim_staff_2020: Not met. The model script provided was only set up to provide results from days 7, 14 and 21. The figures require daily results, so I needed to modify the code to output that.
+
+@kim_modelling_2021: Not met. Had to write code to find aorta sizes of people with AAA-related deaths.
+
+@anagnostou_facs-charm_2022: Fully met. Although worth noting this only had one scenario/version of model and one output to reproduce.
+
+@johnson_cost_2021: Note met.
+It has an output that is in "per 1000" and, although it outputs the columns required to calculate this, I found it very tricky to work out which columns to use and how to transform them to get this output, and so feel this is not met (as feels like a seperate output, and not something simple like a mean, and as it felt so tricky to work out).
+
+@hernandez_optimal_2015: Fully met.
+
+@wood_value_2021: Fully met.
+
+**Reflections:**
+
+* Calculate and provide all the outputs required
+* Appreicate this can be a bit "ambiguous" (e.g.
+if its just plotting a mean or simple calculation, then didn't consider that here) (however, combined with other criteria, we do want them to provide code to calculate outputs, so we would want them to provide that anyway)
+* Tom: This is a headline.
+I suspect we can find supporting citations elsewhere from other fields.
+Its a reporting guideline thing too, but in natural language things can get very ambiguous still!
+Would be good to make that point as well I think.
+
+:::
 
@@
 
-## Model is provided in a "runnable" format
+## Include code to generate the tables, figures and other reported results
+
+### Summary
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ❌ | 🟡 | ❌ | ❌ | 🟡 | 🟡 | ✅ |
+
+### Provide code to process results into tables
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | N/A | 🟡 | ❌ | N/A | ❌ | ❌ | ✅ |
+
+@shoaib_simulation_2021: Not met.
+
+@huang_optimizing_2019: Not applicable. No tables in scope.
+
+@lim_staff_2020: Partially met.
+It outputs the results in a similar structure to the paper (like a section of a table).
+However, it doesn't have the full code to produce a table outright, for any of the tables, so additional processing still required.
+
+@kim_modelling_2021: Not met.
+Had to write code to generate tables, which included correctly implementing calculation of excess e.g.
+deaths, scaling to population size, and identify which columns provide the operation outcomes.
+
+@anagnostou_facs-charm_2022: Not applicable. No tables in scope.
+
+@johnson_cost_2021: Not met. Had to write code to generate tables, which took me a while as I got confused over thinks like which tables / columns / scenarios to use.
+
+@hernandez_optimal_2015: Not met.
+
+@wood_value_2021: Fully met.
+
+**Reflections:**
+
+* It can take a bit of time to do this processing, and it can be tricky/confusing to do correctly, so very handy for it to be provided.
+* Common issue.
+
+### Provide code to process results into figures
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ❌ | ❌ | ❌ | ❌ | 🟡 | 🟡 | ✅ |
+
+@shoaib_simulation_2021: Not met.
+
+@huang_optimizing_2019: Not met.
+Had to write code from scratch.
+For one of the figures, it would have been handy if informed that plot was produced by a simmer function (as didn’t initially realise this).
+It also took a bit of time for me to work out how to transform the figure axes as this was not mentioned in the paper (and no code was provided for these).
+It was also unclear and a bit tricky to work out how to standardise the density in the figures (since it is only described in the text and no formula/calculations are provided there or in the code).
+
+@lim_staff_2020, @kim_modelling_2021 and @anagnostou_facs-charm_2022: Not met. However, the simplicity and repetition of the figures was handy.
+
+@johnson_cost_2021: Partially met.
+For Figure 3, most of the required code for the figure was provided, which was super helpful.
+However, this wasn't complete, and for all others figures, I had to start from scratch writing the code.
+
+@hernandez_optimal_2015: Partially met.
+Provides a few example `ggplot`s, but these are not all the plots, nor exactly matching article, nor including any of the pre-processing required before the plots, and so could only serve as a starting point (though that was still really handy).
+
+@wood_value_2021: Fully met. Figures match article, with one minor exception that I had to add smoothing to the lines on one of the figures.
+
+**Reflections:**
+
+* It can take a bit of time to do this processing, particularly if the figure involves any transformations (and less so if the figure is simple), so very handy for it to be provided.
+* Also, handy if the full code can be provided for all figures (although partial code is more helpful than none at all).
+* Common issue.
+
+### Provide code to calculate in-text results
+
+By "in-text results", I am referred to results that are mentioned in the text but not included in/cannot be deduced from any of the tables or figures.
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ❌ | N/A | ❌ | N/A | N/A | N/A | N/A |
+
+@shoaib_simulation_2021, @huang_optimizing_2019, @kim_modelling_2021: Not met.
+
+@lim_staff_2020, @anagnostou_facs-charm_2022, @johnson_cost_2021, @hernandez_optimal_2015, @wood_value_2021: Not applicable (no in-text results).
+
+**Reflections:**
+
+* Provide code to calculate in-text results
+* Universal issue, for those with in-text results not otherwise captured in tables and figures
+
+:::
+
+## Recommendations to support troubleshooting and reuse
+
+### Design
+
+::: {.callout-warning icon=false collapse=true}
+
+## Separate model code from applications
 
@@
 
-## Model is designed to be run programmatically (i.e. can run model with different parameters without needing to change the model code)
-
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ |
-
-@shoaib_simulation_2021: Not met.
-The model is set up as classes and run using a function.
-However, it is not designed to allow any variation in inputs.
-Everything uses default inputs, and it designed in such a way that - if you wish to vary model parameters - you need to directly change these in the script itself.
-
-@huang_optimizing_2019: Fully met. Model was set up as a function, with many of the required parameters already set as "changeable" inputs to that function.
-
-@lim_staff_2020: Fully met.
-The model is created from a series of functions and run with a for loop that iterates through different parameters.
-As such, the model is able to be run programmatically (within that for loop, which varied e.g.
-staff per shift and so on and re-ran the model).
-
-@kim_modelling_2021: Fully met. Each scenario is an R script which states different parameters and then calls functions to run model.
-
-@anagnostou_facs-charm_2022: Fully met. Change inputs in input `.csv` files.
-
-@johnson_cost_2021: Fully met. Creates a list of `input` which are then used by a `run()` function.
-
-@hernandez_optimal_2015: Fully met. Model created from classes, which accept some inputs and can run the model.
-
-@wood_value_2021: Fully met. Changes inputs to run all scenarios from a single `.R` file.
-
-**Reflections:**
-
-* Design model so that you can re-run it with different parameters without needing to make changes to the model code itself.
-    * This allows you to run multiple versions of the model with the same script.
-    * It also reduces the likelihood of missing errors (e.g. if miss changing an input parameter somewhere, or input the wrong parameters and don't realise).
-* This was an uncommon issue.
-* Note, this just refers to the basic set-up, with items below like hard coding parameters also being very important in this context.
-
-:::
-
-::: {.callout-warning icon=false collapse=true}
-
-## Don't hard code parameters that you will want to change for scenario analyses
+## Avoid hard-coded parameters
+
+Don't hard code parameters that you will want to change for scenario analyses
 
@@
 
-## Use relative file paths
-
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ✅ | N/A | N/A | ✅ | ✅ | N/A | ✅ | ✅ |
-
-@shoaib_simulation_2021: Fully met. Just provides file path, so file is saved into current/run directory.
-
-@huang_optimizing_2019: Not applicable. All inputs defined within script. Outputs were not saved to file/s.
-
-@lim_staff_2020: Not applicable. All inputs defined within script. Outputs were not saved to file/s.
-
-@kim_modelling_2021: Fully met. Uses relative file paths for sourcing model and input parameters (gets current directory, then navigates from there).
-
-@anagnostou_facs-charm_2022: Fully met. Uses relative imports of local code files.
-
-@johnson_cost_2021: Not applicable.
-All inputs defined within script.
-Outputs are not specifically saved to a file (just that the .md and image files were automatically saved when the .Rmd file was knit).
-EpicR is package import.
-
-@hernandez_optimal_2015: Fully met. Creates folder in current working directory based on date/time to store results.
-
-@wood_value_2021: Fully met.
-Although I then changed things a bit as reorganised repository and prefer not to work with `setwd()`, these were set up in such a way that it would be really easy to correct file path, just by setting working directory at start of script.
-
-**Reflections:**
-
-* This was not an issue for any studies - but included to note this was a "facilitator", as would have needed to amend if they weren't (and Tom noted that this is a common problem that he runs into elsewhere).
-
-:::
-
-::: {.callout-warning icon=false collapse=true}
-
-## Avoid large amounts of code duplication
+## Minimise code duplication
 
@@
 
+### Clarity
+
 ::: {.callout-warning icon=false collapse=true}
 
-## Include sufficient comments in the code
+## Comment sufficiently
 
@@
 
-## Run time and memory usage
+::: {.callout-caution icon=false collapse=true}
+
+## Ensure clarity and consistency in the model results tables
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ✅ | ✅ | ❌ | ✅ | ❌ | ✅ | ✅ |
+
+@shoaib_simulation_2021: Not met.
+There were two alternative results spreadsheets with some duplicate metrics but sometimes differing results between them, which made it a bit confusing to work out what to use.
+
+@huang_optimizing_2019, @lim_staff_2020, and @anagnostou_facs-charm_2022: Fully met. Didn't experience issues interpreting the contents of the output table/s.
+
+@kim_modelling_2021: Not met.
+It took me a little while to work out what surgery columns I needed, and to realise I needed to combine two of them.
+This required looking at what inputs genreated this, and referring to a input data dictionary.
+
+@johnson_cost_2021: Not met. I had mistakes and confusion figuring out which results tables I needed, which columns to use, and which scenarios to use from the tables.
+
+@hernandez_optimal_2015: Fully met. Straightforward with key information provided.
+
+@wood_value_2021: Fully met. I didn't need to work with the output tables, but from looking at them now, they make sense.
+
+**Reflections:**
+
+* Don't provide alternative results for the same metrics
+* Make it clear what each colum/category in the results table means, if it might not be immediately clear.
+* Make differences between seperate results tables clear.
+* Tom: In a RAP for simulation world we have a env + model + script that gets you to the exact results table you see in the paper and this isn't a problem (although more time consuiming to setup).
+
+:::
 
@@
 
-## Quicker models are easier to work with
-
-I have not evaluated like as a criteria, as a long run time is not inherently a bad thing.
-However, I definitely found that the run time of models had a big impact on how easy it was to reproduce results as longer run times meant it was tricky (or even impossible) to run in the first place, or tricky to re-run.
-
+## Include run instructions
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ❌ | ❌ | 🟡 | ✅ | ✅ | ❌ | ❌ |
+
+@shoaib_simulation_2021: Not met. No instructions, although is just a single script that you run.
+
+@huang_optimizing_2019: Not met. Not provided in runnable form but, regardless, no instructions for running it as it is provided (as a web application - i.e. no info on how to get that running).
+
+@lim_staff_2020: Not met. No instructions, although is just a single script that you run.
+
+@kim_modelling_2021: Partially met. README tells you which folder has the scripts you need, although nothing further. Although all you need to do is run them.
+
+@anagnostou_facs-charm_2022: Fully met. Clear README with instructions on how to run the model was really helpful.
+
+@johnson_cost_2021: Fully met. README has mini description of model and clear instructions on how to install and run the model.
+
+@hernandez_optimal_2015: Not met.
+
+@wood_value_2021: Not met. No instructions, although it was fairly self explanatory (single script `master.R` to run, then processing scripts named after items in article e.g. `fig7.R`).
+
+**Reflections:**
+
+* Even if as simple as running a script, include instructions on how to do so
+* In simpler projects (e.g. single script), this can be less of a problem.
+* Common issue
+* Tom: Evidence for STARS essential component of minimum documentation.
+
+:::
+
+::: {.callout-important icon=false collapse=true}
+
+## State run times and machine specifications
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| 🟡 | ❌ | 🟡 | ❌ | ❌ | 🟡 | 🟡 | 🟡 |
+
+### State run time
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ✅ | ❌ | ❌ | ❌ | ❌ | ✅ | 🟡 | 🟡 |
+
+@shoaib_simulation_2021: Fully met. Run time stated in paper (but not repository).
+
+@huang_optimizing_2019: Not met.
+
+@lim_staff_2020: Not met.
+
+@kim_modelling_2021: Not met. A prior paper describing the model development mentions the run time, but not the current paper or repository, so this is easily missed.
+
+@anagnostou_facs-charm_2022: Not met!
+Although it only took seconds, you could argue that stating this is still important if there were some error that made it look like the model were running continuously (e.g.
+stuck in a loop) - and as it helps someone identify that they are able to run it on their machine
+
+@johnson_cost_2021: Fully met.
+In the README, they state the the run time with 100 million agents is 16 hours, which was very handy to know, as I then just got stuck in running with fewer agents while troubleshooting.
+
+@hernandez_optimal_2015: Partially met.
+Some of the run times are mentioned in the paper, but not all, although this did help indicate that we would anticipate other s scenarios to similarly take hours to run.
+
+@wood_value_2021: Partially met. In the paper, they state that it takes less than five minutes for each scenario, but this feels like half the picture, given the total run time was 48 hours.
+
+**Reflections:**
+
+* For long models with no statement, it can take a while to realise that it's not an error in the code or anything, but actually just a long run time!
+And hard to know how long to expect, and whether it is without the capacities of your machine and so on.
+* Ideally include statement of run time in repository as well as paper.
+* Ideally include run time of all components of analysis (e.g. all scenarios).
+* Common issue.
+* Tom: This supports the inclusion of section 5.4 in the STRESS-DES guidelines
+    * Response: But think it is also important that this is in the repository itself, and not just the paper.
+
+### State machine specification
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ❌ | ✅ | ❌ | ❌ | ❌ | ❌ | ❌ |
+
+Regarding the one that did describe it:
+
+* @lim_staff_2020: Describe in article ("desktop computer (Intel Core i5 3.5 GHz, 8 GB RAM)")
+
+### Computationally expensive models
+
+Regarding whether models were computationally expensive...
+
+* @shoaib_simulation_2021, @huang_optimizing_2019, and @lim_staff_2020, @anagnostou_facs-charm_2022: No issues
+* @kim_modelling_2021: Unable to run on my machine (`serial` took too long to run (would have to leave laptop on for many many hours which isn't feasible), and `parallel` was too computationally expensive and crashed the machine (with the original number of people)).
+This is not mentioned in the repository or paper, but only referred to in a prior publication.
+Would've been handy if it included suggestions like reducing number of people and so on (which is what I had to do to feasibly run it).
+* @johnson_cost_2021: It becomes more computationally expensive if try to run lots at once in simultaneous terminals.
+Didn't try running one on local machine with full parameter due to long run time making it infeasible, but knowing my system specs, it should have been able to if did.
+* @hernandez_optimal_2015: This had long run times but I don't know if it was computationally expensive or not - I just know that I didn't run into any issues (but I didn't record memory usage, so its possible a lower-specced machine might).
+* @wood_value_2021: Not applicable. As stated in their prior paper, the model is constrained by processing time, not computer memory.
+
+**Reflections:**
+
+* Some models are so computationally expensive that it may be simply impossible to run it a feasible length of time without a high powered machine.
+* Handy to mention memory requirements so someone with lower spec machine can ensure they would be able to run it.
+* If a model is computationally expensive, it would be good to provide suggested alternatives that allow it to be run on lower spec machines
+* Not a common problem - only relevant to computationally expensive models
+* Tom: Agree it makes sense to report this, and is captured in reporting guidelines like STRESS-DES.
+
+:::
+
+### Functionality
+
+::: {.callout-important icon=false collapse=true}
+
+## Optimise model run time
+
+The run time of models had a big impact on how easy it was to reproduce results as longer run times meant it was tricky (or even impossible) to run in the first place, or tricky to re-run.
 The studies where I made adjustments were:
@@
 
-::: {.callout-important icon=false collapse=true}
-
-## For slow models, state the expected run time
-
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ✅ | ❌ | ❌ | ❌ | N/A | ✅ | 🟡 | 🟡 |
-
-@shoaib_simulation_2021: Fully met. Run time stated in paper (but not repository).
-
-@huang_optimizing_2019: Not met.
-
-@lim_staff_2020: Not met.
-
-@kim_modelling_2021: Not met. A prior paper describing the model development mentions the run time, but not the current paper or repository, so this is easily missed.
-
-@anagnostou_facs-charm_2022: Not applicable.
-Very quick!
-Seconds!
-So not particularly relevant - although, you could argue, potentially still important if there were some error that made it look like the model were running continuously (e.g.
-stuck in a loop) - although this is relatively unlikely.
-
-@johnson_cost_2021: Fully met.
-In the README, they state the the run time with 100 million agents is 16 hours, which was very handy to know, as I then just got stuck in running with fewer agents while troubleshooting.
-
-@hernandez_optimal_2015: Partially met.
-Some of the run times are mentioned in the paper, but not all, although this did help indicate that we would anticipate other s scenarios to similarly take hours to run.
-
-@wood_value_2021: Partially met. In the paper, they state that it takes less than five minutes for each scenario, but this feels like half the picture, given the total run time was 48 hours.
-
-**Reflections:**
-
-* For long models with no statement, it can take a while to realise that it's not an error in the code or anything, but actually just a long run time!
-And hard to know how long to expect, and whether it is without the capacities of your machine and so on.
-* Ideally include statement of run time in repository as well as paper.
-* Ideally include run time of all components of analysis (e.g. all scenarios).
-* Common issue.
-* Tom: This supports the inclusion of section 5.4 in the STRESS-DES guidelines
-    * Response: But think it is also important that this is in the repository itself, and not just the paper.
-
-:::
-
-::: {.callout-important icon=false collapse=true}
-
-## For computationally expensive models, state memory usage and provide alternatives for lower spec machines
-
-As I felt this was relatively subjective, as depending on what I felt to be "computationally expensive", as I didn't record the memory usage of all models, it felt unfair to do this as a checklist, and so have just informally noted below:
-
-* @shoaib_simulation_2021, @huang_optimizing_2019, and @lim_staff_2020: Not applicable. Didn't find it to be too computationally expensive for my machine.
-* @kim_modelling_2021: Unable to run on my machine (`serial` took too long to run (would have to leave laptop on for many many hours which isn't feasible), and `parallel` was too computationally expensive and crashed the machine (with the original number of people)).
-This is not mentioned in the repository or paper, but only referred to in a prior publication.
-Would've been handy if it included suggestions like reducing number of people and so on (which is what I had to do to feasibly run it).
-* @anagnostou_facs-charm_2022: Not applicable. Runs in seconds.
-* @johnson_cost_2021: It becomes more computationally expensive if try to run lots at once in simultaneous terminals.
-Didn't try running one on local machine with full parameter due to long run time making it infeasible, but knowing my system specs, it should have been able to if did.
-* @hernandez_optimal_2015: This had long run times but I don't know if it was computationally expensive or not - I just know that I didn't run into any issues (but I didn't record memory usage, so its possible a lower-specced machine might).
-* @wood_value_2021: Not applicable. As stated in their prior paper, the model is constrained by processing time, not computer memory.
-
-**Reflections:**
-
-* Some models are so computationally expensive that it may be simply impossible to run it a feasible length of time without a high powered machine.
-* Handy to mention memory requirements so someone with lower spec machine can ensure they would be able to run it.
-* If a model is computationally expensive, it would be good to provide suggested alternatives that allow it to be run on lower spec machines
-* Not a common problem - only relevant to computationally expensive models
-* Tom: Agree it makes sense to report this, and is captured in reporting guidelines like STRESS-DES.
-
-:::
-
-## Parameters, scenarios and outputs
-
-::: {.callout-tip icon=false collapse=true}
-
-## Provide code for all scenarios
-
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | ❌ | N/A | 🟡 | ❌ | ✅ |
-
-@shoaib_simulation_2021: Not met.
-There were several instances where it took quite a while to understand how and where to modify the code in order to run scenarios (e.g.
-no arrivals, transferring admin work, reducing doctor intervention in deliveries).
-
-@huang_optimizing_2019: Not met.
-Set up a notebook to programmatically run the model scenarios.
-It took alot of work to modify and write code that could run the scenarios, and I often made mistakes in my interpretation for the implementation of scenarios, which could be avoided if code for those scenarios was provided.
-
-@lim_staff_2020: Not met.
-Several parameters or scenarios were not incorporated in the code, and had to be added (e.g.
-with conditional logic to skip or change code run, removing hard-coding, adding parameters to existing).
-
-@kim_modelling_2021: Not met. Took alot of work to change model from for loop to function, to set all parameters as inputs (some were hard coded), and add conditional logic of scenarios when required.
-
-@anagnostou_facs-charm_2022: Not applicable. No scenarios.
-
-@johnson_cost_2021: Partially met. Has all base case scenarios, but not sensitivity analysis.
-
-@hernandez_optimal_2015: Not met. Took a while to figure out how to implement scenarios.
-
-@wood_value_2021: Fully met.
-
-**Reflections:**
-
-* Common issue
-* Time consuming and tricky to resolve
-* Tom: This is a headline. Also, links to importance of reproducible analytical pipelines (RAP) for simulation.
-
-:::
-
-::: {.callout-tip icon=false collapse=true}
-
-## All the required outputs are calculated/provided
-
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ✅ | ✅ |
-
-@shoaib_simulation_2021: Not met. Had to add some outputs and calculations (e.g. proportion of childbirth cases referred, standard deviation)
-
-@huang_optimizing_2019: Not met.
-It has a complicated output (standardised density of patient in queue) that I was never certain on whether I correctly calculated.
-Although it outputs the columns required to calculate it, due its complexity, I feel this was not met, as it feels like a whole new output in its own right (and not just something simple like a mean).
-
-@lim_staff_2020: Not met. The model script provided was only set up to provide results from days 7, 14 and 21. The figures require daily results, so I needed to modify the code to output that.
-
-@kim_modelling_2021: Not met. Had to write code to find aorta sizes of people with AAA-related deaths.
-
-@anagnostou_facs-charm_2022: Fully met. Although worth noting this only had one scenario/version of model and one output to reproduce.
-
-@johnson_cost_2021: Note met.
-It has an output that is in "per 1000" and, although it outputs the columns required to calculate this, I found it very tricky to work out which columns to use and how to transform them to get this output, and so feel this is not met (as feels like a seperate output, and not something simple like a mean, and as it felt so tricky to work out).
-
-@hernandez_optimal_2015: Fully met.
-
-@wood_value_2021: Fully met.
-
-**Reflections:**
-
-* Calculate and provide all the outputs required
-* Appreicate this can be a bit "ambiguous" (e.g.
-if its just plotting a mean or simple calculation, then didn't consider that here) (however, combined with other criteria, we do want them to provide code to calculate outputs, so we would want them to provide that anyway)
-* Tom: This is a headline.
-I suspect we can find supporting citations elsewhere from other fields.
-Its a reporting guideline thing too, but in natural language things can get very ambiguous still!
-Would be good to make that point as well I think.
-
-:::
-
-::: {.callout-tip icon=false collapse=true}
-
-## Include correct parameters in the script (even if just for one scenario)
-
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| 🟡 | ❌ | 🟡 | ✅ | ✅ | ✅ | ❌ | ✅ |
-
-@shoaib_simulation_2021: Partially met. Script is set with parameters for base configuration 1, with the exception of number of replications.
-
-@huang_optimizing_2019: Not met. The baseline model in the script did not match the baseline model (or any scenario) in the paper, so had to modify parameters.
-
-@lim_staff_2020: Partially met.
-The included parameters were corrected, but the baseline scenario included varying staff strength to 2, and the provided code only varied 4 and 6.
-I had to add some code that enabled it to run with staff strength 2 (as there were an error that occured if you tried to set that).
-
-@kim_modelling_2021: Fully met.
-
-@anagnostou_facs-charm_2022: Fully met.
-
-@johnson_cost_2021: Fully met. Base case parameters all correct.
-
-@hernandez_optimal_2015: Not met.
-As agreed with the author, this is likely the primary reason for the discrepancy in these results - they are very close, and we see similar patterns, but not reproduced.
-Unfortunately, several parameters were wrong, and although we changed those we spotted, we anticipate there could be others we hadn't spotted that might explain the remaining discrepancies.
-
-@wood_value_2021: Fully met.
-
-**Reflections:**
-
-* At least provide a script that can run the baseline model as in the paper (even if not providing the scenarios)
-* This can introduce difficulties - when some parameters are wrong, you rely on the paper to check which parameters are correct or not, but if the paper doesn't mention every single parameter (which is reasonably likely, as this includes those not varied by scenarios), then you aren't able to be sure that the model you are running is correct.
-* This can make a really big difference, and be likely cause of managing to reproduce everything v.s. nothing, if it impacts all aspects of the results.
-* Tom: I think this comes back to minimum verification as well. I think the "at least for one scenario" idea of yours is excellent.
-
-:::
-
-::: {.callout-tip icon=false collapse=true}
-
-## Provide all the required parameters
-
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | ✅ | ✅ | ✅ | ❌ | ✅ |
-
-@shoaib_simulation_2021: Some parameters that could not be calculated were not provided - ie. what consultation boundaries to use when mean length of doctor consultation was 2.5 minutes
-
-@huang_optimizing_2019: Not met.
-In this case, patient arrivals and resource numbers were listed in the paper, and there were several discprepancies between this and the provided code.
-However, for many of the model parameters like length of appointment, these were not mentioned in the paper, and so it was not possible to confirm whether or not those were correct.
-Hence, marked as not met, as the presence of discrepenancies for several other parameters puts these into doubt.
-
-@lim_staff_2020: Not met. For Figure 5, had to guess the value for `staff_per_shift`.
-
-@kim_modelling_2021: Fully met.
-
-@anagnostou_facs-charm_2022: Fully met.
-
-@johnson_cost_2021: Fully met. Could determine appropriate parameters for sensitivity analysis from figures in article.
-
-@hernandez_optimal_2015: Not met.
-The results have a large impact by the bounding set, but this was not mentioned in the paper or repository, and required me looking at the numbers in results and GitHub commit history to estimate the appropriate bounds to use.
-
-@wood_value_2021: Fully met.
-
-**Reflections:**
-
-* Provide all required parameters
-* Tom: Evidence to support STRESS-DES 3.3
-
-:::
-
-::: {.callout-tip icon=false collapse=true}
-
-## If not provided in the script, then *clearly* present all parameters in the paper
-
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | 🟡 | N/A | N/A | ✅ | 🟡 | N/A |
-
-@shoaib_simulation_2021: Not met.
-Although there was a scenario table, this did not include all the parameters I would need to change.
-It was more challenging to identify parameters that were only described in the body of the article.
-There were also some discrepancies in parameters between the main text of the article, and the tables and figures.
-Some scenarios were quite ambiguous/unclear from their description in the text, and I initially misunderstood the required parameters for the scenarios.
-
-@huang_optimizing_2019: Not met. As described above, paper didn't adequately describe all parameters.
-
-@lim_staff_2020: Partially met. Nearly all parameters are in the paper table, and others are described in the article. However, didn't provide information for the `staff_per_shift` for Figure 5.
-
-@kim_modelling_2021 and @anagnostou_facs-charm_2022: Not applicable. All provided.
-
-@johnson_cost_2021: Fully met. All parameters clearly in the two figures presenting the sensitivity analysis, and didn't have to look elsewhere beyond that.
-
-@hernandez_optimal_2015: Most parameters are relatively easily identified from the text or figure legends (though would be easier if provided in a table or similar).
-Parameter for bounding was not provided in paper.
-
-@wood_value_2021: Not applicable. All provided.
-
-**Reflections:**
-
-* Provide parameters in a table (including for each scenario), as it can be difficult/ambiguous to interpret them from the text, and hard to spot them too.
-    * Tom: The ambiguity of the natural language for scenarios was an important finding.
-* Be sure to mention every parameter that gets changed (e.g. for @lim_staff_2020, as there wasn't a default `staff_per_shift` across all scenarios, but not stated for the scenario, had to guess it).
-* Tom: Evidence to support STRESS-DES 3.3
-
-:::
-
-::: {.callout-tip icon=false collapse=true}
-
-## If will need to process parameters, provide required calculations
-
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ✅ | N/A | N/A | N/A | N/A | N/A | N/A |
-
-@shoaib_simulation_2021: Not met. It was unclear how to estimate inter-arrival time.
-
-@huang_optimizing_2019: Fully met.
-The calculations for inter-arrival times were provided in the code, and the inputs to the code were the number of arrivals, as reported in the paper, and so making it easy to compare those parameters and check if numbers were correct or not.
-
-@lim_staff_2020: Not applicable. The parameter not provided is not one that you would calculate.
-
-@kim_modelling_2021 and @anagnostou_facs-charm_2022: Not applicable. All provided.
-
-@johnson_cost_2021: Not applicable. No processing of parameters required.
-
-@hernandez_optimal_2015: Not applicable.
-
-@wood_value_2021: Not applicable. All provided.
-
-**Reflections:**
-
-* If you are going to be mentioning the "pre-processed" values at all, then its important to include the calculation (ideally in the code, as that is the clearest demonstration of exactly what you did)
-* Tom: This is a very good point for RAP.
-
-:::
-
-## Output format
-
 ::: {.callout-caution icon=false collapse=true}
@@
 
-## Understandable output tables
-
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ✅ | ✅ | ❌ | ✅ | ❌ | ✅ | ✅ |
-
-@shoaib_simulation_2021: Not met.
-There were two alternative results spreadsheets with some duplicate metrics but sometimes differing results between them, which made it a bit confusing to work out what to use.
-
-@huang_optimizing_2019, @lim_staff_2020, and @anagnostou_facs-charm_2022: Fully met. Didn't experience issues interpreting the contents of the output table/s.
-
-@kim_modelling_2021: Not met.
-It took me a little while to work out what surgery columns I needed, and to realise I needed to combine two of them.
-This required looking at what inputs genreated this, and referring to a input data dictionary.
-
-@johnson_cost_2021: Not met. I had mistakes and confusion figuring out which results tables I needed, which columns to use, and which scenarios to use from the tables.
-
-@hernandez_optimal_2015: Fully met. Straightforward with key information provided.
-
-@wood_value_2021: Fully met. I didn't need to work with the output tables, but from looking at them now, they make sense.
-
-**Reflections:**
-
-* Don't provide alternative results for the same metrics
-* Make it clear what each colum/category in the results table means, if it might not be immediately clear.
-* Make differences between seperate results tables clear.
-* Tom: In a RAP for simulation world we have a env + model + script that gets you to the exact results table you see in the paper and this isn't a problem (although more time consuiming to setup).
+## Avoid excessive output files
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| N/A | N/A | N/A | N/A | N/A | N/A | ❌ | N/A |
+
+For @hernandez_optimal_2015 the default behaviour of the script was to output lots of files from each round (so you could easily have 90, 100, 200+ files), which were then not used in analysis (as it just depended on an aggregate results file).
+Although these individual files might be useful during quality control, as a default behaviour of the script, it could easily make the repository quite busy/littered with files.
+
+* Tom reflected that this is more of a general housekeeping issue. He agrees and says its ok to do this, but perhaps they need a run mode that does not produce these verification files
 
@@
 
-## Avoid large file sizes if possible
+## Address large file sizes
 
@@
 
-## Seeds
+## Other recommendations
 
@@
 
-## Use seeds to control stochasticity
-
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | ✅ | ✅ | ✅ | ✅ | ✅ |
+## Be aware of potential system dependencies
+
+There can also be system dependencies, which will vary between systems, and may not be obvious if researchers already have these installed.
+We identified these when setting up the docker environments (which act like "fresh installs"):
+
+* @shoaib_simulation_2021, @lim_staff_2020, @anagnostou_facs-charm_2022 - no dependencies
+* @huang_optimizing_2019, @kim_modelling_2021, @johnson_cost_2021 and @wood_value_2021 - libcurl4-openssl-dev, libssl-dev, libxml2-dev, libglpk-dev, libicu-dev - as well as `tk` for Johnson et al.
+2021
+* @hernandez_optimal_2015 - wget, build-essential, libssl-dev, libffi-dev, libbz2-dev, libreadline-dev, libsqlite3-dev, zlib1g-dev, libncurses5-dev, libgdbm-de, libnss3-dev, tk-dev, liblzma-dev, libsqlite3-dev, lzma, ca-certificates, curl, git
+
+Although it would be unreasonable for authors to be aware of and list all system dependencies, given they may not be aware of them, this does show the benefit of creating something like docker in identifying them and making note of them within the docker files.
+
+This issue was specific to (a) R studies, and (b) the study with an unsupported version of Python that required building it from source in the docker file.
+
+:::
+
+::: {.callout-warning icon=false collapse=true}
+
+## Model is designed to be run programmatically (i.e. can run model with different parameters without needing to change the model code)
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ |
 
 @shoaib_simulation_2021: Not met.
-The lack of seeds wasn't actually a barrier to the reproduction though due to the replication number.
-I later add seeds so my results could be reproduced, and found that the ease of setting seeds with salabim was a greater facilitator to the work.
-I only had to change one or two lines of code to then get consistent results between runs (unlike other simulation software like SimPy where you have to consider the use of seeds by different sampling functions).
-Moreover, by default, salabim would have set a seed (although overridden by original authors to enable them to run replications).
+The model is set up as classes and run using a function.
+However, it is not designed to allow any variation in inputs.
+Everything uses default inputs, and it designed in such a way that - if you wish to vary model parameters - you need to directly change these in the script itself.
+
+@huang_optimizing_2019: Fully met. Model was set up as a function, with many of the required parameters already set as "changeable" inputs to that function.
+
+@lim_staff_2020: Fully met.
+The model is created from a series of functions and run with a for loop that iterates through different parameters.
+As such, the model is able to be run programmatically (within that for loop, which varied e.g.
+staff per shift and so on and re-ran the model).
+
+@kim_modelling_2021: Fully met. Each scenario is an R script which states different parameters and then calls functions to run model.
+
+@anagnostou_facs-charm_2022: Fully met. Change inputs in input `.csv` files.
+
+@johnson_cost_2021: Fully met. Creates a list of `input` which are then used by a `run()` function.
+
+@hernandez_optimal_2015: Fully met. Model created from classes, which accept some inputs and can run the model.
+
+@wood_value_2021: Fully met. Changes inputs to run all scenarios from a single `.R` file.
+
+**Reflections:**
+
+* Design model so that you can re-run it with different parameters without needing to make changes to the model code itself.
+    * This allows you to run multiple versions of the model with the same script.
+    * It also reduces the likelihood of missing errors (e.g. if miss changing an input parameter somewhere, or input the wrong parameters and don't realise).
+* This was an uncommon issue.
+* Note, this just refers to the basic set-up, with items below like hard coding parameters also being very important in this context.
+
+:::
+
+::: {.callout-warning icon=false collapse=true}
+
+## Use relative file paths
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ✅ | N/A | N/A | ✅ | ✅ | N/A | ✅ | ✅ |
+
+@shoaib_simulation_2021: Fully met. Just provides file path, so file is saved into current/run directory.
+
+@huang_optimizing_2019: Not applicable. All inputs defined within script. Outputs were not saved to file/s.
+
+@lim_staff_2020: Not applicable. All inputs defined within script. Outputs were not saved to file/s.
+
+@kim_modelling_2021: Fully met. Uses relative file paths for sourcing model and input parameters (gets current directory, then navigates from there).
+
+@anagnostou_facs-charm_2022: Fully met. Uses relative imports of local code files.
+
+@johnson_cost_2021: Not applicable.
+All inputs defined within script.
+Outputs are not specifically saved to a file (just that the .md and image files were automatically saved when the .Rmd file was knit).
+EpicR is package import.
+
+@hernandez_optimal_2015: Fully met. Creates folder in current working directory based on date/time to store results.
+
+@wood_value_2021: Fully met.
+Although I then changed things a bit as reorganised repository and prefer not to work with `setwd()`, these were set up in such a way that it would be really easy to correct file path, just by setting working directory at start of script.
+
+**Reflections:**
+
+* This was not an issue for any studies - but included to note this was a "facilitator", as would have needed to amend if they weren't (and Tom noted that this is a common problem that he runs into elsewhere).
+
+:::
+
+::: {.callout-tip icon=false collapse=true}
+
+## Provide all the required parameters
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ❌ | ❌ | ✅ | ✅ | ✅ | ❌ | ✅ |
+
+@shoaib_simulation_2021: Some parameters that could not be calculated were not provided - ie. what consultation boundaries to use when mean length of doctor consultation was 2.5 minutes
 
 @huang_optimizing_2019: Not met.
-It would have been beneficial to include seeds, as there was a fair amount of variability, so with seeds I could then I could be sure that my results do not differ from the original simply due to randomness.
-
-@lim_staff_2020: Not met.
-The results obtained looked very similar to the original article, with minimal differences that I felt to be within the expected variation from the model stochasticity.
-However, if seeds had been present, we would have been able to say with certainty.
-I did not feel I needed to add seeds during the reproduction to get the same results.
-
-@kim_modelling_2021: Fully met. Included a seed, although I don't get identical results as I had to reduce number of people in simulation.
+In this case, patient arrivals and resource numbers were listed in the paper, and there were several discprepancies between this and the provided code.
+However, for many of the model parameters like length of appointment, these were not mentioned in the paper, and so it was not possible to confirm whether or not those were correct.
+Hence, marked as not met, as the presence of discrepenancies for several other parameters puts these into doubt.
+
+@lim_staff_2020: Not met. For Figure 5, had to guess the value for `staff_per_shift`.
+
+@kim_modelling_2021: Fully met.
 
 @anagnostou_facs-charm_2022: Fully met.
-The authors included a random seed so the results I got were identical to the original (so no need for any subjectivity in deciding whether its similar enough, as I could perfectly reproduce).
-
-@johnson_cost_2021: Fully met. At start of script, authors `set.seed(333)`.
-
-@hernandez_optimal_2015: Fully met. This ensured consistent results between runs of the script, which was really helpful.
-
-@wood_value_2021: Fully met. Sets seed based on replication number.
-
-**Reflections:**
-
-* Depending on your model and the outputs/type of output you are looking at, the lack of seeds can have varying impacts on the appearance of your results, and can make the subjective judgement of whether results are consistent harder (if discrepancies could be attributed to not having consistent seeds or not).
-* It can be really quite simple to include seeds.
-* Over half of the studies did include seed control in their code.
-* Tom: There seems little argument against doing this.
-worth noting that commerical software does this for you and possibly explains why authors didn't do this themselves if that was their background (lack of knowledge?).
-* Tom: Note simpy is independent of any sampling mechanism.
-We could just use python's random module and set a single seed if needed (although you lose CRN) and we can setup our models so that we only need to set a single seed.
-* Tom: A key part of STARS 2.0 for reproducibility
-
-:::
-
-## Code to produce article results
-
-This is a common problem across all item types, and a key part of STARS 2.0 for reproducibility.
-
-::: {.callout-warning icon=false collapse=true}
-
-## Provide code to process results into tables
-
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | N/A | 🟡 | ❌ | N/A | ❌ | ❌ | ✅ |
+
+@johnson_cost_2021: Fully met. Could determine appropriate parameters for sensitivity analysis from figures in article.
+
+@hernandez_optimal_2015: Not met.
+The results have a large impact by the bounding set, but this was not mentioned in the paper or repository, and required me looking at the numbers in results and GitHub commit history to estimate the appropriate bounds to use.
+
+@wood_value_2021: Fully met.
+
+**Reflections:**
+
+* Provide all required parameters
+* Tom: Evidence to support STRESS-DES 3.3
+
+:::
+
+::: {.callout-tip icon=false collapse=true}
+
+## If not provided in the script, then *clearly* present all parameters in the paper
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ❌ | 🟡 | N/A | N/A | ✅ | 🟡 | N/A |
 
 @shoaib_simulation_2021: Not met.
-
-@huang_optimizing_2019: Not applicable. No tables in scope.
-
-@lim_staff_2020: Partially met.
-It outputs the results in a similar structure to the paper (like a section of a table).
-However, it doesn't have the full code to produce a table outright, for any of the tables, so additional processing still required.
-
-@kim_modelling_2021: Not met.
-Had to write code to generate tables, which included correctly implementing calculation of excess e.g.
-deaths, scaling to population size, and identify which columns provide the operation outcomes.
-
-@anagnostou_facs-charm_2022: Not applicable. No tables in scope.
-
-@johnson_cost_2021: Not met. Had to write code to generate tables, which took me a while as I got confused over thinks like which tables / columns / scenarios to use.
-
-@hernandez_optimal_2015: Not met.
-
-@wood_value_2021: Fully met.
-
-**Reflections:**
-
-* It can take a bit of time to do this processing, and it can be tricky/confusing to do correctly, so very handy for it to be provided.
-* Common issue.
-
-:::
-
-::: {.callout-warning icon=false collapse=true}
-
-## Provide code to process results into figures
-
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | ❌ | ❌ | 🟡 | 🟡 | ✅ |
-
-@shoaib_simulation_2021: Not met.
-
-@huang_optimizing_2019: Not met.
-Had to write code from scratch.
-For one of the figures, it would have been handy if informed that plot was produced by a simmer function (as didn’t initially realise this).
-It also took a bit of time for me to work out how to transform the figure axes as this was not mentioned in the paper (and no code was provided for these).
-It was also unclear and a bit tricky to work out how to standardise the density in the figures (since it is only described in the text and no formula/calculations are provided there or in the code).
-
-@lim_staff_2020, @kim_modelling_2021 and @anagnostou_facs-charm_2022: Not met. However, the simplicity and repetition of the figures was handy.
-
-@johnson_cost_2021: Partially met.
-For Figure 3, most of the required code for the figure was provided, which was super helpful.
-However, this wasn't complete, and for all others figures, I had to start from scratch writing the code.
-
-@hernandez_optimal_2015: Partially met.
-Provides a few example `ggplot`s, but these are not all the plots, nor exactly matching article, nor including any of the pre-processing required before the plots, and so could only serve as a starting point (though that was still really handy).
-
-@wood_value_2021: Fully met. Figures match article, with one minor exception that I had to add smoothing to the lines on one of the figures.
-
-**Reflections:**
-
-* It can take a bit of time to do this processing, particularly if the figure involves any transformations (and less so if the figure is simple), so very handy for it to be provided.
-* Also, handy if the full code can be provided for all figures (although partial code is more helpful than none at all).
-* Common issue.
-
-:::
-
-::: {.callout-warning icon=false collapse=true}
-
-## Provide code to calculate in-text results
-
-By "in-text results", I am referred to results that are mentioned in the text but not included in/cannot be deduced from any of the tables or figures.
-
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | N/A | ❌ | N/A | N/A | N/A | N/A |
-
-@shoaib_simulation_2021, @huang_optimizing_2019, @kim_modelling_2021: Not met.
-
-@lim_staff_2020, @anagnostou_facs-charm_2022, @johnson_cost_2021, @hernandez_optimal_2015, @wood_value_2021: Not applicable (no in-text results).
-
-**Reflections:**
-
-* Provide code to calculate in-text results
-* Universal issue, for those with in-text results not otherwise captured in tables and figures
-
-:::
-
-## Documentation
-
-::: {.callout-important icon=false collapse=true}
-
-## Include instructions on how to run the model/script
-
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ❌ | ❌ | ❌ | 🟡 | ✅ | ✅ | ❌ | ❌ |
-
-@shoaib_simulation_2021: Not met. No instructions, although is just a single script that you run.
-
-@huang_optimizing_2019: Not met. Not provided in runnable form but, regardless, no instructions for running it as it is provided (as a web application - i.e. no info on how to get that running).
-
-@lim_staff_2020: Not met. No instructions, although is just a single script that you run.
-
-@kim_modelling_2021: Partially met. README tells you which folder has the scripts you need, although nothing further. Although all you need to do is run them.
-
-@anagnostou_facs-charm_2022: Fully met. Clear README with instructions on how to run the model was really helpful.
-
-@johnson_cost_2021: Fully met. README has mini description of model and clear instructions on how to install and run the model.
-
-@hernandez_optimal_2015: Not met.
-
-@wood_value_2021: Not met. No instructions, although it was fairly self explanatory (single script `master.R` to run, then processing scripts named after items in article e.g. `fig7.R`).
-
-**Reflections:**
-
-* Even if as simple as running a script, include instructions on how to do so
-* In simpler projects (e.g. single script), this can be less of a problem.
-* Common issue
-* Tom: Evidence for STARS essential component of minimum documentation.
-
-:::
-
-## Other
+Although there was a scenario table, this did not include all the parameters I would need to change.
+It was more challenging to identify parameters that were only described in the body of the article.
+There were also some discrepancies in parameters between the main text of the article, and the tables and figures.
+Some scenarios were quite ambiguous/unclear from their description in the text, and I initially misunderstood the required parameters for the scenarios.
+
+@huang_optimizing_2019: Not met. As described above, paper didn't adequately describe all parameters.
+
+@lim_staff_2020: Partially met. Nearly all parameters are in the paper table, and others are described in the article. However, didn't provide information for the `staff_per_shift` for Figure 5.
+
+@kim_modelling_2021 and @anagnostou_facs-charm_2022: Not applicable. All provided.
+
+@johnson_cost_2021: Fully met. All parameters clearly in the two figures presenting the sensitivity analysis, and didn't have to look elsewhere beyond that.
+
+@hernandez_optimal_2015: Most parameters are relatively easily identified from the text or figure legends (though would be easier if provided in a table or similar).
+Parameter for bounding was not provided in paper.
+
+@wood_value_2021: Not applicable. All provided.
+
+**Reflections:**
+
+* Provide parameters in a table (including for each scenario), as it can be difficult/ambiguous to interpret them from the text, and hard to spot them too.
+    * Tom: The ambiguity of the natural language for scenarios was an important finding.
+* Be sure to mention every parameter that gets changed (e.g. for @lim_staff_2020, as there wasn't a default `staff_per_shift` across all scenarios, but not stated for the scenario, had to guess it).
+* Tom: Evidence to support STRESS-DES 3.3
+
+:::
+
+::: {.callout-tip icon=false collapse=true}
+
+## If will need to process parameters, provide required calculations
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ✅ | N/A | N/A | N/A | N/A | N/A | N/A |
+
+@shoaib_simulation_2021: Not met. It was unclear how to estimate inter-arrival time.
+
+@huang_optimizing_2019: Fully met.
+The calculations for inter-arrival times were provided in the code, and the inputs to the code were the number of arrivals, as reported in the paper, and so making it easy to compare those parameters and check if numbers were correct or not.
+
+@lim_staff_2020: Not applicable. The parameter not provided is not one that you would calculate.
+
+@kim_modelling_2021 and @anagnostou_facs-charm_2022: Not applicable. All provided.
+
+@johnson_cost_2021: Not applicable. No processing of parameters required.
+
+@hernandez_optimal_2015: Not applicable.
+
+@wood_value_2021: Not applicable. All provided.
+
+**Reflections:**
+
+* If you are going to be mentioning the "pre-processed" values at all, then its important to include the calculation (ideally in the code, as that is the clearest demonstration of exactly what you did)
+* Tom: This is a very good point for RAP.
+
+:::
 
@@
 
-**Excessive number of files**.
-For @hernandez_optimal_2015 the default behaviour of the script was to output lots of files from each round (so you could easily have 90, 100, 200+ files), which were then not used in analysis (as it just depended on an aggregate results file).
-Although these individual files might be useful during quality control, as a default behaviour of the script, it could easily make the repository quite busy/littered with files.
-
-* Tom reflected that this is more of a general housekeeping issue. He agrees and says its ok to do this, but perhaps they need a run mode that does not produce these verification files
-
 **Classes**. @hernandez_optimal_2015: Structured code into classes, which was nice to work with/amend.
 
-**Version history and releases**.
-@johnson_cost_2021 had commits to their GitHub repository after the publication date.
-It wasn't clear which version aligned with the publication.
-However, the most recent commits add clear README instructions to the repository.
-We decided to use the latest version of the repository, but it would have beneficial to have releases/versions/a change log that would help to outline the commit history in relation to the publication and any subsequent changes.
-
 ## References

### 2024-12-10 pages/reflections.qmd
docs(reflections): redid summary graph and corrected callout colours

@@
 
+It **excludes** the "Other section".
+It also excludes a few criteria which weren't felt particularly relevant/suitable to mark as met or not.
+These were "link publication to a specific version of the code", "optimise model run time" and "avoid large file sizes".
+
 ```{python}
@@
 criteria_dict = {
-  'List packages': [2, 3, 3, 0],
-  'Provide versions': [0, 6, 2, 0],
-  'Model in "runnable" format': [7, 0, 1, 0],
-  'Can run some programmatically': [7, 0, 1, 0],
-  '''Don't hard code scenario param.''': [3, 2, 2, 1],
-  'Relative file paths': [5, 0, 0, 3],
-  'Avoid duplication': [5, 0, 3, 0],
-  'Sufficient comments': [1, 3, 4, 0],
-  'If slow, state run time': [2, 2, 3, 1],
-  'Provide scenario code': [1, 1, 5, 1],
-  'Provide all required outputs': [3, 0, 5, 0],
-  'Include correct parameters': [4, 2, 2, 0],
-  'Provide all required parameters': [4, 0, 4, 0],
-  'If not, clearly state in paper': [1, 2, 2, 3],
-  'If process param., provide calc.': [1, 0, 1, 6],
-  'Save output to file': [4, 0, 4, 0],
-  'Understandable output tables': [5, 0, 3, 0],
-  'Use seeds': [5, 0, 3, 0],
-  'Code to make tables': [1, 1, 4, 2],
-  'Code to make figures': [1, 2, 5, 0],
-  'Code to process in-text results': [0, 0, 3, 5],
-  'Run instructions': [2, 1, 5, 0],
+    'Share code with an open licence': [4, 0, 4, 0],
+    'List required packages and versions': [0, 6, 2, 0],
+    'Provide code for all scenarios<br>and sensitivity analyses': [1, 1, 5, 1],
+    'Ensure model parameters are correct': [4, 2, 2, 0],
+    'Control randomness': [5, 0, 3, 0],
+    'Include code to calculate all<br>required model outputs': [3, 0, 5, 0],
+    'Include code to generate the tables,<br>figures and other reported results': [1, 3, 4, 0],
+    'Separate model code from applications': [1, 0, 1, 6],
+    'Avoid hard-coded parameters': [3, 2, 2, 1],
+    'Minimise code duplication': [5, 0, 3, 0],
+    'Comment sufficiently': [1, 3, 4, 0],
+    'Ensure clarity and consistency<br>in the model results tables': [5, 0, 3, 0],
+    'Include run instructions': [2, 1, 5, 0],
+    'State run times and<br>machine specifications': [0, 5, 3, 0],
+    'Save output to a file': [4, 0, 4, 0],
+    'Avoid excessive output files': [7, 0, 1, 0]
 }
@@
 
+![](../images/reproduction_wheel.png)
+
 ### Set-up
@@
 
-| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
-| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| | | | | | ❌ | | |
-
-<!--TODO: Check if any other studies had commits after publication-->
+Whether or not they did it:
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
+
+Then, considering how "applicable" it feels... although you could argue those where I have marked "non-applicable" would become applicable with the addition of any new commits to the repository.
+
+| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
+| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
+| N/A | N/A | N/A | ❌ | N/A | ❌ | N/A | N/A |
+
+@shoaib_simulation_2021, @hernandez_optimal_2015: N/A.
+Not met but not an issue as last commit (with exception of any related to licence from our communication) is prior to publication, so marked as not applicable.
+
+@huang_optimizing_2019, @lim_staff_2020, @anagnostou_facs-charm_2022, @wood_value_2021: N/A. Only 1 commit (excluding repo creation), or only commits on one day.
+
+@kim_modelling_2021: Not met. Had commits to their GitHub repository after the publication date - though these largely appear related to a different model in the same repository, or for a fix.
 
@@
 
-### Packages and versions
+**Packages and versions**
 
@@
 
-### Packages
+**Packages**
 
@@
 
-### Versions
+**Versions**
 
@@
 
-::: {.callout-note icon=false collapse=true}
+::: {.callout-tip icon=false collapse=true}
 
@@
 
-::: {.callout-tip icon=false collapse=true}
+::: {.callout-warning icon=false collapse=true}
 
@@
 
-### Summary
+**Summary**
 
@@
 
-### Provide code to process results into tables
+**Provide code to process results into tables**
 
@@
 
-### Provide code to process results into figures
+**Provide code to process results into figures**
 
@@
 
-### Provide code to calculate in-text results
+**Provide code to calculate in-text results**
 
@@
 
+![](../images/troubleshooting_wheel.png)
+
 ### Design
 
-::: {.callout-warning icon=false collapse=true}
+::: {.callout-caution icon=false collapse=true}
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| ✅ | ❌ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ |
-
-@shoaib_simulation_2021: Fully met. Provided as a single `.py` file which ran model with function `main()`.
-
-@huang_optimizing_2019: Not met.
+| N/A | ❌ | N/A | N/A | ✅ | N/A | N/A | N/A |
+
+For studies where this is relevant (i.e. with applications):
+
+* @huang_optimizing_2019: Not met.
 The model code was provided within the code for a web application, but the paper was not focused on this application, and instead on specific model scenarios.
 I had to extract the model code and transform it into a format that was "runnable" as an R script/notebook.
-
-@lim_staff_2020: Fully met. Provided as a single `.py` file which ran the model with a for loop.
-
-@kim_modelling_2021: Fully met. Has seperate `.R` scripts for each scenario which ran the model by calling functions from elsewhere in repository.
-
-@anagnostou_facs-charm_2022: Fully met. Can run model from command line.
-
-@johnson_cost_2021: Fully met. Model provided as a package (which is an R interface for the C++ model).
-
-@hernandez_optimal_2015: Fully met. The model (python code) can be run from `main.py`.
-
-@wood_value_2021: Fully met. Provided as a single `.R` file which ran the model with a for loop.
+* @anagnostou_charm_2022: Fully met. Code for web app in a seperate repository to model code.
+
+For other studies, regarding whether the model code was in a "runnable" format and not embedded within anything else...
+
+* @shoaib_simulation_2021: Provided as a single `.py` file which ran model with function `main()`.
+* @lim_staff_2020: Provided as a single `.py` file which ran the model with a for loop.
+* @kim_modelling_2021: Has seperate `.R` scripts for each scenario which ran the model by calling functions from elsewhere in repository.
+* @johnson_cost_2021: Model provided as a package (which is an R interface for the C++ model).
+* @hernandez_optimal_2015: The model (python code) can be run from `main.py`.
+* @wood_value_2021: Provided as a single `.R` file which ran the model with a for loop.
 
@@
 
-::: {.callout-warning icon=false collapse=true}
+::: {.callout-caution icon=false collapse=true}
 
@@
 
-::: {.callout-caution icon=false collapse=true}
+::: {.callout-important icon=false collapse=true}
 
@@
 
+**Summary (whether stated both)**
+
 | @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
@@
 
-### State run time
+**State run time**
 
@@
 
-### State machine specification
+**State machine specification**
 
@@
 
-### Computationally expensive models
+**Computationally expensive models**
 
@@
 
-::: {.callout-important icon=false collapse=true}
+::: {.callout-note icon=false collapse=true}
 
@@
 
-::: {.callout-caution icon=false collapse=true}
+::: {.callout-note icon=false collapse=true}
 
@@
 | :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
-| N/A | N/A | N/A | N/A | N/A | N/A | ❌ | N/A |
+| ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ❌ | ✅ |
 
@@
 
-::: {.callout-warning icon=false collapse=true}
+::: {.callout-tip icon=false collapse=true}
 

### 2025-01-07 pages/reflections.qmd
docs(reflections): add version link to summary chart, and add counts of applicable criteria to wheel figures

@@
 It also excludes a few criteria which weren't felt particularly relevant/suitable to mark as met or not.
-These were "link publication to a specific version of the code", "optimise model run time" and "avoid large file sizes".
+These were "optimise model run time" and "avoid large file sizes".
 
@@
     'Share code with an open licence': [4, 0, 4, 0],
+    'Link publication to a specific<br>version of the code': [0, 0, 2, 6],
     'List required packages and versions': [0, 6, 2, 0],
